### 2016-01-11 sections/data0.0.tex
Seprating sections

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%DATA
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

\section{DATA}
Our sample contains photometric and spectroscopic data of M31 and M101, as well as their measured properties such as SFR, stellar mass, dust luminosity, metallicity, and gas mass.    
%M31 data: observed ones;
    \subsection{M31 data}
     Our M31 data sample contains data from ten regions from outer part of the disk . Data for PAH are for M31 spectroscopy data for our 10 regions came from observations using {\it Spitzer}/Infrared Spectrograph \citep{Dim15}. \cite{Dim15}

%M31 data: measured ones;
%M101 data: observed ones;

### 2016-01-11 sections/intro0.0.tex
Seprating sections

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Intro
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{Introduction}
% ideas about science of paper will add the them at the end

% maybe a little bit about PAH and other properties of nearby galaxies

% data mining in general?ANN?

### 2016-01-11 sections/method0.0.tex
Seprating sections

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Method
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

\section{METHOD}
 \subsection{Self Organizing Maps}

 Kohonen Self organizing map (or self organizing map, SOM) is an unsupervised neural network for mapping and visualizing a complex and non linear high dimension data introduced by \citep{Kohonen82}. 
 SOM is a clustering method which reduces the dimension of data to lower dimensions usually 1 or 2D while preserving topological features of the original data.
 Results of SOM contains nodes (usually hexagonal ones) that arranged in 1D or 2D arrays.
 Each nodes may contain one or more samples from input data and distance between nodes represents similarity or dissimilarity of underlying samples. 
 In the way that similar data are closer together in the array and further nodes go, they become more different.
 %Sahar_self_notes: maybe "some" is better instead of one or more
 Also, a weight vector ``$w$" with same dimension of the input data associates with each node.
 Thus the SOM is a technique that shows a simple geometry relationship of a non-linear high dimension data on a map \citep{Kohonen98}. 
   \subsubsection{Algorithm of SOM}

 Having a data which contains vectors, $V \in \Re^n$. Therefore, each node contains a weight vectors $w\in \Re^n$. The process of creating SOM, happens over series of $N$ iterations. For each iteration :

  1) assigning a random weight vector

  2) from the data a vector will be choose randomly and present to a network

  3) calculating the Euclidean distance for each node j as  $D_j^2= \sum_{i=0}^{i=n} (V_i - w_i)^2 $ to find the smallest value for "$D_{j_{min}}$". The winner node is calling Best Matching Unit (BMU)

  4) Compute the radius of the neighbourhood of the BMU to find nodes that all are within the neighbourhood distance of the BMU. The weight vectors of these nodes will be affected in the next steps. This value is arbitrary but initially can be chosen to be half of the size of the SOM and then it decades exponentially over the time:
  %Sahar_self_note: or Whatever matlab prefers
   \begin{equation}
   r(t) = r^0_{BMU}e^{(-t/\tau)}
   \end{equation}
   where $\tau$ is a decay constant and usually set to be the same as number of iterations, $N$.

   5) The weight vector of every nodes within the neighbourhood will be adjusted as:
   \begin{equation}
   w(t+1)=w(t)+L(t) \times(v(t)-w(t))
   \end{equation}
   where $L(t) = e^{(-t/\tau}$ is the learning factor which decrease with time.

   6) Repeat these steps for $N$ times.

 \subsection{Test Model}
 Before we start using SOM on our data, we apply this model in a test sample. Our test sample contains SED of 142 galaxies between redshift 0.5 $ \leq$ Z $\leq $ 1, which their physical information such as age, stellar mass and specific star formation are available. \cite{Hossein12} used trained network to classified their spectrum based on SED models from \cite{Kinney96} and \cite{Coleman80}.

 We create various SOM maps with different numbers of neurons and neighbourhood

### 2016-01-11 main text/draft0.0.tex
Separating sections

\documentclass[useAMS,usenatbib]{mn2e}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{natbib}
\bibliographystyle{mn2e}
\usepackage{times}
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{color,soul}
\usepackage{import}

\newcommand \kpc        {\,{\rm kpc}}
\newcommand \sigmagas    {$\Sigma_{\rm \bld {gas }} $\ }
\newcommand \sigmatotalgas {$\Sigma_{\rm \bld {total\, gas }} $\ }
\newcommand \eqsigmagas    {\Sigma_{\rm \bld {gas }}}
\newcommand \sigmasfr     {$\Sigma_{\rm \bld {SFR }} $\ }
\newcommand \eqsigmasfr     {\Sigma_{\rm \bld {SFR }}}
\newcommand \sigmastar    {$\Sigma_{\rm \bld {star }} $\ }
\newcommand \eqsigmastar    {\Sigma_{\rm \bld {star }}}
\newcommand \halpha    {H$\alpha $\ }
\newcommand \um    {$\mu$m\ }
\newcommand \mice {$\mu$m}
\newcommand \nprime {N$^\prime$}
\newcommand \eqnprime {N^\prime}
\newcommand \Spitzer {{\it Spitzer }}
\newcommand \Galex {GALEX }
\newcommand \Herschel {{\it Herschel }}
\newcommand \aaj {A\&A}
\newcommand \aarv {A\&ARv}%: Astronomy and Astrophysics Review (the)
\newcommand \aas{A\&AS}%: Astronomy and Astrophysics Supplement Series
\newcommand \afz {Afz}%: Astrofizika
\newcommand \aj {AJ}%: Astronomical Journal (the)
\newcommand \apss {Ap\&SS}%: Astrophysics and Space Science
\newcommand \apj {ApJ}
\newcommand \apjs {ApJS}%: Astrophysical Journal Supplement Series (the)
\newcommand \araa {ARA\&A} %: Annual Review of Astronomy and Astrophysics
\newcommand \asp {ASP Conf. Ser.}%: Astronomy Society of the Pacific Conference Series
\newcommand \azh {Azh}%: Astronomicheskij Zhurnal
\newcommand \baas {BAAS}%: Bulletin of the American Astronomical Society
\newcommand \mem {Mem. RAS}%: Memoirs of the Royal Astronomical Society
\newcommand \mnassa {MNASSA}%: Monthly Notes of the Astronomical Society of Southern Africa
\newcommand \mnras {MNRAS} %: Monthly Notices of the Royal Astronomical Society
%\newcommand {Nature}%(do not abbreviate)
\newcommand \pasj {PASJ}%: Publications of the Astronomical Society of Japan
\newcommand \pasp {PASP}%: Publications of the Astronomical Society of the Pacific
\newcommand \qjras {QJRAS}%: Quarterly Journal of the Royal Astronomical Society
\newcommand \mex {Rev. Mex. Astron. Astrofis.}%: Revista Mexicana de Astronomia y Astrofisica
%\newcommand {Science }%}%(do not abbreviate)
\newcommand \sva {SvA}%: Soviet Astronomy
\newcommand \aap {APP} %:American Academy of Pediatrics
\newcommand \apjl {ApJL} %:The Astrophysical Journal Letters

\begin{document}
% TITLE

\title{Data Mining in Nearby Galaxies}
\author{rahmani.sahar }
\date{\today}
\author[S. Rahmani, et. al.]{S.~Rahmani$^{1}$\thanks{E-mail:
srahma49@uwo.ca}, H.~Teimoorinia$^{2}$, E.~Peeters$^{1}$, P.~Barmby$^{1}$\\
$^{1}$Department of Physics $\&$ Astronomy, Western University, London, ON N6A 3K7, Canada\\
$^{2}$Department of Physics $\&$ Astronomy, University of Victoria, Finnerty Road, Victoria, British Columbia, V8P 1A1, Canada}
\maketitle

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%abstract
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

\begin{abstract} 
Here is the abstract.
%This is just first abstract for this paper!
%M31 was targeted by many probes, and there are variety of data available for this particular galaxy.
%M31 was mapped from X-ray to 21 cm emission. Also, spectroscopy data of different regions of M31 is available in various bands. 
%The vast availability of data for this galaxy makes it a suitable target for data mining and ﬁnding new patterns in this galaxy.
%In this project we are studying 10 regions in M31 from the bulge of the galaxy to the star forming ring. Using self organizing map (SOM) method, we classiﬁed these regions in different groups, based on total star formation rate, total stellar mass, total infrared emission and 3.6 \mice, 4.5 \mice, 5.8 \mice, 8 \mice, 24 \mice, 70 \um and 160 \mice, 2.6 mm, and 21 cm luminosity from the photometry data of the regions, and flux of 5.7 \mice, 6.2 \mice, 7.4 \mice, 7.6 \mice, 7.9\mice, 8.3 \mice, 8.6 \mice, 10.7 \mice, 11.23 \mice, 12.00 \mice, 12.62 \mice, 12.69 \mice, 14.0 \mice, 16.45 \mice, 17.04 \mice, PAH lines, [ArIII], [SIII], [SIV], [NeII], and [NeIII] as well as metallicity of these regions obtained from the spectroscopy data. 
%We divided these regions from 2 to 6 different classes, and for each class we are going to interpret results and check whether these classiﬁcations have a physical meaning or they are just statistically relate to each other. 
%As a result, we can predict some properties of regions in other galaxies by having only few data.

\end{abstract}
\begin{keywords} 
galaxies: individual: M31, galaxies: spiral, galaxies: star formation, galaxies: stellar content, galaxies: ISM, stars: formation, ISM: clouds, methods: observational, methods: statistical, data mining, methods:data analysis, techniques: image processing 
\end{keywords}
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Intro
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\import{../sections/}{intro0.0.tex}
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%DATA
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

\import{../sections/}{data0.0.tex}

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Method
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

\import{../sections/}{method0.0.tex}

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Results
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\import{../sections/}{results0.0.tex}
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Discussion
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

\import{../sections/}{diss0.0.tex}

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Summery
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{SUMMARY}

\section*{ACKNOWLEDGMENTS}
S.R and P.B acknowledge research support from the Natural Sciences and Engineering Research Council of Canada and from the Academic Development Fund of the University of Western Ontario.
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%biblio
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\bibliographystyle{mnras}
\bibliography{ref_mining}

\end{document}

### 2016-01-14 sections/method0.0.tex
minor editing

@@
 
- Kohonen Self organizing map (or self organizing map, SOM) is an unsupervised neural network for mapping and visualizing a complex and non linear high dimension data introduced by \citep{Kohonen82}. 
+ Kohonen Self organizing map (or self organizing map, SOM) is an unsupervised neural network for mapping and visualizing a complex and non linear high dimension data introduced by~\citep{Kohonen82}. 
+ The SOM is a technique that shows a simple geometry relationship of a non-linear high dimension data on a map \citep{Kohonen98}.
  SOM is a clustering method which reduces the dimension of data to lower dimensions usually 1 or 2D while preserving topological features of the original data.
  Results of SOM contains nodes (usually hexagonal ones) that arranged in 1D or 2D arrays.
+
  Each nodes may contain one or more samples from input data and distance between nodes represents similarity or dissimilarity of underlying samples. 
- In the way that similar data are closer together in the array and further nodes go, they become more different.
+ In the way that similar data are closer together in the array and the further nodes go from each other, the more dissimilarity appears between their samples.
  %Sahar_self_notes: maybe "some" is better instead of one or more
- Also, a weight vector ``$w$" with same dimension of the input data associates with each node.
- Thus the SOM is a technique that shows a simple geometry relationship of a non-linear high dimension data on a map \citep{Kohonen98}. 
+ Moreover,a weight vector ``\boldit{W}" with same dimension of the input data associates with each node which will be change during the process and has a key factor in a position of nodes in the map.
+
  \subsubsection{Algorithm of SOM}
 
- Having a data which contains vectors, $V \in \Re^n$.
-Therefore, each node contains a weight vectors $w\in \Re^n$.
+     Assuming we have a data which contains vectors, \boldit{V} $\in \Re^n$.
+Each nodes must contain a weight vector \boldit{W} $\in \Re^n$; this weight vector will be assigned randomly to each node in the begging of the procedure and might change in each iteration.
 The process of creating SOM, happens over series of $N$ iterations.
-For each iteration :
+The number of iteration is provided by user.
+We test our code by varying the number of iterations and find $N = 100$ is optimized for our sample.
+For each iteration:
 
@@
 
-  4) Compute the radius of the neighbourhood of the BMU to find nodes that all are within the neighbourhood distance of the BMU.
+  4) Compute the radius of the neighbourhood of the BMU to find nodes that all are within the neighbourhood distance of the BMU (maximum number of neighbourhood is given by the user).
 The weight vectors of these nodes will be affected in the next steps.
@@
 
+In order to create SOM, we used {\tiny MATLAB} neural network toolbox~\citep{sommatlab}.
+
  \subsection{Test Model}

### 2016-01-15 sections/method0.0.tex
Finishing algorithm section

@@
 \section{METHOD}
+\label{sec: method}
  \subsection{Self Organizing Maps}
+ \label{sec: som}
 
@@
  The SOM is a technique that shows a simple geometry relationship of a non-linear high dimension data on a map \citep{Kohonen98}.
- SOM is a clustering method which reduces the dimension of data to lower dimensions usually 1 or 2D while preserving topological features of the original data.
+ The SOM is a clustering method which reduces the dimension of data to lower dimensions usually 1 or 2D while preserving topological features of the original data.
  Results of SOM contains nodes (usually hexagonal ones) that arranged in 1D or 2D arrays.
@@
  \subsubsection{Algorithm of SOM} 
+ \label{sec: algorithm}
 
-     Assuming we have a data which contains vectors, \boldit{V} $\in \Re^n$.
-Each nodes must contain a weight vector \boldit{W} $\in \Re^n$; this weight vector will be assigned randomly to each node in the begging of the procedure and might change in each iteration.
+     Assuming we have a data set which contains vectors, \boldit{V} $\in \Re^n$ and we want to map them on S1 by S2 map. 
+     We start by creating S1 $\times$ S2 empty neurons. 
+     The initial arrangement of these neurons depends on a map's topology provided by user.
+     Since the topology of the map does not have any affect on the final result, we chose hexagonal topology which is the default topology for SOMs.
+     Then, we assign a random weight vector \boldit{W} $\in \Re^n$ to each node.
      The process of creating SOM, happens over series of $N$ iterations. 
-The number of iteration is provided by user.
-We test our code by varying the number of iterations and find $N = 100$ is optimized for our sample.
-For each iteration:
-
-  1) assigning a random weight vector
-
-  2) from the data a vector will be choose randomly and present to a network
-
-  3) calculating the Euclidean distance for each node j as  $D_j^2= \sum_{i=0}^{i=n} (V_i - w_i)^2 $ to find the smallest value for "$D_{j_{min}}$". The winner node is calling Best Matching Unit (BMU)
-
-  4) Compute the radius of the neighbourhood of the BMU to find nodes that all are within the neighbourhood distance of the BMU (maximum number of neighbourhood is given by the user).
+     During each iteration the weight vectors might change according to the Kohonen learning rule (equation~\ref{equ: weight adj}). 
+     We test our code by varying the number of iterations and find $N = 100$ is optimized for our sample. For each iteration:
+     \begin{enumerate}
+     \item Choose a random vector from our data set.
+     \item Calculate the euclidean distance for each node j as  $D_j^2= \sum_{i=0}^{i=n} (V_i - W_i)^2$, and find a neuron with ``$D_{j_{min}}$".
+This neuron is the winner node and is calling Best Matching Unit (BMU).
+     \item  Compute the radius of the neighbourhood of the BMU to find nodes within this radius.
 The weight vectors of these nodes will be affected in the next steps.
-This value is arbitrary but initially can be chosen to be half of the size of the SOM and then it decades exponentially over the time:
-  %Sahar_self_note: or Whatever matlab prefers
+This value is arbitrary but initially can be chosen to be half of the size of the SOM and then it decades exponentially over each iteration:
    \begin{equation}
-   r(t) = r^0_{BMU}e^{(-t/\tau)}
+   r^t_{BMU} = r^0_{BMU}e^{(-t/\tau)}
    \end{equation}
    where $\tau$ is a decay constant and usually set to be the same as number of iterations, $N$.
-
-   5) The weight vector of every nodes within the neighbourhood will be adjusted as:
+$r^0_{BMU}$ and $r^t_{BMU}$ is the radius of the neighbourhood at 0th and $t$th iteration, respectively.
+   \item Change the weight vectors of the BMU and all the nodes within r(t) as:
    \begin{equation}
-   w(t+1)=w(t)+L(t) \times(v(t)-w(t))
+   \label{equ: weight adj}
+   w(t+1)=w(t)+L(t) \times R(t) \times(v(t)-w(t))
    \end{equation}
-   where $L(t) = e^{(-t/\tau}$ is the learning factor which decrease with time.
-
-   6) Repeat these steps for $N$ times.
+   where $L(t) = e^{(-t/\tau)}$ is the learning factor which prevents divergence of the SOM and $R(t)=exp(-\frac{D_j^2}{2r^t_{BMU}})$ is the influence rate.
+$R(t)$ determines how weight of nodes in the neighbourhood of BMU will change.
+   \item  Repeat these steps for $N$ times.
+    \end{enumerate}
 
     In order to create SOM, we used {\tiny MATLAB} neural network toolbox~\citep{sommatlab}. 
+    In Section~\ref{sec: test model} we used this toolbox to create SOMs from SED of galaxies and learn how this method works and how we can interpret the results.
 
  \subsection{Test Model}
+ \label{sec: test model}
     Before we start using SOM on our data, we apply this model in a test sample. 

### 2016-01-25 sections/data0.0.tex
Adding first bit of M101 data

@@
 \section{DATA}
-Our sample contains photometric and spectroscopic data of M31 and M101, as well as their measured properties such as SFR, stellar mass, dust luminosity, metallicity, and gas mass.    
-%M31 data: observed ones;
+
+%Our sample contains photometric and spectroscopic data of M31 and M101, as well as their measured properties such as SFR, stellar mass, dust luminosity, metallicity, and gas mass.    
+For creating SOM, we used spectroscopy and photometry data as well as their measured properties such as SFR, stellar mass, dust luminosity and mass, metallicity, and gas mass from 10 regions in M31 (Fig~\ref{fig: region in m31}) and 8 regions in M101 (Fig~\ref{fig: region in m101}).
+Table~\ref{tab: data} shows list of the sample and their unit for both M31 and M101.
+%M31 data 
+%%%%% Sahar: More detail?
     \subsection{M31 data}
-     Our M31 data sample contains data from ten regions from outer part of the disk .
-Data for PAH are for M31 spectroscopy data for our 10 regions came from observations using {\it Spitzer}/Infrared Spectrograph \citep{Dim15}.
-\cite{Dim15}
 
-%M31 data: measured ones;
+     The 10 regions in M31 were chosen due to availability of the PAH data for them. 
+     \cite{Dim15} studied PAH for those regions using {\it Spitzer}/Infrared Spectrograph\citep[IRS,][]{Houck04b} observations. 
+     They used {\tiny PAHFIT IDL} tool~\citep{Smith07b} and measured fluxes and equivalent widths of PAH features as well as atomic line features.
+     For spectroscopy part of our sample, we utilized their measured fluxes for PAH lines. 
+     We used radiation hardness index instead of flux of individual atomic line, since they were only calculate the upper limit flux for most of the lines in most of the regions.
+
+     For photometry part of the sample, we used data from \GALEX FUV and NUV channels~\citep{Martin05}, \halpha, [SII] continuum and [OIII} continuum emission~\citep{Massey07}, IRAC channels 1 to 4~\citep{Barmby06}, MIPS24 and 70~$\mu$m~\citep{Gordon06}, PACS100 and 160~$\mu$m and SPIRE250, 350, and 500~$\mu$m~\citep{Fritz12}.
+     We changed units of all our data to Wm$^{-2}$ to be the same unit as PAH fluxes.
+     We used $^{12}$CO (J:$1\rightarrow0$) line~\citep{Nieten06} and the atomic gas (H\,{\sc I}) 21~cm emission from \cite{Chemin09}.
+     We also utilized SFR(FUV + 24$\mu$m), stellar mass, total gas mass data from \cite{Rahmani16}, and dust luminosity and mass data from \cite{Draine14}.
+
 %M101 data: observed ones;
+    \subsection{M101 data}
+     For M101 galaxy, we used PAH fluxes which had been measured using {\tiny PAHFIT IDL} tool and reported in \cite{Gordon08}. 
+     We used data available on NED~\footnote{The NASA/IPAC Extragalactic Database (NED) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.} website to gather our photometry data of M101.
+     We chose data from \GALEX FUV and NUV channels~\citep{depaz07}, IRAC channels 1 to 4, MIPS24 and 70~$\mu$m~\cite{Dale09}, and  PACS100 and 160~$\mu$m and SPIRE250, 350, and 500~$\mu$m~\cite{Kennicutt11}.

### 2016-01-25 sections/method0.0.tex
Adding first bit of M101 data

@@
      During each iteration the weight vectors might change according to the Kohonen learning rule (equation~\ref{equ: weight adj}). 
-     We test our code by varying the number of iterations and find $N = 100$ is optimized for our sample. For each iteration:
+      In each iteration:
      \begin{enumerate}
@@
 The weight vectors of these nodes will be affected in the next steps.
-This value is arbitrary but initially can be chosen to be half of the size of the SOM and then it decades exponentially over each iteration:
+This value is arbitrary and initially can be set to be as high as half of the SOM size and then it decades exponentially over each iteration:
    \begin{equation}
@@
     In order to create SOM, we used {\tiny MATLAB} neural network toolbox~\citep{sommatlab}. 
+    We created different SOM with different sizes, initial neighbourhood, and iteration numbers to find the optimize result for our sample.
+    We test our code by varying the number of iterations and find $N = 100$ is optimized for our sample.
     In Section~\ref{sec: test model} we used this toolbox to create SOMs from SED of galaxies and learn how this method works and how we can interpret the results.

### 2016-01-26 sections/data0.0.tex
Adding a table of available data

@@
 Table~\ref{tab: data} shows list of the sample and their unit for both M31 and M101.
+
+\import{../sections/tables/}{tab_data.tex}
+
 %M31 data 
@@
      We used $^{12}$CO (J:$1\rightarrow0$) line~\citep{Nieten06} and the atomic gas (H\,{\sc I}) 21~cm emission from \cite{Chemin09}.
-     We also utilized SFR(FUV + 24$\mu$m), stellar mass, total gas mass data from \cite{Rahmani16}, and dust luminosity and mass data from \cite{Draine14}.
+     We also utilized SFR(FUV + 24$\mu$m), stellar mass, total gas mass, and total infrared (TIR) emission data from \cite{Rahmani16}, and dust luminosity and mass data from \cite{Draine14}.
 
@@
      We chose data from \GALEX FUV and NUV channels~\citep{depaz07}, IRAC channels 1 to 4, MIPS24 and 70~$\mu$m~\cite{Dale09}, and  PACS100 and 160~$\mu$m and SPIRE250, 350, and 500~$\mu$m~\cite{Kennicutt11}.
+     Same as M31 data, we used $^{12}$CO (J:$1\rightarrow0$) line~\citep{Helfer03} and the atomic gas (H\,{\sc I}) 21~cm emission from \cite{Walter08} data.
+     For SFR, stellar and total gas map we used followed method described in \cite{Rahmani16} to create these maps.

### 2016-01-27 main text/draft0.0.tex
minor editing
Adding first bit of M101 data
Writing about ordering and tuning phase in the method section.

@@
 \newcommand \nprime {N$^\prime$}
+\newcommand \boldit {\textbf{\textit{}}}
 \newcommand \eqnprime {N^\prime}
@@
 
-\title{Data Mining in Nearby Galaxies}
+\title{Mining in archival data of Nearby Galaxies}
 \author{rahmani.sahar }
@@
 \begin{abstract} 
-Here is the abstract.
-%This is just first abstract for this paper!
-%M31 was targeted by many probes, and there are variety of data available for this particular galaxy.
-%M31 was mapped from X-ray to 21 cm emission. Also, spectroscopy data of different regions of M31 is available in various bands. 
-%The vast availability of data for this galaxy makes it a suitable target for data mining and ﬁnding new patterns in this galaxy.
-%In this project we are studying 10 regions in M31 from the bulge of the galaxy to the star forming ring.
-Using self organizing map (SOM) method, we classiﬁed these regions in different groups, based on total star formation rate, total stellar mass, total infrared emission and 3.6 \mice, 4.5 \mice, 5.8 \mice, 8 \mice, 24 \mice, 70 \um and 160 \mice, 2.6 mm, and 21 cm luminosity from the photometry data of the regions, and flux of 5.7 \mice, 6.2 \mice, 7.4 \mice, 7.6 \mice, 7.9\mice, 8.3 \mice, 8.6 \mice, 10.7 \mice, 11.23 \mice, 12.00 \mice, 12.62 \mice, 12.69 \mice, 14.0 \mice, 16.45 \mice, 17.04 \mice, PAH lines, [ArIII], [SIII], [SIV], [NeII], and [NeIII] as well as metallicity of these regions obtained from the spectroscopy data.
+ The vast availability of data for nearby galaxies makes them  suitable target for data mining  in order to ﬁnd new patterns in these galaxies.
+In this project we are studying data from 10 regions in M31 and 8 regions in M101.Based on available information for these two galaxies we classified these regions in different groups  using self organizing map (SOM) method.
 %We divided these regions from 2 to 6 different classes, and for each class we are going to interpret results and check whether these classiﬁcations have a physical meaning or they are just statistically relate to each other.
@@
 S.R and P.B acknowledge research support from the Natural Sciences and Engineering Research Council of Canada and from the Academic Development Fund of the University of Western Ontario.
+This research has made use of the NASA/IPAC Extragalactic Database (NED), which is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.
 %----------------------------------------------------------------------------------------
@@
 \bibliographystyle{mnras}
-\bibliography{ref_mining}
+\bibliography{ref_mining.bib}
 

### 2016-01-27 sections/data0.0.tex
Writing about ordering and tuning phase in the method section.

@@
      For spectroscopy part of our sample, we utilized their measured fluxes for PAH lines. 
-     We used radiation hardness index instead of flux of individual atomic line, since they were only calculate the upper limit flux for most of the lines in most of the regions.
+     \cite{Dim15} also reported metallicity of these regions (using results from \cite{Sanders12} for most regions), which e used them in our input sample.
+     We used radiation hardness index (RHI) instead of flux of individual atomic line, since they were only calculate the upper limit flux for most of the lines in most of the regions.
 
@@
      For M101 galaxy, we used PAH fluxes which had been measured using {\tiny PAHFIT IDL} tool and reported in \cite{Gordon08}.
+     We also added their measurement of metallicity and RHI for these regions to our sample.
      We used data available on NED~\footnote{The NASA/IPAC Extragalactic Database (NED) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.} website to gather our photometry data of M101.
@@
      Same as M31 data, we used $^{12}$CO (J:$1\rightarrow0$) line~\citep{Helfer03} and the atomic gas (H\,{\sc I}) 21~cm emission from \cite{Walter08} data.
-     For SFR, stellar and total gas map we used followed method described in \cite{Rahmani16} to create these maps.
+     SFR(FUV + 24$\mu$m), stellar and total gas map were calculated followed method described in \cite{Rahmani16} to create these maps.

### 2016-01-27 sections/method0.0.tex
Writing about ordering and tuning phase in the method section.

@@
 
+ \cite{Geach12} presented the application of the SOM and demonstrate the algorithm of the SOM in detail.
+In this section we are going to talk briefly about the algorithm of the SOM, how we create our maps and a test model which will help to interpret our results.
+
  \subsubsection{Algorithm of SOM} 
  \label{sec: algorithm}
-
      Assuming we have a data set which contains vectors, \boldit{V} $\in \Re^n$ and we want to map them on S1 by S2 map. 
@@
         \end{equation}
-   where $L(t) = e^{(-t/\tau)}$ is the learning factor which prevents divergence of the SOM and $R(t)=exp(-\frac{D_j^2}{2r^t_{BMU}})$ is the influence rate.
+        where $L(t) = L_0 e^{(-t/\tau)}$ is the learning factor which prevents divergence of the SOM and $R(t)=exp(-\frac{D_j^2}{2r^t_{BMU}})$ is the influence rate.
 $R(t)$ determines how weight of nodes in the neighbourhood of BMU will change.
@@
 
-    In order to create SOM, we used {\tiny MATLAB} neural network toolbox~\citep{sommatlab}. 
+     In order to create SOM, we used {\tiny MATLAB} neural network toolbox~\citep[ NEWSOM,][]{matlabtolbox}.
+     {\tiny MATLAB} code, works in two phases. Phase one is the ``ordering phase". 
+     This phase starts with maximum neighbourhood distance (which is initially provided by user), and initial learning factor of 0.9 as a default values. 
+     The ordering phase continues for requested number of iterations and during that steps changes the parameters in the way that in the last iteration learning factor is 0.02 and the neighbourhood distance is 1.
+
+     The second phase is the ``tuning phase".
+     In this phase the neighbourhood distance is at its minimum, but learning factor decreases very slowly.
+     This minimum neighbourhood distance and slowly decreasing the leaning factor helps to fine tune the topology results and causes the more stable SOM. 
+     The number of iterations in this tuning phase most be much more than the number iterations in ordering phase, to allow the tuning happens slowly. 
+     We chose number of epochs the tuning phase be 3 times more than number of epochs in the ordering phase.
+
      We created different SOM with different sizes, initial neighbourhood, and iteration numbers to find the optimize result for our sample.
-    We test our code by varying the number of iterations and find $N = 100$ is optimized for our sample.
+     We test our code by varying the number of iterations in ordering phase and find $N = 100$  is optimized for our sample.
      In Section~\ref{sec: test model} we used this toolbox to create SOMs from SED of galaxies and learn how this method works and how we can interpret the results.

### 2016-01-29 main text/draft0.0.tex
Finishin test model part

@@
 
-\title{Mining in archival data of Nearby Galaxies}
+\title{Mining in Nearby Galaxies}
 \author{rahmani.sahar }
@@
 \begin{abstract} 
- The vast availability of data for nearby galaxies makes them  suitable target for data mining  in order to ﬁnd new patterns in these galaxies.
-In this project we are studying data from 10 regions in M31 and 8 regions in M101.Based on available information for these two galaxies we classified these regions in different groups  using self organizing map (SOM) method.
+ The vast availability of data for nearby galaxies makes them suitable targets for data mining in order to find new patterns in these galaxies.
+In this project we are studying data from 10 regions in M31 and 8 regions in M101.Based on available information for these two galaxies we classified these regions in different groups using unsupervised self organizing map (SOM) method.
 %We divided these regions from 2 to 6 different classes, and for each class we are going to interpret results and check whether these classiﬁcations have a physical meaning or they are just statistically relate to each other.

### 2016-01-29 sections/method0.0.tex
Finishin test model part

@@
 
-     In order to create SOM, we used {\tiny MATLAB} neural network toolbox~\citep[ NEWSOM,][]{matlabtolbox}.
-     {\tiny MATLAB} code, works in two phases. Phase one is the ``ordering phase". 
-     This phase starts with maximum neighbourhood distance (which is initially provided by user), and initial learning factor of 0.9 as a default values. 
+     In order to create SOM, we used {\tiny MATLAB} neural network toolbox~\citep[NNT,][]{matlabtolbox}.
+     SOM in {\tiny NNT} works in two phases. 
+     Phase one is the ``ordering phase". 
+     This phase starts with maximum neighbourhood distance (which is initially provided by user), and initial learning factor of 0.9 which is a default value for the learning factor. 
      The ordering phase continues for requested number of iterations and during that steps changes the parameters in the way that in the last iteration learning factor is 0.02 and the neighbourhood distance is 1.
@@
 
-     We created different SOM with different sizes, initial neighbourhood, and iteration numbers to find the optimize result for our sample.
-     We test our code by varying the number of iterations in ordering phase and find $N = 100$  is optimized for our sample.
-     In Section~\ref{sec: test model} we used this toolbox to create SOMs from SED of galaxies and learn how this method works and how we can interpret the results.
+     To show our results, we combine two of the {\tiny NNT}'s built-in plots. 
+     A Hits map, which shows number of hits for each neurons, and a distances map, which shows the same neurons and the distance between them. 
+     To combine these two maps, we wrote number of hits in each neurons in the neurons in a distance map.
+     The neurons with zero hit, left empty  (i.e. Fig~\ref{fig: testmodel2by2}).
+     In distance maps, the grey hexagonal shape areas represent the neurons.
+     The red lines between neurons, show the immediate neighbours.
+     The distances in a distance map are showing by colours.
+     The darker colour represents the larger distance between neurons; whilst the lighter colours means there is small distance between neurons.
+
+     We created different SOM with different grids, initial neighbourhood, and iteration numbers to find the optimize result for our sample.
+     varying grids of the maps helps us to monitor whether grouping regions in smaller maps is real or its because of the shortage of the neurons.
+     We test our code by varying the number of iterations in the ordering phase and find $N = 100$  is optimized for our sample.
+     In Section~\ref{sec: test model} we used NNT to create SOMs from SED of galaxies and learn how this method works and how we can interpret the results.
 
@@
  \label{sec: test model}
-    Before we start using SOM on our data, we apply this model in a test sample. 
-    Our test sample contains SED of 142 galaxies between redshift 0.5 $ \leq$ Z $\leq $ 1, which their physical information such as age, stellar mass and specific star formation are available. 
-    \cite{Hossein12} used trained network to classified their spectrum based on SED models from \cite{Kinney96} and \cite{Coleman80}.
+ %the sole puprpes of this section is to show how to read the SOM results. 
+    Before we start creating SOM for our data, we apply this model on an already studied sample. 
+    Our test sample contains spectral energy distribution (SED) as well as properties such as age, stellar mass and specific star formation rate of 142 galaxies with redshift 0.5 $ \leq$ Z $\leq $ 1, which were measured and studied by \cite{Hossein12}.
+   % \cite{Hossein12} used supervised neural network method to classify galaxies' spectrum based on SED models from \cite{Kinney96} and \cite{Coleman80}.
+    We used SOM to group galaxies based on their SED. For each galaxy, fluxes on different wavelengths were an input of the program.
 
-    We create various SOM maps with different numbers of neurons and neighbourhood
+    Then, We created various SOM maps with different girds and neighbourhoods. 
+    For each map, SOM grouped the galaxies based on their similarities. 
+    Galaxies with the most similarity in their SED gathered in the same neurons, the one with more similar spectral type have a light colour (i.e.
+bright yellow) between them, and the galaxies with the least similarity in their spectral type have black colour between them (Figs~\ref{fig: testmodel2by2} and~\ref{fig: testmodel3by2}).
+
+    To illustrate these results more clearly, we averaged SED of the galaxies in each neurons and showed them in the same order as neurons in SOM (Figs~\ref{fig: sed_testmodel2by2} and~\ref{fig: sed_testmodel3by2}).
+    Figs~\ref{fig: testmodel1} and~\ref{fig: testmodel2}, shows SOM results and the SED corresponding to them in $2\times2$ and $3\times2$ grids, respectively.  
+    Top panel of the Fig~\ref{fig: testmodel1} shows the combined hits and distance map for  $2\times2$ map.
+Since numbers in each neurons is the numbers of the galaxies in that neurons, we can say we divided our 142 galaxies in a group of 30, 50 and two groups of 29.
+In lower panel of Fig ~\ref{fig: testmodel1}, plot (a) shows averaged SED of 30 galaxies, plot (d) shows the average SED of 50 galaxies, and plots (c) and (b) show the average SED of 29 galaxies.
+
+    The colour between neurons with 34 galaxies and neurons with 54 galaxies is black, which indicate these two neurons have a maximum distance from each other and galaxies in those neurons are the least similar ones.
+By looking at the average SED plots for those two neurons, one can clearly see that the averaged SED of these two groups of galaxies are completely different.
+%should I talked about what kind of SED are they.
+    On the other hand, the colour between neurons with 54 galaxies and 29 galaxies is yellow, which shows the similarity and closeness of galaxies in these two neurons. 
+    Again, by looking at the average SED plots (c and d), it is clear that the averaged SED of these two groups are the most similar ones. 
+    In Fig~\ref{fig: sed_testmodel2by2} plots (a) and (b) shows some similarity, if we look at the distance map (Fig~\ref{fig: testmodel2by2}) we could see colours between neurons related to these two groups is bright orange which is relatively bright which represents some similarity between these two groups.
+
+    In Fig~\ref{fig: testmodel2}, although the number of galaxies in each neurons are smaller due to higher number of neurons, one could see similar patterns. 
+    The average SED of the galaxies in neurons connected with bright colours are more similar to each other than the average SED of the galaxies in neurons connected with dark colours.
+    In the $3\times2$ grid, since the galaxies have more space to separate, they gathered in the smaller groups. 
+    However, most of the galaxies, which shared the same neurons, or were in the neurons close to each other, in Fig~\ref{fig: testmodel1} stayed in the neurons which are close to each other.
+
+    One can increase the grids of the maps to the point that each neurons contain max 1 galaxy. 
+    This situation eventually happens because no two galaxies are exactly alike.
+    Even in this case, galaxies with similar SED stay in a area which all the neurons are connected with yellow colour, and the galaxies with different type of SED are separated from them with darker colours (Fig~\ref{fig: testmodel3}).
+    Note that, empty neurons in the SOM results have their weight vectors and if we apply this network on the other set of data, based on similarity of the new data set to our sample, they could sit in the empty neurons.
+
+    \begin{figure}
+        \centering
+        \begin{subfigure}[b]{0.5\textwidth}
+            \centering
+            \includegraphics[width=0.7\textwidth]{../images/test_model/2by2_nei3.pdf}
+            \caption{A combination of the hits and distance map in $2\times2$ SOM. }
+             \label{fig: testmodel2by2}
+        \end{subfigure}
+        \hfill
+        \begin{subfigure}[b]{0.5\textwidth} 
+            \centering
+            \includegraphics[width=\textwidth]{../images/test_model/SED_total2by2nei3.png}
+            \caption{An average SED of galaxies in  $2\times2$ gird.}
+             \label{fig: sed_testmodel2by2}
+        \end{subfigure}
+        \caption{SOM result of the SED of the 142 galaxies in redshift of 0.5 $ \leq$ Z $\leq $ 1 with size of $2\times2$.
+Top: shows a combination of the hits and distance map in $2\times2$ SOM.
+Gray hexagonal shape areas represent neurons.
+Number of on each neurons shows the number of galaxies grouped in that neurons.
+Red lines connected neighbour neurons to each other, and colours between neurons are a scale of distance between neurons.
+Bottom: shows the Average SED of the galaxies in same neurons.
+Plots a, b, c, and d are averaged SED of galaxies in neurons with a number of 30, 29, 29, and 54, respectively.}
+        \label{fig: testmodel1}
+
+    \end{figure}
+
+    \begin{figure}
+        \centering
+        \begin{subfigure}[b]{0.5\textwidth}
+            \centering
+            \includegraphics[width=0.7\textwidth]{../images/test_model/3by2_nei3.pdf}
+            \caption{The same as Fig~\ref{fig: testmodel2by2} with size of $3\times2$.}
+             \label{fig: testmodel3by2}
+        \end{subfigure}
+        \hfill
+        \begin{subfigure}[b]{0.5\textwidth} 
+            \centering
+            \includegraphics[width=\textwidth]{../images/test_model/SED_total2by3nei3.png}
+            \caption{The same as Fig~\ref{fig: sed_testmodel2by2} with size of $3\times2$.}
+             \label{fig: sed_testmodel3by2}
+        \end{subfigure}
+        \caption{The same as Fig~\ref{fig: testmodel1}, but here we show results of SOM with size of $3\times2$.  }
+        \label{fig: testmodel2}
+
+    \end{figure}
+    \begin{figure}
+        \centering
+        \includegraphics[width=0.4\textwidth]{../images/test_model/50by50_nei3.pdf}
+        \caption{The same as Fig~\ref{fig: testmodel2by2} with size of $50\times50$.}
+        \label{fig: testmodel3}
+    \end{figure}

### 2016-02-22 images/M31/1dsoms.tex
Adding 1D SOM res. for M31

\begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
            %\centering
                    \includegraphics[width=\textwidth]{../images/M31/all/dist1by2.jpeg}
                    \caption{$1\times2$}
                     \label{fig: 1by2all}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.5\textwidth}
                     \includegraphics[width=\textwidth]{../images/M31/all/dist1by5.jpeg}
                     \caption{$1\times5$}
                     \label{fig: 1by5all}
                \end{subfigure}
                \hfill
                \hfill
                \begin{subfigure}[b]{0.5\textwidth}
                     \includegraphics[width=\textwidth]{../images/M31/all/dist1by10.jpeg}
                     \caption{$1\times10$}
                     \label{fig: 1by10all}
                \end{subfigure}
                \caption{1D results from all data}
            \end{figure}

            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../images/M31/derived_ones/dist1by2.jpeg}
                    \caption{$1\times2$}
                    \label{fig: 1by2derived}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.5\textwidth}
                    \includegraphics[width=\textwidth]{../images/M31/derived_ones/dist1by5.jpeg}
                    \caption{$1\times5$}
                    \label{fig: 1by5derived}
                \end{subfigure}
                \hfill
                \hfill
                \begin{subfigure}[b]{0.5\textwidth}
                    \includegraphics[width=\textwidth]{../images/M31/derived_ones/dist1by10.jpeg}
                    \caption{$1\times10$}
                    \label{fig: 1by10derived}
                \end{subfigure}
                \caption{1D results from derived ones}
                \label{fig: 1Dsoms}
            \end{figure}

### 2016-02-22 main text/draft0.0.tex
Adding 1D SOM res. for M31

@@
 \usepackage{amsmath}
-\usepackage{hyperref}
+%\usepackage{hyperref}
 \usepackage{graphicx}
@@
 \usepackage{float}
-\usepackage{caption}
+%\usepackage{caption}
 \usepackage{subcaption}
@@
 \usepackage{import}
+\usepackage[T1]{fontenc}
+\usepackage{ae,aecompl}
+\usepackage{amssymb}	% Extra maths symbols
+\usepackage{multicol}        % Multi-column entries in tables
+\usepackage{bm}		% Bold maths symbols, including upright Greek
+\usepackage{pdflscape}	% Landscape pages
+%\usepackage{booktabs,fixltx2e}
+\usepackage[flushleft]{threeparttable}
 
@@
 \newcommand \Spitzer {{\it Spitzer }}
-\newcommand \Galex {GALEX }
+\newcommand \GALEX {GALEX }
 \newcommand \Herschel {{\it Herschel }}
+\newcommand{\sii}{S~{\textsc II}\ } 
+\newcommand{\oiii}{O~{\textsc III}\ } 
+\newcommand{\hi}{H~{\textsc I}\ }
+
 \newcommand \aaj {A\&A}
@@
 \begin{abstract} 
- The vast availability of data for nearby galaxies makes them suitable targets for data mining in order to find new patterns in these galaxies.
+ The vast availability of data for nearby galaxies makes them suitable targets for exploratory data analysis in order to find new patterns in these galaxies.
 In this project we are studying data from 10 regions in M31 and 8 regions in M101.Based on available information for these two galaxies we classified these regions in different groups using unsupervised self organizing map (SOM) method.
@@
 \section*{ACKNOWLEDGMENTS}
-S.R and P.B acknowledge research support from the Natural Sciences and Engineering Research Council of Canada and from the Academic Development Fund of the University of Western Ontario.
+S.R.
+and P.B.
+acknowledge research support from the Natural Sciences and Engineering Research Council of Canada.
 This research has made use of the NASA/IPAC Extragalactic Database (NED), which is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.

### 2016-02-22 sections/data0.0.tex
Adding M101 regions
Adding 1D SOM res. for M31

@@
 %Our sample contains photometric and spectroscopic data of M31 and M101, as well as their measured properties such as SFR, stellar mass, dust luminosity, metallicity, and gas mass.    
-For creating SOM, we used spectroscopy and photometry data as well as their measured properties such as SFR, stellar mass, dust luminosity and mass, metallicity, and gas mass from 10 regions in M31 (Fig~\ref{fig: region in m31}) and 8 regions in M101 (Fig~\ref{fig: region in m101}).
+For creating SOM, we used spectroscopy and photometry data as well as their measured properties such as SFR, stellar mass, dust luminosity and mass, metallicity, and gas mass from 10 regions in M31 (Fig~\ref{fig: regions in m31}) and 8 regions in M101 (Fig~\ref{fig: regions in m101}).
 Table~\ref{tab: data} shows list of the sample and their unit for both M31 and M101.
@@
 \import{../sections/tables/}{tab_data.tex}
+
+\begin{figure}
+   \begin{subfigure}[b]{0.5\textwidth}
+        \centering
+    %\centering
+        \includegraphics[width=0.97\textwidth]{../images/M31/M31_3.png}
+        \caption{MIPS24 image of M31, with position of 10 regions that we studies.}
+        \label{fig: regions in m31}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.5\textwidth}
+        \includegraphics[width=\textwidth]{../images/M101/M101.png}
+        \caption{IRAC1 image of M101, with position of our 8 regions that we studies.}
+    \label{fig: regions in m101}
+    \end{subfigure}
+\end{figure}
 
@@
 
-     For photometry part of the sample, we used data from \GALEX FUV and NUV channels~\citep{Martin05}, \halpha, [SII] continuum and [OIII} continuum emission~\citep{Massey07}, IRAC channels 1 to 4~\citep{Barmby06}, MIPS24 and 70~$\mu$m~\citep{Gordon06}, PACS100 and 160~$\mu$m and SPIRE250, 350, and 500~$\mu$m~\citep{Fritz12}.
+     For photometry part of the sample, we used data from \GALEX FUV and NUV channels~\citep{Martin05}, \halpha, [\sii] continuum and [\oiii] continuum emission~\citep{Massey07}, IRAC channels 1 to 4~\citep{Barmby06}, MIPS24 and 70~$\mu$m~\citep{Gordon06}, PACS100 and 160~$\mu$m and SPIRE250, 350, and 500~$\mu$m~\citep{Fritz12}.
      We changed units of all our data to Wm$^{-2}$ to be the same unit as PAH fluxes.
@@
      We used data available on NED~\footnote{The NASA/IPAC Extragalactic Database (NED) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.} website to gather our photometry data of M101.
-     We chose data from \GALEX FUV and NUV channels~\citep{depaz07}, IRAC channels 1 to 4, MIPS24 and 70~$\mu$m~\cite{Dale09}, and  PACS100 and 160~$\mu$m and SPIRE250, 350, and 500~$\mu$m~\cite{Kennicutt11}.
+     We chose data from \GALEX FUV and NUV channels~\citep{depaz07}, IRAC channels 1 to 4, MIPS~24 and 70~$\mu$m~\cite{Dale09}, and  PACS~100 and 160~$\mu$m and SPIRE250, 350, and 500~$\mu$m~\cite{Kennicutt11}.
      Same as M31 data, we used $^{12}$CO (J:$1\rightarrow0$) line~\citep{Helfer03} and the atomic gas (H\,{\sc I}) 21~cm emission from \cite{Walter08} data.

### 2016-02-22 sections/method0.0.tex
Adding 1D SOM res. for M31

@@
 In this section we are going to talk briefly about the algorithm of the SOM, how we create our maps and a test model which will help to interpret our results.
+%PB20160218: contrast SOM with principal component analysis (PCA), which may be more familiar?
 
@@
      In order to create SOM, we used {\tiny MATLAB} neural network toolbox~\citep[NNT,][]{matlabtolbox}.
+     Although size of the SOM could be anything \cite{Vesanto05} suggested that the total number of  $5\sqrt{n}$ neurons provides the most sufficient size.
      SOM in {\tiny NNT} works in two phases. 
@@
    % \cite{Hossein12} used supervised neural network method to classify galaxies' spectrum based on SED models from \cite{Kinney96} and \cite{Coleman80}.
-    We used SOM to group galaxies based on their SED. For each galaxy, fluxes on different wavelengths were an input of the program.
+    We used SOM to group galaxies based on their SED.
+For each galaxy, fluxes on different wavelengths were an input of the program.
+% PB20160218: should say how many data points per galaxy.
+Comment on the individual flux points not being statistically independent?
+Also, this is a fairly different sort of dataset than the M31 data, so need to explain how applicable.
 
@@
 %should I talked about what kind of SED are they.
+%PB: yes.
     On the other hand, the colour between neurons with 54 galaxies and 29 galaxies is yellow, which shows the similarity and closeness of galaxies in these two neurons. 
@@
     Note that, empty neurons in the SOM results have their weight vectors and if we apply this network on the other set of data, based on similarity of the new data set to our sample, they could sit in the empty neurons.
-
+    %PB20160218: need some additional interpretation of the results
     \begin{figure}

### 2016-06-18 main text/draft0.0.tex
finishing R0.0 version.

@@
 \usepackage[flushleft]{threeparttable}
+\usepackage{mwe}    % loads »blindtext« and »graphicx«
+\usepackage{subfig}
 
@@
 \newcommand \eqsigmastar    {\Sigma_{\rm \bld {star }}}
-\newcommand \halpha    {H$\alpha $\ }
-\newcommand \um    {$\mu$m\ }
-\newcommand \mice {$\mu$m}
+\newcommand \halpha    {H$\alpha $}
+\newcommand \um    {$\mu$m}
+%\newcommand \mice {$\mu$m}
 \newcommand \nprime {N$^\prime$}
@@
 \newcommand \Herschel {{\it Herschel }}
-\newcommand{\sii}{S~{\textsc II}\ } 
-\newcommand{\oiii}{O~{\textsc III}\ } 
+\newcommand{\sii}{S~{\textsc II}} 
+\newcommand{\oiii}{O~{\textsc III}} 
 \newcommand{\hi}{H~{\textsc I}\ }
@@
 
-\title{Mining in Nearby Galaxies}
+\title{Data Mining in Nearby Galaxies}
 \author{rahmani.sahar }
 \date{\today}
-\author[S. Rahmani, et. al.]{S.~Rahmani$^{1}$\thanks{E-mail:
-srahma49@uwo.ca}, H.~Teimoorinia$^{2}$, E.~Peeters$^{1}$, P.~Barmby$^{1}$\\
+\author[S. Rahmani, et. al.]{S.~Rahmani$^{1, 2}$\thanks{E-mail:
+srahma49@uwo.ca}, H.~Teimoorinia$^{3}$, E.~Peeters$^{1, 2, 4}$, P.~Barmby$^{1, 2}$\\
 $^{1}$Department of Physics $\&$ Astronomy, Western University, London, ON N6A 3K7, Canada\\
-$^{2}$Department of Physics $\&$ Astronomy, University of Victoria, Finnerty Road, Victoria, British Columbia, V8P 1A1, Canada}
+$^{2}$Center for Planetary Science \& Exploration, Western University, London, ON N6A 3K7, Canada\\
+$^{3}$Department of Physics $\&$ Astronomy, University of Victoria, Finnerty Road, Victoria, British Columbia, V8P 1A1, Canada\\
+$^{4}$SETI Institute, 189 Bernardo Avenue, Suite 100, Mountain View, CA 94043, USA}
 \maketitle
@@
 \begin{abstract} 
- The vast availability of data for nearby galaxies makes them suitable targets for exploratory data analysis in order to find new patterns in these galaxies.
-In this project we are studying data from 10 regions in M31 and 8 regions in M101.Based on available information for these two galaxies we classified these regions in different groups using unsupervised self organizing map (SOM) method.
-%We divided these regions from 2 to 6 different classes, and for each class we are going to interpret results and check whether these classiﬁcations have a physical meaning or they are just statistically relate to each other.
-%As a result, we can predict some properties of regions in other galaxies by having only few data.
+Galaxies are very complex systems; therefore, a complete understanding of them cannot be achieved only from studying linear or logarithmic correlations between their properties and various waveband data.
+In the past few decades, a number of statistical methods have been developed and advanced to study and visualize complex big data.
+We used one of these methods to study properties of nearby galaxies and create a more clear picture of them.
+The vast availability of data for nearby galaxies makes them suitable targets for exploratory data analysis. 
+Spatially resolved maps provide us with a unique view of the inside of galaxies.%and help better understand their properties.
+In this project, we utilized the Kohonen Self Organizing Map (or self organizing map, SOM) method to study data from M31 and M101.
+%SOM is an unsupervised neural network for mapping and visualizing a complex and nonlinear high dimension data while preserving topological features of the original data. 
+%We studied 10 regions in M31 and 8 regions in M101. 
+%These regions were chosen based on the availability of mid-infrared spectroscopy data.
+%For each region in M31, we had 46 data obtained through photometry, spectroscopy, and derived quantities (i.e., star formation rate, stellar mass, gas mass, etc.). 
+%Using results from a correlation coefficient matrix, we reduced the dimension of this dataset and then trained the SOM using the new subset of data. 
+We created SOMs of various sizes and used them to extract information about the galaxies.
+Using smaller-sized SOMs the data were clustered in 2 major groups; and for each group, we found correlations that could not have otherwise seen without clustering. 
+In the maps with larger sizes, we created networks to illustrate the relative relations of the regions with one another. 
+We then applied the SOMs that were generated from the M31 data to from M101. 
+We found regions with similar properties in both galaxies placed in close regions in the SOMs.  
+These results confirm that the generated SOMs can separate regions based on their physical properties, and can be used to make predictions for other regions in nearby galaxies or other targets.
 
@@
 %----------------------------------------------------------------------------------------
-\import{../sections/}{results0.0.tex}
+%\import{../sections/}{results0.0.tex}
+\import{../sections/}{R10.0.tex}
+\import{../sections/}{R20.0.tex}
 %----------------------------------------------------------------------------------------
@@
 
-\import{../sections/}{diss0.0.tex}
+\import{../sections/}{caveat.tex}
 
@@
 \section*{ACKNOWLEDGMENTS}
-S.R.
-and P.B.
+S.R., P.B., and E.P.
 acknowledge research support from the Natural Sciences and Engineering Research Council of Canada.
@@
 \bibliography{ref_mining.bib}
+\import{../sections/}{app_2d.tex}
 

### 2016-06-18 sections/R10.0.tex
finishing R0.0 version.

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Result Part 1: 1D SOMs
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{1D SOMs}
    \label{Sec: 1d_cluster}
%Why 1D maps are useful
    The purpose of the exploring M31 with 1D maps is to monitor the general behaviour of data. 
    1D SOMs can have from the minimum number of clusters, $1\times2$, to the highest number of cluster possible.
    In small sample size like ours, smaller grid SOMs are very useful to find correlations that cannot be found without the clustering the data.
    On the other hand, higher grid 1D SOMs are a helpful tool to get quick insight into data.
%    In the following section, we are going to show how we used 1D SOMs to extract information from available data in M31.
%Clustering
 %   \subsection{Clustering M31 data}

        In order to monitor how the data behaves, we created SOMs with two to fourteen neurons (Fig.~\ref{fig: M31_nets_1d}).
        The $1\times2$ network (Fig.~\ref{fig: M31_net_1by2}) shows how the M31 data can be divided into two broad categories.
        While the $1\times14$ network (Fig.~\ref{fig: M31_net_1by14}) is the first network that all the regions in M31 are completely separated.
        Since in the higher network size, regions have more space to be separated based on their differences, we can see that from $1\times2$ to $1\times14$ network the M31 regions separated from each other more and more till they become completely separated.

        In Fig.~\ref{fig: M31_net_1by2} it is clear that by forcing the regions in the M31 to be divided into two groups, regions 1, 2, 9 and 10 occupy one neurons and the other regions occupy the other neuron.
        The medium grey colour between two neurons tell us that there are some similarity between two groups, but they are not very similar. 
        By increasing the size of the neurones to three, in Fig.~\ref{fig: M31_net_1by3}, we can see that the region 2 separates itself from the other regions and occupies the middle neuron.
        The white colour between two left neurons suggests that regions, which occupy these neurons are very similar to each other, while the black colour between two right neurons indicates the opposite.

        %%%Talking about four right regions
        \cite{Dim15} showed that the regions 1, 2, 9, and 10 have higher PAHs flux intensity compare with other regions (Fig. 5 in \cite{Dim15} paper). 
        %Regions 1, 2, and 9 are in the 10~Kpc ring and region 10 is located in the bulge of M31; however, regions 3 to 8 are located slightly out of the inner ring or the 10~kpc one.
        These regions also have relatively high intensity in the SPIRE bands and have high dust luminosity.
        The higher values in the intensity of the PAHs, SPIRE bands and the dust luminosity could be the reason that these 4 regions become separated from the others in  $1\times2$ network.
        Besides, Regions 1, and 9 are in the 10~Kpc ring, region 2 is slightly out of the 10~Kpc ring and the region 10 is in the bulge of M31; however, regions 3 to 8 are located out of the inner ring or the 10~kpc ring (Fig.~\ref{fig: regions in m31}).   
        The differences in their positions might be the reason of regions 1, 2, 9 and 10 having higher values in some quantities than the others. 
        The similarity in the other inputs values with the other regions causes regions 1, 2, and 9 gradually have more distance with region 10, and move towards other regions in the higher grid SOMs.
       % Therefore, in 1D networks with 14 neurons or higher, regions 1, 2, and 9 completely are separated from region 10, and show more similarity to other regions than to the region 10.

        %%% Repeated from the other paragraphs
        %%%Talking about 6 left regions
        %In both Figs.~\ref{fig: M31_net_1by2} and~\ref{fig: M31_net_1by3} the most left neuron is occupied with regions 3 to 8. 
        %These regions all are located outside the inner or 10~kpc rings (See fig.~\ref{fig: regions in m31}).
        %Since the locations of these regions have similar physical properties, they occupy a same neurons in a smaller SOMs.
        %As it can be seen in the $1\times3$ SOM (Fig.~\ref{fig: M31_net_1by3}), the region 2 is moved to the middle neurons.
       % The fact that this region is slightly out of the 10~kpc ring makes region 2 to be the first region to move towards the neurons that occupied with regions 3 to 8. 
       % In the $1\times14$ SOM (Fig.~\ref{fig: M31_net_1by14}), although all the regions were separated, but the colour between regions 10 to the other regions become completely dark.
       % This dark colour indicates that region 10 is absolutely different, which considering the fact that it is the only regions in the bulge of the galaxy, we expected to see such a distance between this regions and the others.

        \begin{figure}
            \subfloat[$1\times2$~network\label{fig: M31_net_1by2}]{
             \includegraphics[width=0.5\textwidth]{../images0.01/M31/1D/combine_1D_1by2_all.png}
             }
            \hfill
            \subfloat[$1\times3$~network\label{fig: M31_net_1by3}]{
            \includegraphics[width=0.5\textwidth]{../images0.01/M31/1D/combine_1D_1by3_all.png}
             }
             \hfill
            \subfloat[$1\times14$~network\label{fig: M31_net_1by14}]{
             \includegraphics[width=0.5\textwidth]{../images0.01/M31/1D/combine_1D_1by14_all.png}
             }%%% What should I do with this one! It doesn't look good visually
            \caption{SOM of the M31 data from $1\times2$~, $1\times3$~and $1\times14$~grids. The axes show the position of the neurons. The purple Hexagonal shapes represent the neurons. The grey cycle colours show the differences between weight of each neuron with white is the minimum differences and black has the maximum one. The numbers in the plot show the regions that are located in each neuron.}
            \label{fig: M31_nets_1d}
        \end{figure}

        %%Network 1by14
        The network with 14 neurons, in Fig.~\ref{fig: M31_net_1by14}, is the first network which has no neurons with more than one region.
        In a higher grid SOM, network pays more attention to smaller details.
        Therefore, since at least 14 neurons are needed to separate all the 10 regions in M31, we can conclude that some of the regions have very small differences.
        In fig.~\ref{fig: regions in m31}, some the regions are grouped next to each other in the galaxy, which is the reason why some of the regions have vary similar input values.
        In Fig.~\ref{fig: M31_net_1by14}, the most right neuron is occupied by region 10.
        Two black colour between this region and the others indicates the high differences between this neuron and the other ones.
        The region 10 is located in the bulge of M31, and its separation from other regions, which are mostly located around of the inner or outer rings, is due to the fact that most of the input values for this region is much higher than the other regions.
        The region 8 occupies the most right neurons in this network, that suggests that this region has the most differences with the region 10.

    \subsection{Inside of the 2 neurons network}%%% I will find better title for this subsection
        %What is going on in this section
        Using SOMs, we can identify hidden subgroups in our samples. 
        Each of these subgroups were separated from each other, for a reason.
        This reason can vary from having higher values in some specific wavelengths, as discussed in Sec.~\ref{Sec: 1d_cluster}, to some unknown correlations between data, that cannot be seen in other groups or in a Galaxy's data as a whole.
        To investigate the later, we showed the Pearson correlation coefficients for the inputs from regions 3 to 8 in Fig.~\ref{fig: cor_cluster1}, which were clustered together in the $1\times2$ and $1\times3$ networks (see Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}).

        \begin{figure}
        \includegraphics[width=0.5\textwidth]{../images0.01/cor_plots/M31_derived_3_to_8_core_plot_for_paper.pdf}%%% cut the white regions around the figure
        \caption{Same as Fig.~\ref{fig: cor_all}, but here we used data from regions grouped in the left side of the Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}. }
          \label{fig: cor_cluster1}
        \end{figure}

        %%% what regions' version shows and how it compares with the other one:
        In Fig.~\ref{fig: cor_all}, all the PAHs features highly correlate with each other. 
        Also, considering data from all M31 regions, there are very strong correlations between all the PAHs features and PACS~100~$\mu$m~, SPIRE 250 to 500~$\mu$m~emission, L$_{\rm DUST}$, L$_{\rm TIR}$, SFR, and metallicity.
        However, in Fig.~\ref{fig: cor_cluster1},12.0 and 12.7~$\mu$m~ PAHs fluxes do not show any significant or strong correlation with PAH fluxes in other wavelengths or most other quantities.
        The only exceptions are the strong correlation between PAH flux at 12~$\mu$m and dust luminosity, and between 12 and 12.7~$\mu$m PAH fluxes.
        Since there are only 6 regions in the cluster, even one outlier in the data can causes the correlation coefficient become insignificant.
        By removing the outlier, the correlations between 12.0 and 12.7~$\mu$m~ PAHs fluxes and the other quantities show themselves.

        For the rest of the PAHs fluxes in Fig.~\ref{fig: cor_cluster1}, there are not any significant correlations with PACS~100~$\mu$m, L$_{\rm DUST}$, L$_{\rm TIR}$, SFR, or metallicity, too.
        They have correlations with SPIRE emission, but they are weaker than the ones with data from all regions.
        Correlations between PAHs, features and SFR and L$_{\rm TIR}$  are well-studied~\citep[e.g.][]{Tielens08,Peeters04}. 
        Many groups used PAHs features as a tracer of SFR by finding correlation between 
        PAHs emission and SFR derived from extinction corrected \halpha~\citep[e.g.][]{Shipley16,Khramtsova13,Calzetti07}.
        This correlation can be seen in Fig.~\ref{fig: cor_all}, when we considered the data from all regions, but not in Fig.~\ref{fig: cor_cluster1} considering the clustered data.
        Further analysis shows that the absence of the correlation between PAHs features and SFR, is because of one outlier in data. 
        When we disregard the outlier data, high correlation between 6.2 to 11.3~$\mu$m~PAHs features and SFR (and L$_{\rm TIR}$) appears again.
        Strong ant-correlation between 6.2 to 11.3~$\mu$m~PAHs features and RHI, stellar mass, \halpha, \sii, \oiii, and IRAC~5.6~$\mu$m~emission in Fig.~\ref{fig: cor_cluster1} had not be seen in Fig.~\ref{fig: cor_all}.
     %   In Fig.~\ref{fig: cor_cluster1}, 6.2, 7.7, 8.3, 8.6, and 11.3~$\mu$m~PAHs features show strong anti-correlations with RHI, stellar mass, \halpha, \sii, \oiii, and IRAC~5.6~$\mu$m~emission.
        Anti-correlations between PAHs features and the \halpha, \sii, and \oiii~emission could be result of one the followings. 
        The optical data are not corrected for dust extinction. The PAHs features correlate with dust, and \halpha emission is sensitive to dust extinction. Therefore, more PAHs features, means more dust and less \halpha emission (The same for \sii~and \Oiii~emission).
        Or it is the affect of observing choice, if the apertures are located in the edge of the regions we would expect too see more PAHs and less \halpha emission. %ehhhhh %%% reference?
        The anti-correlation between 6.2 to 11.3~$\mu$m~PAHs features and RHI have been seen in other studies, too~\citep[e.g.][]{Dim15, Gordon08, Wu06}.
        \cite{Wu06} discussed this ant-correlation could be the result of destruction of the PAHs due to the high amount of the harder radiation (thus higher RHI).
        On the other hand, \cite{Gordon08} the harder radiation could make the photodissociation regions (PDRs) smaller.
        The PAHs features are mostly coming from the PDRs that are surrounded by H {\sc II} regions, and their underlying continuum emission is from the H {\sc II} regions.
        Therefore, the lower flux of the PAHs features could be the result of the smaller size of PDRs.
        The later reason, which could also describe the anti-correlation between PAHs features and \halpha~emission, seems to be the more possible one. 
        %%% The anti correlation with stellar mass?!! with IRAC3?!!

       Despite the fact that some of the (anti)-correlations in Fig.~\ref{fig: cor_cluster1} might have physical meaning, we have to remind that, we only used 6 regions to calculate these correlation coefficients.
       Having 6 data points in the sample is not high enough to have a strong conclusion about the PAHs in M31.%%% it doesn't sound right:((
        However, we can conclude that since the correlation coefficients derived from the clustered data (Fig.~\ref{fig: cor_cluster1}) varies from correlation coefficients derived from the data from the all regions (Fig.~\ref{fig: cor_all}), SOM separated a hidden cluster of the data, which their properties are different than the others. %%Again eh!

### 2016-06-18 sections/R20.0.tex
finishing R0.0 version.

 %----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Result Part 2: 2D SOMs
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
 \section{2D SOMs}
 Although 1D networks are great to have a general idea about the data, they are not showing a whole picture. 
        Therefore, we created $10\times10$ 2D networks to study the data in details.
 Since in 1D SOMs, each neuron has maximum two immediate neighbours, 1D SOMs can't provide show complicated relations in data.
However, 
            \subsubsubsection{Subsets}
            In subset 0 presented the derived values and values that had not been used to create any of derived values.
            Fig.~\ref{fig: all_derived_ones} shows the SOM and the weight plane of each input data from subset 0.
            Regions 4 and 7 are in the top left of Fig.~\ref{fig: all_derived_ones} and in the second neighbourhood of each other, with very bright light between their nodes which represents that weight of these nodes are similar to each other. 
            The positions of these two regions in the galaxy are really close and they both are on almost same distance from the star forming ring in galaxy.
            Both of these regions are right on the edge of the star forming rings in the galaxy. 
            Position of the region 3 on the SOM is close to the position of the regions 4 and 7, but with darker colour between the nodes. 
            This region in M31 is close to regions 4 and 7 but on the outer side of the star forming ring.
            \import{../sections/image_texts/}{all.tex}
            Regions 5, 8 and 6 are close to each other on the SOM.
            These three regions are around the inner ring of the galaxy.
            Since region 5 is right outside the inner rings whereas regions 6 and 8 are in inner part of the inner ring, this region has more distance and more weight from the regions 6 and 8.
            Regions 1 and 9 are close to each other and in the end side of the star forming ring. 
            Region 2 is more distant from other regions in the galaxy. 
            However, it is right out side the star forming too. 
            Therefore, its place in SOM somehow is close to the positions of the regions 1,3 and 9.
            The weights between region 2 and the other three regions are relatively high, due to fact that the region 2 is basically placed on the opposite side of the galaxy. 
            Region 10 is placed in the bulge of the galaxy, and its position on the SOM is isolated from all the other regions.

            In order to analyse affect of any input data on the final SOM, we created SOMs from various subsets of data and compare their results with one another and with SOM created from all data listed in subset 0.
            %%\subsection{Increasing dimension of input data one by one}
            We started the analysis by creating SOMs using only PAHs data, and using all data from subset 0 except PAHs ones(Fig.~\ref{fig: PAHS_or_not_PAHs}). 
            Then, we increased the dimension of PAH only data gradually by adding data from subset 0 to it, i.e. the first map in Fig~\ref{fig: inc_D_col3s} was created from PAHs data and H$\alpha$ emission, the second one was created from PAHs, H$\alpha$ emission and [\sii] continuum, and so on.

        \import{../sections/image_texts/}{col11by26.tex}

         We then generated some sub-samples of the data based on the weight planes in the Figs.~\ref{fig: all_derived_ones} to~\ref{fig: subset7}.
        We first removed data with larger weights (with darker colours) in most of the neurons, one at a time (see tables~\ref{tab: subset1} -~\ref{tab: subset4}).
        For subset sample 1 from Table~\ref{tab: subset1}, we used all the values from subset 0 excluding data from stellar mass. 
        We removed IRAC 5.7 $\mu$m; [\sii] continuum and [\oiii] continuum; PAH8.3 $\mu$m, PAH12.0 $\mu$m, PAH17.0 $\mu$m, [~\oiii] continuum, stellar mass and metallicity from subset 0, and generated subset samples 2 to 4, respectively (Tables~\ref{tab: subset2} to~\ref{tab: subset4}).
        Table~\ref{tab: subset5} shows the list of data that were used in a subset sample 5, which is data from subset 0 except the fact that instead of the individual PAH fluxes we added them together and have total PAH flux. 
        For subset sample 6 (Table~\ref{tab: subset6}), we removed SPIRE 250 and 500~$\mu$m, and for subset sample 7 (Table~\ref{tab: subset7}) we removed [\sii] flux, SPIRE 250 and 500~$\mu$m and TIR emission from subset sample 5.
        Figs.~\ref{fig: subset1} to~\ref{fig: subset7} show SOM and input data weight planes created from subset samples 1 to 7, respectively.

        The left side of the Fig.~\ref{fig: subset1} shows SOM results from Table~\ref{tab: subset1}. 
        In the SOM map, regions 1 and 9 are closer to region 10. 
        The regions 1 and 9 are the ones with lowest stellar mass, on the other side region 10 has the highest stellar mass. 
        Since the stellar mass was one of the most distinct differences between these regions, removing stellar mass from input data reduced the distance between these regions.
        Regions 5, 6 and 8 are in the same relative distance from each other, but they all are closer to the position of the region 10.
        Distance between regions 2 and 3 is reduced but in the meantime the colour between them became darker.

        \import{../sections/tables/}{subset1.tex}
        \import{../sections/image_texts/}{subset1.tex}

%\subsubsection{subset4}

        Changing from separate value for each PAH to a single value for the total PAH, caused small changes to our the SOM map (Fig.~\ref{fig: subset5}). 
        Distance between the position of the regions 6 an 8 increased significantly, while the position of region 2 moved closer to the positions of the regions 4 and 7.
        The winner neurons for the regions 3 and 5 are moved towards each other, but the colours between them became much more darker. 
%\subsubsection{subset5}
        \import{../sections/tables/}{subset5.tex}
        \import{../sections/image_texts/}{subset5.tex}

        Fig.~\ref{fig: subset6} shows the results from Table~\ref{tab: subset6}, which includes all the data from Table~\ref{tab: subset5} except fluxes from SPIRE 250 and 500~$\mu$m.
        For most of the regions, although we see the changes in the positions, the colours between neurons changed, too. 
        Which we can conclude that these changes are because of the different initial values in the weights.
        However, the distance between the positions of the regions 4 and 2 increased.
        The same happened for distance between regions 7, 3 and 6.
        In both cases, flux values in SPIRE 250 and 500~$\mu$m for these regions are similar to each other, and removing these two parameters from input moved the positions of the regions further. 
%\subsubsection{subset6}
        \import{../sections/tables/}{subset6.tex}
        \import{../sections/image_texts/}{subset6.tex}

%\subsubsection{subset7}
\subsubsection{Prediction observing data using M31}

        %%What about M101; Is it going to behave in the same way! how corr matrix, look like for M101 data?
   \subsection{ Validating networks using M101 data}
      %%% 10x10 networks using subsets of data to create networks; make prediction based on results;
      %%%% 10x10 checking data with M101 data
      %%% Combine M31 + M101 data to make new prediction

### 2016-06-18 sections/app_2d.tex
finishing R0.0 version.

\newpage
\appendix
\section{2D SOMs of subsets}
        \import{../sections/image_texts/}{col3byall.tex}
        In Fig.~\ref{fig: subset2}, which is the SOM results from data listed in Table~\ref{tab: subset2}, distance between positions of the region 7, and region 3 is much larger compare to the one in Fig.~\ref{fig: all_derived_ones}. 
        IRAC 5.7~$\mu$m flux in the region 7 and the region 3 is similar to each other. 
        Therefore, removing flux from IRAC 5.7 $\mu$m removed the one source of similarity in these two regions and they moved further from each other in the SOM.
        The positions of the regions 2 and 9 are closer to each other, but the weight distance between them is much higher (the colours between them are became almost black). 
        In general by removing IRAC 5.7 $\mu$m  flux data from the input data, the colours between regions become much more darker.
        \import{../sections/tables/}{subset2.tex}
        \import{../sections/image_texts/}{subset2.tex}

        In Fig.~\ref{fig: subset3}, the positions from the region 9 is much closer to the positions of the regions 4 and 7. 
        Since region 4 and 5 have a similar [~\oiii] and [~\sii] continuum fluxes, by removing these two values from the input data distance between regions 4 and 5 became much smaller.
        The positions of the regions 2 and 6 are closer together, but the colours between their neurons are darker.
        The wining neurons for regions 1 and 9 are moved further from each other, but the colours between them are slightly lighter. 
        moreover, similar to regions 4 and 5, [~\oiii] and [~\sii] continuum fluxes for regions 1 and 9, and regions 8 and 6 are similar to each other, and removing these two values from input data, reduces the similarity between these regions. Therefore, they moved further from each other. 
        \import{../sections/tables/}{subset3.tex}
        \import{../sections/image_texts/}{subset3.tex}

        In the results from the subset 4 in Fig.~\ref{fig: subset4}, regions 8 and 6 moved closer to each other. 
        These two regions have distinct metallicity, removing metallicity from input data caused these two stay in a closer neurons. 
        Since regions 1 and 2 have similar metallicity and total PAHs, and their total stellar mass are comparable, removing these values from input data made the position of the regions 1 and 2 moved further from each other. 
        \import{../sections/tables/}{subset4.tex}
        \import{../sections/image_texts/}{subset4.tex}

        The positions of the region 8 and 5 are moved closer in Fig.~\ref{fig: subset7}.
        Both of these regions are around the inner ring inside the galaxy.
        Therefore, both of them have similar values in most of the input parameters.
        However, they have very different fluxes in IRAC 5.7 $\mu$m and [~\sii] continuum, which removing these two fluxes from the input data moved their position on the SOM closer.
        TIR luminosity and IRAC 5.7 $\mu$m flux for regions 3 and 5 are different, and removing them from the input data caused the distance between their position decreases. 
        In Fig.~\ref{fig: subset7} the relations between all the other regions are mostly unchanged.
        \import{../sections/tables/}{subset7.tex}
        \import{../sections/image_texts/}{subset7.tex}

### 2016-06-18 sections/data0.0.tex
finishing R0.0 version.

@@
 
-%Our sample contains photometric and spectroscopic data of M31 and M101, as well as their measured properties such as SFR, stellar mass, dust luminosity, metallicity, and gas mass.    
-For creating SOM, we used spectroscopy and photometry data as well as their measured properties such as SFR, stellar mass, dust luminosity and mass, metallicity, and gas mass from 10 regions in M31 (Fig~\ref{fig: regions in m31}) and 8 regions in M101 (Fig~\ref{fig: regions in m101}).
-Table~\ref{tab: data} shows list of the sample and their unit for both M31 and M101.
+We gathered data from 10 regions in M31 (Fig.~\ref{fig: regions in m31})  and 8 regions in M101 (Fig.~\ref{fig: regions in m101})  inputs for SOM maps.
+We chose those specific regions due to availability of the PAHs data for them.
+Besides PAHs data, for each galaxy, we chose spectroscopy and photometry data as well as their derived properties, such as SFR, stellar mass, dust luminosity (L$_{\rm DUST}$) and mass, metallicity, and gas mass.
+Table~\ref{tab: data} shows list of the data and their unit for both M31 and M101.
+We divided each values by the area of their region (in arcsec$^2$), to be able to compare values in both galaxies without being worried about their distances.
+The resolution of the data varies from less than 1$\arcsec$ to $60\arcsec \times 90 \arcsec$.
+Any attempt to match the PSF for these range, causes to use all the spectroscopic data.
+Besides the convolution methods conserve the flux per area.
+Therefore, we did not do any PSF matching in this paper and we used data in their original resolutions.
 
@@
 
+% \begin{figure}
+%   \begin{subfigure}[b]{0.5\textwidth}
+%         \centering
+%     %\centering
+%         \includegraphics[width=0.97\textwidth]{../images0.0/M31/M31.png}
+%         \caption{MIPS24 image of M31, with position of 10 regions that we studies.}
+%         \label{fig: regions in m31}
+%     \end{subfigure}
+%     \hfill
+%     \begin{subfigure}[b]{0.5\textwidth}
+%         \includegraphics[width=\textwidth]{../images0.01/M101/M101.png}
+%         \caption{IRAC1 image of M101, with position of our 8 regions that we studies.}
+%     \label{fig: regions in m101}
+%     \end{subfigure}
+%     \caption{Position of the data in M31 (up) and M101 (down).}
+% \end{figure}
+
   \begin{figure}
-   \begin{subfigure}[b]{0.5\textwidth}
-        \centering
-    %\centering
-        \includegraphics[width=0.97\textwidth]{../images/M31/M31_3.png}
-        \caption{MIPS24 image of M31, with position of 10 regions that we studies.}
-        \label{fig: regions in m31}
-    \end{subfigure}
+    \subfloat[MIPS24 image of M31, with position of 10 regions.\label{fig: regions in m31}]{
+      \includegraphics[width=0.5\textwidth]{../images0.0/M31/M31.png}
+    }
     \hfill
-    \begin{subfigure}[b]{0.5\textwidth}
-        \includegraphics[width=\textwidth]{../images/M101/M101.png}
-        \caption{IRAC1 image of M101, with position of our 8 regions that we studies.}
-    \label{fig: regions in m101}
-    \end{subfigure}
+    \subfloat[IRAC1 image of M101, with position of our 8 regions.\label{fig: regions in m101}]{
+      \includegraphics[width=0.5\textwidth]{../images0.01/M101/M101.png}
+    }
+    \caption{Position of the data in M31 (up) and M101 (down).}
+    \label{fig:dummy}
   \end{figure}
@@
      We used $^{12}$CO (J:$1\rightarrow0$) line~\citep{Nieten06} and the atomic gas (H\,{\sc I}) 21~cm emission from \cite{Chemin09}.
-     We also utilized SFR(FUV + 24$\mu$m), stellar mass, total gas mass, and total infrared (TIR) emission data from \cite{Rahmani16}, and dust luminosity and mass data from \cite{Draine14}.
+     We also utilized SFR(FUV + 24$\mu$m), stellar mass, total gas mass, and total infrared (TIR) luminosity (L$_{\rm TIR}$) data from \cite{Rahmani16}, and L$_{\rm DUST}$ and mass data from \cite{Draine14}.
 
-%M101 data: observed ones;
     \subsection{M101 data}

### 2016-06-18 sections/intro0.0.tex
Adding 1D SOM res. for M31
finishing R0.0 version.

@@
 \section{Introduction}
-% ideas about science of paper will add the them at the end
+%General information about galaxies %(Maybe it is too generic?!!)
+Inside each galaxies are millions of stars and large amount of dust and gas, which all have affect on each others' formation, evolution and extinction.
+Galaxies are an active and complicated systems, that are constantly changing.
+There are extensive amount of studies about correlations between galaxies' emission and their physical properties, both observationally and theoretically %(Some references here). 
+With all these studies our knowledge about the underlying processes in formation and evolution of galaxies expands every day, but the details of how these process work are still undetermined.
 
-% maybe a little bit about PAH and other properties of nearby galaxies
+% Nearby galaxies and their importance 
+Nearby galaxies plays an important role in improving studies about galaxies' formation and evolution.
+These galaxies are close enough to be able to observe various regions inside the galaxies in details.
+As a result, many studies were devoted to find relations between physical properties of the galaxies in both spatially resolved regions and galaxies as a whole %(Some more references here)
+, and many others used these results to analyze data from high-redshift galaxies.%(Some more references here)
+The amount of the data that is acquired from nearby galaxies is increasing daily.
+Advances in technology helps to both observe and store enormous amount of data from the sky.
+Telescopes and surveys gatherer data from nearby galaxies in different wavelengths and from these data we can measure physical properties of galaxies (e.g.
+stellar mass, star formation rate (SFR), dust mass, gas mass).
+%(Some more references here)
 
-% data mining in general?ANN?
+M31, with distance of $\sim 0.78$~Mpc~\citep{McConnachie05}, is one of the closest spiral galaxies to the Milky way and provide us very unique view of inside of a spiral galaxy.
+Therefore,
+
+% A little bit about PAH and other properties of nearby galaxies?!
+
+% data mining and clustering in general; when we have so many data and we want to map them
+\cite{Ball10} did an extensive review of data mining and machine learning and their usage in astronomy.
+
+%SOM is a good method for knowledge discovery projects;
+%SOM in Astronomy and mention we do not have any SOM in nearby galaxies
+%this project 1 M31 and its extensive data
+
+%supervised and unsupervised network

### 2016-06-29 main text/draft0.0.tex
V1

@@
 \usepackage{amsmath}
-%\usepackage{hyperref}
+\usepackage{hyperref}
 \usepackage{graphicx}
 \usepackage{natbib}
-\bibliographystyle{mn2e}
 \usepackage{times}
@@
 \newcommand \Herschel {{\it Herschel }}
-\newcommand{\sii}{S~{\textsc II}} 
-\newcommand{\oiii}{O~{\textsc III}} 
-\newcommand{\hi}{H~{\textsc I}\ }
+\newcommand \sii {S~{\textsc II}} 
+\newcommand \oiii {O~{\textsc III}} 
+\newcommand \hi {H~{\textsc I}\ }
 
@@
 \newcommand \mnras {MNRAS} %: Monthly Notices of the Royal Astronomical Society
-%\newcommand {Nature}%(do not abbreviate)
 \newcommand \pasj {PASJ}%: Publications of the Astronomical Society of Japan
@@
 \newcommand \mex {Rev. Mex. Astron. Astrofis.}%: Revista Mexicana de Astronomia y Astrofisica
-%\newcommand {Science }%}%(do not abbreviate)
 \newcommand \sva {SvA}%: Soviet Astronomy
@@
 \begin{document}
-% TITLE
-
 \title{Data Mining in Nearby Galaxies}
-\author{rahmani.sahar }
-\date{\today}
 \author[S. Rahmani, et. al.]{S.~Rahmani$^{1, 2}$\thanks{E-mail:
@@
 The vast availability of data for nearby galaxies makes them suitable targets for exploratory data analysis. 
-Spatially resolved maps provide us with a unique view of the inside of galaxies.%and help better understand their properties.
-In this project, we utilized the Kohonen Self Organizing Map (or self organizing map, SOM) method to study data from M31 and M101.
+Spatially resolved maps provide us with a unique view of the inside of galaxies. %and help better understand their properties.
+In this project, we utilized the Kohonen Self Organizing Map (SOM) method to study data from M31 and M101.
 %SOM is an unsupervised neural network for mapping and visualizing a complex and nonlinear high dimension data while preserving topological features of the original data.
@@
 These results confirm that the generated SOMs can separate regions based on their physical properties, and can be used to make predictions for other regions in nearby galaxies or other targets. 
-
 \end{abstract}
@@
 
-\import{../sections/}{caveat.tex}
+%\import{../sections/}{caveat.tex}
 
@@
 \section{SUMMARY}
+\label{sec: summary}
+Self-organizing maps can be used to explore hidden subgroups and underlying structure of the data.
+In this project we investigated applications of the Self-organizing maps in data from nearby galaxies.
+We utilized the SOM method to study data from two well-studied galaxies; M31 and M101.
+Data from nearby galaxies can be clustered in various networks with different sizes/dimensions based on the information needed from the data. 
+A network with one dimension and a few neurons, can be used for general classification, while for more detailed clustering, a higher number of neurons should be used.
+
+Using smaller-sized self-organizing maps, the M31 data were clustered in 2 major groups; we found correlations that could not have otherwise been seen without clustering.
+For example in Sec.~\ref{sec: inside_the_2_neurons}, we found that six of the regions in M31 create a subgroup of data, that have lower amount of PAHs flux.
+Flux from the PAHs features in these regions highly anti-correlated with \halpha~emission despite that considering Flux from the PAHs features in all regions highly correlates with SFR.
+Our analyses of smaller-sized networks showed that using this method we can find hidden subgroups in data to extend our knowledge of inside the galaxies.
+
+In the maps with larger sizes, networks can be used to illustrate the relative relations of the regions with one another.
+We found the relative similarity between M31 regions, by varying the size of networks.
+A one-dimensional network with 14 neurons was needed in order to
+separate all 10 regions; we concluded that some of the region in M31 (e.g. regions 4 and 7) are very similar.
+A two-dimensional networks provide us a more complete picture of the data.
+Using these networks, we show a relative relations between regions in M31.
+
+We introduced self-organizing maps as a method that can be used to predict the amount of various quantities based on the relative positions of the regions in the networks.
+By converting the relative distance between regions to the probability distribution function, we could predict unobserved/unmeasured properties of the galaxies with 10 per cent uncertainty.
+We also applied the SOMs from M31 data to M101 data and found regions with similar properties in both galaxies placed in close regions in the SOMs.
+We show that using this ability of the SOM, we can predict properties of regions in other nearby galaxies very fast.
 
 \section*{ACKNOWLEDGMENTS}
+The authors thank A. Tammour for her useful comments. 
 S.R., P.B., and E.P.
@@
 %----------------------------------------------------------------------------------------
-\bibliographystyle{mnras}
+\bibliographystyle{mn2e}
 \bibliography{ref_mining.bib}

### 2016-06-29 sections/R10.0.tex
V1

@@
 %----------------------------------------------------------------------------------------
-\section{1D SOMs}
+\section{One dimensional Self-organizing maps}
     \label{Sec: 1d_cluster}
 %Why 1D maps are useful
-    The purpose of the exploring M31 with 1D maps is to monitor the general behaviour of data. 
+    The purpose of the exploring M31 data with 1D maps is to monitor the general behaviour of data. 
     1D SOMs can have from the minimum number of clusters, $1\times2$, to the highest number of cluster possible.
-    In small sample size like ours, smaller grid SOMs are very useful to find correlations that cannot be found without the clustering the data.
+    In a small sample like ours, smaller grid SOMs are very useful to find correlations that cannot be found without the clustering the data.
     On the other hand, higher grid 1D SOMs are a helpful tool to get quick insight into data.
@@
         While the $1\times14$ network (Fig.~\ref{fig: M31_net_1by14}) is the first network that all the regions in M31 are completely separated.
-        Since in the higher network size, regions have more space to be separated based on their differences, we can see that from $1\times2$ to $1\times14$ network the M31 regions separated from each other more and more till they become completely separated.
+        Since in the higher network sizes, regions have more space to be separated based on their differences, we can see that from $1\times2$ to $1\times14$ network the M31 regions separated from each other increasingly, until they are completely separated.
 
-        In Fig.~\ref{fig: M31_net_1by2} it is clear that by forcing the regions in the M31 to be divided into two groups, regions 1, 2, 9 and 10 occupy one neurons and the other regions occupy the other neuron.
-        The medium grey colour between two neurons tell us that there are some similarity between two groups, but they are not very similar. 
+        In Fig.~\ref{fig: M31_net_1by2}, it is clear that by forcing the regions in the M31 to be divided into two groups, regions 1, 2, 9 and 10 occupy one neuron and the other regions occupy the other one.
+        The medium grey colour between two neurons indicates that there are some similarity between two groups, but they are not very similar. 
         By increasing the size of the neurones to three, in Fig.~\ref{fig: M31_net_1by3}, we can see that the region 2 separates itself from the other regions and occupies the middle neuron.
-        The white colour between two left neurons suggests that regions, which occupy these neurons are very similar to each other, while the black colour between two right neurons indicates the opposite.
+        The white colour between two left neurons suggests that regions, which occupy these neurons are very similar to each other, while the black colour between two right neurons expresses otherwise.
 
         %%%Talking about four right regions
-        \cite{Dim15} showed that the regions 1, 2, 9, and 10 have higher PAHs flux intensity compare with other regions (Fig. 5 in \cite{Dim15} paper). 
+        \cite{Dim15} showed that the regions 1, 2, 9, and 10 have higher PAHs flux intensity compare to other regions (Fig. 5 in \cite{Dim15} paper). 
         %Regions 1, 2, and 9 are in the 10~Kpc ring and region 10 is located in the bulge of M31; however, regions 3 to 8 are located slightly out of the inner ring or the 10~kpc one.
         These regions also have relatively high intensity in the SPIRE bands and have high dust luminosity.
-        The higher values in the intensity of the PAHs, SPIRE bands and the dust luminosity could be the reason that these 4 regions become separated from the others in  $1\times2$ network.
+        The higher values in the intensity of the PAHs, SPIRE bands and the dust luminosity could be the reason that these 4 regions become separated from the others, in $1\times2$ network.
         Besides, Regions 1, and 9 are in the 10~Kpc ring, region 2 is slightly out of the 10~Kpc ring and the region 10 is in the bulge of M31; however, regions 3 to 8 are located out of the inner ring or the 10~kpc ring (Fig.~\ref{fig: regions in m31}).
         The differences in their positions might be the reason of regions 1, 2, 9 and 10 having higher values in some quantities than the others. 
-        The similarity in the other inputs values with the other regions causes regions 1, 2, and 9 gradually have more distance with region 10, and move towards other regions in the higher grid SOMs.
+        The similarity in the other input values with the other regions causes regions 1, 2, and 9 gradually move towards other regions, and have more distance with region 10, in the higher grid SOMs.
        % Therefore, in 1D networks with 14 neurons or higher, regions 1, 2, and 9 completely are separated from region 10, and show more similarity to other regions than to the region 10.
@@
         %%Network 1by14
-        The network with 14 neurons, in Fig.~\ref{fig: M31_net_1by14}, is the first network which has no neurons with more than one region.
-        In a higher grid SOM, network pays more attention to smaller details.
+        The network with 14 neurons, in Fig.~\ref{fig: M31_net_1by14}, is the first network, that has no neuron to be occupied with more than one region.
+        In a higher grid SOM, network pays more attention to smaller details and differences in the input data.
         Therefore, since at least 14 neurons are needed to separate all the 10 regions in M31, we can conclude that some of the regions have very small differences.
-        In fig.~\ref{fig: regions in m31}, some the regions are grouped next to each other in the galaxy, which is the reason why some of the regions have vary similar input values.
+        Regions that are located in similar area in M31, like region 7 and 4 (see Fig.~\ref{fig: regions in m31}), are most likely show more similarity to each other.
         In Fig.~\ref{fig: M31_net_1by14}, the most right neuron is occupied by region 10.
         Two black colour between this region and the others indicates the high differences between this neuron and the other ones.
-        The region 10 is located in the bulge of M31, and its separation from other regions, which are mostly located around of the inner or outer rings, is due to the fact that most of the input values for this region is much higher than the other regions.
-        The region 8 occupies the most right neurons in this network, that suggests that this region has the most differences with the region 10.
+        The region 10 is located in the bulge of M31, and its separation from other regions, which are mostly located around the inner or outer rings, is due to the fact that most of the input values for this region is much higher than the other regions.
+        The region 8 occupies the most right neurons in this network, that suggests that this region has the most differences with region 10.
 
@@
         %What is going on in this section
+        \label{sec: inside_the_2_neurons}
         Using SOMs, we can identify hidden subgroups in our samples. 
@@
         %%% what regions' version shows and how it compares with the other one:
-        In Fig.~\ref{fig: cor_all}, all the PAHs features highly correlate with each other. 
-        Also, considering data from all M31 regions, there are very strong correlations between all the PAHs features and PACS~100~$\mu$m~, SPIRE 250 to 500~$\mu$m~emission, L$_{\rm DUST}$, L$_{\rm TIR}$, SFR, and metallicity.
-        However, in Fig.~\ref{fig: cor_cluster1},12.0 and 12.7~$\mu$m~ PAHs fluxes do not show any significant or strong correlation with PAH fluxes in other wavelengths or most other quantities.
-        The only exceptions are the strong correlation between PAH flux at 12~$\mu$m and dust luminosity, and between 12 and 12.7~$\mu$m PAH fluxes.
-        Since there are only 6 regions in the cluster, even one outlier in the data can causes the correlation coefficient become insignificant.
-        By removing the outlier, the correlations between 12.0 and 12.7~$\mu$m~ PAHs fluxes and the other quantities show themselves.
+        In Fig.~\ref{fig: cor_all}, which shows the Pearson correlation coefficients from data in all 10 regions, all the PAHs features highly correlate with each other. 
+        Also, there are very strong correlations between all the PAHs features and PACS~100~$\mu$m~, SPIRE 250 to 500~$\mu$m~emission, L$_{\rm dust}$, L$_{\rm TIR}$, SFR, and metallicity.
+        However, in Fig.~\ref{fig: cor_cluster1}, 12.0 and 12.7~$\mu$m~PAHs fluxes do not show any significant or strong correlation with PAH fluxes in other wavelengths or most of the other quantities.
+        The only exceptions are the strong correlation between PAH flux at 12~$\mu$m and L$_{\rm dust}$, and between 12 and 12.7~$\mu$m PAH fluxes.
+        Since there are only 6 regions in this cluster, even one outlier in the data may cause the correlation coefficient become insignificant.
+        By removing the outlier, the correlations between 12.0 and 12.7~$\mu$m~PAHs fluxes and the other quantities show themselves.
 
-        For the rest of the PAHs fluxes in Fig.~\ref{fig: cor_cluster1}, there are not any significant correlations with PACS~100~$\mu$m, L$_{\rm DUST}$, L$_{\rm TIR}$, SFR, or metallicity, too.
+        For the rest of the PAHs fluxes in Fig.~\ref{fig: cor_cluster1}, there are not any significant correlations with PACS~100~$\mu$m, L$_{\rm dust}$, L$_{\rm TIR}$, SFR, or metallicity, neither.
         They have correlations with SPIRE emission, but they are weaker than the ones with data from all regions.
-        Correlations between PAHs, features and SFR and L$_{\rm TIR}$  are well-studied~\citep[e.g.][]{Tielens08,Peeters04}. 
-        Many groups used PAHs features as a tracer of SFR by finding correlation between 
+        Correlations between PAHs features and SFR, and L$_{\rm TIR}$ are well-studied~\citep[e.g.][]{Tielens08,Peeters04}. 
+        Many groups used PAHs features as a tracer of SFR by finding correlations between 
         PAHs emission and SFR derived from extinction corrected \halpha~\citep[e.g.][]{Shipley16,Khramtsova13,Calzetti07}.
-        This correlation can be seen in Fig.~\ref{fig: cor_all}, when we considered the data from all regions, but not in Fig.~\ref{fig: cor_cluster1} considering the clustered data.
-        Further analysis shows that the absence of the correlation between PAHs features and SFR, is because of one outlier in data. 
-        When we disregard the outlier data, high correlation between 6.2 to 11.3~$\mu$m~PAHs features and SFR (and L$_{\rm TIR}$) appears again.
+        These correlations are seen in Fig.~\ref{fig: cor_all}, when we considered the data from all regions, but not in Fig.~\ref{fig: cor_cluster1} when considering the clustered data.
+        Further analyses show that the absence of correlations between PAHs features and SFR, is because of one outlier in data. 
+        When we disregard the outlier data, high correlations between 6.2 to 11.3~$\mu$m~PAHs features and SFR (and L$_{\rm TIR}$) reappear.
         Strong ant-correlation between 6.2 to 11.3~$\mu$m~PAHs features and RHI, stellar mass, \halpha, \sii, \oiii, and IRAC~5.6~$\mu$m~emission in Fig.~\ref{fig: cor_cluster1} had not be seen in Fig.~\ref{fig: cor_all}.
      %   In Fig.~\ref{fig: cor_cluster1}, 6.2, 7.7, 8.3, 8.6, and 11.3~$\mu$m~PAHs features show strong anti-correlations with RHI, stellar mass, \halpha, \sii, \oiii, and IRAC~5.6~$\mu$m~emission.
-        Anti-correlations between PAHs features and the \halpha, \sii, and \oiii~emission could be result of one the followings. 
-        The optical data are not corrected for dust extinction.
+
+        Anti-correlations between PAHs features and the \halpha, \sii, and \oiii~emission could be the result of one the followings. 
+        First, the optical data are not corrected for dust extinction.
         The PAHs features correlate with dust, and \halpha emission is sensitive to dust extinction.
-Therefore, more PAHs features, means more dust and less \halpha emission (The same for \sii~and \Oiii~emission).
-        Or it is the affect of observing choice, if the apertures are located in the edge of the regions we would expect too see more PAHs and less \halpha emission. %ehhhhh %%% reference?
-        The anti-correlation between 6.2 to 11.3~$\mu$m~PAHs features and RHI have been seen in other studies, too~\citep[e.g.][]{Dim15, Gordon08, Wu06}.
-        \cite{Wu06} discussed this ant-correlation could be the result of destruction of the PAHs due to the high amount of the harder radiation (thus higher RHI).
-        On the other hand, \cite{Gordon08} the harder radiation could make the photodissociation regions (PDRs) smaller.
-        The PAHs features are mostly coming from the PDRs that are surrounded by H {\sc II} regions, and their underlying continuum emission is from the H {\sc II} regions.
+        Therefore, more PAHs features, means more dust and less \halpha~emission (The same for \sii~and \oiii~emission).
+        Second, it is the effect of observing apertures.
+        If the regions are located in the edge of the H {\sc II} regions we would expect too see more PAHs and less \halpha~emission. %%% reference?
+        The anti-correlations between 6.2 to 11.3~$\mu$m~PAHs features and RHI have been seen in other studies, too~\citep[e.g.][]{Dim15, Gordon08, Wu06}.
+        \cite{Wu06} discussed these ant-correlations could be the result of destruction of the PAHs due to the high amount of the harder radiation (thus higher RHI).
+        On the other hand, \cite{Gordon08} argued that the harder radiation could make the photodissociation regions (PDRs) smaller.
+        The PAHs features are mostly coming from the PDRs that are surrounded by H {\sc II} regions, and the PAHs features underlying continuum emission is from the H {\sc II} regions.
         Therefore, the lower flux of the PAHs features could be the result of the smaller size of PDRs.
-        The later reason, which could also describe the anti-correlation between PAHs features and \halpha~emission, seems to be the more possible one. 
+        The later reason, which could also describe the anti-correlation between PAHs features and \halpha~emission, seems to be the more probable one. 
         %%% The anti correlation with stellar mass?!! with IRAC3?!!
 
-       Despite the fact that some of the (anti)-correlations in Fig.~\ref{fig: cor_cluster1} might have physical meaning, we have to remind that, we only used 6 regions to calculate these correlation coefficients.
-       Having 6 data points in the sample is not high enough to have a strong conclusion about the PAHs in M31.%%% it doesn't sound right:((
-        However, we can conclude that since the correlation coefficients derived from the clustered data (Fig.~\ref{fig: cor_cluster1}) varies from correlation coefficients derived from the data from the all regions (Fig.~\ref{fig: cor_all}), SOM separated a hidden cluster of the data, which their properties are different than the others.
+       Despite the fact that some of the (anti)-correlations in Fig.~\ref{fig: cor_cluster1} might have physical meanings, we have to mention that, we only used 6 regions to calculate these correlation coefficients.
+       Having 6 data points as a sample of the study is not high enough to have a strong conclusion about the PAHs in M31.%%% it doesn't sound right:((
+        However, we can conclude that since the correlation coefficients derived from the clustered data (Fig.~\ref{fig: cor_cluster1}) differs from correlation coefficients derived from the data from the all regions (Fig.~\ref{fig: cor_all}), SOM separated a hidden cluster of the data, which their properties are different than the others.
 %%Again eh!

### 2016-06-29 sections/R20.0.tex
V1

@@
 %----------------------------------------------------------------------------------------
- \section{2D SOMs}
- Although 1D networks are great to have a general idea about the data, they are not showing a whole picture. 
+ \section{Two dimensional self-organizing maps}
+ \label{sec: 2d_cluster}
+    Although 1D networks are great to have a general idea about the data, neurons in 1D maps have maximum two neighbours, which causes some limitation in the results.
+    In 2D networks, each neuron has two to six neighbours, which allowed them to to capture a whole picture of the complicated relations in the input data.
     Therefore, we created $10\times10$ 2D networks to study the data in details.
- Since in 1D SOMs, each neuron has maximum two immediate neighbours, 1D SOMs can't provide show complicated relations in data.
-However, 
-            \subsubsubsection{Subsets}
-            In subset 0 presented the derived values and values that had not been used to create any of derived values.
-            Fig.~\ref{fig: all_derived_ones} shows the SOM and the weight plane of each input data from subset 0.
-            Regions 4 and 7 are in the top left of Fig.~\ref{fig: all_derived_ones} and in the second neighbourhood of each other, with very bright light between their nodes which represents that weight of these nodes are similar to each other.
-            The positions of these two regions in the galaxy are really close and they both are on almost same distance from the star forming ring in galaxy.
-            Both of these regions are right on the edge of the star forming rings in the galaxy. 
-            Position of the region 3 on the SOM is close to the position of the regions 4 and 7, but with darker colour between the nodes. 
-            This region in M31 is close to regions 4 and 7 but on the outer side of the star forming ring.
+    As mentioned in previous sections, the size of SOMs are arbitrary and users must decide about it based on what their goals of using SOMs are.
+    In this section we chose $10\times10$ size despite that we knew, from the size of our input data, that most of the neurons would be empty.
+    Using 2D networks, we are mostly interested in the ability of the SOMs in showing underlying structure of the data rather than its clustering features.
     \import{../sections/image_texts/}{all.tex}
-            Regions 5, 8 and 6 are close to each other on the SOM.
-            These three regions are around the inner ring of the galaxy.
-            Since region 5 is right outside the inner rings whereas regions 6 and 8 are in inner part of the inner ring, this region has more distance and more weight from the regions 6 and 8.
-            Regions 1 and 9 are close to each other and in the end side of the star forming ring. 
-            Region 2 is more distant from other regions in the galaxy. 
-            However, it is right out side the star forming too. 
-            Therefore, its place in SOM somehow is close to the positions of the regions 1,3 and 9.
-            The weights between region 2 and the other three regions are relatively high, due to fact that the region 2 is basically placed on the opposite side of the galaxy. 
-            Region 10 is placed in the bulge of the galaxy, and its position on the SOM is isolated from all the other regions.
+    Fig.~\ref{fig: all_derived_ones} shows the 2D SOM of M31 data.
+    Similar to the Fig.~\ref{fig: M31_net_1by14}, all the 10 regions completely separated from each other in Fig.~\ref{fig: all_derived_ones}.
 
-            In order to analyse affect of any input data on the final SOM, we created SOMs from various subsets of data and compare their results with one another and with SOM created from all data listed in subset 0.
-            %%\subsection{Increasing dimension of input data one by one}
-            We started the analysis by creating SOMs using only PAHs data, and using all data from subset 0 except PAHs ones(Fig.~\ref{fig: PAHS_or_not_PAHs}). 
-            Then, we increased the dimension of PAH only data gradually by adding data from subset 0 to it, i.e.
-the first map in Fig~\ref{fig: inc_D_col3s} was created from PAHs data and H$\alpha$ emission, the second one was created from PAHs, H$\alpha$ emission and [\sii] continuum, and so on.
+    Regions 4 and 7 are in the top left of Fig.~\ref{fig: all_derived_ones} with very bright colour between their neurons, which presents that these two regions are very similar.
+    Considering the position of these two regions in M31 (Both of these regions are right on the edge of the star forming rings in the galaxy), similarity of these two regions were predictable.
+    Position of region 3 on the SOM is close to the position of regions 4 and 7, but with darker colour between the nodes. 
+    In Fig.~\ref{fig: regions in m31} it is clear that, this region in M31 is closer to regions 4 and 7 than any other region, but it is on the outer side of the star forming ring.
+    Regions 5 and 6 are in their second neighbourhood on the SOM, with a medium gray colour between them.
+    These two regions are around the inner ring of the galaxy.
+    Regions 8 and 6 are both in the inner ring of M31, but region 6 is in the region with more star forming activities, which could be the main reason for their relative distance in the SOM in Fig.~\ref{fig: all_derived_ones}.
 
-        \import{../sections/image_texts/}{col11by26.tex}
+    Regions 1 and 9 are close to each other, and in the same side of the star forming ring. 
+    However, region 1 is in an area of the galaxy with lesser diffuse \halpha~emission than region 9, that might be the reason for their distances in SOM.
+    Region 2 is more distant from other regions in the galaxy, and placed in the star forming ring.
+    However, similar to regions 1 and 4, region 2 is located in an area of the galaxy with less diffused \halpha~emission.
+    Therefore, place of region 2 in the SOM is more favoured towards regions 1 and 4. 
+    Region 10 is placed in the bulge of the galaxy, and its position on the SOM is isolated from all the other regions by a strip of a dark colours.
 
-         We then generated some sub-samples of the data based on the weight planes in the Figs.~\ref{fig: all_derived_ones} to~\ref{fig: subset7}.
-        We first removed data with larger weights (with darker colours) in most of the neurons, one at a time (see tables~\ref{tab: subset1} -~\ref{tab: subset4}).
-        For subset sample 1 from Table~\ref{tab: subset1}, we used all the values from subset 0 excluding data from stellar mass. 
-        We removed IRAC 5.7 $\mu$m; [\sii] continuum and [\oiii] continuum; PAH8.3 $\mu$m, PAH12.0 $\mu$m, PAH17.0 $\mu$m, [~\oiii] continuum, stellar mass and metallicity from subset 0, and generated subset samples 2 to 4, respectively (Tables~\ref{tab: subset2} to~\ref{tab: subset4}).
-        Table~\ref{tab: subset5} shows the list of data that were used in a subset sample 5, which is data from subset 0 except the fact that instead of the individual PAH fluxes we added them together and have total PAH flux.
-        For subset sample 6 (Table~\ref{tab: subset6}), we removed SPIRE 250 and 500~$\mu$m, and for subset sample 7 (Table~\ref{tab: subset7}) we removed [\sii] flux, SPIRE 250 and 500~$\mu$m and TIR emission from subset sample 5.
-        Figs.~\ref{fig: subset1} to~\ref{fig: subset7} show SOM and input data weight planes created from subset samples 1 to 7, respectively.
+    In order to analyse effects of any input data on the final SOM, in the following we created SOMs from various subsets of data.
+    We compare results of the subsets with one another and with SOM created from all data in Fig.~\ref{fig: all_derived_ones}.
 
-        The left side of the Fig.~\ref{fig: subset1} shows SOM results from Table~\ref{tab: subset1}. 
-        In the SOM map, regions 1 and 9 are closer to region 10. 
-        The regions 1 and 9 are the ones with lowest stellar mass, on the other side region 10 has the highest stellar mass. 
-        Since the stellar mass was one of the most distinct differences between these regions, removing stellar mass from input data reduced the distance between these regions.
-        Regions 5, 6 and 8 are in the same relative distance from each other, but they all are closer to the position of the region 10.
+    \subsection{Subsets}
+    \label{sec: subsets}
+            For analysing subsets, we creating SOMs by using only PAHs data, as well as using all data except PAHs ones (Fig.~\ref{fig: PAHS_or_not_PAHs}).
+             \import{../sections/image_texts/}{PAHS_or_not_PAHs.tex}
+            Comparing the SOM from all data in Fig.~\ref{fig: all_derived_ones} with the SOMs in Fig.~\ref{fig: PAHS_or_not_PAHs}, showed that the general position of regions in those networks are the same.
+            The region 10 is in one corner of the all three networks.
+            However, in Fig.~\ref{fig: all_derived_ones} and Fig.~\ref{fig: wt_pahs}, region 10 is isolated from the other regions, while in Fig.~\ref{fig: only_pahs}, region 10 is much less isolated and only shows complete dissimilarity with region 8.
+            Regions 9 and 10 are totally isolated in SOMs in Fig.~\ref{fig: wt_pahs}, but in Fig.~\ref{fig: only_pahs}, they are more similar to other regions.
+            In both SOMs in Fig.~\ref{fig: PAHS_or_not_PAHs}, there are dissimilarities between regions in M31 but in Fig.~\ref{fig: wt_pahs}, the colours are much darker than the ones in Fig.~\ref{fig: only_pahs}.
+            This indicates that there are more similarity between PAHs features from all 10 regions then the other input data.
+
+            We increased the dimension of input data in Fig.~\ref{fig: only_pahs} (PAH only data), gradually, by adding data from other quantities of galaxies to the input data. 
+            The order of adding data is the same as order of data in Fig.~\ref{fig: cor_all}, i.e.
+SOM in Fig~\ref{fig: inc_D_col3s}a was created from PAHs data and H$\alpha$ emission as input data, SOM in Fig~\ref{fig: inc_D_col3s}b created from PAHs, H$\alpha$ emission and [\sii] continuum as input data, and so on.
+            \import{../sections/image_texts/}{col3byall.tex}
+
+            SOM algorithm assigns random weight to each network, that causes the overall position of regions in networks (even with the same input data) changes in each run of the algorithm.
+            However, the position of each region regarding to other regions changes dramatically only because of the new sets of input data is given to the algorithm (assuming all the initial values for the run are intact).
+            In all SOMs in Fig~\ref{fig: inc_D_col3s}, region 10 is located in the corner of the SOMs, but in  Figs~\ref{fig: inc_D_col3s}a,~\ref{fig: inc_D_col3s}d,~\ref{fig: inc_D_col3s}g,~\ref{fig: inc_D_col3s}k, and ~\ref{fig: inc_D_col3s}l, it is placed in the left side of the SOMs and in the others it is in the right side of the networks.
+            In our discussion on differences between networks, we do not address the changes in the network due to initialization of the SOM algorithm and only consider the effect of changing the input data in the network.
+
+            Comparing Figs.~\ref{fig: inc_D_col3s}a to ~\ref{fig: inc_D_col3s}o shows that adding \halpha~emission data to PAHs features causes regions 9 and 10 become isolated. 
+            Increasing dimension of the input data makes region 10 more isolated.
+            The relative position of regions 4 and 7 stays the same with increasing the input data. 
+            Adding SPIRE 350, 500~$\mu$m emission and L$_{\rm dust}$ do not have any adequate effect on the networks.
+            Stellar mass, total gas mass, dust mass and RHI data alternate the distances between neurons effectively, but it seems that adding SFR, L$_{\rm TIR}$ and metallicity data revoke those changes.
+
+            We generated other subsets of the data based on the results in Figs~\ref{fig: inc_D_col3s} to study effects of the input data on SOMs, further.
+            Subset 1, that are listed in Tab.~\ref{tab: subset1}, includes all the inputs data except data from stellar mass.
+            Tab.~\ref{tab: subset5} is the list of data that were used in a subset 2, which includes all data except the fact that instead of the individual PAH fluxes we added them all together and have total PAH flux.
+            For subset 3 ( in Tab.~\ref{tab: subset6}), we removed SPIRE 250 and 500~$\mu$m from subset 2.
+            Figs.~\ref{fig: subset1} --~\ref{fig: subset6} show SOMs that are created by data from subsets 1 to 3, respectively.
+            The rest of the subsets are discussed in the Appendix.~\ref{sec: app_2d_soms_SOMN}.
+
+            The results from Table~\ref{tab: subset1} is shown in Fig.~\ref{fig: subset1}. 
+            In this SOM compare with the SOM from all the data in Fig.~\ref{fig: all_derived_ones}, regions 1 and 9 are closer to region 10. 
+            Regions 1 and 9 are the ones with lowest stellar mass values, and region 10 has the highest stellar mass value among those 10 regions. 
+            Since the differences in the amount of the stellar mass were one of the most distinct differences between these three regions, removing stellar mass from input data reduced the distance between these regions.
+            Regions 5, 6 and 8 are in the same relative distance from each other as in Fig.~\ref{fig: all_derived_ones}, but they all are closer to the position of the region 10.
             Distance between regions 2 and 3 is reduced but in the meantime the colour between them became darker.
@@
 
-%\subsubsection{subset4}
+            Changing from separate values for each PAH features to a single value for the total PAHs caused small changes to the SOM map in Fig.~\ref{fig: subset5} compare to the one in Fig.~\ref{fig: all_derived_ones}.
+            Distance between the relative position of regions 6 and 8 increased significantly, while the position of region 2 moved closer to the positions of regions 4 and 7.
+            The winner neurons for regions 3 and 5 moved towards each other, but the colours between them became much more darker.
 
-        Changing from separate value for each PAH to a single value for the total PAH, caused small changes to our the SOM map (Fig.~\ref{fig: subset5}). 
-        Distance between the position of the regions 6 an 8 increased significantly, while the position of region 2 moved closer to the positions of the regions 4 and 7.
-        The winner neurons for the regions 3 and 5 are moved towards each other, but the colours between them became much more darker. 
-%\subsubsection{subset5}
             \import{../sections/tables/}{subset5.tex}
@@
 
-        Fig.~\ref{fig: subset6} shows the results from Table~\ref{tab: subset6}, which includes all the data from Table~\ref{tab: subset5} except fluxes from SPIRE 250 and 500~$\mu$m.
-        For most of the regions, although we see the changes in the positions, the colours between neurons changed, too. 
-        Which we can conclude that these changes are because of the different initial values in the weights.
-        However, the distance between the positions of the regions 4 and 2 increased.
-        The same happened for distance between regions 7, 3 and 6.
-        In both cases, flux values in SPIRE 250 and 500~$\mu$m for these regions are similar to each other, and removing these two parameters from input moved the positions of the regions further. 
-%\subsubsection{subset6}
+            Fig.~\ref{fig: subset6} shows the SOM generated from data that are listed in Tab.~\ref{tab: subset6}, which includes all the data from Tab.~\ref{tab: subset5} except SPIRE 250 and 500~$\mu$m emission.
+            Although for most of the regions we see the changes in their positions, the colours between neurons changed, too. 
+            %Therefore, we can conclude that these changes caused by the differences in the initial assigned weights.
+            The distance between the positions of the regions 4 and 2 are increased.
+            The same happened for distances between regions 7, 3 and 6.
+            In both cases, SPIRE 250 and 500~$\mu$m emission of these regions are similar to one another, and removing these two parameters from input data moved the positions of the regions further from each other.
             \import{../sections/tables/}{subset6.tex}
@@
 
-%\subsubsection{subset7}
+            %Subsets, that some of them  are studied in this section, can be used to learn about the effect of each input on the map as well as they can be used to predict unobserved quantities in the galaxy.
             \subsubsection{Prediction observing data using M31}
 
-        %%What about M101; Is it going to behave in the same way! how corr matrix, look like for M101 data?
-   \subsection{ Validating networks using M101 data}
-      %%% 10x10 networks using subsets of data to create networks; make prediction based on results;
-      %%%% 10x10 checking data with M101 data
-      %%% Combine M31 + M101 data to make new prediction
+                On SOMs we can see relations between the input data from each region regarding to the other regions.
+                These relations are shown by colour in SOMs, when white is 100 per cent similarity and black is 0 per cent similarity.
+                Therefore, we have the probability distribution of quantities of each values given data from other regions.
+                We can use these probability distribution to estimate missing data for regions.
+
+                To demonstrate this conclusion, we assumed the stellar mass value for region 1 is unknown.
+                Therefore, we need a SOM that are generated from all the inputs data for all regions except stellar mass (e.g subset 1 in Fig.~\ref{fig: subset1}).
+                \import{../sections/image_texts/}{sim_subset1.tex}
+                We found the shortest path between region 1 and the other regions and measure their relative similarity ($p_j$).
+                Assuming the maximum similarity is 100 per cent between two neurons (white colour), we multiply the similarity values along the shortest path between two regions to find $p_j$ between region 1 and the other regions (Fig.~\ref{fig: sim_subset1}).
+                In both Figs.~\ref{fig: subset1} and ~\ref{fig: sim_subset1} are clear that region 1 shows more similarity to regions 2 and 9 than the others and the most dissimilarity to region 8.
+
+                We measured probability of stellar mass given other quantities of the region 1 ($P(m_1\mid \forall_1)$) using Equation~\ref{equ: prob1}.
+                \begin{equation}
+                \label{equ: prob1}
+                    P(m_1\mid \forall_1) = \sum_{j=2}^{10}p_j*m_j
+                \end{equation}
+                Where $m_1$ is the stellar mass of region 1 and $m_j$ is the stellar mass of region j (any other region).
+                We estimated the stellar mass to be $\sim1377$~M$\odot$ which is 10 per cent less than the observed values.
+                This type of the prediction from SOM networks can be used to predict observation values in observational proposals or can be used in pre-phase studies of the big missions such as the James Webb Space Telescope (JWST) and LLST.
+
+    \subsection{Validating networks using M101 data}
+    Another application of SOM for nearby galaxies is that to apply the trained networks on the data from other galaxies in order to prediction properties of the regions in them. %%eh
+    As an example of this application, we generated an SOM using data from M31 that held in common with M101 data (Fig.~\ref{fig: subset9}a). 
+    In this SOM, the same as the others, region 10 is separated from other regions in M31.
+    Regions 7 and 4 are close to each other with very light colours between their neurons, and the same as the other SOMs regions 6, 8, and 5 are close to each other, but with medium dark colour between them.
+    \import{../sections/image_texts/}{subset9.tex}
+
+    We applied the SOM created using M31 data in Fig.~\ref{fig: subset9}a on M101 data (Fig.~\ref{fig: subset9}b).
+    Region 6 in M31 and region 2 in M101 both occupied the same neuron in the network in Fig.~\ref{fig: subset9}, which immediately suggest that these two regions have similar properties. 
+    Region 2 in M101 is a bright H {\sc II} region that is located at the end of the one of the M101 spiral arm (see Fig.~\ref{fig: regions in m101}). 
+    Region 6 in M31 is located near the inner ring of the galaxy (see Fig.~\ref{fig: regions in m31}).
+    Both regions have relatively low amount of PAHs emission and medium amount of the SFR regarding the other regions in the galaxy, which makes them very similar regions.
+
+    Region 7 in M101 is located in the nucleus of the galaxy and have relatively higher quantities than the other regions.
+    This region is located in the top right side of the network in Fig.~\ref{fig: subset9}, which is close to location of region 10 in the network.
+    Since the bulge of a spiral galaxy has different environment from its nucleus, region 7 in M101 and region 10 in M31 are not occupied the same neuron in the SOM, and have a medium grey colour between their neurons.
+
+    Region 1 in M101 is located near the nucleus of M101 (see Fig.~\ref{fig: regions in m101}), but has considerably lower values in all the quantities than the ones in region 7.
+    The lower values for fluxes of the PAH features, and relatively moderate amount of the SFR caused this region places between region 4 and 5 of M31 in the network. 
+    Fig.~\ref{fig: subset9}b shows that region 4 in M101 is separated itself from other regions and located between region 9 and 10 in M31.
+    \cite{Gordon08} showed that this region is a diffuse nebula in M101, with high amount of fluxes of PAH features. 
+    This region also shows a high amount of the SFR and the stellar mass, which describes why the location of region 4 from M101 in the SOM is close to regions 9 and 10 from M31.
+
+    In this section we showed that we can use networks that are created by data from nearby galaxies, to study the properties of other galaxies in a fast way.
+    We should note that we created our networks using values for 26 quantities from 10 regions in M31, which does not consider as a "big sample".
+    Increasing dimension of the data and the number of regions would help to have more reliable networks.

### 2016-06-29 sections/app_2d.tex
V1

@@
 \section{2D SOMs of subsets}
-        \import{../sections/image_texts/}{col3byall.tex}
+\label{sec: app_2d_soms_SOMN}
+
+        We removed IRAC 5.7 $\mu$m; [\sii] continuum and [\oiii] continuum; PAH8.3 $\mu$m, PAH12.0 $\mu$m, PAH17.0 $\mu$m, [~\oiii] continuum, stellar mass and metallicity from subset 0, and generated subset samples 2 to 4, respectively (Tables~\ref{tab: subset2} to~\ref{tab: subset4}).
         In Fig.~\ref{fig: subset2}, which is the SOM results from data listed in Table~\ref{tab: subset2}, distance between positions of the region 7, and region 3 is much larger compare to the one in Fig.~\ref{fig: all_derived_ones}.
@@
         Therefore, removing flux from IRAC 5.7 $\mu$m removed the one source of similarity in these two regions and they moved further from each other in the SOM.
+        For subset sample 7 (Table~\ref{tab: subset7}) we removed [\sii] flux, SPIRE 250 and 500~$\mu$m and TIR emission from subset 2 (~\ref{tab: subset5}).
         The positions of the regions 2 and 9 are closer to each other, but the weight distance between them is much higher (the colours between them are became almost black). 

### 2016-06-29 sections/data0.0.tex
V1

@@
 
-\section{DATA}
+\section{Sample of study}
+\label{Sec: data_SOMN}
 
-We gathered data from 10 regions in M31 (Fig.~\ref{fig: regions in m31})  and 8 regions in M101 (Fig.~\ref{fig: regions in m101})  inputs for SOM maps.
+We gathered data from 10 regions in M31 (Fig.~\ref{fig: regions in m31}) and 8 regions in M101 (Fig.~\ref{fig: regions in m101}) as inputs for SOMs.
 We chose those specific regions due to availability of the PAHs data for them.
-Besides PAHs data, for each galaxy, we chose spectroscopy and photometry data as well as their derived properties, such as SFR, stellar mass, dust luminosity (L$_{\rm DUST}$) and mass, metallicity, and gas mass.
-Table~\ref{tab: data} shows list of the data and their unit for both M31 and M101.
-We divided each values by the area of their region (in arcsec$^2$), to be able to compare values in both galaxies without being worried about their distances.
-The resolution of the data varies from less than 1$\arcsec$ to $60\arcsec \times 90 \arcsec$.
-Any attempt to match the PSF for these range, causes to use all the spectroscopic data.
-Besides the convolution methods conserve the flux per area.
-Therefore, we did not do any PSF matching in this paper and we used data in their original resolutions.
+Besides PAHs data, for each galaxy, we chose spectroscopy and photometry data as well as their derived properties, such as SFR, stellar mass, dust luminosity (L$_{\rm dust}$) and mass, metallicity, and gas mass.
+Table~\ref{tab: data} shows the full list of the data and their unit for both M31 and M101.
+We divided each values by the area of their region (in arcsec$^2$), to remove the distance factor from the data compare values of quantities in both galaxies.
+Since the resolution of the data varies from less than 1$\arcsec$ to $60\arcsec \times 90 \arcsec$, any attempt to match the resolutions causes loosing all the information in some of the input data (e.g.
+the spectroscopic data).
+On the other hand, in this project we used flux (or value of the quantities) per area as inputs of SOMs, which the convolution methods conserve it~\citep{Aniano12}.
+Therefore, we did not perform any resolution matching in this paper and used data in their original resolutions.
 
@@
   \begin{figure}
-    \subfloat[MIPS24 image of M31, with position of 10 regions.\label{fig: regions in m31}]{
+    \subfloat[MIPS 24~$\mu$m image of M31 from~\cite{Gordon06}, with position of 10 regions \label{fig: regions in m31}]{
       \includegraphics[width=0.5\textwidth]{../images0.0/M31/M31.png}
@@
     \hfill
-    \subfloat[IRAC1 image of M101, with position of our 8 regions.\label{fig: regions in m101}]{
-      \includegraphics[width=0.5\textwidth]{../images0.01/M101/M101.png}
-    }
-    \caption{Position of the data in M31 (up) and M101 (down).}
+    \subfloat[IRAC 3.6~$\mu$m image of M101~\cite{Dale09}, with position of 8 regions.\label{fig: regions in m101}]{
+      \includegraphics[width=0.5\textwidth]{../images0.01/M101/M101.png}}
+    \caption{Position of regions that the input data for SOM that obtained from there in M31 (up) and M101 (down).}
     \label{fig:dummy}
@@
 %M31 data 
-%%%%% Sahar: More detail?
+%%%%% Sahar: More detail, right?
     \subsection{M31 data}
+     \label{Sec: data_M31_SOMN}
 
      The 10 regions in M31 were chosen due to availability of the PAH data for them. 
-     \cite{Dim15} studied PAH for those regions using {\it Spitzer}/Infrared Spectrograph\citep[IRS,][]{Houck04b} observations. 
-     They used {\tiny PAHFIT IDL} tool~\citep{Smith07b} and measured fluxes and equivalent widths of PAH features as well as atomic line features.
-     For spectroscopy part of our sample, we utilized their measured fluxes for PAH lines. 
-     \cite{Dim15} also reported metallicity of these regions (using results from \cite{Sanders12} for most regions), which e used them in our input sample.
-     We used radiation hardness index (RHI) instead of flux of individual atomic line, since they were only calculate the upper limit flux for most of the lines in most of the regions.
+     \cite{Dim15} studied PAH for those regions using {\it Spitzer}/Infrared Spectrograph~\citep[IRS,][]{Houck04b} observations. 
+     They used {\sc PAHFIT IDL} tool~\citep{Smith07b} and measured fluxes and equivalent widths of PAH features as well as atomic line features.
+     %For spectroscopy part of our sample, we utilized their measured fluxes for PAH lines. 
+     \cite{Dim15} also measured metallicity and of radiation hardness index (RHI) for these 10 regions.
+     We used the measured fluxes for PAHs featured, metallicity and RHI of each region as an input for SOMs.
 
-     For photometry part of the sample, we used data from \GALEX FUV and NUV channels~\citep{Martin05}, \halpha, [\sii] continuum and [\oiii] continuum emission~\citep{Massey07}, IRAC channels 1 to 4~\citep{Barmby06}, MIPS24 and 70~$\mu$m~\citep{Gordon06}, PACS100 and 160~$\mu$m and SPIRE250, 350, and 500~$\mu$m~\citep{Fritz12}.
-     We changed units of all our data to Wm$^{-2}$ to be the same unit as PAH fluxes.
-     We used $^{12}$CO (J:$1\rightarrow0$) line~\citep{Nieten06} and the atomic gas (H\,{\sc I}) 21~cm emission from \cite{Chemin09}.
-     We also utilized SFR(FUV + 24$\mu$m), stellar mass, total gas mass, and total infrared (TIR) luminosity (L$_{\rm TIR}$) data from \cite{Rahmani16}, and L$_{\rm DUST}$ and mass data from \cite{Draine14}.
+     We used \GALEX FUV and NUV channels~\citep{Martin05}, \halpha, [\sii] narrow badn and [\oiii] narrow band~\citep{Massey07}, IRAC channels 1 to 4~\citep{Barmby06}, MIPS24 and 70~$\mu$m~\citep{Gordon06}, PACS100 and 160~$\mu$m and SPIRE250, 350, and 500~$\mu$m~\citep{Fritz12} emission for photometry part of the sample.
+     We changed units of all fluxes to Wm$^{-2}$ to be the same unit as PAHs fluxes.
+     $^{12}$CO (J:$1\rightarrow0$) line~\citep{Nieten06} and the atomic gas (H\,{\sc I}) 21~cm emission from~\cite{Chemin09} were added to the input data. 
+     For derived values, we utilized SFR(FUV + 24$\mu$m), stellar mass, mass of molecular clouds, mass of atomic gas (H\,{\sc I}), total gas mass, and total infrared (TIR) luminosity (L$_{\rm TIR}$) data from \cite{Rahmani16}, and L$_{\rm dust}$ and mass data from \cite{Draine14}.
 
     \subsection{M101 data}
-     For M101 galaxy, we used PAH fluxes which had been measured using {\tiny PAHFIT IDL} tool and reported in \cite{Gordon08}.
+    \label{Sec: data_M101_SOMN} 
+     For M101 galaxy, we used PAH fluxes which had been measured using {\sc PAHFIT IDL} tool and reported in \cite{Gordon08}.
      We also added their measurement of metallicity and RHI for these regions to our sample.
      We used data available on NED~\footnote{The NASA/IPAC Extragalactic Database (NED) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.} website to gather our photometry data of M101.
-     We chose data from \GALEX FUV and NUV channels~\citep{depaz07}, IRAC channels 1 to 4, MIPS~24 and 70~$\mu$m~\cite{Dale09}, and  PACS~100 and 160~$\mu$m and SPIRE250, 350, and 500~$\mu$m~\cite{Kennicutt11}.
-     Same as M31 data, we used $^{12}$CO (J:$1\rightarrow0$) line~\citep{Helfer03} and the atomic gas (H\,{\sc I}) 21~cm emission from \cite{Walter08} data.
-     SFR(FUV + 24$\mu$m), stellar and total gas map were calculated followed method described in \cite{Rahmani16} to create these maps.
+     We chose data from \GALEX FUV and NUV channels~\citep{depaz07}, IRAC channels 1 to 4, MIPS~24 and 70~$\mu$m~\cite{Dale09}, and  PACS~100 and 160~$\mu$m and SPIRE250, 350, and 500~$\mu$m emission from~\cite{Kennicutt11}.
+     The Same as M31 data, we used $^{12}$CO (J:$1\rightarrow0$) line~\citep{Helfer03} and the atomic gas (H\,{\sc I}) 21~cm emission from \cite{Walter08} data.
+     SFR(FUV + 24$\mu$m), stellar and total gas mass map were calculated using the same methods that M31 data were derived in \cite{Rahmani16}.
+
+      Some of the correlations between some wavelengths and properties of galaxies are well-known.
+     For example, \citep{Rahmani16} used IRAC1 band emission to calculate the stellar mass, or FUV, NUV and MIPS24 emission to measure the SFR values. 
+     To make sure that we wouldn't use some of the observed data as an input data in various forms, we removed all the observed data, that were used to calculate these properties from the input sample.
+     We used these sample as the main input for creating SOMs.
+     Fig.~\ref{fig: cor_all} shows Pearson correlation coefficients with a confidence level of $95\%$ for the input data.
+
+      \begin{figure}
+                \centering
+                \includegraphics[width=0.5\textwidth]{../images0.01/cor_plots/M31_all_derived_ones_core_plot_for_paper.pdf}
+            \caption{Pearson correlation coefficients with a confidence level of 95$\%$ for all the in the subset 0.
+The colours show the Pearson correlation coefficients where 1 means highly correlated and -1 is highly anti-correlated quantities.
+The non-significant correlations were left empty.}
+            \label{fig: cor_all}
+        \end{figure}

### 2016-06-29 sections/intro0.0.tex
V1

--- 2016-01-11 sections/intro0.0.tex
@@
 %----------------------------------------------------------------------------------------
-\section{Introduction}
-% ideas about science of paper will add the them at the end
+\section{Introduction} %%( I am not really happy with this introduction but it is the best I can have for now:/ )
+%General information about galaxies %(Maybe it is too generic?!!)
+Inside each galaxy, there are millions of stars and large amount of dust and gas, which all affect on each others' formation, evolution and extinction.
+Galaxies are an active and complicated systems, that are constantly changing.
+There are extensive amount of studies about correlations between galaxies' emission and their physical properties, both observationally and theoretically %(Some references here). 
+These studies expands our knowledge of the underlying processes in formation and evolution of galaxies every day, but the details of how these process work are still undetermined.
 
-% maybe a little bit about PAH and other properties of nearby galaxies
+% Nearby galaxies and their importance 
+Nearby galaxies play an important role in learning about galaxies' formation and evolution.
+These galaxies are close enough to be able to observe various regions inside them in details.
+As a result, many studies are devoted to find relations between physical properties of the galaxies in both spatially resolved regions and galaxies as a whole%(Some more references here)
+, and many others use these results in analyzing data from high-redshift galaxies. %(Some more references here)
+The amount of data that is acquired from nearby galaxies is increasing daily.
+Advances in technology helps to both observe and store enormous amount of data from sky.%The sky?! 
+Telescopes and surveys gather data from nearby galaxies in variuse wavelengths and from these data we can measure physical properties of galaxies (e.g.
+stellar mass, star formation rate (SFR), dust mass, gas mass)~\citep[e.g.][]{Calzetti07,Dale09,Eskew12}.
 
-% data mining in general?ANN?
+% A little bit about M31 and previous studies in M31.
+The Andromeda galaxy (M31), with a distance of $\sim$0.78~Mpc~\citep{McConnachie05}, is the closest spiral galaxy to the Milky Way.
+Images of this galaxy provide us a detail view of inside of a spiral galaxy from distance.
+M31 data was a target of many telescopes (e.g.
+{\it Hubble} \citep{Dalcanton12}, \Spitzer\citep{Wener04}, \Herschel\citep{Pilbratt10} space telescopes) and was a subject of many more studies \citep[e.g.][and references therein]{Barmby06, Gordon06, Azimlu11, Sanders12, Dim15, Rahmani16}.
+
+\cite{Barmby06} used data from Spitzer Infrared Array Camera \citep[IRAC;][]{Fazio04} to show evidence of Polycyclic Aromatic Hydrocarbons (PAH)s in interstellar medium (ISM) of M31.
+Using the mid-IR data from Multiband Imaging Photometer for Spitzer (MIPS), \cite{Gordon06} studied the morphology of the dust in M31.
+\cite{Azimlu11} and \cite{Sanders12} catalogued and studied H {\sc II} regions of M31.
+\cite{Draine14, Mattsson14, Viaene14, Smith12} and~\cite{Fritz12} used \Herschel data to study dust in the ISM of the galaxy.
+Properties of the current stars in the galaxy were studied by~\cite{Tamm12} and~\cite{Massey07}. %%%And some from PHAT survey
+\cite{Rahmani16, Ford13} and \cite{Tabatabaei10} measured the SFR in M31 in order to study star formation laws, and \cite{Dim15} and \cite{Kapala15} used spectroscopic data of the galaxy to study PAHs and other line emissions in the ISM.
+
+Although all these studies measured some properties of M31, or answered specific scientific questions about this galaxy, we still do not have a complete picture of undergoing processes in the galaxy.
+The amount of the observed data and measured quantities of M31 makes this galaxy a suitable target for a knowledge discovery and data mining study.
+Knowledge discovery and data mining methods are designed to extract hidden information from data and are tested in many astronomical studies.
+However, to the best of our knowledge, this study is the first study that uses a data mining method on data from nearby galaxies. %%% ehh
+
+% data mining and clustering in general; when we have so many data and we want to map them
+\cite{Ball10} wrote an extensive review of data mining and machine learning, and their usages in astronomy.
+A data mining algorithm learns about data from sets of trainings, which can be supervised or unsupervised.
+The supervised trainings refer to methods, that use examples of the desired output to learn about input data and are valuable tools to classify data with known target values.
+On the contrary, the unsupervised methods train without any prior knowledge of output results. 
+They solely work based on the underlying structure of input data.   
+The unsupervised methods are very useful tools in knowledge discovery studies on input data, which we do not have any insight of them (or when we want to make sure that we did not miss any valuable information in our previous studies).
+%%% ehh to after or part.
+
+%SOM
+One the most tested methods of data mining in astronomy is the artificial neural networks (ANNs)~\citep[e.g.][and references therein]{Hossein12, Hossein14,Hossein16,Ellison16a}.
+ANNs are designed to work in the same way that the neurons work in a human mind.
+They are networks of interconnected neurons (nodes), which all of the connections are weighted.
+These networks are used to study about nonlinear and complex relations between input and output data.
+%These relations can be applied to the new sets of data with similar feature
+
+One of the most well-known unsupervised neural network in astronomy is a Kohonen self-organizing map (also called self-organizing map, or SOM).
+SOMs map and visualize a complex and nonlinear high dimension data~\citep{Kohonen82} and show simple geometrical relationships in non-linear high dimensional data~\citep{Kohonen98}.
+The result of a SOM is a 1D or 2D network of neurons, which shows the positions of clusters and their relative distance.
+Since 1990s, many studies utilized SOMs for object classification and clustering (e.g.
+classifying quasars' spectra, star/galaxy classifications, gamma-ray bursts clustering and classification of light curves), and photometric redshift estimations~\citep[e.g.][]{Odewahn92, Hernandez94, Murtagh95, Maehoenen95,Scaringi09,Geach12,Fustes13,Meusinger16,Rahmani16b} %%% Why I cannot add submitted in front of the high-z paper
+
+% other Unsupervised methods
+The purpose of this project is to have a new insight into nearby galaxies using M31 data with focusing on relations between PAHs and other properties of the galaxy.
+To fulfill this purpose, an unsupervised data mining method is the most suitable choice. %%eh  
+K-means algorithm, SOMs, and hierarchical clustering are main unsupervised methods that are used in astronomical studies~\citep[e.g.][]{DAbrusco12, Aycha16}. %%add one or two more
+
+For both K-means and SOM algorithms, the user must define the number of clusters, and the algorithms decide how to separate the data into desired number of the clusters.
+In the hierarchical clustering method, the user must define dissimilarity between the groups, and the algorithm combines (or divides) existing groups based on their dissimilarity and creates a hierarchical structure.
+Comparing SOMs, K-means and hierarchical clustering shows that in some cases hierarchical clustering method miss-classifies the data~\citep[][and references therein]{Mangiameli96}.
+We chose SOM method over K-means due to the fact that SOMs not only clusters data, but also shows similarity and dissimilarity between each cluster.
+Therefore, we can cluster our sample data and study the underlying structure of data, simultaneously.
+
+%this project 1 M31 and its extensive data we do not have any SOM in nearby galaxies
+In this project we apply SOM algorithm on M31 data, and trained 1D and 2D networks.
+Using smaller size networks we study the properties of the clusters and investigate relations between PAHs features with other features in M31.
+We create 2D SOMs from subsets of data as well as all available data, which helps us to understand the effect of each input in the position of the clusters in the SOM, which leads to prediction of the unmeasured quantities in a galaxy.
+Assuming that all the spiral nearby galaxies have similar properties, we apply 2D trained networks on data from the Pinwheel Galaxy (M101), which is another spiral nearby galaxy. 
+If our hypothesis is correct, we should be able to see that regions in M31 and M101 with the same positions in the SOM have the same properties.
+
+In Section $\S$~\ref{Sec: data_SOMN}, we present the sample data from M31 and M101, that we use in this study. 
+We describe the SOM method in Section $\S$~\ref{sec: method}. 
+The results of the 1D SOM networks and studying PAHs in M31 is presented in Section $\S$~\ref{Sec: 1d_cluster}.
+In Section $\S$~\ref{sec: 2d_cluster}, we present the result of 2D SOM networks and how we use them to extract information about other galaxies.
+In Section $\S$~\ref{sec: summary}, we summarize our results and discuss potential future work in this subject.
+
+%SOM in Astronomy continued.
+% Large spectroscopic surveys have made available integrated spectra of millions of galaxies.
+% These integrated spectra combine the light of billions of individual stars and nebulae within a galaxy, and
+% finding patterns and common characteristics between galaxies can be a complex task.
+% \citet{In12} introduced a new clustering tool based on the SOM method for analyzing these large datasets.
+% They used $\sim 60000$ spectra from the Sloan Digital Sky Survey \citep[SDSS;][]{Abazajian09} to test their tool, and created very large SOMs to analyze the type of spectra/objects.
+% They also generated SOMs from quasars' spectra in order to find unusual types of spectra. 
+% Later, \citet{Meusinger16} used these SOMs and updated data from SDSS and other surveys to find a new class of quasars.
+% The other application of SOMs is to find outliers or errors in the data.
+% \citet{Fustes13} produced a package based on SOM to classify spectra from the GAIA survey that were previously classified as ``unknown'' by the SDSS pipeline.
+This package can recognize an astronomical object from instrumental errors, and then classify the object based on its spectrum.
+
+%Compare diff methods and say why we chose SOM!
+
+%supervised and unsupervised network

### 2016-06-29 sections/method0.0.tex
V1

--- 2016-01-27 sections/method0.0.tex
@@
  \label{sec: som}
-
- Kohonen Self organizing map (or self organizing map, SOM) is an unsupervised neural network for mapping and visualizing a complex and non linear high dimension data introduced by~\citep{Kohonen82}. 
- The SOM is a technique that shows a simple geometry relationship of a non-linear high dimension data on a map \citep{Kohonen98}.
- The SOM is a clustering method which reduces the dimension of data to lower dimensions usually 1 or 2D while preserving topological features of the original data.
- Results of SOM contains nodes (usually hexagonal ones) that arranged in 1D or 2D arrays.
-
- Each nodes may contain one or more samples from input data and distance between nodes represents similarity or dissimilarity of underlying samples. 
- In the way that similar data are closer together in the array and the further nodes go from each other, the more dissimilarity appears between their samples.
- %Sahar_self_notes: maybe "some" is better instead of one or more
- Moreover,a weight vector ``\boldit{W}" with same dimension of the input data associates with each node which will be change during the process and has a key factor in a position of nodes in the map.
-
- \cite{Geach12} presented the application of the SOM and demonstrate the algorithm of the SOM in detail.
-In this section we are going to talk briefly about the algorithm of the SOM, how we create our maps and a test model which will help to interpret our results.
-
- \subsubsection{Algorithm of SOM} 
- \label{sec: algorithm}
-     Assuming we have a data set which contains vectors, \boldit{V} $\in \Re^n$ and we want to map them on S1 by S2 map. 
-     We start by creating S1 $\times$ S2 empty neurons. 
-     The initial arrangement of these neurons depends on a map's topology provided by user.
-     Since the topology of the map does not have any affect on the final result, we chose hexagonal topology which is the default topology for SOMs.
-     Then, we assign a random weight vector \boldit{W} $\in \Re^n$ to each node.
+ The SOM is a clustering method which reduces the dimension of data to lower dimensions, while preserving topological features of the original data~\citep{Kohonen98}. 
+ The results of the SOM are shown with a map of neurons.
+ Each neuron has a fixed position in the map, and may contain one or more samples from input data, \boldit{V} $\in \Re^n$.
+ A weight vector,~\boldit{W} $\in \Re^n$, with the same dimension as the input data is associated with each node and will be varied during the training process.
  The process of creating SOM, happens over series of $N$ iterations.
-     During each iteration the weight vectors might change according to the Kohonen learning rule (equation~\ref{equ: weight adj}). 
-      In each iteration:
-     \begin{enumerate}
-        \item Choose a random vector from our data set.
-        \item Calculate the euclidean distance for each node j as  $D_j^2= \sum_{i=0}^{i=n} (V_i - W_i)^2$, and find a neuron with ``$D_{j_{min}}$".
+ In each iteration, the algorithm calculates the euclidean distance for each node j as  $D_j^2= \sum_{i=0}^{i=n} (V_i - W_i)^2$, and finds a neuron with ``$D_{j_{min}}$". 
  This neuron is the winner node and is calling Best Matching Unit (BMU). 
-        \item  Compute the radius of the neighbourhood of the BMU to find nodes within this radius.
-The weight vectors of these nodes will be affected in the next steps.
-This value is arbitrary and initially can be set to be as high as half of the SOM size and then it decades exponentially over each iteration:
-        \begin{equation}
-            r^t_{BMU} = r^0_{BMU}e^{(-t/\tau)}
-        \end{equation}
-        where $\tau$ is a decay constant and usually set to be the same as number of iterations, $N$.
-$r^0_{BMU}$ and $r^t_{BMU}$ is the radius of the neighbourhood at 0th and $t$th iteration, respectively.
-        \item Change the weight vectors of the BMU and all the nodes within r(t) as:
+ The weight vectors in the neighbourhood of BMU will change according to the Kohonen learning rule (equation~\ref{equ: weight adj}). 
   \begin{equation}
@@
  \end{equation}
-        where $L(t) = L_0 e^{(-t/\tau)}$ is the learning factor which prevents divergence of the SOM and $R(t)=exp(-\frac{D_j^2}{2r^t_{BMU}})$ is the influence rate.
-$R(t)$ determines how weight of nodes in the neighbourhood of BMU will change.
-        \item  Repeat these steps for $N$ times.
-     \end{enumerate}
+where $L(t) = L_0 e^{(-t/\tau)}$ is the learning factor, which prevents the divergence of the SOM and $R(t)=\exp(-\frac{D_j^2}{2r^t_{BMU}})$ is the influence rate, which determines how the weight of each node will change.
+Values for number of neurons, L(t) and R(t) are arbitrary. 
+~\cite{Geach12} and \cite{Rahmani16b} demonstrate the algorithm of the SOM in more details.
 
-     In order to create SOM, we used {\tiny MATLAB} neural network toolbox~\citep[ NEWSOM,][]{matlabtolbox}.
-     {\tiny MATLAB} code, works in two phases. Phase one is the ``ordering phase". 
-     This phase starts with maximum neighbourhood distance (which is initially provided by user), and initial learning factor of 0.9 as a default values. 
-     The ordering phase continues for requested number of iterations and during that steps changes the parameters in the way that in the last iteration learning factor is 0.02 and the neighbourhood distance is 1.
+     In order to create SOM, we used {\sc MATLAB} neural network toolbox~\citep[NNT,][]{matlabtolbox}.
+     An SOM in {\sc NNT} can be created by {\sc newsom} library which works in two phases; ``ordering phase" and ``tuning phase" . 
+     Phase one is the ``ordering phase". 
+     This phase starts with maximum neighbourhood distance, and initial high learning factor usually 0.9 which is provided by user. 
+     The ordering phase continues for requested number of iterations and it continues till the learning factor reduces to tuning phase leaning factor and the neighbourhood distance reaches to the number set by the user.
 
@@
 
-     We created different SOM with different sizes, initial neighbourhood, and iteration numbers to find the optimize result for our sample.
-     We test our code by varying the number of iterations in ordering phase and find $N = 100$  is optimized for our sample.
-     In Section~\ref{sec: test model} we used this toolbox to create SOMs from SED of galaxies and learn how this method works and how we can interpret the results.
+     To present our results, we use {\sc nnt}'s built-in plotting tool.
+     Specifically, we combine two of the plots in this tool: a hits map, which shows the number of times each neuron has became the winner (hits), and a distance map, which shows the distance between weight vectors of those neurons.
+     In the maps, the purple hexagonal shapes shows the neurons. 
+     The distances are shown by the grey cycle colours: the darker the colour, the larger the distance between neurons.
+     Neurons with zero hits are left empty.
+     In Section~\ref{sec: mock_sample} we used {\sc newsom} to create SOMs from a mock sample to illustrate how this method works and how we can interpret the results.
 
- \subsection{Test Model}
- \label{sec: test model}
-    Before we start using SOM on our data, we apply this model in a test sample. 
-    Our test sample contains SED of 142 galaxies between redshift 0.5 $ \leq$ Z $\leq $ 1, which their physical information such as age, stellar mass and specific star formation are available. 
-    \cite{Hossein12} used trained network to classified their spectrum based on SED models from \cite{Kinney96} and \cite{Coleman80}.
+     One feature of the SOM method is that there is no rule and restriction on number of clusters.
+     Users must decide the size of networks based on their data set and their usages of the results .
+     There has been few attempts to find a rule for restricting the number of neurons based on the input sample \citep[e.g.][]{Vesanto05}, but none of them are certain. 
+     We varied size of SOMs from $1\times2$ to $50\times50$ to choose the most suitable size for our maps, and found that based on the size of our sample, the 2D SOMs to be 10$\times$10. 
+     We create the final SOMs with initial values for number of iterations in ordering phase, ordering phase learning factor, tuning phase learning factor, and tuning phase neighbourhood distance of 500, 0.9, 0.02, and 1, respectively.
+     %Also for each grid we created different SOM with different, learning factors, neighbourhood distances, and iteration numbers to find the optimize result for our sample.
+     %Based on our data we created our final SOMs with following initial values: number of iteration in ordering phase = 1000; ordering phase learning factor = 0.9; tuning phase learning factor= 0.02; and tuning phase neighbourhood distance to be 1.
+     %All the other parameters are default values in {\sc newsom} library and cannot be changed by the users.
 
-    We create various SOM maps with different numbers of neurons and neighbourhood
+\subsection{Mock sample}
+\label{sec: mock_sample}
+
+         \begin{figure}
+                \centering
+                \includegraphics[width=0.5\textwidth]{../images0.01/mock_sample.png}
+            \caption{SOM of the mock sample.
+The axes show the position of the neurons.
+Hexagonal shapes represent the neurons.
+The grey cycle colours show the differences between weight of each neuron where white is the minimum differences and black has the maximum one.}
+            \label{fig: sample}
+        \end{figure}
+
+To show how self-organizing maps work, we created a mock sample, which contains a few regions.
+We gave two information to each sample; amount of dust and the SFR.
+ Therefore, we have a simple input data with low dimension; each entry only can get either 0 or 1 as high or low SFR, and 0 or 0.5 to show high or low amount of dust for the mock regions.
+ We generated an SOM with the size of $10 \times 10$ from the sample, using the method that described in Sec.~\ref{sec: som}.
+ Fig. ~\ref{fig: sample} shows the SOM of the mock sample. 
+ The axes show the position of the neurons in a $10 \times 10$ network and the hexagonal shapes are the neurons.
+
+Using this method, as expected, we are able to divide the mock sample into 4 distinct groups: regions with high SFR and high amount of dust, regions with low SFR and high amount of dust, regions with high SFR and low amount of dust, and regions low SFR and low amount of dust.
+The plot in the Fig.~\ref{fig: sample}, clearly shows these divisions.
+In that plot, the upper part belongs to regions with low amount of dust, while the lower part belongs to the high amount of dust.
+The left part of the plot, is where regions with low SFR belong to and the right side is for high SFR regions.
+Grey to black colours show the border between regions.
+This network is considered as a trained network, and can used to cluster any new data set with similar entries.
+
+Having two regions with exactly the same values in all their quantities in the real world is almost impossible. 
+Therefore, one can find a network with high amount of the neurons, which separates the input data completely, and clusters them into separate groups.
+However, if the input data has high similarity, the number of neurons must be much higher than the number of input samples to be able to separate the groups from each other. 
+Therefore, it is up to the user to decide the similarity or dissimilarity between the input data based on the number of neurons.

### 2016-07-04 main text/draft0.0.tex
draftv0.01

--- 2016-06-18 main text/draft0.0.tex
@@
 \newcommand \Herschel {{\it Herschel }}
-\newcommand{\sii}{S~{\textsc II}} 
-\newcommand{\oiii}{O~{\textsc III}} 
-\newcommand{\hi}{H~{\textsc I}\ }
+\newcommand \sii {[S~{\textsc II}]} 
+\newcommand \oiii {[O~{\textsc III}]} 
+\newcommand \hi {H~{\textsc I}\ }
 
@@
 \section{SUMMARY}
+\label{sec: summary}
+
+We present results of studying spatially resolved regions in nearby galaxies using 
+The Self-organizing maps both cluster data and show relative distance between each cluster. 
+Therefore, we utilized it to find hidden subgroups in the data as well as finding relation between those groups.
+
+Using smaller-sized self-organizing maps, the M31 data are clustered into two major groups, which lead us to correlations that could not have otherwise been seen without clustering.
+We found that six of the regions in M31 create a subgroup of data, that have relatively lower amount of Mid- and far-infrared emission.
+PAH fluxes in these regions are highly anti-correlated with \halpha, \sii, \oiii~and IRAC 5.8~$\mu$m emission, stellar mass and RHI.
+These anti-correlations are insignificant when data from the whole galaxy are considered.
+We discussed possible reasons for these anti-correlations and argued that the most probable reason to PAHs anti-correlate with optical emission and RHI is having harder radiation.
+Harder radiation makes the size of H {\sc II} regions bigger and the size of PDRs smaller, which cause more \halpha~emission and less PAHs, respectively.
+
+PAHs in clustered data also show anti-correlation with stellar mass.
+We discussed the possibility of that higher stellar mass might destroy PAHs and as a result we see anti-correlation between them.
+However, we did not find any correlation between 8/24~$\mu$m emission, as a tracer of PAH abundance, and stellar mass.
+Unlike previous studies, we also did not find any correlation between 8/250~$\mu$m emission and stellar mass. 
+This results show that PAHs in the clustered regions in M31, do not heated by old stellar populations.
+
+In the maps with larger sizes, networks can be used to illustrate the relative relations of the regions with one another.
+We found the relative similarity between M31 regions, by varying the size of networks.
+A one-dimensional network with 14 neurons was needed in order to
+separate all 10 regions; we concluded that some of the region in M31 (e.g. regions 4 and 7) have very similar properties.
+
+A two-dimensional networks provide us a more complete picture of the data.
+We created various subsets from input data and generated different networks which helped us to show a relative relations between regions in M31 more clearly.
+We showed that region 10 always become isolated in networks, except when we only used PAHs data to create a network.
+In that network region 10 blends more with other regions and only shows differences with data from region 8.
+These results suggest that the PAHs in all 10 regions have almost the same properties.
+
+% We introduced self-organizing maps as a method that can be used to predict the amount of various quantities based on the relative positions of the regions in the networks.
+% By converting the relative distance between regions to the probability distribution function, we could predict unobserved/unmeasured properties of the galaxies with 10 per cent uncertainty.
+We also applied the SOMs from M31 data to M101 data and found regions with similar properties in both galaxies placed in close regions in the SOMs.
+We show that using this ability of the SOM, we can predict properties of regions in other nearby galaxies very fast.
+We should note that we created our networks using values for 26 quantities from 10 regions in M31, which does not consider as a "big sample".
+Increasing dimension of the data and the number of regions would help to have more reliable networks.
+In future we can apply these networks on data from other nearby galaxies (e.g. M33 and M83), and learn about the properties of regions on those galaxies.
 
 \section*{ACKNOWLEDGMENTS}
+The authors thank A. Tammour for her useful comments. 
 S.R., P.B., and E.P.

### 2016-07-04 sections/data0.0.tex
draftv0.01

@@
 We gathered data from 10 regions in M31 (Fig.~\ref{fig: regions in m31}) and 8 regions in M101 (Fig.~\ref{fig: regions in m101}) as inputs for SOMs.
-We chose those specific regions due to availability of the PAHs data for them.
-Besides PAHs data, for each galaxy, we chose spectroscopy and photometry data as well as their derived properties, such as SFR, stellar mass, dust luminosity (L$_{\rm dust}$) and mass, metallicity, and gas mass.
+We chose those specific regions due to availability of the PAH observations for them.
+Besides PAH data, for each galaxy, we chose spectroscopy and photometry observations as well as their derived properties, such as SFR, stellar mass, dust luminosity (L$_{\rm dust}$) and mass, metallicity, and gas mass.
 Table~\ref{tab: data} shows the full list of the data and their unit for both M31 and M101.
-We divided each values by the area of their region (in arcsec$^2$), to remove the distance factor from the data compare values of quantities in both galaxies.
+We divided each value by the area of their region (in arcsec$^2$), to remove the distance factor from the data compare values of quantities in both galaxies.
 Since the resolution of the data varies from less than 1$\arcsec$ to $60\arcsec \times 90 \arcsec$, any attempt to match the resolutions causes loosing all the information in some of the input data (e.g.
 the spectroscopic data).
-On the other hand, in this project we used flux (or value of the quantities) per area as inputs of SOMs, which the convolution methods conserve it~\citep{Aniano12}.
-Therefore, we did not perform any resolution matching in this paper and used data in their original resolutions.
+On the other hand, in this project we used flux (or value of the quantities) per area as inputs of SOMs, which the convolution methods conserve~\citep{Aniano12}.
+Therefore, we did not perform any resolution matching in this paper and used data in their original resolution.
 
@@
     \subfloat[MIPS 24~$\mu$m image of M31 from~\cite{Gordon06}, with position of 10 regions \label{fig: regions in m31}]{
-      \includegraphics[width=0.5\textwidth]{../images0.0/M31/M31.png}
+      \includegraphics[width=0.5\textwidth]{../images0.01/M31/M31.png}
     }
     \hfill
-    \subfloat[IRAC 3.6~$\mu$m image of M101~\cite{Dale09}, with position of 8 regions.\label{fig: regions in m101}]{
+    \subfloat[IRAC 3.6~$\mu$m image of M101~\citep{Dale09}, with position of 8 regions.\label{fig: regions in m101}]{
       \includegraphics[width=0.5\textwidth]{../images0.01/M101/M101.png}}
@@
      The 10 regions in M31 were chosen due to availability of the PAH data for them. 
-     \cite{Dim15} studied PAH for those regions using {\it Spitzer}/Infrared Spectrograph~\citep[IRS,][]{Houck04b} observations. 
-     They used {\sc PAHFIT IDL} tool~\citep{Smith07b} and measured fluxes and equivalent widths of PAH features as well as atomic line features.
+     \cite{Dim15} studied PAH for those regions using {\it Spitzer}/IRS observations. 
+     They used~{\sc PAHFIT IDL} tool~\citep{Smith07b} and measured fluxes and equivalent widths of PAH features as well as atomic line features.
      %For spectroscopy part of our sample, we utilized their measured fluxes for PAH lines. 
-     \cite{Dim15} also measured metallicity and of radiation hardness index (RHI) for these 10 regions.
-     We used the measured fluxes for PAHs featured, metallicity and RHI of each region as an input for SOMs.
+     \cite{Dim15} also measured metallicity and radiation hardness index (RHI) for these 10 regions.
+     We used the measured fluxes for PAH featured, metallicity and RHI of each region as an input for SOMs.
 
-     We used \GALEX FUV and NUV channels~\citep{Martin05}, \halpha, [\sii] narrow badn and [\oiii] narrow band~\citep{Massey07}, IRAC channels 1 to 4~\citep{Barmby06}, MIPS24 and 70~$\mu$m~\citep{Gordon06}, PACS100 and 160~$\mu$m and SPIRE250, 350, and 500~$\mu$m~\citep{Fritz12} emission for photometry part of the sample.
-     We changed units of all fluxes to Wm$^{-2}$ to be the same unit as PAHs fluxes.
+ We used \GALEX FUV and NUV channels~\citep{Martin05}, \halpha, \sii~and \oiii narrow band~\citep{Massey07}, IRAC channels 1 to 4~\citep{Barmby06}, MIPS24 and 70~$\mu$m~\citep{Gordon06}, PACS100 and 160~$\mu$m and SPIRE250, 350, and 500~$\mu$m~\citep{Fritz12} emission for photometry part of the sample.
+     We changed units of all fluxes to Wm$^{-2}$ to be the same unit as PAH fluxes.
      $^{12}$CO (J:$1\rightarrow0$) line~\citep{Nieten06} and the atomic gas (H\,{\sc I}) 21~cm emission from~\cite{Chemin09} were added to the input data. 
@@
     \label{Sec: data_M101_SOMN} 
-     For M101 galaxy, we used PAH fluxes which had been measured using {\sc PAHFIT IDL} tool and reported in \cite{Gordon08}.
+     For M101, we used PAH fluxes which had been measured using {\sc PAHFIT IDL} tool and reported in \cite{Gordon08}.
      We also added their measurement of metallicity and RHI for these regions to our sample.
      We used data available on NED~\footnote{The NASA/IPAC Extragalactic Database (NED) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.} website to gather our photometry data of M101.
-     We chose data from \GALEX FUV and NUV channels~\citep{depaz07}, IRAC channels 1 to 4, MIPS~24 and 70~$\mu$m~\cite{Dale09}, and  PACS~100 and 160~$\mu$m and SPIRE250, 350, and 500~$\mu$m emission from~\cite{Kennicutt11}.
-     The Same as M31 data, we used $^{12}$CO (J:$1\rightarrow0$) line~\citep{Helfer03} and the atomic gas (H\,{\sc I}) 21~cm emission from \cite{Walter08} data.
-     SFR(FUV + 24$\mu$m), stellar and total gas mass map were calculated using the same methods that M31 data were derived in \cite{Rahmani16}.
+     We chose data from \GALEX FUV and NUV channels~\citep{depaz07}, IRAC channels 1 to 4, MIPS~24 and 70~$\mu$m~\cite{Dale09}, and  PACS~100 and 160~$\mu$m and SPIRE~250, 350, and 500~$\mu$m emission from~\cite{Kennicutt11}.
+     Similar to M31 data, we used $^{12}$CO (J:$1\rightarrow0$) line~\citep{Helfer03} and the atomic gas (H\,{\sc I}) 21~cm emission from \cite{Walter08}.
+     SFR(FUV + 24$\mu$m), stellar and total gas mass map were calculated using the same methods that M31 data were derived in~\cite{Rahmani16}.
 
      Some of the correlations between some wavelengths and properties of galaxies are well-known.
-     For example, \citep{Rahmani16} used IRAC1 band emission to calculate the stellar mass, or FUV, NUV and MIPS24 emission to measure the SFR values. 
-     To make sure that we wouldn't use some of the observed data as an input data in various forms, we removed all the observed data, that were used to calculate these properties from the input sample.
+     Emission in 3.6$\mu$m band traces the old stellar population very well~\citep[e.g]{Leitherer99,Smith07a} and it is used to calculate the stellar mass~\citep{Eskew12}.
+     FUV, \halpha, and TIR emission are some of indicators of star forming regions.
+     In this project we used SFR traced by FUV emission which corrected for foreground stars using NUV emission and for dust extinction using 24$\mu$m emission.
+     TIR emission is calculated from modified version of~\cite{Draine07} calibration using using 8, 24, 70, and 160 $\mu$m emission~\citep{Boquien10}.
+     To make sure that we do not use the observed data as an input data in various forms, we removed all the observed data, that were used to calculate properties of the galaxies from the input sample.
      We used these sample as the main input for creating SOMs.

### 2016-07-04 sections/image_texts/all.tex
Updating fig.s Captions

\begin{figure}
        \centering
        \includegraphics[width=0.5\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and26.png}
    \caption{Two dimensional SOM of M31 using $10\times10$ grid. Similar to figs.\ref{fig: sample} and \ref{fig: M31_nets_1d}, The hexagonal shapes show the neurons and the grey cycle colours between neurons show the differences between weight of each neuron.}
    \label{fig: all_derived_ones}
\end{figure}

### 2016-07-04 sections/image_texts/col3byall.tex
Updating fig.s Captions

\begin{figure*}
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and11.png}
        \label{fig: col3and11_dist}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and12.png}
        \label{fig: col3and12_dist}
    \end{subfigure}
        \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and13.png}
        \label{fig: col3and13_dist}
    \end{subfigure}
        \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and14.png}
        \label{fig: col3and14_dist}
    \end{subfigure}
        \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and15.png}
        \label{fig: col3and15_dist}
    \end{subfigure}
        \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and16.png}
        \label{fig: col3and16_dist}
    \end{subfigure}
        \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and17.png}
        \label{fig: col3and17_dist}
    \end{subfigure}
        \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and18.png}
        \label{fig: col3and18_dist}
    \end{subfigure}
        \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and19.png}
        \label{fig: col3and19_dist}
    \end{subfigure}
        \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and20.png}
        \label{fig: col3and20_dist}
    \end{subfigure}        \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and21.png}
        \label{fig: col3and21_dist}
    \end{subfigure}
            \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and22.png}
        \label{fig: col3and22_dist}
    \end{subfigure}
            \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and23.png}
        \label{fig: col3and23_dist}
    \end{subfigure}
            \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and24.png}
        \label{fig: col3and24_dist}
    \end{subfigure}
            \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and25.png}
        \label{fig: col3and25_dist}
    \end{subfigure}
    \caption{Similar to Fig.~\ref{fig: all_derived_ones}, here we show the result from increasing dimension of input data from Fig.~\ref{fig: only_pahs} to 25, gradually. The order of input data is the same as order of data in Fig.~\ref{fig: cor_cluster1}.}
    \label{fig: inc_D_col3s}
\end{figure*}

### 2016-07-04 sections/image_texts/subset9.tex
Updating fig.s Captions

\begin{figure}
 \begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/image_subsets/subset9_dist_with_hits_t.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.5\textwidth}
    \includegraphics[width=\textwidth]{../../images0.01/M31/2D/image_subsets/subset9_dist_with_hits_v.png}
    \end{subfigure}
    \caption{Similar to Fig.~\ref{fig: all_derived_ones}, here we show up: the result from subset of data in M31 which is similar to data in M101; Down: the same network of up, but the input data are from M101.}
    \label{fig: subset9}
\end{figure}

### 2016-07-04 sections/R10.0.tex

@@
         %%%Talking about four right regions
-        \cite{Dim15} showed that the regions 1, 2, 9, and 10 have higher PAHs flux intensity compare to other regions (Fig. 5 in \cite{Dim15} paper). 
+        \cite{Dim15} showed that the regions 1, 2, 9, and 10 have higher PAH flux intensity compare to other regions (Fig. 5 in \cite{Dim15}). 
         %Regions 1, 2, and 9 are in the 10~Kpc ring and region 10 is located in the bulge of M31; however, regions 3 to 8 are located slightly out of the inner ring or the 10~kpc one.
-        These regions also have relatively high intensity in the SPIRE bands and have high dust luminosity.
-        The higher values in the intensity of the PAHs, SPIRE bands and the dust luminosity could be the reason that these 4 regions become separated from the others, in $1\times2$ network.
+        These regions also have relatively high intensity in all the MIR and FIR bands, and have high dust luminosity and dust mass.
+        The higher values in these values could be the reason that these 4 regions become separated from the others, in $1\times2$ network.
         Besides, Regions 1, and 9 are in the 10~Kpc ring, region 2 is slightly out of the 10~Kpc ring and the region 10 is in the bulge of M31; however, regions 3 to 8 are located out of the inner ring or the 10~kpc ring (Fig.~\ref{fig: regions in m31}).
@@
         %%Network 1by14
-        The network with 14 neurons, in Fig.~\ref{fig: M31_net_1by14}, is the first network, that has no neuron to be occupied with more than one region.
+        The network with 14 neurons, in Fig.~\ref{fig: M31_net_1by14}, is the first network, that has no neuron occupied by more than one region.
         In a higher grid SOM, network pays more attention to smaller details and differences in the input data.
@@
         The region 10 is located in the bulge of M31, and its separation from other regions, which are mostly located around the inner or outer rings, is due to the fact that most of the input values for this region is much higher than the other regions.
-        The region 8 occupies the most right neurons in this network, that suggests that this region has the most differences with region 10.
+        The region 8 occupies the most right neurons in this network, that suggests that this region has the most differences from region 10.
 
-    \subsection{Inside of the 2 neurons network}%%% I will find better title for this subsection
+    \subsection{Inside the 2 neuron network}%%% I will find better title for this subsection
         %What is going on in this section
@@
         Each of these subgroups were separated from each other, for a reason.
-        This reason can vary from having higher values in some specific wavelengths, as discussed in Sec.~\ref{Sec: 1d_cluster}, to some unknown correlations between data, that cannot be seen in other groups or in a Galaxy's data as a whole.
+        This reason can vary from having higher values in some specific wavelengths, as discussed in Sec.~\ref{Sec: 1d_cluster}, to some unknown correlations between data, that cannot be seen in other groups or in a Galaxy as a whole.
         To investigate the later, we showed the Pearson correlation coefficients for the inputs from regions 3 to 8 in Fig.~\ref{fig: cor_cluster1}, which were clustered together in the $1\times2$ and $1\times3$ networks (see Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}).
@@
         %%% what regions' version shows and how it compares with the other one:
-        In Fig.~\ref{fig: cor_all}, which shows the Pearson correlation coefficients from data in all 10 regions, all the PAHs features highly correlate with each other. 
-        Also, there are very strong correlations between all the PAHs features and PACS~100~$\mu$m~, SPIRE 250 to 500~$\mu$m~emission, L$_{\rm dust}$, L$_{\rm TIR}$, SFR, and metallicity.
-        However, in Fig.~\ref{fig: cor_cluster1}, 12.0 and 12.7~$\mu$m~PAHs fluxes do not show any significant or strong correlation with PAH fluxes in other wavelengths or most of the other quantities.
+        In Fig.~\ref{fig: cor_all}, which shows the Pearson correlation coefficients from data in all 10 regions, all the PAH features highly correlate with each other. 
+        Also, there are very strong correlations between all the PAH features and PACS~100~$\mu$m~, SPIRE 250 to 500~$\mu$m~emission, L$_{\rm dust}$, L$_{\rm TIR}$, SFR, and metallicity.
+        However, in Fig.~\ref{fig: cor_cluster1}, 12.0 and 12.7~$\mu$m~PAH fluxes do not show any significant or strong correlation with PAH fluxes in other wavelengths or most of the other quantities.
         The only exceptions are the strong correlation between PAH flux at 12~$\mu$m and L$_{\rm dust}$, and between 12 and 12.7~$\mu$m PAH fluxes.
-        Since there are only 6 regions in this cluster, even one outlier in the data may cause the correlation coefficient become insignificant.
-        By removing the outlier, the correlations between 12.0 and 12.7~$\mu$m~PAHs fluxes and the other quantities show themselves.
+        Since there are only 6 regions in this cluster, even one outlier in the data may cause the correlation coefficient to become insignificant.
+        By removing the outlier, the correlations between 12.0 and 12.7~$\mu$m~PAH fluxes and the other quantities show themselves.
 
-        For the rest of the PAHs fluxes in Fig.~\ref{fig: cor_cluster1}, there are not any significant correlations with PACS~100~$\mu$m, L$_{\rm dust}$, L$_{\rm TIR}$, SFR, or metallicity, neither.
+        For the rest of the PAH fluxes in Fig.~\ref{fig: cor_cluster1}, there are not any significant correlations with PACS~100~$\mu$m, L$_{\rm dust}$, L$_{\rm TIR}$, SFR, or metallicity, neither.
         They have correlations with SPIRE emission, but they are weaker than the ones with data from all regions.
-        Correlations between PAHs features and SFR, and L$_{\rm TIR}$ are well-studied~\citep[e.g.][]{Tielens08,Peeters04}. 
-        Many groups used PAHs features as a tracer of SFR by finding correlations between 
-        PAHs emission and SFR derived from extinction corrected \halpha~\citep[e.g.][]{Shipley16,Khramtsova13,Calzetti07}.
+        Correlations between PAH features and SFR, and L$_{\rm TIR}$ are well-studied~\citep[e.g.][]{Tielens08,Peeters04}. 
+        Many groups used PAH features as a tracer of SFR by finding correlations between 
+        PAH emission and SFR derived from extinction corrected \halpha~\citep[e.g.][]{Shipley16,Khramtsova13,Calzetti07}.
         These correlations are seen in Fig.~\ref{fig: cor_all}, when we considered the data from all regions, but not in Fig.~\ref{fig: cor_cluster1} when considering the clustered data.
-        Further analyses show that the absence of correlations between PAHs features and SFR, is because of one outlier in data. 
-        When we disregard the outlier data, high correlations between 6.2 to 11.3~$\mu$m~PAHs features and SFR (and L$_{\rm TIR}$) reappear.
-        Strong ant-correlation between 6.2 to 11.3~$\mu$m~PAHs features and RHI, stellar mass, \halpha, \sii, \oiii, and IRAC~5.6~$\mu$m~emission in Fig.~\ref{fig: cor_cluster1} had not be seen in Fig.~\ref{fig: cor_all}.
-     %   In Fig.~\ref{fig: cor_cluster1}, 6.2, 7.7, 8.3, 8.6, and 11.3~$\mu$m~PAHs features show strong anti-correlations with RHI, stellar mass, \halpha, \sii, \oiii, and IRAC~5.6~$\mu$m~emission.
+        Further analyses show that the absence of correlations between PAH fluxes and SFR, is because of one outlier in data (Region 6). 
+        When we disregard the outlier data, high correlations between 6.2 to 11.3~$\mu$m~PAHs and SFR (and L$_{\rm TIR}$) reappear.
+        Strong ant-correlation between 6.2 to 11.3~$\mu$m~PAH features and RHI, stellar mass, \halpha, \sii, \oiii, and IRAC~5.6~$\mu$m~emission in Fig.~\ref{fig: cor_cluster1} had not be seen in Fig.~\ref{fig: cor_all}.
 
-        Anti-correlations between PAHs features and the \halpha, \sii, and \oiii~emission could be the result of one the followings. 
+        Anti-correlations between PAH features and the \halpha, \sii, and \oiii~emission could be the result of one the following. 
         First, the optical data are not corrected for dust extinction.
-        The PAHs features correlate with dust, and \halpha emission is sensitive to dust extinction.
-        Therefore, more PAHs features, means more dust and less \halpha~emission (The same for \sii~and \oiii~emission).
+        The PAH features correlate with amount of dust while \halpha~emission anti-correlate with amount of dust due to extinction \citep{Calzetti94}.
+        Therefore,higher amount of PAH fluxes means higher amount of dust abundance and less \halpha~emission (The same for \sii~and \oiii~emission).
         Second, it is the effect of observing apertures.
-        If the regions are located in the edge of the H {\sc II} regions we would expect too see more PAHs and less \halpha~emission. %%% reference?
-        The anti-correlations between 6.2 to 11.3~$\mu$m~PAHs features and RHI have been seen in other studies, too~\citep[e.g.][]{Dim15, Gordon08, Wu06}.
-        \cite{Wu06} discussed these ant-correlations could be the result of destruction of the PAHs due to the high amount of the harder radiation (thus higher RHI).
+        If the observed regions are located in the edge of the H {\sc II} regions we would expect too see more PAH and less \halpha~emission. %%% reference?
+        The anti-correlations between 6.2 to 11.3~$\mu$m~PAH features and RHI have been seen in other studies, too~\citep[e.g.][]{Dim15, Gordon08, Wu06}.
+        \cite{Wu06} discussed these ant-correlations could be the result of destruction of the PAH due to the high amount of harder radiation (thus higher RHI).
         On the other hand, \cite{Gordon08} argued that the harder radiation could make the photodissociation regions (PDRs) smaller.
-        The PAHs features are mostly coming from the PDRs that are surrounded by H {\sc II} regions, and the PAHs features underlying continuum emission is from the H {\sc II} regions.
-        Therefore, the lower flux of the PAHs features could be the result of the smaller size of PDRs.
-        The later reason, which could also describe the anti-correlation between PAHs features and \halpha~emission, seems to be the more probable one. 
-        %%% The anti correlation with stellar mass?!! with IRAC3?!!
+        The PAH features are mostly coming from the PDRs that are surrounded by H {\sc II} regions, and the PAH features underlying continuum emission is from the H {\sc II} regions.
+        Therefore, the lower flux of the PAH features could be the result of the smaller size of PDRs.
+        The later reason, which could also describe the anti-correlation between PAH features and \halpha~emission, seems to be the more probable one.
 
-       Despite the fact that some of the (anti)-correlations in Fig.~\ref{fig: cor_cluster1} might have physical meanings, we have to mention that, we only used 6 regions to calculate these correlation coefficients.
-       Having 6 data points as a sample of the study is not high enough to have a strong conclusion about the PAHs in M31.%%% it doesn't sound right:((
-        However, we can conclude that since the correlation coefficients derived from the clustered data (Fig.~\ref{fig: cor_cluster1}) differs from correlation coefficients derived from the data from the all regions (Fig.~\ref{fig: cor_all}), SOM separated a hidden cluster of the data, which their properties are different than the others.
+        The strong anti-correlation between PAHs and stellar mass shows, despite the general assumption that the one of the main source of heating PAHs is stellar emission~\citep[e.g][]{Haas02,Bendo08,Calapa14, Lu14,Jones15}, the higher stellar mass decreases PAH emission.
+        Using M33 data,~\cite{Calapa14} showed that 8/250~$\mu$m luminosity ratio correlate with 3.6~$\mu$m emission, which translates to stellar mass, and conclude that the PAH emission traces the old stellar population.
+        In Fig.~\ref{fig: cor_cluster1}, we see a week anti-correlation between SPIRE 250~$\mu$m emission and the stellar mass.
+        We couldn't see any correlation between 8/250~$\mu$m luminosity and stellar mass, neither in clustered data nor in all 10 regions.
+      %  The results from~\cite{Calapa14} were based on data from the whole galaxy and has a relatively high scatter.
+      %It is possible that all the 10 regions in M31 simply aligned with the scatter of the correlation.
+Further analysis on M31 data is required to see weather the anti-correlation in this regions is extended to whole galaxy or it is only for these 6 regions.
+
+        Studies showed that strong stellar emission could lead to destruction of PAHs ~\citep[e.g.][]{Clayton03,Seok14}.
+        To test that whether anti-correlation between stellar mass and PAH emission is the result of the destruction of PAHs in high stellar mass, or that high stellar mass obscures PAH emission, we compared PAH abundance with stellar mass for the clustered regions.
+        The ratio of 8/24~$\mu$m emission, which can be considered as a proxy for PAH abundances~\citep[e.g.][]{Sandstrom10,Khramtsova13}, does not anti-correlate with stellar mass for neither the clustered data nor all 10 regions.
+        Therefore, we conclude that in our sample of studies the high stellar mass does not causes the destruction of PAHs.
+
+        The anti-correlation between stellar mass and PAHs could be result of the position of the regions in M31.
+        Regions 5, 6, and 8 are located on the stellar disk of the galaxy and have relatively high stellar mass and low PAHs. 
+        According to~\cite{Dim15}, regions 5 and 8 are only two regions in our sample that are not include an H {\sc II} region, which could be the reason of low PAHs for these regions.
+        Regions 4 and 7 have similar quantities for both stellar mass and PAHs and region 3 has high PAHs and low stellar mass.
+        Thus without data from more regions in M31, we cannot confidently say that higher stellar mass decreases PAH fluxes.
+        %% Sahar: Can we have higher PAHs absorbes stellar mass and thats why we see the anti-correlation?!!!
+
+       % On the other hand, if we divide SFR by stellar mass, which give us specific star formation rate (sSFR), we see strong correlation between sSFR and 6.2 to 11.3~$\mu$m fluxes for clustered regions,
+
+       Regardless of the fact that some of the (anti)-correlations in Fig.~\ref{fig: cor_cluster1} might have physical meanings, we have to mention that, we only used 6 regions to calculate these correlation coefficients.
+       Having 6 data points as a sample of the study is not high enough to have a strong conclusion about the PAH in M31.%%% it doesn't sound right:((
+        However, we can conclude that since the correlation coefficients derived from the clustered data (Fig.~\ref{fig: cor_cluster1}) differs from correlation coefficients derived from the data from the all regions (Fig.~\ref{fig: cor_all}), SOM separated a hidden cluster of the data, for which their properties are different than the others.
 %%Again eh!

### 2016-07-04 sections/R20.0.tex

@@
     In this section we chose $10\times10$ size despite that we knew, from the size of our input data, that most of the neurons would be empty.
-    Using 2D networks, we are mostly interested in the ability of the SOMs in showing underlying structure of the data rather than its clustering features.
+    Using 2D networks, we are mostly interested in the ability of the SOMs to showing underlying structure of the data rather than its clustering features.
     \import{../sections/image_texts/}{all.tex}
     Fig.~\ref{fig: all_derived_ones} shows the 2D SOM of M31 data.
-    Similar to the Fig.~\ref{fig: M31_net_1by14}, all the 10 regions completely separated from each other in Fig.~\ref{fig: all_derived_ones}.
+    Similar to the Fig.~\ref{fig: M31_net_1by14}, all the 10 regions are completely separated from each other in Fig.~\ref{fig: all_derived_ones}.
 
@@
     Position of region 3 on the SOM is close to the position of regions 4 and 7, but with darker colour between the nodes. 
-    In Fig.~\ref{fig: regions in m31} it is clear that, this region in M31 is closer to regions 4 and 7 than any other region, but it is on the outer side of the star forming ring.
+    In Fig.~\ref{fig: regions in m31} it is clear that this region in M31 is closer to regions 4 and 7 than any other region, but it is on the outer side of the star forming ring.
     Regions 5 and 6 are in their second neighbourhood on the SOM, with a medium gray colour between them.
     These two regions are around the inner ring of the galaxy.
-    Regions 8 and 6 are both in the inner ring of M31, but region 6 is in the region with more star forming activities, which could be the main reason for their relative distance in the SOM in Fig.~\ref{fig: all_derived_ones}.
+    Regions 8 and 6 are both in the inner ring of M31, but region 6 is in the region with more star formation, which could be the main reason for their relative distance in the SOM in Fig.~\ref{fig: all_derived_ones}.
 
     Regions 1 and 9 are close to each other, and in the same side of the star forming ring. 
-    However, region 1 is in an area of the galaxy with lesser diffuse \halpha~emission than region 9, that might be the reason for their distances in SOM.
+    However, region 1 is in an area of the galaxy with less diffuse \halpha~emission than region 9, that might be the reason for their distances in SOM.
     Region 2 is more distant from other regions in the galaxy, and placed in the star forming ring.
-    However, similar to regions 1 and 4, region 2 is located in an area of the galaxy with less diffused \halpha~emission.
+    However, similar to regions 1 and 4, region 2 is located in an area of the galaxy with less diffuse \halpha~emission.
     Therefore, place of region 2 in the SOM is more favoured towards regions 1 and 4. 
@@
              \import{../sections/image_texts/}{PAHS_or_not_PAHs.tex}
-            Comparing the SOM from all data in Fig.~\ref{fig: all_derived_ones} with the SOMs in Fig.~\ref{fig: PAHS_or_not_PAHs}, showed that the general position of regions in those networks are the same.
-            The region 10 is in one corner of the all three networks.
+            Comparing the SOM from all data in Fig.~\ref{fig: all_derived_ones} with the SOMs in Fig.~\ref{fig: PAHS_or_not_PAHs} shows that the general position of regions in those networks are the same.
+            Region 10 is in one corner of all three networks.
             However, in Fig.~\ref{fig: all_derived_ones} and Fig.~\ref{fig: wt_pahs}, region 10 is isolated from the other regions, while in Fig.~\ref{fig: only_pahs}, region 10 is much less isolated and only shows complete dissimilarity with region 8.
@@
             Figs.~\ref{fig: subset1} --~\ref{fig: subset6} show SOMs that are created by data from subsets 1 to 3, respectively.
-            The rest of the subsets are discussed in the Appendix.~\ref{sec: app_2d_soms_SOMN}.
+            The rest of the subsets are discussed in Appendix.~\ref{sec: app_2d_soms_SOMN}.
 
             The results from Table~\ref{tab: subset1} is shown in Fig.~\ref{fig: subset1}. 
-            In this SOM compare with the SOM from all the data in Fig.~\ref{fig: all_derived_ones}, regions 1 and 9 are closer to region 10. 
+            In this SOM compared with the SOM from all the data in Fig.~\ref{fig: all_derived_ones}, regions 1 and 9 are closer to region 10. 
             Regions 1 and 9 are the ones with lowest stellar mass values, and region 10 has the highest stellar mass value among those 10 regions. 
-            Since the differences in the amount of the stellar mass were one of the most distinct differences between these three regions, removing stellar mass from input data reduced the distance between these regions.
-            Regions 5, 6 and 8 are in the same relative distance from each other as in Fig.~\ref{fig: all_derived_ones}, but they all are closer to the position of the region 10.
+            Since the differences in the amount of stellar mass was one of the most distinct differences between these three regions, removing stellar mass from input data reduced the distance between these regions.
+            Regions 5, 6 and 8 are in the same relative distance from each other as in Fig.~\ref{fig: all_derived_ones}, but they all are closer to the position of region 10.
             Distance between regions 2 and 3 is reduced but in the meantime the colour between them became darker.
@@
             Fig.~\ref{fig: subset6} shows the SOM generated from data that are listed in Tab.~\ref{tab: subset6}, which includes all the data from Tab.~\ref{tab: subset5} except SPIRE 250 and 500~$\mu$m emission.
-            Although for most of the regions we see the changes in their positions, the colours between neurons changed, too. 
+            Although for most of the regions we see the changes in their positions, the colours between neurons changes as well. 
             %Therefore, we can conclude that these changes caused by the differences in the initial assigned weights.
@@
             %Subsets, that some of them  are studied in this section, can be used to learn about the effect of each input on the map as well as they can be used to predict unobserved quantities in the galaxy.
-            \subsubsection{Prediction observing data using M31}
 
-                On SOMs we can see relations between the input data from each region regarding to the other regions.
-                These relations are shown by colour in SOMs, when white is 100 per cent similarity and black is 0 per cent similarity.
-                Therefore, we have the probability distribution of quantities of each values given data from other regions.
-                We can use these probability distribution to estimate missing data for regions.
+            % \subsubsection{Prediction observing data using M31}
 
-                To demonstrate this conclusion, we assumed the stellar mass value for region 1 is unknown.
-                Therefore, we need a SOM that are generated from all the inputs data for all regions except stellar mass (e.g subset 1 in Fig.~\ref{fig: subset1}).
-                \import{../sections/image_texts/}{sim_subset1.tex}
-                We found the shortest path between region 1 and the other regions and measure their relative similarity ($p_j$).
-                Assuming the maximum similarity is 100 per cent between two neurons (white colour), we multiply the similarity values along the shortest path between two regions to find $p_j$ between region 1 and the other regions (Fig.~\ref{fig: sim_subset1}).
-                In both Figs.~\ref{fig: subset1} and ~\ref{fig: sim_subset1} are clear that region 1 shows more similarity to regions 2 and 9 than the others and the most dissimilarity to region 8.
+            %     On SOMs we can see relations between the input data from each region regarding to the other regions.
+            %     These relations are shown by colour in SOMs, when white is 100 per cent similarity and black is 0 per cent similarity.
+            %     Therefore, we have the probability distribution of quantities of each values given data from other regions.
+            %     We can use these probability distribution to estimate missing data for regions.
 
-                We measured probability of stellar mass given other quantities of the region 1 ($P(m_1\mid \forall_1)$) using Equation~\ref{equ: prob1}.
-                \begin{equation}
-                \label{equ: prob1}
-                    P(m_1\mid \forall_1) = \sum_{j=2}^{10}p_j*m_j
-                \end{equation}
-                Where $m_1$ is the stellar mass of region 1 and $m_j$ is the stellar mass of region j (any other region).
-                We estimated the stellar mass to be $\sim1377$~M$\odot$ which is 10 per cent less than the observed values.
-                This type of the prediction from SOM networks can be used to predict observation values in observational proposals or can be used in pre-phase studies of the big missions such as the James Webb Space Telescope (JWST) and LLST.
+            %     To demonstrate this conclusion, we assumed the stellar mass value for region 1 is unknown.
+            %     Therefore, we need a SOM that are generated from all the inputs data for all regions except stellar mass (e.g subset 1 in Fig.~\ref{fig: subset1}).
+            %     \import{../sections/image_texts/}{sim_subset1.tex}
+            %     We found the shortest path between region 1 and the other regions and measure their relative similarity ($p_j$).
+            %     Assuming the maximum similarity is 100 per cent between two neurons (white colour), we multiply the similarity values along the shortest path between two regions to find $p_j$ between region 1 and the other regions (Fig.~\ref{fig: sim_subset1}).
+            %     In both Figs.~\ref{fig: subset1} and ~\ref{fig: sim_subset1} are clear that region 1 shows more similarity to regions 2 and 9 than the others and the most dissimilarity to region 8.
 
-    \subsection{Validating networks using M101 data}
-    Another application of SOM for nearby galaxies is that to apply the trained networks on the data from other galaxies in order to prediction properties of the regions in them. %%eh
-    As an example of this application, we generated an SOM using data from M31 that held in common with M101 data (Fig.~\ref{fig: subset9}a). 
+            %     We measured probability of stellar mass given other quantities of the region 1 ($P(m_1\mid \forall_1)$) using Equation~\ref{equ: prob1}.
+            %     \begin{equation}
+            %     \label{equ: prob1}
+            %         P(m_1\mid \forall_1) = \sum_{j=2}^{10}p_j*m_j
+            %     \end{equation}
+            %     Where $m_1$ is the stellar mass of region 1 and $m_j$ is the stellar mass of region j (any other region).
+            %     We estimated the stellar mass to be $\sim1377$~M$\odot$ which is 10 per cent less than the observed values.
+            %     This type of the prediction from SOM networks can be used to predict observation values in observational proposals or can be used in pre-phase studies of the big missions such as the James Webb Space Telescope (JWST) and LLST.
+
+    \subsection{Testing networks using M101 data}
+    Another application of SOM for nearby galaxies is to apply the trained networks on the data from other galaxies in order to predict properties of the observed regions in them. %%eh
+    Therefore, we generated an SOM using data from M31 that hold in common with M101 data (Fig.~\ref{fig: subset9}a). 
+    \cite{Dim15} compared PAHs in M31 with those from H {\sc II} regions in M101, and showed the similarity between PAHs from these two galaxies (For more detail see \cite{Dim15} and \cite{Gordon08}).
     In this SOM, the same as the others, region 10 is separated from other regions in M31.
@@
     We applied the SOM created using M31 data in Fig.~\ref{fig: subset9}a on M101 data (Fig.~\ref{fig: subset9}b).
-    Region 6 in M31 and region 2 in M101 both occupied the same neuron in the network in Fig.~\ref{fig: subset9}, which immediately suggest that these two regions have similar properties. 
+    Region 5 in M31 and region 8 in M101 and regions 6 in M31 and region 2 in M101 occupied neurons with white colour between them in the network in Fig.~\ref{fig: subset9}, which immediately suggest that these regions have similar properties.
+
     Region 2 in M101 is a bright H {\sc II} region that is located at the end of the one of the M101 spiral arm (see Fig.~\ref{fig: regions in m101}). 
@@
 
-    Region 7 in M101 is located in the nucleus of the galaxy and have relatively higher quantities than the other regions.
+    Region 5 in M31 is in inner ring of the galaxy and it is one of two regions in M31 that are not an  H {\sc II} region.
+    region 8 in M101 is in a spiral arm of the galaxy.
+    Relatively low stellar mass, SFR and SPIRE band emission caused these two regions have close distance in the map.
+    In Sec.~\ref{Sec: 1d_cluster} we showed that regions 3 to 8 in M31 have similar properties, in Fig.~\ref{fig: subset9}b we see that regions 1 to 3 and 5 to 8 in M101 are located near regions 3 to 8 in M101.
+    These regions all have medium or low amount of PAHs, dust and SFR compare to the rest of them.
+
+    Region 7 in M101 is located in the nucleus of the galaxy and has relatively higher quantities than the other regions.
     This region is located in the top right side of the network in Fig.~\ref{fig: subset9}, which is close to location of region 10 in the network.
@@
 
+    Knowing effect of each data entry on the networks From Section~\ref{sec: subsets}, we can have ideas about that data entry that we do
     In this section we showed that we can use networks that are created by data from nearby galaxies, to study the properties of other galaxies in a fast way.
-    We should note that we created our networks using values for 26 quantities from 10 regions in M31, which does not consider as a "big sample".
-    Increasing dimension of the data and the number of regions would help to have more reliable networks.
+    We should note that, since we normalized data before using them in the networks, we only see a relative properties of the regions.
+    Therefore, we need data from few regions in the galaxy to use this network cannot use these networks to learn about properties of a single region in other galaxies.

### 2016-07-04 sections/image_texts/PAHS_or_not_PAHs.tex

\begin{figure}
    \begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols11and26.png}
    \caption{Without PAHs}
    \label{fig: wt_pahs}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.5\textwidth}
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and10.png}
    \caption{Only PAHs}
    \label{fig: only_pahs}
    \end{subfigure}
    \caption{Similar to Fig.~\ref{fig: all_derived_ones}, here we show the result of up: SOM from data excluding PAHs; Down: SOM from PAHs data}
    \label{fig: PAHS_or_not_PAHs}
\end{figure}

### 2016-07-04 sections/intro0.0.tex

@@
 %General information about galaxies %(Maybe it is too generic?!!)
-Inside each galaxy, there are millions of stars and large amount of dust and gas, which all affect on each others' formation, evolution and extinction.
-Galaxies are an active and complicated systems, that are constantly changing.
-There are extensive amount of studies about correlations between galaxies' emission and their physical properties, both observationally and theoretically %(Some references here). 
-These studies expands our knowledge of the underlying processes in formation and evolution of galaxies every day, but the details of how these process work are still undetermined.
+% Inside each galaxy, there are millions of stars and large amount of dust and gas, which all affect on each others' formation, evolution and extinction.
+% Galaxies are an active and complicated systems, that are constantly changing.
+% There are extensive amount of studies about correlations between galaxies' emission and their physical properties, both observationally and theoretically %(Some references here). 
+% These studies expands our knowledge of the underlying processes in formation and evolution of galaxies every day, but the details of how these process work are still undetermined.
 
@@
 Nearby galaxies play an important role in learning about galaxies' formation and evolution.
-These galaxies are close enough to be able to observe various regions inside them in details.
+These galaxies are close enough to be able to observe various regions inside them in detail.
 As a result, many studies are devoted to find relations between physical properties of the galaxies in both spatially resolved regions and galaxies as a whole%(Some more references here)
@@
 Advances in technology helps to both observe and store enormous amount of data from sky.%The sky?! 
-Telescopes and surveys gather data from nearby galaxies in variuse wavelengths and from these data we can measure physical properties of galaxies (e.g.
+Telescopes and surveys gather data from nearby galaxies in various wavelengths and from these data we can measure physical properties of galaxies (e.g.
 stellar mass, star formation rate (SFR), dust mass, gas mass)~\citep[e.g.][]{Calzetti07,Dale09,Eskew12}.
@@
 Images of this galaxy provide us a detail view of inside of a spiral galaxy from distance.
-M31 data was a target of many telescopes (e.g.
-{\it Hubble} \citep{Dalcanton12}, \Spitzer\citep{Wener04}, \Herschel\citep{Pilbratt10} space telescopes) and was a subject of many more studies \citep[e.g.][and references therein]{Barmby06, Gordon06, Azimlu11, Sanders12, Dim15, Rahmani16}.
+M31 was a target of many telescopes (e.g.
+{\it Hubble} \citep{Dalcanton12}, \Spitzer\citep{Wener04}, \Herschel\citep{Pilbratt10} space telescopes) and was a subject of many more studies.
+% \citep[e.g.][and references therein]{Barmby06, Gordon06, Azimlu11, Sanders12, Dim15, Rahmani16}.
 
-\cite{Barmby06} used data from Spitzer Infrared Array Camera \citep[IRAC;][]{Fazio04} to show evidence of Polycyclic Aromatic Hydrocarbons (PAH)s in interstellar medium (ISM) of M31.
+\cite{Barmby06} used data from Spitzer Infrared Array Camera \citep[IRAC;][]{Fazio04} to how evidence of Polycyclic Aromatic Hydrocarbons (PAH)s in interstellar medium (ISM) of M31.
+%or to study the stellar and nonstellar mid-infrared (MIR) emission in M31. ?! 
 Using the mid-IR data from Multiband Imaging Photometer for Spitzer (MIPS), \cite{Gordon06} studied the morphology of the dust in M31.
@@
 Properties of the current stars in the galaxy were studied by~\cite{Tamm12} and~\cite{Massey07}. %%%And some from PHAT survey
-\cite{Rahmani16, Ford13} and \cite{Tabatabaei10} measured the SFR in M31 in order to study star formation laws, and \cite{Dim15} and \cite{Kapala15} used spectroscopic data of the galaxy to study PAHs and other line emissions in the ISM.
+\cite{Rahmani16, Ford13} and \cite{Tabatabaei10} measured the SFR in M31 in order to study star formation laws, and \cite{Dim15} and \cite{Kapala15} used spectroscopic data the galaxy to study PAHs and other line emission in the ISM.
 
@@
 % data mining and clustering in general; when we have so many data and we want to map them
-\cite{Ball10} wrote an extensive review of data mining and machine learning, and their usages in astronomy.
+\cite{Ball10} wrote an extensive review of data mining and machine learning, and their usage in astronomy.
 A data mining algorithm learns about data from sets of trainings, which can be supervised or unsupervised.
-The supervised trainings refer to methods, that use examples of the desired output to learn about input data and are valuable tools to classify data with known target values.
+The supervised training refer to methods that use examples of the desired output to learn about input data and are valuable tools to classify data with known target values.
 On the contrary, the unsupervised methods train without any prior knowledge of output results. 
-They solely work based on the underlying structure of input data.   
+They work solely based on the underlying structure of input data.   
 The unsupervised methods are very useful tools in knowledge discovery studies on input data, which we do not have any insight of them (or when we want to make sure that we did not miss any valuable information in our previous studies).
@@
 %SOM
-One the most tested methods of data mining in astronomy is the artificial neural networks (ANNs)~\citep[e.g.][and references therein]{Hossein12, Hossein14,Hossein16,Ellison16a}.
-ANNs are designed to work in the same way that the neurons work in a human mind.
+One the most tested methods of data mining in astronomy is the artificial neural networks (ANNs)~\citep[e.g.][and references therein]{ Hossein14,Hossein16}.
+ANNs are designed to work in the same way that the neurons work in a human brain.
 They are networks of interconnected neurons (nodes), which all of the connections are weighted.
@@
 
-% other Unsupervised methods
+ %%add a little bit about PAHs in M31, dim15, drain14 and refs. therein. talk about what questions are still remained unanswered.
 The purpose of this project is to have a new insight into nearby galaxies using M31 data with focusing on relations between PAHs and other properties of the galaxy.
-To fulfill this purpose, an unsupervised data mining method is the most suitable choice. %%eh  
+There are very few studies on relations between properties of M31 with its PAH features.
+To fulfill this purpose, an unsupervised data mining method is the most suitable choice.
+\cite{Cesarsky98} studied PAH spectra in four regions in M31 and showed that PAH features in M31 differ from the PAH spectra in other galaxies; in the way that there are  week or no 6.2 - 8.6~$\mu$m with enhanced 11.2~$\mu$m emission in M31 spectra.
+However, \cite{Dim15} by using {\it Spitzer}/Infrared Spectrograph~\citep[IRS,][]{Houck04b} observations indicate that the PAH spectra of M31 has the same features as spectra of other nearby star forming galaxies.
+Using MIR photometry data of M31,\cite{Barmby06} compared the observed 8~$\mu$m luminosity with other star formation indicators in the galaxy and found good agreements among them, and \cite{Draine14} found the PAH abundance in M31 is almost constant up to R$\sim 20$~Kpc.
+Therefore, using data mining techniques, we aim to study PAH features in more detail.
+
 K-means algorithm, SOMs, and hierarchical clustering are main unsupervised methods that are used in astronomical studies~\citep[e.g.][]{DAbrusco12, Aycha16}. %%add one or two more
-
 For both K-means and SOM algorithms, the user must define the number of clusters, and the algorithms decide how to separate the data into desired number of the clusters.
-In the hierarchical clustering method, the user must define dissimilarity between the groups, and the algorithm combines (or divides) existing groups based on their dissimilarity and creates a hierarchical structure.
+In the hierarchical clustering method, the user must define dissimilarity between the groups, the algorithm combines (or divides) existing groups based on their dissimilarity and creates a hierarchical structure.
 Comparing SOMs, K-means and hierarchical clustering shows that in some cases hierarchical clustering method miss-classifies the data~\citep[][and references therein]{Mangiameli96}.
-We chose SOM method over K-means due to the fact that SOMs not only clusters data, but also shows similarity and dissimilarity between each cluster.
-Therefore, we can cluster our sample data and study the underlying structure of data, simultaneously.
+We chose SOM method over K-means due to the fact that SOMs not only cluster data, but also show similarity and dissimilarity between each cluster.
+Therefore, we can cluster our sample data and study the underlying structure, simultaneously.
 
@@
 In this project we apply SOM algorithm on M31 data, and trained 1D and 2D networks.
-Using smaller size networks we study the properties of the clusters and investigate relations between PAHs features with other features in M31.
-We create 2D SOMs from subsets of data as well as all available data, which helps us to understand the effect of each input in the position of the clusters in the SOM, which leads to prediction of the unmeasured quantities in a galaxy.
-Assuming that all the spiral nearby galaxies have similar properties, we apply 2D trained networks on data from the Pinwheel Galaxy (M101), which is another spiral nearby galaxy. 
+Using smaller networks we study the properties of the clusters and investigate relations between PAH features with other quantities in M31.
+We create 2D SOMs from subsets of data as well as all available data, which helps us to understand the effect of each input in the position of the clusters in the SOM.%, which leads to prediction of the unmeasured quantities in a galaxy.
+We apply 2D trained networks on data from the Pinwheel Galaxy (M101), which is a spiral nearby galaxy, to check weather that all the spiral nearby galaxies have similar properties,
 If our hypothesis is correct, we should be able to see that regions in M31 and M101 with the same positions in the SOM have the same properties.
 
-In Section $\S$~\ref{Sec: data_SOMN}, we present the sample data from M31 and M101, that we use in this study. 
+In Section $\S$~\ref{Sec: data_SOMN}, we present the sample data from M31 and M101 that we use in this study. 
 We describe the SOM method in Section $\S$~\ref{sec: method}. 

### 2016-07-04 main text/draft0.0.tex
Update draft0.0.tex
edits to abstract and affiliations. Added note re: keywords.

@@
 $^{1}$Department of Physics $\&$ Astronomy, Western University, London, ON N6A 3K7, Canada\\
-$^{2}$Center for Planetary Science \& Exploration, Western University, London, ON N6A 3K7, Canada\\
+$^{2}$Centre for Planetary Science \& Exploration, Western University, London, ON N6A 3K7, Canada\\
 $^{3}$Department of Physics $\&$ Astronomy, University of Victoria, Finnerty Road, Victoria, British Columbia, V8P 1A1, Canada\\
@@
 \begin{abstract} 
-Galaxies are very complex systems; therefore, a complete understanding of them cannot be achieved only from studying linear or logarithmic correlations between their properties and various waveband data.
-In the past few decades, a number of statistical methods have been developed and advanced to study and visualize complex big data.
-We used one of these methods to study properties of nearby galaxies and create a more clear picture of them.
+Galaxies are very complex systems; a complete understanding of them cannot be achieved only from studying linear or logarithmic correlations between their properties.
 The vast availability of data for nearby galaxies makes them suitable targets for exploratory data analysis. 
-Spatially resolved maps provide us with a unique view of the inside of galaxies. %and help better understand their properties.
-In this project, we utilized the Kohonen Self Organizing Map (SOM) method to study data from M31 and M101.
+In the past few decades, a number of statistical methods have been developed and advanced to study and visualize complex datasets.
+We used one of these methods to study the properties of nearby galaxies and create a clearer picture of them.
+%Spatially resolved maps provide us with a unique view of the inside of galaxies. %and help better understand their properties.
+In this project, we utilized the Kohonen Self Organizing Map (SOM) method to study observations of the nearby galaxies M31 and M101.
 %SOM is an unsupervised neural network for mapping and visualizing a complex and nonlinear high dimension data while preserving topological features of the original data.
@@
 We created SOMs of various sizes and used them to extract information about the galaxies.
-Using smaller-sized SOMs the data were clustered in 2 major groups; and for each group, we found correlations that could not have otherwise seen without clustering. 
+Using smaller-sized SOMs, we found that the data were clustered in 2 major groups; for each group, we found correlations that could not have otherwise been seen without clustering. 
 In the maps with larger sizes, we created networks to illustrate the relative relations of the regions with one another. 
-We then applied the SOMs that were generated from the M31 data to from M101. 
-We found regions with similar properties in both galaxies placed in close regions in the SOMs.  
-These results confirm that the generated SOMs can separate regions based on their physical properties, and can be used to make predictions for other regions in nearby galaxies or other targets. 
+We then applied the SOMs that were generated from the M31 data to data from M101 and 
+found that regions with similar properties in both galaxies were placed in close regions in the SOMs.  
+These results confirm that the generated SOMs can separate regions based on their physical properties and can be used to make predictions for other regions in nearby galaxies or other targets. 
 \end{abstract}
-\begin{keywords} 
+\begin{keywords} %PB: I think MNRAS only lets you have up to 6 and they are supposed to be from here: http://journals.aas.org/authors/keywords2013.html
 galaxies: individual: M31, galaxies: spiral, galaxies: star formation, galaxies: stellar content, galaxies: ISM, stars: formation, ISM: clouds, methods: observational, methods: statistical, data mining, methods:data analysis, techniques: image processing

### 2016-07-04 main text/draft0.0.tex
Update draft0.0.tex
edits to summary. Removed phrases like "we concluded that.."

@@
 
-We present results of studying spatially resolved regions in nearby galaxies using 
-The Self-organizing maps both cluster data and show relative distance between each cluster. 
-Therefore, we utilized it to find hidden subgroups in the data as well as finding relation between those groups.
+We present results of studying spatially resolved regions in nearby galaxies using Kohonen self-organizing maps.
+Self-organizing maps both cluster data and show relative distance between the clusters. 
+We utilized the method to find hidden subgroups in the data as well as finding relations between those groups.
 
-Using smaller-sized self-organizing maps, the M31 data are clustered into two major groups, which lead us to correlations that could not have otherwise been seen without clustering.
-We found that six of the regions in M31 create a subgroup of data, that have relatively lower amount of Mid- and far-infrared emission.
-PAH fluxes in these regions are highly anti-correlated with \halpha, \sii, \oiii~and IRAC 5.8~$\mu$m emission, stellar mass and RHI.
-These anti-correlations are insignificant when data from the whole galaxy are considered.
-We discussed possible reasons for these anti-correlations and argued that the most probable reason to PAHs anti-correlate with optical emission and RHI is having harder radiation.
-Harder radiation makes the size of H {\sc II} regions bigger and the size of PDRs smaller, which cause more \halpha~emission and less PAHs, respectively.
+Using smaller-sized self-organizing maps, we found that the M31 data are clustered into two major groups, which led us to correlations that could not have otherwise been seen without clustering.
+Six of the regions in M31 create a subgroup with relatively lower mid- and far-infrared emission.
+PAH fluxes in these regions are highly anti-correlated with \halpha, \sii, \oiii~and IRAC 5.8~$\mu$m emission, stellar mass and radiation hardness index.
+These anti-correlations are insignificant when the full dataset is considered.
+The most probable reason for PAHs to anti-correlate with optical emission line and RHI is a harder radiation field.
+This makes the size of H {\sc II} regions bigger and the size of photo-dissociation regions smaller, causing more \halpha~emission and less PAH emission, respectively.
 
-PAHs in clustered data also show anti-correlation with stellar mass.
-We discussed the possibility of that higher stellar mass might destroy PAHs and as a result we see anti-correlation between them.
-However, we did not find any correlation between 8/24~$\mu$m emission, as a tracer of PAH abundance, and stellar mass.
+PAHs in clustered data also show an anti-correlation with stellar mass.
+We discussed the possibility that higher stellar mass might destroy PAHs;
+however, we did not find any correlation between 8/24~$\mu$m emission, as a tracer of PAH abundance, and stellar mass.
 Unlike previous studies, we also did not find any correlation between 8/250~$\mu$m emission and stellar mass. 
-This results show that PAHs in the clustered regions in M31, do not heated by old stellar populations.
+This result shows that PAHs in the clustered regions in M31 are not heated by the old stellar populations.
 
-In the maps with larger sizes, networks can be used to illustrate the relative relations of the regions with one another.
-We found the relative similarity between M31 regions, by varying the size of networks.
+In self-organizing maps with larger sizes, networks can be used to illustrate the relations of the regions with one another.
+We found the relative similarity between M31 regions by varying the size of the networks.
 A one-dimensional network with 14 neurons was needed in order to
-separate all 10 regions; we concluded that some of the region in M31 (e.g. regions 4 and 7) have very similar properties.
-
-A two-dimensional networks provide us a more complete picture of the data.
-We created various subsets from input data and generated different networks which helped us to show a relative relations between regions in M31 more clearly.
-We showed that region 10 always become isolated in networks, except when we only used PAHs data to create a network.
-In that network region 10 blends more with other regions and only shows differences with data from region 8.
+separate all 10 regions; some of the regions in M31 (e.g. regions 4 and 7) have very similar properties.
+% PB joining paragraphs
+Two-dimensional networks provide us with a more complete picture of the data.
+We created various subsets of the input data and generated different networks which helped to show relations between regions in M31 more clearly.
+Region 10 always becomes isolated in the networks, except when we  used only PAH data to create a network. %PB: remind the reader where regions 8 and 10 are
+In that network region 10 blends more with other regions and only shows differences with the data from region 8.
 These results suggest that the PAHs in all 10 regions have almost the same properties.
@@
 % By converting the relative distance between regions to the probability distribution function, we could predict unobserved/unmeasured properties of the galaxies with 10 per cent uncertainty.
-We also applied the SOMs from M31 data to M101 data and found regions with similar properties in both galaxies placed in close regions in the SOMs.
-We show that using this ability of the SOM, we can predict properties of regions in other nearby galaxies very fast.
-We should note that we created our networks using values for 26 quantities from 10 regions in M31, which does not consider as a "big sample".
-Increasing dimension of the data and the number of regions would help to have more reliable networks.
-In future we can apply these networks on data from other nearby galaxies (e.g. M33 and M83), and learn about the properties of regions on those galaxies.
+Applying the SOMs from M31 to observations of M101, we found regions with similar properties in both galaxies placed in close regions in the SOMs.
+Using this ability of the SOM, we can predict properties of regions in other nearby galaxies very quickly.
+The networks we created used values for 26 quantities from 10 regions in M31, which is not a large sample.
+Increasing the dimension of the data and the number of regions would yield more reliable networks.
+In future we can apply these networks on data from other nearby galaxies (e.g. M33 and M83) and learn about the properties of regions in those galaxies.
 
 \section*{ACKNOWLEDGMENTS}
-The authors thank A. Tammour for her useful comments. 
+The authors thank Dr A.\ Tammour for useful comments. 
 S.R., P.B., and E.P.

### 2016-07-04 sections/data0.0.tex
Updating fig.s Captions
Update data0.0.tex
grammar and wording edits, plus a few comments.

--- 2016-06-18 sections/data0.0.tex
@@
 
-\section{DATA}
+\section{Study sample}
+\label{Sec: data_SOMN}
 
-We gathered data from 10 regions in M31 (Fig.~\ref{fig: regions in m31})  and 8 regions in M101 (Fig.~\ref{fig: regions in m101})  inputs for SOM maps.
-We chose those specific regions due to availability of the PAHs data for them.
-Besides PAHs data, for each galaxy, we chose spectroscopy and photometry data as well as their derived properties, such as SFR, stellar mass, dust luminosity (L$_{\rm DUST}$) and mass, metallicity, and gas mass.
-Table~\ref{tab: data} shows list of the data and their unit for both M31 and M101.
-We divided each values by the area of their region (in arcsec$^2$), to be able to compare values in both galaxies without being worried about their distances.
-The resolution of the data varies from less than 1$\arcsec$ to $60\arcsec \times 90 \arcsec$.
-Any attempt to match the PSF for these range, causes to use all the spectroscopic data.
-Besides the convolution methods conserve the flux per area.
-Therefore, we did not do any PSF matching in this paper and we used data in their original resolutions.
+Our study includes 10 regions in M31 (Fig.~\ref{fig: regions in m31}) and 8 regions in M101 (Fig.~\ref{fig: regions in m101}). 
+These specific regions were chosen for the availability of mid-infrared PAH spectroscopy.
+Besides PAH line strnegths, for each galaxy, we use spectroscopic and photometric observations as well as their derived properties, such as SFR, stellar mass, dust luminosity (L$_{\rm dust}$) and mass, metallicity, and gas mass.
+Table~\ref{tab: data} shows the full list of data and their units for both M31 and M101.
+Observed values were divided by the area of their region (in arcsec$^2$), to remove the distance factor from the data and compare values across galaxies.
+Since the spatial resolution of the observations varies from $<1\arcsec$ to $60\arcsec \times 90 \arcsec$, any attempt to match resolution would have caused a loss of information in some of the input quantities (e.g.
+the spectroscopic data).
+In this project we used flux per unit area, which the convolution methods conserve~\citep{Aniano12}, as the input data.
+Therefore, we did not perform any resolution matching and used data at their original resolution. %PB: Need to discuss these last few sentences; not sure I understand what you're saying.
 
@@
   \begin{figure}
-    \subfloat[MIPS24 image of M31, with position of 10 regions.\label{fig: regions in m31}]{
-      \includegraphics[width=0.5\textwidth]{../images0.0/M31/M31.png}
+    \subfloat[MIPS 24~$\mu$m image of M31~\citep{Gordon06}, with position of 10 regions from~\cite{Dim15} \label{fig: regions in m31}]{
+      \includegraphics[width=0.5\textwidth]{../images0.01/M31/M31.png}
     }
     \hfill
-    \subfloat[IRAC1 image of M101, with position of our 8 regions.\label{fig: regions in m101}]{
-      \includegraphics[width=0.5\textwidth]{../images0.01/M101/M101.png}
-    }
-    \caption{Position of the data in M31 (up) and M101 (down).}
+    \subfloat[IRAC 3.6~$\mu$m image of M101~\citep{Dale09}, with position of 8 regions.\label{fig: regions in m101}]{
+      \includegraphics[width=0.5\textwidth]{../images0.01/M101/M101.png}}
+    \caption{Position of regions that the input data for SOM that obtained from there in M31 (up) and M101 (down).}
     \label{fig:dummy}
@@
 %M31 data 
-%%%%% Sahar: More detail?
-    \subsection{M31 data}
+%%%%% Sahar: More detail, right?
+    \subsection{M31 observations}
+     \label{Sec: data_M31_SOMN}
 
-     The 10 regions in M31 were chosen due to availability of the PAH data for them. 
-     \cite{Dim15} studied PAH for those regions using {\it Spitzer}/Infrared Spectrograph\citep[IRS,][]{Houck04b} observations. 
-     They used {\tiny PAHFIT IDL} tool~\citep{Smith07b} and measured fluxes and equivalent widths of PAH features as well as atomic line features.
-     For spectroscopy part of our sample, we utilized their measured fluxes for PAH lines. 
-     \cite{Dim15} also reported metallicity of these regions (using results from \cite{Sanders12} for most regions), which e used them in our input sample.
-     We used radiation hardness index (RHI) instead of flux of individual atomic line, since they were only calculate the upper limit flux for most of the lines in most of the regions.
+     %The 10 regions in M31 were chosen due to availability of the PAH data for them. 
+     \cite{Dim15} using {\it Spitzer}/IRS observations to study PAHs in 10 regions chosen to span a range of mid-infrared flux ratios in M31. 
+     Fluxes and equivalent widths of PAH and atomic line features were measured using the~{\sc PAHFIT IDL} tool~\citep{Smith07b}.
+     %For spectroscopy part of our sample, we utilized their measured fluxes for PAH lines. 
+     \cite{Dim15} also measured metallicity and radiation hardness index (RHI) for these 10 regions.
+     We used the measured PAH feature fluxes, metallicity and RHI of each region as an input for SOMs.
 
-     For photometry part of the sample, we used data from \GALEX FUV and NUV channels~\citep{Martin05}, \halpha, [\sii] continuum and [\oiii] continuum emission~\citep{Massey07}, IRAC channels 1 to 4~\citep{Barmby06}, MIPS24 and 70~$\mu$m~\citep{Gordon06}, PACS100 and 160~$\mu$m and SPIRE250, 350, and 500~$\mu$m~\citep{Fritz12}.
-     We changed units of all our data to Wm$^{-2}$ to be the same unit as PAH fluxes.
-     We used $^{12}$CO (J:$1\rightarrow0$) line~\citep{Nieten06} and the atomic gas (H\,{\sc I}) 21~cm emission from \cite{Chemin09}.
-     We also utilized SFR(FUV + 24$\mu$m), stellar mass, total gas mass, and total infrared (TIR) luminosity (L$_{\rm TIR}$) data from \cite{Rahmani16}, and L$_{\rm DUST}$ and mass data from \cite{Draine14}.
+    For the photometry part of the sample, we used the \GALEX~\citep{Martin05} far-ultraviolet and near-ultraviolet (FUV and NUV) channel images; \halpha, \sii~and \oiii narrow band images~\citep{Massey07}, IRAC 3.6, 4.5, 5.8 and 8.0$\mu$m images ~\citep{Barmby06}; MIPS24 and 70~$\mu$m~images\citep{Gordon06}; and PACS 100 and 160~$\mu$m and SPIRE 250, 350, and 500~$\mu$m~\citep{Fritz12} images.
+     The units of all fluxes were converted to W~m$^{-2}$ in order to be the same as the PAH fluxes.
+     $^{12}$CO (J:$1\rightarrow0$) line emission images~\citep{Nieten06} and atomic gas (H\,{\sc I}) 21~cm emission images from~\cite{Chemin09} were added to the input data. 
+     For derived values, we utilized SFR(FUV + 24$\mu$m), stellar mass, molecular gas mass, atomic gas mass, total gas mass, and total infrared (TIR) luminosity (L$_{\rm TIR}$) from \cite{Rahmani16}, and L$_{\rm dust}$ and mass from \cite{Draine14}.
 
-    \subsection{M101 data}
-     For M101 galaxy, we used PAH fluxes which had been measured using {\tiny PAHFIT IDL} tool and reported in \cite{Gordon08}.
-     We also added their measurement of metallicity and RHI for these regions to our sample.
-     We used data available on NED~\footnote{The NASA/IPAC Extragalactic Database (NED) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.} website to gather our photometry data of M101.
-     We chose data from \GALEX FUV and NUV channels~\citep{depaz07}, IRAC channels 1 to 4, MIPS~24 and 70~$\mu$m~\cite{Dale09}, and  PACS~100 and 160~$\mu$m and SPIRE250, 350, and 500~$\mu$m~\cite{Kennicutt11}.
-     Same as M31 data, we used $^{12}$CO (J:$1\rightarrow0$) line~\citep{Helfer03} and the atomic gas (H\,{\sc I}) 21~cm emission from \cite{Walter08} data.
-     SFR(FUV + 24$\mu$m), stellar and total gas map were calculated followed method described in \cite{Rahmani16} to create these maps.
+    \subsection{M101 observations}
+    \label{Sec: data_M101_SOMN} 
+     \cite{Gordon08} measured PAH fluxes, metallicity and RHI for M101 in XX regions chosen.. % PB: reason for selecting?
+%     We also added their measurement of metallicity and RHI for these regions to our sample.
+     We used NED~\footnote{The NASA/IPAC Extragalactic Database (NED) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.} website to gather imaging observations of M101, including
+      \GALEX FUV and NUV~\citep{depaz07}, IRAC $3.6-8.0\mu$m, MIPS~24 and 70~$\mu$m~\citep{Dale09}, and  PACS~100 and 160~$\mu$m and SPIRE~250, 350, and 500~$\mu$m emission from~\cite{Kennicutt11}.
+     As for M31, we used $^{12}$CO (J:$1\rightarrow0$) line emission images~\citep{Helfer03} and atomic gas (H\,{\sc I}) 21~cm emission images from \cite{Walter08}.
+     SFR(FUV + 24$\mu$m), stellar and total gas mass maps were calculated using the same methods as for M31.
+
+     Some of the correlations between single-wavelength emission and galaxy properties are well-known.
+     Emission in the 3.6$\mu$m band traces the old stellar population very well~\citep[e.g]{Leitherer99,Smith07a} and it can be used to calculate the stellar mass~\citep{Eskew12}.
+     FUV, \halpha, and TIR emission are indicators of star forming regions.
+     In this project we used the SFR traced by the FUV emission, corrected for foreground stars using NUV emission and for dust extinction using 24$\mu$m emission.
+     Total infrared emission is calculated from a modified version of~\cite{Draine07} calibration using using 8, 24, 70, and 160 $\mu$m emission~\citep{Boquien10}.
+     To make sure that we do not use the observed data as input data in multiple forms, we removed all the observed data that were used to calculate galaxies properties from the input sample.
+     We used this sample of observations as the main input for creating SOMs.
+     Fig.~\ref{fig: cor_all} shows the Pearson correlation coefficients between the observations computed with a confidence level of $95\%$.
+
+      \begin{figure}
+                \centering
+                \includegraphics[width=0.5\textwidth]{../images0.01/cor_plots/M31_all_derived_ones_core_plot_for_paper.pdf}
+            \caption{Pearson correlation coefficients with a confidence level of 95$\%$ for all data in subset 0.
+The colours show the Pearson correlation coefficients where 1 means highly correlated and $-1$ means highly anti-correlated quantities.
+The non-significant correlations were left empty.}
+            \label{fig: cor_all}
+        \end{figure}

### 2016-07-04 sections/R20.0.tex
Update R20.0.tex
edits up to but not including last subsection

@@
  \label{sec: 2d_cluster}
-    Although 1D networks are great to have a general idea about the data, neurons in 1D maps have maximum two neighbours, which causes some limitation in the results.
-    In 2D networks, each neuron has two to six neighbours, which allowed them to to capture a whole picture of the complicated relations in the input data.
-    Therefore, we created $10\times10$ 2D networks to study the data in details.
-    As mentioned in previous sections, the size of SOMs are arbitrary and users must decide about it based on what their goals of using SOMs are.
-    In this section we chose $10\times10$ size despite that we knew, from the size of our input data, that most of the neurons would be empty.
-    Using 2D networks, we are mostly interested in the ability of the SOMs to showing underlying structure of the data rather than its clustering features.
+    Although 1D networks are helpful to give a general idea about the data, neurons in 1D maps have a maximum of two neighbours, which can limit the usefulness of the results.
+    In 2D networks, each neuron has two to six neighbours, which allows them to to capture a complete picture of the complicated relations in the input data.
+    Accordingly, we created $10\times10$ 2D networks to study the data in detail.
+    As mentioned in previous sections, the size of SOMs are arbitrary and must be decided by users based on their goals for use of the SOM.
+    In this section we chose $10\times10$ size despite knowing, from the size of our input data, that most of the neurons would be empty.
+    Using 2D networks, we are mostly interested in the ability of the SOMs to show the underlying structure of the data rather than its clustering features.
     \import{../sections/image_texts/}{all.tex}
-    Fig.~\ref{fig: all_derived_ones} shows the 2D SOM of M31 data.
-    Similar to the Fig.~\ref{fig: M31_net_1by14}, all the 10 regions are completely separated from each other in Fig.~\ref{fig: all_derived_ones}.
+    Fig.~\ref{fig: all_derived_ones} shows the 2D SOM of the M31 data.
+    Similar to Fig.~\ref{fig: M31_net_1by14}, all the 10 regions are completely separated from each other in Fig.~\ref{fig: all_derived_ones}.
 
-    Regions 4 and 7 are in the top left of Fig.~\ref{fig: all_derived_ones} with very bright colour between their neurons, which presents that these two regions are very similar.
-    Considering the position of these two regions in M31 (Both of these regions are right on the edge of the star forming rings in the galaxy), similarity of these two regions were predictable.
-    Position of region 3 on the SOM is close to the position of regions 4 and 7, but with darker colour between the nodes. 
-    In Fig.~\ref{fig: regions in m31} it is clear that this region in M31 is closer to regions 4 and 7 than any other region, but it is on the outer side of the star forming ring.
-    Regions 5 and 6 are in their second neighbourhood on the SOM, with a medium gray colour between them.
-    These two regions are around the inner ring of the galaxy.
-    Regions 8 and 6 are both in the inner ring of M31, but region 6 is in the region with more star formation, which could be the main reason for their relative distance in the SOM in Fig.~\ref{fig: all_derived_ones}.
+    Regions 4 and 7 are in the top left of Fig.~\ref{fig: all_derived_ones} with a very bright colour between their neurons, indicating that these two regions are very similar.
+    Considering the position of these two regions in M31 (both right on the edge of the star forming rings in the galaxy), similarity of these two regions was predictable.
+    The position of region 3 on the SOM is close to the position of regions 4 and 7, but with a darker colour between the nodes. 
+    In Fig.~\ref{fig: regions in m31} it is clear that this region in M31 is physically closer to regions 4 and 7 than to any other region, but it is on the outer side of the star forming ring.
+    Regions 5 and 6 are in the second neighbourhood on the SOM, with a medium gray colour between them.
+    These two regions are physically located around the inner ring of the galaxy.
+    Regions 8 and 6 are both in the inner ring of M31, but region 6's location has more star formation, which could be the main reason for their relative distance in the SOM in Fig.~\ref{fig: all_derived_ones}.
 
     Regions 1 and 9 are close to each other, and in the same side of the star forming ring. 
-    However, region 1 is in an area of the galaxy with less diffuse \halpha~emission than region 9, that might be the reason for their distances in SOM.
-    Region 2 is more distant from other regions in the galaxy, and placed in the star forming ring.
+    However, region 1 is in an area of the galaxy with less diffuse \halpha~emission than region 9, which might be the reason for their distances in SOM.
+    Region 2 is more distant from other regions in the galaxy and placed in the star forming ring.
     However, similar to regions 1 and 4, region 2 is located in an area of the galaxy with less diffuse \halpha~emission.
-    Therefore, place of region 2 in the SOM is more favoured towards regions 1 and 4. 
-    Region 10 is placed in the bulge of the galaxy, and its position on the SOM is isolated from all the other regions by a strip of a dark colours.
+    Therefore, the place of region 2 in the SOM tends towards regions 1 and 4. 
+    Region 10 is in the bulge of the galaxy, and its position on the SOM is isolated from all the other regions by a strip of a dark colours.
 
     In order to analyse effects of any input data on the final SOM, in the following we created SOMs from various subsets of data.
-    We compare results of the subsets with one another and with SOM created from all data in Fig.~\ref{fig: all_derived_ones}.
+    We compare results of the subsets with one another and with the SOM created from all data in Fig.~\ref{fig: all_derived_ones}.
 
@@
     \label{sec: subsets}
-            For analysing subsets, we creating SOMs by using only PAHs data, as well as using all data except PAHs ones (Fig.~\ref{fig: PAHS_or_not_PAHs}).
+            For analysing subsets, we creating SOMs by using only PAH data, as well as using all data except the PAHs (Fig.~\ref{fig: PAHS_or_not_PAHs}).
              \import{../sections/image_texts/}{PAHS_or_not_PAHs.tex}
@@
             However, in Fig.~\ref{fig: all_derived_ones} and Fig.~\ref{fig: wt_pahs}, region 10 is isolated from the other regions, while in Fig.~\ref{fig: only_pahs}, region 10 is much less isolated and only shows complete dissimilarity with region 8.
-            Regions 9 and 10 are totally isolated in SOMs in Fig.~\ref{fig: wt_pahs}, but in Fig.~\ref{fig: only_pahs}, they are more similar to other regions.
+            Regions 9 and 10 are totally isolated in the SOMs in Fig.~\ref{fig: wt_pahs}, but in Fig.~\ref{fig: only_pahs}, they are more similar to other regions.
             In both SOMs in Fig.~\ref{fig: PAHS_or_not_PAHs}, there are dissimilarities between regions in M31 but in Fig.~\ref{fig: wt_pahs}, the colours are much darker than the ones in Fig.~\ref{fig: only_pahs}.
-            This indicates that there are more similarity between PAHs features from all 10 regions then the other input data.
+            This indicates that there is more similarity between the PAH features over all 10 regions than between the other input data.
 
-            We increased the dimension of input data in Fig.~\ref{fig: only_pahs} (PAH only data), gradually, by adding data from other quantities of galaxies to the input data. 
-            The order of adding data is the same as order of data in Fig.~\ref{fig: cor_all}, i.e.
-SOM in Fig~\ref{fig: inc_D_col3s}a was created from PAHs data and H$\alpha$ emission as input data, SOM in Fig~\ref{fig: inc_D_col3s}b created from PAHs, H$\alpha$ emission and [\sii] continuum as input data, and so on.
+            We increased the dimension of input data in Fig.~\ref{fig: only_pahs} (PAH only data) gradually, by adding other quantities to the input data. 
+            The order in which data were added is the same as the order in Fig.~\ref{fig: cor_all}, i.e.
+the SOM in Fig~\ref{fig: inc_D_col3s}a was created from PAH and H$\alpha$ emission as input data, the SOM in Fig~\ref{fig: inc_D_col3s}b created from PAHs, H$\alpha$ emission and [\sii] continuum, and so on.
             \import{../sections/image_texts/}{col3byall.tex}
 
-            SOM algorithm assigns random weight to each network, that causes the overall position of regions in networks (even with the same input data) changes in each run of the algorithm.
-            However, the position of each region regarding to other regions changes dramatically only because of the new sets of input data is given to the algorithm (assuming all the initial values for the run are intact).
+            The SOM algorithm assigns a random weight to each network that causes the overall position of regions in networks (even with the same input data) to change in each run of the algorithm.
+            However, the position of each region relative to other regions changes dramatically only when the new sets of input data are given to the algorithm (assuming all the initial values for the run are unchanged).
             In all SOMs in Fig~\ref{fig: inc_D_col3s}, region 10 is located in the corner of the SOMs, but in  Figs~\ref{fig: inc_D_col3s}a,~\ref{fig: inc_D_col3s}d,~\ref{fig: inc_D_col3s}g,~\ref{fig: inc_D_col3s}k, and ~\ref{fig: inc_D_col3s}l, it is placed in the left side of the SOMs and in the others it is in the right side of the networks.
-            In our discussion on differences between networks, we do not address the changes in the network due to initialization of the SOM algorithm and only consider the effect of changing the input data in the network.
+            In our discussion on differences between networks, we do not address the changes in the network due to initialization of the SOM algorithm and only consider the effect of changing the input data.
 
-            Comparing Figs.~\ref{fig: inc_D_col3s}a to ~\ref{fig: inc_D_col3s}o shows that adding \halpha~emission data to PAHs features causes regions 9 and 10 become isolated. 
-            Increasing dimension of the input data makes region 10 more isolated.
-            The relative position of regions 4 and 7 stays the same with increasing the input data. 
-            Adding SPIRE 350, 500~$\mu$m emission and L$_{\rm dust}$ do not have any adequate effect on the networks.
+            Comparing Figs.~\ref{fig: inc_D_col3s}a to ~\ref{fig: inc_D_col3s}o shows that adding \halpha~emission data to PAH features causes regions 9 and 10 become isolated. 
+            Increasing the dimension of the input data makes region 10 more isolated.
+            The relative positions of regions 4 and 7 stay the same with increasing the dimensions of the input data. 
+            Adding SPIRE 350, 500~$\mu$m emission and L$_{\rm dust}$ does not have any obvious effect on the networks.
             Stellar mass, total gas mass, dust mass and RHI data alternate the distances between neurons effectively, but it seems that adding SFR, L$_{\rm TIR}$ and metallicity data revoke those changes.
 
-            We generated other subsets of the data based on the results in Figs~\ref{fig: inc_D_col3s} to study effects of the input data on SOMs, further.
-            Subset 1, that are listed in Tab.~\ref{tab: subset1}, includes all the inputs data except data from stellar mass.
-            Tab.~\ref{tab: subset5} is the list of data that were used in a subset 2, which includes all data except the fact that instead of the individual PAH fluxes we added them all together and have total PAH flux.
-            For subset 3 ( in Tab.~\ref{tab: subset6}), we removed SPIRE 250 and 500~$\mu$m from subset 2.
-            Figs.~\ref{fig: subset1} --~\ref{fig: subset6} show SOMs that are created by data from subsets 1 to 3, respectively.
-            The rest of the subsets are discussed in Appendix.~\ref{sec: app_2d_soms_SOMN}.
+            We generated other subsets of the data based on the results in Figs~\ref{fig: inc_D_col3s} to further study the effects of the input data on SOMs.
+            Subset 1, listed in Tab.~\ref{tab: subset1}, includes all the input data except stellar mass.
+            Tab.~\ref{tab: subset5} lists data used in subset 2, which includes all data except that the PAH fluxes are combined into a total PAH flux. 
+            For subset 3 ( in Tab.~\ref{tab: subset6}), SPIRE 250 and 500~$\mu$m were removed from subset 2.
+            Figs.~\ref{fig: subset1} --~\ref{fig: subset6} show SOMs created by data from subsets 1 to 3, respectively.
+            The remaining subsets are discussed in Appendix.~\ref{sec: app_2d_soms_SOMN}.
 
-            The results from Table~\ref{tab: subset1} is shown in Fig.~\ref{fig: subset1}. 
-            In this SOM compared with the SOM from all the data in Fig.~\ref{fig: all_derived_ones}, regions 1 and 9 are closer to region 10. 
+            The results from Table~\ref{tab: subset1} are shown in Fig.~\ref{fig: subset1}. 
+            In this SOM, compared with the SOM from all the data in Fig.~\ref{fig: all_derived_ones}, regions 1 and 9 are closer to region 10. 
             Regions 1 and 9 are the ones with lowest stellar mass values, and region 10 has the highest stellar mass value among those 10 regions. 
             Since the differences in the amount of stellar mass was one of the most distinct differences between these three regions, removing stellar mass from input data reduced the distance between these regions.
-            Regions 5, 6 and 8 are in the same relative distance from each other as in Fig.~\ref{fig: all_derived_ones}, but they all are closer to the position of region 10.
+            Regions 5, 6 and 8 have the same relative distance from each other as in Fig.~\ref{fig: all_derived_ones}, but they all are closer to the position of region 10.
             Distance between regions 2 and 3 is reduced but in the meantime the colour between them became darker.
@@
 
-            Changing from separate values for each PAH features to a single value for the total PAHs caused small changes to the SOM map in Fig.~\ref{fig: subset5} compare to the one in Fig.~\ref{fig: all_derived_ones}.
-            Distance between the relative position of regions 6 and 8 increased significantly, while the position of region 2 moved closer to the positions of regions 4 and 7.
-            The winner neurons for regions 3 and 5 moved towards each other, but the colours between them became much more darker.
+            Changing from separate values for each PAH features to a single value for the total PAHs caused small changes to the SOM map in Fig.~\ref{fig: subset5} compared to the one in Fig.~\ref{fig: all_derived_ones}.
+            The distance between the positions of regions 6 and 8 increased significantly, while the position of region 2 moved closer to the positions of regions 4 and 7.
+            The winner neurons for regions 3 and 5 moved towards each other, but the colours between them became much darker.
 
@@
 
-            Fig.~\ref{fig: subset6} shows the SOM generated from data that are listed in Tab.~\ref{tab: subset6}, which includes all the data from Tab.~\ref{tab: subset5} except SPIRE 250 and 500~$\mu$m emission.
+            Fig.~\ref{fig: subset6} shows the SOM generated from data listed in Tab.~\ref{tab: subset6}, which includes all the data from Tab.~\ref{tab: subset5} except for  the SPIRE 250 and 500~$\mu$m emission.
             Although for most of the regions we see the changes in their positions, the colours between neurons changes as well. 
             %Therefore, we can conclude that these changes caused by the differences in the initial assigned weights.
-            The distance between the positions of the regions 4 and 2 are increased.
-            The same happened for distances between regions 7, 3 and 6.
-            In both cases, SPIRE 250 and 500~$\mu$m emission of these regions are similar to one another, and removing these two parameters from input data moved the positions of the regions further from each other.
+            The distance between the positions of the regions 4 and 2 is increased as are the
+            distances between regions 7, 3 and 6.
+            In both cases, SPIRE 250 and 500~$\mu$m emission of these regions are similar to one another, and removing these two parameters from the input data moved the positions of the regions further from each other.
             \import{../sections/tables/}{subset6.tex}
@@
 
-    \subsection{Testing networks using M101 data}
+    \subsection{Testing networks using M101 observations}
     Another application of SOM for nearby galaxies is to apply the trained networks on the data from other galaxies in order to predict properties of the observed regions in them. %%eh

### 2016-07-05 sections/image_texts/all.tex
Update all.tex
wording changes

@@
         \includegraphics[width=0.5\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and26.png}
-    \caption{Two dimensional SOM of M31 using $10\times10$ grid.
-Similar to figs.\ref{fig: sample} and \ref{fig: M31_nets_1d}, The hexagonal shapes show the neurons and the grey cycle colours between neurons show the differences between weight of each neuron.}
+    \caption{Two-dimensional self-organizing map of M31 observations using a $10\times10$ grid.
+Similar to Figs.\ref{fig: sample} and \ref{fig: M31_nets_1d}, the hexagonal shapes show the neurons and the grey scale colours between neurons show the differences between weights of each neuron.}
     \label{fig: all_derived_ones}

### 2016-07-05 sections/image_texts/col3byall.tex
Update col3byall.tex
wording

@@
     \end{subfigure}
-    \caption{Similar to Fig.~\ref{fig: all_derived_ones}, here we show the result from increasing dimension of input data from Fig.~\ref{fig: only_pahs} to 25, gradually.
-The order of input data is the same as order of data in Fig.~\ref{fig: cor_cluster1}.}
+    \caption{Similar to Fig.~\ref{fig: all_derived_ones}, the result from gradually increasing the dimension of the input data from Fig.~\ref{fig: only_pahs} to 25.
+The order of the input data is the same as the order in Fig.~\ref{fig: cor_cluster1}.}
     \label{fig: inc_D_col3s}

### 2016-07-05 sections/R10.0.tex

@@
 %----------------------------------------------------------------------------------------
-\section{One dimensional Self-organizing maps}
+\section{One dimensional self-organizing maps}
     \label{Sec: 1d_cluster}
 %Why 1D maps are useful
-    The purpose of the exploring M31 data with 1D maps is to monitor the general behaviour of data. 
-    1D SOMs can have from the minimum number of clusters, $1\times2$, to the highest number of cluster possible.
-    In a small sample like ours, smaller grid SOMs are very useful to find correlations that cannot be found without the clustering the data.
-    On the other hand, higher grid 1D SOMs are a helpful tool to get quick insight into data.
+    The purpose of  exploring the M31 data with 1D maps is to monitor the general behaviour of data. 
+    One-dimensional SOMs can have the minimum number of clusters, $1\times2$, up to the highest number of clusters possible.
+    In a small sample like ours, smaller grid SOMs are very useful to find correlations that cannot be found without  clustering the data.
+    On the other hand, larger grid 1D SOMs are a helpful tool to get quick insight into the data.
 %    In the following section, we are going to show how we used 1D SOMs to extract information from available data in M31.
@@
         The $1\times2$ network (Fig.~\ref{fig: M31_net_1by2}) shows how the M31 data can be divided into two broad categories.
-        While the $1\times14$ network (Fig.~\ref{fig: M31_net_1by14}) is the first network that all the regions in M31 are completely separated.
-        Since in the higher network sizes, regions have more space to be separated based on their differences, we can see that from $1\times2$ to $1\times14$ network the M31 regions separated from each other increasingly, until they are completely separated.
+        The $1\times14$ network (Fig.~\ref{fig: M31_net_1by14}) is the first network in which all the regions in M31 are completely separated.
+        Since in the higher network sizes, regions have more space to be separated based on their differences,  going from the $1\times2$ to the $1\times14$ network the distance between M31 regions increases, until they are completely separated.
 
-        In Fig.~\ref{fig: M31_net_1by2}, it is clear that by forcing the regions in the M31 to be divided into two groups, regions 1, 2, 9 and 10 occupy one neuron and the other regions occupy the other one.
-        The medium grey colour between two neurons indicates that there are some similarity between two groups, but they are not very similar. 
-        By increasing the size of the neurones to three, in Fig.~\ref{fig: M31_net_1by3}, we can see that the region 2 separates itself from the other regions and occupies the middle neuron.
-        The white colour between two left neurons suggests that regions, which occupy these neurons are very similar to each other, while the black colour between two right neurons expresses otherwise.
+      Fig.~\ref{fig: M31_net_1by2} shows that by forcing the regions in the M31 to be divided into two groups, regions 1, 2, 9 and 10 occupy one neuron and the other regions occupy the other one.
+        The medium grey colour between two neurons indicates that there are some similarities between two groups, but they are not very similar. 
+        By increasing the size of the neurons to three, in Fig.~\ref{fig: M31_net_1by3}, we can see that region 2 separates itself from the other regions and occupies the middle neuron.
+        The white colour between two left neurons suggests that the regions which occupy these neurons are very similar to each other, while the black colour between two right neurons indicates otherwise.
 
         %%%Talking about four right regions
-        \cite{Dim15} showed that the regions 1, 2, 9, and 10 have higher PAH flux intensity compare to other regions (Fig. 5 in \cite{Dim15}). 
+        \cite{Dim15} showed that regions 1, 2, 9, and 10 have higher PAH line fluxes compared to other regions (Fig. 5 in \cite{Dim15}). 
         %Regions 1, 2, and 9 are in the 10~Kpc ring and region 10 is located in the bulge of M31; however, regions 3 to 8 are located slightly out of the inner ring or the 10~kpc one.
-        These regions also have relatively high intensity in all the MIR and FIR bands, and have high dust luminosity and dust mass.
-        The higher values in these values could be the reason that these 4 regions become separated from the others, in $1\times2$ network.
-        Besides, Regions 1, and 9 are in the 10~Kpc ring, region 2 is slightly out of the 10~Kpc ring and the region 10 is in the bulge of M31; however, regions 3 to 8 are located out of the inner ring or the 10~kpc ring (Fig.~\ref{fig: regions in m31}).
-        The differences in their positions might be the reason of regions 1, 2, 9 and 10 having higher values in some quantities than the others. 
-        The similarity in the other input values with the other regions causes regions 1, 2, and 9 gradually move towards other regions, and have more distance with region 10, in the higher grid SOMs.
+        These regions also have relatively high intensities in all the mid-infrared and far-infrared bands and have high dust luminosity and dust mass.
+        The higher values for these quantities could be the reason that these 4 regions become separated from the others in the $1\times2$ network.
+        Regions 1 and 9 are in the 10~kpc ring, region 2 is slightly out of the 10~kpc ring and region 10 is in the bulge of M31; however, regions 3 to 8 are located out of the inner ring or the 10~kpc ring (Fig.~\ref{fig: regions in m31}).
+        The differences in their positions might be the reason for regions 1, 2, 9 and 10 having higher values in some quantities than the others. 
+        Similarities with the other regions in the other input values causes regions 1, 2, and 9 to gradually move towards other regions and away from region 10 in the higher grid SOMs.
        % Therefore, in 1D networks with 14 neurons or higher, regions 1, 2, and 9 completely are separated from region 10, and show more similarity to other regions than to the region 10.
@@
              }%%% What should I do with this one! It doesn't look good visually
-            \caption{SOM of the M31 data from $1\times2$~, $1\times3$~and $1\times14$~grids.
+            \caption{SOM of the M31 data from $1\times2$, $1\times3$~and $1\times14$~grids.
 The axes show the position of the neurons.
-The purple Hexagonal shapes represent the neurons.
-The grey cycle colours show the differences between weight of each neuron with white is the minimum differences and black has the maximum one.
-The numbers in the plot show the regions that are located in each neuron.}
+The purple hexagonal shapes represent the neurons.
+The grey scale colours show the differences between weight of the neurons, with white as the minimum difference and black as the maximum.
+The numbers in the plot show the M31 regions located in each neuron.}
             \label{fig: M31_nets_1d}
@@
         %%Network 1by14
-        The network with 14 neurons, in Fig.~\ref{fig: M31_net_1by14}, is the first network, that has no neuron occupied by more than one region.
-        In a higher grid SOM, network pays more attention to smaller details and differences in the input data.
-        Therefore, since at least 14 neurons are needed to separate all the 10 regions in M31, we can conclude that some of the regions have very small differences.
-        Regions that are located in similar area in M31, like region 7 and 4 (see Fig.~\ref{fig: regions in m31}), are most likely show more similarity to each other.
-        In Fig.~\ref{fig: M31_net_1by14}, the most right neuron is occupied by region 10.
-        Two black colour between this region and the others indicates the high differences between this neuron and the other ones.
-        The region 10 is located in the bulge of M31, and its separation from other regions, which are mostly located around the inner or outer rings, is due to the fact that most of the input values for this region is much higher than the other regions.
-        The region 8 occupies the most right neurons in this network, that suggests that this region has the most differences from region 10.
+        The network with 14 neurons, in Fig.~\ref{fig: M31_net_1by14}, is the first network that has no neuron occupied by more than one M31 region.
+        In a larger-grid SOM, the network pays more attention to smaller details and differences in the input data.
+        Therefore, since at least 14 neurons are needed to separate all 10 regions in M31, we can conclude that some of the regions have very small differences.
+        Regions that are located in similar areas in M31, like region 7 and 4 (see Fig.~\ref{fig: regions in m31}), are most likely to show more similarities to each other.
+        In Fig.~\ref{fig: M31_net_1by14}, the right-most neuron is occupied by region 10.
+        Two black colours between this region and the others indicate the large differences between this neuron and the other ones.
+       Region 10 is located in the bulge of M31, and its separation from other regions, which are mostly located around the inner or outer rings, is due to the fact that most of the input values for this region are much higher than the other regions.
+%PB: so is the SOM just telling us that the surface brightness is higher in the bulge?
+        The region 8 occupies the right-most neuron in this network, suggesting that this region has the most differences from region 10.
 
@@
         \label{sec: inside_the_2_neurons}
-        Using SOMs, we can identify hidden subgroups in our samples. 
-        Each of these subgroups were separated from each other, for a reason.
-        This reason can vary from having higher values in some specific wavelengths, as discussed in Sec.~\ref{Sec: 1d_cluster}, to some unknown correlations between data, that cannot be seen in other groups or in a Galaxy as a whole.
-        To investigate the later, we showed the Pearson correlation coefficients for the inputs from regions 3 to 8 in Fig.~\ref{fig: cor_cluster1}, which were clustered together in the $1\times2$ and $1\times3$ networks (see Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}).
+        Using self-organizing maps, we can identify hidden subgroups in our samples. 
+        Each of these subgroups were separated from each other for a reason.
+        This reason can vary from having higher values in some specific properties, as discussed in Sec.~\ref{Sec: 1d_cluster}, to some unknown correlations between data that cannot be seen in other groups or in the galaxy as a whole.
+        To investigate the latter, we show in Fig.~\ref{fig: cor_cluster1} the Pearson correlation coefficients for the inputs from regions 3 to 8, which were clustered together in the $1\times2$ and $1\times3$ networks (see Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}).
 
@@
         \includegraphics[width=0.5\textwidth]{../images0.01/cor_plots/M31_derived_3_to_8_core_plot_for_paper.pdf}%%% cut the white regions around the figure
-        \caption{Same as Fig.~\ref{fig: cor_all}, but here we used data from regions grouped in the left side of the Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}. }
+        \caption{Same as Fig.~\ref{fig: cor_all}, but here we used data from regions grouped in the left sides of Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}. }
           \label{fig: cor_cluster1}
@@
         %%% what regions' version shows and how it compares with the other one:
-        In Fig.~\ref{fig: cor_all}, which shows the Pearson correlation coefficients from data in all 10 regions, all the PAH features highly correlate with each other. 
+        In Fig.~\ref{fig: cor_all}, which shows the Pearson correlation coefficients from data in all 10 regions, all the PAH features are highly correlated with each other. 
         Also, there are very strong correlations between all the PAH features and PACS~100~$\mu$m~, SPIRE 250 to 500~$\mu$m~emission, L$_{\rm dust}$, L$_{\rm TIR}$, SFR, and metallicity.
-        However, in Fig.~\ref{fig: cor_cluster1}, 12.0 and 12.7~$\mu$m~PAH fluxes do not show any significant or strong correlation with PAH fluxes in other wavelengths or most of the other quantities.
-        The only exceptions are the strong correlation between PAH flux at 12~$\mu$m and L$_{\rm dust}$, and between 12 and 12.7~$\mu$m PAH fluxes.
+        However, in Fig.~\ref{fig: cor_cluster1}, the 12.0 and 12.7~$\mu$m~PAH fluxes do not show any significant or strong correlation with PAH fluxes in other wavelengths, or with most of the other quantities.
+        The only exceptions are the strong correlations between PAH flux at 12~$\mu$m and L$_{\rm dust}$, and between the 12 and 12.7~$\mu$m PAH fluxes.
         Since there are only 6 regions in this cluster, even one outlier in the data may cause the correlation coefficient to become insignificant.
         By removing the outlier, the correlations between 12.0 and 12.7~$\mu$m~PAH fluxes and the other quantities show themselves.
+%PB: need to discuss which one is the outlier and why it is reasonable to remove it
 
-        For the rest of the PAH fluxes in Fig.~\ref{fig: cor_cluster1}, there are not any significant correlations with PACS~100~$\mu$m, L$_{\rm dust}$, L$_{\rm TIR}$, SFR, or metallicity, neither.
-        They have correlations with SPIRE emission, but they are weaker than the ones with data from all regions.
+        For the remaining PAH fluxes in Fig.~\ref{fig: cor_cluster1}, there are no significant correlations with PACS~100~$\mu$m, L$_{\rm dust}$, L$_{\rm TIR}$, SFR, or metallicity.
+        These fluxes correlate with SPIRE emission, but to a lesser extent than for data from all regions.
         Correlations between PAH features and SFR, and L$_{\rm TIR}$ are well-studied~\citep[e.g.][]{Tielens08,Peeters04}. 
-        Many groups used PAH features as a tracer of SFR by finding correlations between 
-        PAH emission and SFR derived from extinction corrected \halpha~\citep[e.g.][]{Shipley16,Khramtsova13,Calzetti07}.
+        Many groups have used PAH features as a tracer of SFR by finding correlations between 
+        PAH emission and SFR derived from extinction-corrected \halpha~\citep[e.g.][]{Shipley16,Khramtsova13,Calzetti07}.
         These correlations are seen in Fig.~\ref{fig: cor_all}, when we considered the data from all regions, but not in Fig.~\ref{fig: cor_cluster1} when considering the clustered data.
-        Further analyses show that the absence of correlations between PAH fluxes and SFR, is because of one outlier in data (Region 6). 
-        When we disregard the outlier data, high correlations between 6.2 to 11.3~$\mu$m~PAHs and SFR (and L$_{\rm TIR}$) reappear.
-        Strong ant-correlation between 6.2 to 11.3~$\mu$m~PAH features and RHI, stellar mass, \halpha, \sii, \oiii, and IRAC~5.6~$\mu$m~emission in Fig.~\ref{fig: cor_cluster1} had not be seen in Fig.~\ref{fig: cor_all}.
+        Further analyses show that the absence of correlations between PAH fluxes and SFR, is because of one outlier: Region 6. 
+        When we disregard this region, high correlations between 6.2 to 11.3~$\mu$m~PAHs and SFR (and L$_{\rm TIR}$) reappear.
+        Strong anti-correlations between 6.2 to 11.3~$\mu$m~PAH features and RHI, stellar mass, \halpha, \sii, \oiii, and IRAC~5.6~$\mu$m~emission in Fig.~\ref{fig: cor_cluster1} were not seen in Fig.~\ref{fig: cor_all}.
 
-        Anti-correlations between PAH features and the \halpha, \sii, and \oiii~emission could be the result of one the following. 
+        Anti-correlations between PAH features and the \halpha, \sii, and \oiii~emission could be the result of one of the following. 
         First, the optical data are not corrected for dust extinction.
-        The PAH features correlate with amount of dust while \halpha~emission anti-correlate with amount of dust due to extinction \citep{Calzetti94}.
-        Therefore,higher amount of PAH fluxes means higher amount of dust abundance and less \halpha~emission (The same for \sii~and \oiii~emission).
-        Second, it is the effect of observing apertures.
-        If the observed regions are located in the edge of the H {\sc II} regions we would expect too see more PAH and less \halpha~emission. %%% reference?
-        The anti-correlations between 6.2 to 11.3~$\mu$m~PAH features and RHI have been seen in other studies, too~\citep[e.g.][]{Dim15, Gordon08, Wu06}.
-        \cite{Wu06} discussed these ant-correlations could be the result of destruction of the PAH due to the high amount of harder radiation (thus higher RHI).
+        The PAH features correlate with the amount of dust while \halpha~emission anti-correlates with amount of dust due to extinction \citep{Calzetti94}.
+        Therefore, higher PAH fluxes imply higher dust abundance and less \halpha~emission, and the same for \sii~and \oiii~emission.
+        Second, is the possible effect of observing apertures.
+        If the observed regions are located near the edge of H {\sc II} regions we would expect to see more PAH and less \halpha~emission. %%% reference? PB: I will try to find one.
+        The anti-correlations between 6.2 to 11.3~$\mu$m~PAH features and RHI have been seen in other studies, as well~\citep[e.g.][]{Dim15, Gordon08, Wu06}.
+        \cite{Wu06} suggested these anti-correlations could be the result of PAH destruction due to a high amount of harder radiation (thus higher RHI).
         On the other hand, \cite{Gordon08} argued that the harder radiation could make the photodissociation regions (PDRs) smaller.
-        The PAH features are mostly coming from the PDRs that are surrounded by H {\sc II} regions, and the PAH features underlying continuum emission is from the H {\sc II} regions.
+        The PAH features are mostly coming from the PDRs that are surrounded by H {\sc II} regions, and the PAH features' underlying continuum emission is from the H {\sc II} regions.
         Therefore, the lower flux of the PAH features could be the result of the smaller size of PDRs.
@@
 
-        The strong anti-correlation between PAHs and stellar mass shows, despite the general assumption that the one of the main source of heating PAHs is stellar emission~\citep[e.g][]{Haas02,Bendo08,Calapa14, Lu14,Jones15}, the higher stellar mass decreases PAH emission.
-        Using M33 data,~\cite{Calapa14} showed that 8/250~$\mu$m luminosity ratio correlate with 3.6~$\mu$m emission, which translates to stellar mass, and conclude that the PAH emission traces the old stellar population.
-        In Fig.~\ref{fig: cor_cluster1}, we see a week anti-correlation between SPIRE 250~$\mu$m emission and the stellar mass.
-        We couldn't see any correlation between 8/250~$\mu$m luminosity and stellar mass, neither in clustered data nor in all 10 regions.
+        The strong anti-correlation between PAHs and stellar mass suggests that, despite the general assumption that one of the main source of heating PAHs is stellar emission~\citep[e.g][]{Haas02,Bendo08,Calapa14, Lu14,Jones15}, a higher stellar mass decreases PAH emission.
+        In observations of M33,~\cite{Calapa14} showed that the 8/250~$\mu$m luminosity ratio correlates with 3.6~$\mu$m emission, which translates to stellar mass, and conclude that the PAH emission traces the old stellar population.
+        In Fig.~\ref{fig: cor_cluster1}, we see a weak anti-correlation between SPIRE 250~$\mu$m emission and the stellar mass.
+        We see no correlation between 8/250~$\mu$m luminosity and stellar mass, either in clustered data or in all 10 regions.
       %  The results from~\cite{Calapa14} were based on data from the whole galaxy and has a relatively high scatter.
@@
 
-        Studies showed that strong stellar emission could lead to destruction of PAHs ~\citep[e.g.][]{Clayton03,Seok14}.
-        To test that whether anti-correlation between stellar mass and PAH emission is the result of the destruction of PAHs in high stellar mass, or that high stellar mass obscures PAH emission, we compared PAH abundance with stellar mass for the clustered regions.
-        The ratio of 8/24~$\mu$m emission, which can be considered as a proxy for PAH abundances~\citep[e.g.][]{Sandstrom10,Khramtsova13}, does not anti-correlate with stellar mass for neither the clustered data nor all 10 regions.
-        Therefore, we conclude that in our sample of studies the high stellar mass does not causes the destruction of PAHs.
+        Some studies have indicated that strong stellar emission could lead to destruction of PAHs ~\citep[e.g.][]{Clayton03,Seok14}.
+        To test that whether anti-correlation between stellar mass and PAH emission is the result of the destruction of PAHs in high stellar mass regions, or that high stellar mass obscures PAH emission, we compared PAH abundance with stellar mass for the clustered regions.
+        The ratio of 8/24~$\mu$m emission, which can be considered as a proxy for PAH abundances~\citep[e.g.][]{Sandstrom10,Khramtsova13}, does not anti-correlate with stellar mass for either the clustered data or all 10 regions.
+        Therefore, we conclude that in our sample,  stellar mass does not cause the destruction of PAHs.
 
@@
         Regions 5, 6, and 8 are located on the stellar disk of the galaxy and have relatively high stellar mass and low PAHs. 
-        According to~\cite{Dim15}, regions 5 and 8 are only two regions in our sample that are not include an H {\sc II} region, which could be the reason of low PAHs for these regions.
+        According to~\cite{Dim15}, regions 5 and 8 are the only two regions in our sample that do not include an H {\sc II} region, which could be the reason of low PAHs for these regions.
         Regions 4 and 7 have similar quantities for both stellar mass and PAHs and region 3 has high PAHs and low stellar mass.
-        Thus without data from more regions in M31, we cannot confidently say that higher stellar mass decreases PAH fluxes.
+        Without data from more regions in M31, we cannot confidently say that higher stellar mass decreases PAH fluxes.
         %% Sahar: Can we have higher PAHs absorbes stellar mass and thats why we see the anti-correlation?!!!
@@
 
-       Regardless of the fact that some of the (anti)-correlations in Fig.~\ref{fig: cor_cluster1} might have physical meanings, we have to mention that, we only used 6 regions to calculate these correlation coefficients.
-       Having 6 data points as a sample of the study is not high enough to have a strong conclusion about the PAH in M31.%%% it doesn't sound right:((
-        However, we can conclude that since the correlation coefficients derived from the clustered data (Fig.~\ref{fig: cor_cluster1}) differs from correlation coefficients derived from the data from the all regions (Fig.~\ref{fig: cor_all}), SOM separated a hidden cluster of the data, for which their properties are different than the others.
+       Regardless of the fact that some of the (anti)-correlations in Fig.~\ref{fig: cor_cluster1} might have physical meaning, we have to mention that we only used 6 regions to calculate these correlation coefficients.
+       The number of data points is not high enough to yield a strong conclusion about PAH properties in M31.%%% it doesn't sound right:((
+        However, we can conclude that since the correlation coefficients derived from the clustered data (Fig.~\ref{fig: cor_cluster1}) differ from the correlation coefficients derived from the data from the all regions (Fig.~\ref{fig: cor_all}), the SOM separated a hidden cluster of the data which has different properties.
 %%Again eh!

### 2016-07-05 sections/R20.0.tex

@@
     \subsection{Testing networks using M101 observations}
-    Another application of SOM for nearby galaxies is to apply the trained networks on the data from other galaxies in order to predict properties of the observed regions in them. %%eh
-    Therefore, we generated an SOM using data from M31 that hold in common with M101 data (Fig.~\ref{fig: subset9}a). 
-    \cite{Dim15} compared PAHs in M31 with those from H {\sc II} regions in M101, and showed the similarity between PAHs from these two galaxies (For more detail see \cite{Dim15} and \cite{Gordon08}).
-    In this SOM, the same as the others, region 10 is separated from other regions in M31.
-    Regions 7 and 4 are close to each other with very light colours between their neurons, and the same as the other SOMs regions 6, 8, and 5 are close to each other, but with medium dark colour between them.
+    Another application of self-organizing maps made with data from a single galaxy is to apply its trained networks on data from other galaxies to make predictions. %%eh
+    To demonstrate this, we generated an SOM using only M31 measurements which were also available for M101 (Fig.~\ref{fig: subset9}a). 
+    \cite{Dim15} compared PAHs in M31 with those from H {\sc II} regions in M101, and showed the similarity between PAHs om these two galaxies (For more detail see \cite{Dim15} and \cite{Gordon08}).
+    In this SOM, as in the others, region 10 is separated from other regions in M31.
+    Regions 7 and 4 are close to each other with very light colours between their neurons, and as in the other SOMs regions 6, 8, and 5 are close to each other, but with medium dark colour between them.
     \import{../sections/image_texts/}{subset9.tex}
 
-    We applied the SOM created using M31 data in Fig.~\ref{fig: subset9}a on M101 data (Fig.~\ref{fig: subset9}b).
-    Region 5 in M31 and region 8 in M101 and regions 6 in M31 and region 2 in M101 occupied neurons with white colour between them in the network in Fig.~\ref{fig: subset9}, which immediately suggest that these regions have similar properties.
+    We applied the SOM created using M31 data in Fig.~\ref{fig: subset9}a to M101 data (Fig.~\ref{fig: subset9}b).
+    Region 5 in M31 and region 8 in M101 and regions 6 in M31 and region 2 in M101 occupied neurons with a white colour between them in the network in Fig.~\ref{fig: subset9}, which immediately suggests that these regions have similar properties.
+    %PB join paragraphs
+    Region 2 in M101 is a bright H {\sc II} region located at the end of the one of the M101 spiral arms (see Fig.~\ref{fig: regions in m101}) while
+    region 6 in M31 is located near the inner star-forming ring (see Fig.~\ref{fig: regions in m31}).
+    Both regions have relatively low PAH emission and a median amount of  SFR compared to other regions in the galaxy,  makeing them very similar.
 
-    Region 2 in M101 is a bright H {\sc II} region that is located at the end of the one of the M101 spiral arm (see Fig.~\ref{fig: regions in m101}). 
-    Region 6 in M31 is located near the inner ring of the galaxy (see Fig.~\ref{fig: regions in m31}).
-    Both regions have relatively low amount of PAHs emission and medium amount of the SFR regarding the other regions in the galaxy, which makes them very similar regions.
+    Region 5 in M31 is in the inner ring of the galaxy and it is one of two regions in M31 that are not an  H {\sc II} region, while
+    region 8 in M101 is in a spiral arm of the galaxy.
+    Relatively low stellar mass, SFR and SPIRE band emission caused these two regions to be nearby in the map.
+    In Sec.~\ref{Sec: 1d_cluster} we showed that regions 3 to 8 in M31 have similar properties; in Fig.~\ref{fig: subset9}b we see that regions 1 to 3 and 5 to 8 in M101 are located near regions 3 to 8 in M101.
+    These regions all have medium or low PAH emission, dust and SFR compared to the remaining regions.
 
-    Region 5 in M31 is in inner ring of the galaxy and it is one of two regions in M31 that are not an  H {\sc II} region.
-    region 8 in M101 is in a spiral arm of the galaxy.
-    Relatively low stellar mass, SFR and SPIRE band emission caused these two regions have close distance in the map.
-    In Sec.~\ref{Sec: 1d_cluster} we showed that regions 3 to 8 in M31 have similar properties, in Fig.~\ref{fig: subset9}b we see that regions 1 to 3 and 5 to 8 in M101 are located near regions 3 to 8 in M101.
-    These regions all have medium or low amount of PAHs, dust and SFR compare to the rest of them.
+    Region 7 in M101 is located in the nucleus of the galaxy and has relatively higher values of the quantities than the other regions.
+    This region is located in the top right side of the network in Fig.~\ref{fig: subset9},  close to the location of M31 region 10 in the network.
+    Since the bulge of a spiral galaxy has a different environment from its nucleus, region 7 in M101 and region 10 in M31 do not occupy the same neuron in the SOM, and have a medium grey colour between their neurons.
 
-    Region 7 in M101 is located in the nucleus of the galaxy and has relatively higher quantities than the other regions.
-    This region is located in the top right side of the network in Fig.~\ref{fig: subset9}, which is close to location of region 10 in the network.
-    Since the bulge of a spiral galaxy has different environment from its nucleus, region 7 in M101 and region 10 in M31 are not occupied the same neuron in the SOM, and have a medium grey colour between their neurons.
+    Region 1 in M101 is also located near the nucleus of M101 (see Fig.~\ref{fig: regions in m101}), but has considerably lower values in all the quantities compared to region 7.
+    The lower values for fluxes of the PAH features and moderate amount of the SFR caused this region to be placed between M31 regions 4 and 5 in the network. 
+    Fig.~\ref{fig: subset9}b shows that region 4 in M101 is separated from other regions and located between M31 regions 9 and 10.
+    \cite{Gordon08} showed that this region is a diffuse nebula in M101, with high PAH emission. 
+    This region also shows a high SFR and stellar mass, explaining why the location of M101 region 4 in the SOM is close to that of M31 regions 9 and 10.
 
-    Region 1 in M101 is located near the nucleus of M101 (see Fig.~\ref{fig: regions in m101}), but has considerably lower values in all the quantities than the ones in region 7.
-    The lower values for fluxes of the PAH features, and relatively moderate amount of the SFR caused this region places between region 4 and 5 of M31 in the network. 
-    Fig.~\ref{fig: subset9}b shows that region 4 in M101 is separated itself from other regions and located between region 9 and 10 in M31.
-    \cite{Gordon08} showed that this region is a diffuse nebula in M101, with high amount of fluxes of PAH features. 
-    This region also shows a high amount of the SFR and the stellar mass, which describes why the location of region 4 from M101 in the SOM is close to regions 9 and 10 from M31.
-
-    Knowing effect of each data entry on the networks From Section~\ref{sec: subsets}, we can have ideas about that data entry that we do
+    %PB: this paragraph seems to be unfinished?
+    Knowing the effects of the different input quantities on the networks from Section~\ref{sec: subsets}, we can have ideas about that data entry that we do
     In this section we showed that we can use networks that are created by data from nearby galaxies, to study the properties of other galaxies in a fast way.
-    We should note that, since we normalized data before using them in the networks, we only see a relative properties of the regions.
+    We should note that, since we normalized data before using them in the networks, we only see relative properties of the regions.
     Therefore, we need data from few regions in the galaxy to use this network cannot use these networks to learn about properties of a single region in other galaxies.

### 2016-07-05 sections/intro0.0.tex

--- 2016-06-18 sections/intro0.0.tex
@@
 %----------------------------------------------------------------------------------------
-\section{Introduction}
+\section{Introduction} %%( I am not really happy with this introduction but it is the best I can have for now:/ )
 %General information about galaxies %(Maybe it is too generic?!!)
-Inside each galaxies are millions of stars and large amount of dust and gas, which all have affect on each others' formation, evolution and extinction.
-Galaxies are an active and complicated systems, that are constantly changing.
-There are extensive amount of studies about correlations between galaxies' emission and their physical properties, both observationally and theoretically %(Some references here). 
-With all these studies our knowledge about the underlying processes in formation and evolution of galaxies expands every day, but the details of how these process work are still undetermined.
+% Inside each galaxy, there are millions of stars and large amount of dust and gas, which all affect on each others' formation, evolution and extinction.
+% Galaxies are an active and complicated systems, that are constantly changing.
+% There are extensive amount of studies about correlations between galaxies' emission and their physical properties, both observationally and theoretically %(Some references here). 
+% These studies expands our knowledge of the underlying processes in formation and evolution of galaxies every day, but the details of how these process work are still undetermined.
 
 % Nearby galaxies and their importance 
-Nearby galaxies plays an important role in improving studies about galaxies' formation and evolution.
-These galaxies are close enough to be able to observe various regions inside the galaxies in details.
-As a result, many studies were devoted to find relations between physical properties of the galaxies in both spatially resolved regions and galaxies as a whole %(Some more references here)
-, and many others used these results to analyze data from high-redshift galaxies.%(Some more references here)
-The amount of the data that is acquired from nearby galaxies is increasing daily.
-Advances in technology helps to both observe and store enormous amount of data from the sky.
-Telescopes and surveys gatherer data from nearby galaxies in different wavelengths and from these data we can measure physical properties of galaxies (e.g.
-stellar mass, star formation rate (SFR), dust mass, gas mass).
-%(Some more references here)
+Nearby galaxies play an important role in our understanding of galaxies' formation and evolution.
+These galaxies are close enough that we are able to observe regions inside them in detail.
+As a result, many studies have been devoted to finding relations between physical properties of galaxies both in spatially-resolved regions and in galaxies as a whole%(Some more references here)
+, and many others use these results in analyzing observations of high-redshift galaxies. %(Some more references here)
+%The amount of data that is acquired from nearby galaxies is increasing daily. %PB: not sure this sentence adds much.
+Advances in technology allow us to both observe and store enormous amounts of data from the sky.%The sky?! 
+Telescopes and surveys make observations of nearby galaxies in various wavelengths and from these data we can measure physical properties such as stellar mass, star formation rate (SFR), dust mass, and gas mass~\citep[e.g.[]{Calzetti07,Dale09,Eskew12}.
 
-M31, with distance of $\sim 0.78$~Mpc~\citep{McConnachie05}, is one of the closest spiral galaxies to the Milky way and provide us very unique view of inside of a spiral galaxy.
-Therefore,
+% A little bit about M31 and previous studies in M31.
+The Andromeda galaxy (M31), at a distance of $\sim 0.78$~Mpc~\citep{McConnachie05}, is the closest spiral galaxy to the Milky Way.
+Images of this galaxy provide us with a detailed view of the inside of a spiral galaxy as seen from a distance.
+M31 has been observed by many telescopes including the {\it Hubble} \citep{Dalcanton12}, \Spitzer\citep{Wener04}, \Herschel\citep{Pilbratt10} space telescopes and has been the subject of many more studies.
+% \citep[e.g.][and references therein]{Barmby06, Gordon06, Azimlu11, Sanders12, Dim15, Rahmani16}.
+%PB: need a different reference from Dalcanton here -- the Spitzer and eErschel ones are about the telescopes and not a specific program.
+Or you can drop the telescope references entirely.
+% PB joining these 2 paragraphs
+\cite{Barmby06} used data from the \Spitzer Infrared Array Camera \citep[IRAC;][]{Fazio04} to show the spatial distribution of Polycyclic Aromatic Hydrocarbons (PAHs) in the interstellar medium (ISM) of M31.
+%or to study the stellar and nonstellar mid-infrared (MIR) emission in M31. ?! 
+Using data from the Multiband Imaging Photometer for Spitzer (MIPS), \cite{Gordon06} studied the morphology of M31's dust.
+\cite{Azimlu11} and \cite{Sanders12} catalogued and studied H {\sc II} regions of M31.
+\cite{Draine14, Mattsson14, Viaene14, Smith12} and~\cite{Fritz12} used \Herschel data to study dust in the ISM of the galaxy.
+Properties of the current stars in the galaxy were studied by~\cite{Tamm12} and~\cite{Massey07}. %%%And some from PHAT survey
+\cite{Rahmani16, Ford13} and \cite{Tabatabaei10} measured the SFR in M31 in order to study star formation laws, and \cite{Dim15} and \cite{Kapala15} used infrared spectroscopy to study PAHs and atomic and molecular line emission in the ISM.
 
-% A little bit about PAH and other properties of nearby galaxies?!
+Although all these studies measured some properties of M31, or answered specific scientific questions about this galaxy, we still do not have a complete picture of underlying processes in the galaxy.
+The amount of observational data and measured quantities for M31 makes this galaxy a suitable target for a knowledge discovery and data mining study.
+Knowledge discovery and data mining methods are designed to extract hidden information from data and have been tested in many astronomical studies.
+However, to the best of our knowledge, this study is the first to use a data mining method on observations of nearby galaxies. %%% ehh
 
 % data mining and clustering in general; when we have so many data and we want to map them
-\cite{Ball10} did an extensive review of data mining and machine learning and their usage in astronomy.
+\cite{Ball10} gave an extensive review of data mining and machine learning and their usage in astronomy.
+A data mining algorithm learns about data from training, which can be supervised or unsupervised.
+Supervised training refers to methods that use examples of the desired output to learn about input data; these are valuable tools for classifying data with known target values.
+Unsupervised methods train without any prior knowledge of output results: 
+they work solely based on the underlying structure of the input data.   
+The unsupervised methods are very useful tools in knowledge discovery studies, where we have limited pre-expectations for the data or when we want to make sure that we did not miss any valuable information in  previous studies.
+%%% ehh to after or part.
 
-%SOM is a good method for knowledge discovery projects;
-%SOM in Astronomy and mention we do not have any SOM in nearby galaxies
-%this project 1 M31 and its extensive data
+%SOM
+Some of the most tested methods of data mining in astronomy are artificial neural networks (ANNs)~\citep[e.g.][and references therein]{ Hossein14,Hossein16}.
+ANNs are designed to work in the same way that the neurons work in a human brain.
+They are networks of interconnected neurons (nodes), in which all of the connections are weighted.
+These networks are used to study nonlinear and complex relations between input and output data.
+%These relations can be applied to the new sets of data with similar feature
+% PB joining these paragraphs
+One of the most well-known unsupervised neural networks in astronomy is a Kohonen self-organizing map (also called self-organizing map, or SOM).
+SOMs map and visualize complex data~\citep{Kohonen82} and show simple geometrical relationships in non-linear high dimensional data~\citep{Kohonen98}.
+The result of a SOM is a 1D or 2D network of neurons, which shows the positions of clusters and their relative distance.
+Since the 1990s, many studies utilized SOMs for object classification and clustering (e.g.
+classifying quasars' spectra, star/galaxy classifications, gamma-ray burst clustering and light curve classification) and photometric redshift estimation~\citep[e.g.][]{Odewahn92, Hernandez94, Murtagh95, Maehoenen95,Scaringi09,Geach12,Fustes13,Meusinger16,Rahmani16b} %%% Why I cannot add submitted in front of the high-z paper %PB: MNRAS style guide says "Private communications or papers in preparation should be listed as such in the text, but omitted from the reference list, e.g.
+Smith (in preparation) shows that… " -- but I'm not clear on whether this applied to submitted papers or not
+
+ %%add a little bit about PAHs in M31, dim15, drain14 and refs. therein. talk about what questions are still remained unanswered.
+The purpose of the present work is to use M31 observations to generate new insights into nearby galaxies, with a focus on relations between PAHs and other properties of the galaxy.
+There are very few studies on relations between properties of M31 with its PAH features.
+To fulfill this purpose, an unsupervised data mining method is the most suitable choice.
+\cite{Cesarsky98} studied PAH spectra in four regions in M31 and found that PAH features in M31 differ from those in other galaxies in having weak or no $6.2 - 8.6\mu$m emission with enhanced 11.2~$\mu$m emission.
+However, \cite{Dim15} by using {\it Spitzer}/Infrared Spectrograph~\citep[IRS,][]{Houck04b} observations, found that the PAH spectra of M31 have the same features as the spectra of other nearby star-forming galaxies.
+Using IRAC imaging observations,\cite{Barmby06} compared the observed 8~$\mu$m luminosity with other star formation indicators in the galaxy and found good agreement, and \cite{Draine14} found that the PAH abundance in M31 is almost constant up to a galactocentric radius of $\sim 20$~kpc.
+%Therefore, using data mining techniques, we aim to study PAH features in more detail. %PB: not sure this sentence adds much.
+
+%PB: would this paragraph go better if it was before the previous one ("purpose of the present work") ? Or possibly in the method section?
+K-means algorithm, SOMs, and hierarchical clustering are the main unsupervised methods that are used in astronomical studies~\citep[e.g.][]{DAbrusco12, Aycha16}. %%add one or two more
+For both K-means and SOM algorithms, the user must define the number of clusters, and the algorithms decide how to separate the data into desired number of clusters.
+In the hierarchical clustering method, the user must define dissimilarity between the groups; the algorithm combines (or divides) existing groups based on their dissimilarity and creates a hierarchical structure.
+Comparing SOMs, K-means and hierarchical clustering shows that in some cases hierarchical clustering method mis-classifies the data~\citep[][and references therein]{Mangiameli96}.
+We chose the SOM method over K-means due to the fact that SOMs not only cluster data, but also show similarities and dissimilarities between the clusters.
+Therefore, we can cluster our sample data and study the underlying structure, simultaneously.
+
+%this project 1 M31 and its extensive data we do not have any SOM in nearby galaxies
+In this project we apply the self-organizing map algorithm to M31 data, training 1D and 2D networks.
+Using the smaller networks we study the properties of the clusters and investigate relations between PAH features and other quantities in M31.
+We create 2D SOMs from subsets of the data as well as all available data, which helps us to understand the effect of each input in the position of the clusters in the SOM.%, which leads to prediction of the unmeasured quantities in a galaxy.
+We apply the 2D trained networks to  observations of the Pinwheel Galaxy (M101), another nearby spiral  galaxy, to check whether it has similar properties.
+If our hypothesis is correct, we should be able to see that regions in M31 and M101 with the same positions in the SOM have the same properties.
+
+In Section $\S$~\ref{Sec: data_SOMN}, we present the observational data from M31 and M101 that we use in this study. 
+We describe the SOM method in Section $\S$~\ref{sec: method}. 
+The results of the 1D SOM networks and the studying of PAHs in M31 are presented in Section $\S$~\ref{Sec: 1d_cluster}.
+In Section $\S$~\ref{sec: 2d_cluster}, we present the results of 2D SOM networks and their use in extracting information about other galaxies.
+In Section $\S$~\ref{sec: summary}, we summarize our results and discuss potential future work in this subject.
+
+%SOM in Astronomy continued.
+% Large spectroscopic surveys have made available integrated spectra of millions of galaxies.
+% These integrated spectra combine the light of billions of individual stars and nebulae within a galaxy, and
+% finding patterns and common characteristics between galaxies can be a complex task.
+% \citet{In12} introduced a new clustering tool based on the SOM method for analyzing these large datasets.
+% They used $\sim 60000$ spectra from the Sloan Digital Sky Survey \citep[SDSS;][]{Abazajian09} to test their tool, and created very large SOMs to analyze the type of spectra/objects.
+% They also generated SOMs from quasars' spectra in order to find unusual types of spectra. 
+% Later, \citet{Meusinger16} used these SOMs and updated data from SDSS and other surveys to find a new class of quasars.
+% The other application of SOMs is to find outliers or errors in the data.
+% \citet{Fustes13} produced a package based on SOM to classify spectra from the GAIA survey that were previously classified as ``unknown'' by the SDSS pipeline.
+This package can recognize an astronomical object from instrumental errors, and then classify the object based on its spectrum.
+
+%Compare diff methods and say why we chose SOM!
 

### 2016-07-05 sections/method0.0.tex

@@
  \label{sec: som}
- The SOM is a clustering method which reduces the dimension of data to lower dimensions, while preserving topological features of the original data~\citep{Kohonen98}. 
+ The SOM is a clustering method which reduces the dimensionality of data, while preserving topological features ~\citep{Kohonen98}. 
  The results of the SOM are shown with a map of neurons.
  Each neuron has a fixed position in the map, and may contain one or more samples from input data, \boldit{V} $\in \Re^n$.
- A weight vector,~\boldit{W} $\in \Re^n$, with the same dimension as the input data is associated with each node and will be varied during the training process.
- The process of creating SOM, happens over series of $N$ iterations.
- In each iteration, the algorithm calculates the euclidean distance for each node j as  $D_j^2= \sum_{i=0}^{i=n} (V_i - W_i)^2$, and finds a neuron with ``$D_{j_{min}}$". 
+ A weight vector,~\boldit{W} $\in \Re^n$, with the same dimension as the input data, is associated with each node and will be varied during the training process.
+ The process of creating an SOM  happens over a series of $N$ iterations.
+ In each iteration, the algorithm calculates the Euclidean distance for each node $j$ as  $D_j^2= \sum_{i=0}^{i=n} (V_i - W_i)^2$, and finds a neuron with $D_{j_, \rm min}}$. 
  This neuron is the winner node and is calling Best Matching Unit (BMU). 
- The weight vectors in the neighbourhood of BMU will change according to the Kohonen learning rule (equation~\ref{equ: weight adj}). 
+ The weight vectors in the neighbourhood of the BMU will change according to the Kohonen learning rule (equation~\ref{equ: weight adj}). 
   \begin{equation}
@@
  \end{equation}
-where $L(t) = L_0 e^{(-t/\tau)}$ is the learning factor, which prevents the divergence of the SOM and $R(t)=\exp(-\frac{D_j^2}{2r^t_{BMU}})$ is the influence rate, which determines how the weight of each node will change.
-Values for number of neurons, L(t) and R(t) are arbitrary. 
-~\cite{Geach12} and \cite{Rahmani16b} demonstrate the algorithm of the SOM in more details.
+where $L(t) = L_0 e^{(-t/\tau)}$ is the learning factor, which prevents the divergence of the SOM, and $R(t)=\exp(-\frac{D_j^2}{2r^t_{BMU}})$ is the influence rate, which determines how the weight of each node will change.
+Values for the number of neurons, $L(t)$ and $R(t)$ are arbitrary. 
+~\cite{Geach12} and \cite{Rahmani16b} demonstrate the algorithm of the SOM in more detail.
 
-     In order to create SOM, we used {\sc MATLAB} neural network toolbox~\citep[NNT,][]{matlabtolbox}.
-     An SOM in {\sc NNT} can be created by {\sc newsom} library which works in two phases; ``ordering phase" and ``tuning phase" . 
+     In order to create self-organizing maps, we used the {\sc MATLAB} neural network toolbox~\citep[NNT,][]{matlabtolbox}.
+     An SOM in {\sc NNT} can be created by the {\sc newsom} library which works in two phases, the ``ordering phase" and ``tuning phase" . 
      Phase one is the ``ordering phase". 
-     This phase starts with maximum neighbourhood distance, and initial high learning factor usually 0.9 which is provided by user. 
-     The ordering phase continues for requested number of iterations and it continues till the learning factor reduces to tuning phase leaning factor and the neighbourhood distance reaches to the number set by the user.
-
+     This phase starts with maximum neighbourhood distance, and an initial high learning factor, usually 0.9, which is provided by the user. 
+     The ordering phase continues for the requested number of iterations or until the learning factor reduces to the tuning phase learning factor and the neighbourhood distance reaches the value set by the user.
+%PB: please check edit to this sentence - is "or until" correct?
+     %PB: combine paragraphs
      The second phase is the ``tuning phase".
      In this phase the neighbourhood distance is at its minimum, but learning factor decreases very slowly.
-     This minimum neighbourhood distance and slowly decreasing the leaning factor helps to fine tune the topology results and causes the more stable SOM. 
-     The number of iterations in this tuning phase most be much more than the number iterations in ordering phase, to allow the tuning happens slowly. 
-     We chose number of epochs the tuning phase be 3 times more than number of epochs in the ordering phase.
+     This minimum neighbourhood distance and slowly decreasing learning factor helps to fine tune the topology results and causes a more stable SOM. 
+     The number of iterations in this tuning phase must be much more than the number of iterations in ordering phase, to allow the tuning to happen slowly. 
+     We chose the number of epochs in the tuning phase to be 3 times more than the number of epochs in the ordering phase.
 
      To present our results, we use {\sc nnt}'s built-in plotting tool.
-     Specifically, we combine two of the plots in this tool: a hits map, which shows the number of times each neuron has became the winner (hits), and a distance map, which shows the distance between weight vectors of those neurons.
-     In the maps, the purple hexagonal shapes shows the neurons. 
-     The distances are shown by the grey cycle colours: the darker the colour, the larger the distance between neurons.
+     Specifically, we combine two of the plots in this tool: a hits map, which shows the number of times each neuron has become the winner (hits), and a distance map, which shows the distance between weight vectors of those neurons.
+     In the maps, the purple hexagonal shapes show the neurons. 
+     The distances are shown by the grey-scale colours: the darker the colour, the larger the distance between neurons.
      Neurons with zero hits are left empty.
-     In Section~\ref{sec: mock_sample} we used {\sc newsom} to create SOMs from a mock sample to illustrate how this method works and how we can interpret the results.
+     In Section~\ref{sec: mock_sample} we used {\sc newsom} to create SOMs from a mock sample to illustrate how this method works and how to interpret the results.
 
-     One feature of the SOM method is that there is no rule and restriction on number of clusters.
-     Users must decide the size of networks based on their data set and their usages of the results .
+     One feature of the SOM method is that there is no rule or restriction on number of clusters.
+     Users must decide the size of networks based on their data set and their usage of the results.
      There has been few attempts to find a rule for restricting the number of neurons based on the input sample \citep[e.g.][]{Vesanto05}, but none of them are certain. 
-     We varied size of SOMs from $1\times2$ to $50\times50$ to choose the most suitable size for our maps, and found that based on the size of our sample, the 2D SOMs to be 10$\times$10. 
-     We create the final SOMs with initial values for number of iterations in ordering phase, ordering phase learning factor, tuning phase learning factor, and tuning phase neighbourhood distance of 500, 0.9, 0.02, and 1, respectively.
+     We varied the size of SOMs from $1\times2$ to $50\times50$ to choose the most suitable size for our maps, and found that based on the size of our sample, the best size for the 2D SOMs was 10$\times$10.
+     We created our final SOMs with initial values for number of iterations in ordering phase, ordering phase learning factor, tuning phase learning factor, and tuning phase neighbourhood distance of 500, 0.9, 0.02, and 1, respectively.
      %Also for each grid we created different SOM with different, learning factors, neighbourhood distances, and iteration numbers to find the optimize result for our sample.
@@
 Hexagonal shapes represent the neurons.
-The grey cycle colours show the differences between weight of each neuron where white is the minimum differences and black has the maximum one.}
+The grey-scale colours show the differences between neuron weights, where white is the minimum difference and black is the maximum one.}
             \label{fig: sample}
@@
 
-To show how self-organizing maps work, we created a mock sample, which contains a few regions.
-We gave two information to each sample; amount of dust and the SFR.
- Therefore, we have a simple input data with low dimension; each entry only can get either 0 or 1 as high or low SFR, and 0 or 0.5 to show high or low amount of dust for the mock regions.
- We generated an SOM with the size of $10 \times 10$ from the sample, using the method that described in Sec.~\ref{sec: som}.
+To show how self-organizing maps work, we created a mock sample containing only a few regions.
+Each sample had two properties: amount of dust and star formation rate, where the possible values were
+either 0 or 1 for high or low SFR, and 0 or 0.5 for a high or low amount of dust. %PB: check - correct that 0 means high and 1 means low?
+ We generated an SOM from the sample with a size of $10 \times 10$, using the method described in Sec.~\ref{sec: som}.
  Fig. ~\ref{fig: sample} shows the SOM of the mock sample. 
@@
 
-Using this method, as expected, we are able to divide the mock sample into 4 distinct groups: regions with high SFR and high amount of dust, regions with low SFR and high amount of dust, regions with high SFR and low amount of dust, and regions low SFR and low amount of dust.
-The plot in the Fig.~\ref{fig: sample}, clearly shows these divisions.
-In that plot, the upper part belongs to regions with low amount of dust, while the lower part belongs to the high amount of dust.
-The left part of the plot, is where regions with low SFR belong to and the right side is for high SFR regions.
+Using this method, as expected, we are able to divide the mock sample into 4 distinct groups: regions with high SFR and high dust content, regions with low SFR and high dust content, regions with high SFR and low dust content, and regions with low SFR and dust content.
+The plot in the Fig.~\ref{fig: sample} clearly shows these divisions.
+In that plot, the upper part belongs to regions with low dust content, while the lower part belongs to regions with high dust content.
+The left part of the plot is where regions with low SFR belong and the right side is for high SFR regions.
 Grey to black colours show the border between regions.
-This network is considered as a trained network, and can used to cluster any new data set with similar entries.
+This network is considered to be a trained network, and can be used to cluster any new data set with similar entries.
 
 Having two regions with exactly the same values in all their quantities in the real world is almost impossible. 
-Therefore, one can find a network with high amount of the neurons, which separates the input data completely, and clusters them into separate groups.
+Therefore, one can find a network with a high number of neurons, which separates the input data completely, and clusters them into separate groups.
 However, if the input data has high similarity, the number of neurons must be much higher than the number of input samples to be able to separate the groups from each other. 
 Therefore, it is up to the user to decide the similarity or dissimilarity between the input data based on the number of neurons.
+%PB: this praragraph is tricky for me to understand.
+Might need to try rewriting.

### 2016-07-05 sections/image_texts/all.tex
Updates from ShareLaTeX

--- 2016-07-04 sections/image_texts/all.tex
@@
     \caption{Two dimensional SOM of M31 using $10\times10$ grid.
-Similar to figs.\ref{fig: sample} and \ref{fig: M31_nets_1d}, The hexagonal shapes show the neurons and the grey cycle colours between neurons show the differences between weight of each neuron.}
+Similar to Figs.\ref{fig: sample} and \ref{fig: M31_nets_1d}, The hexagonal shapes show the neurons and the grey cycle colours between neurons show the differences between weight of each neuron.}
     \label{fig: all_derived_ones}

### 2016-07-11 sections/R10.01.tex
Applying the minors corrections

--- 2016-07-05 sections/R10.0.tex
@@
         Two black colours between this region and the others indicate the large differences between this neuron and the other ones.
-       Region 10 is located in the bulge of M31, and its separation from other regions, which are mostly located around the inner or outer rings, is due to the fact that most of the input values for this region are much higher than the other regions.
-%PB: so is the SOM just telling us that the surface brightness is higher in the bulge?
+       Region 10 is located in the bulge of M31, and its separation from other regions, which are mostly located around the inner or outer rings.
+       The SOM shows that this region has a completely different input values than the others.
+       Comparing raw data for regions shows that most of the input values for region 10 are much higher than the other regions, which is the main reason of its isolation.
         The region 8 occupies the right-most neuron in this network, suggesting that this region has the most differences from region 10.
@@
         Since there are only 6 regions in this cluster, even one outlier in the data may cause the correlation coefficient to become insignificant.
-        By removing the outlier, the correlations between 12.0 and 12.7~$\mu$m~PAH fluxes and the other quantities show themselves.
-%PB: need to discuss which one is the outlier and why it is reasonable to remove it
+        If we ignore the outlier values, the correlations between 12.0 and 12.7~$\mu$m~PAH fluxes and the other quantities show themselves. 
+        For example region 8 breaks correlations between 12.0~$\mu$m and 6.2, 7.7, and 8.3~$\mu$m.
+        This region could be part of scatter for these correlations, but with 6 regions in the dataset it is hard to have a concrete conclusion.
 

### 2016-07-11 sections/R20.01.tex
Applying the minors corrections

--- 2016-07-05 sections/R20.0.tex
@@
     Region 5 in M31 and region 8 in M101 and regions 6 in M31 and region 2 in M101 occupied neurons with a white colour between them in the network in Fig.~\ref{fig: subset9}, which immediately suggests that these regions have similar properties.
-    %PB join paragraphs
     Region 2 in M101 is a bright H {\sc II} region located at the end of the one of the M101 spiral arms (see Fig.~\ref{fig: regions in m101}) while
     region 6 in M31 is located near the inner star-forming ring (see Fig.~\ref{fig: regions in m31}).
-    Both regions have relatively low PAH emission and a median amount of  SFR compared to other regions in the galaxy,  makeing them very similar.
+    Both regions have relatively low PAH emission and a median amount of  SFR compared to other regions in the galaxy, making them very similar.
 
@@
 
-    %PB: this paragraph seems to be unfinished?
-    Knowing the effects of the different input quantities on the networks from Section~\ref{sec: subsets}, we can have ideas about that data entry that we do
+    Knowing the effects of the different input quantities on the networks from Section~\ref{sec: subsets}, we can have ideas about data entry from other regions/galaxies.
     In this section we showed that we can use networks that are created by data from nearby galaxies, to study the properties of other galaxies in a fast way.

### 2016-07-11 sections/V0.0/intro0.0.tex
Applying the minors corrections

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Intro
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{Introduction}

%General information about galaxies %(Maybe it is too generic?!!)
% Inside each galaxy, there are millions of stars and large amount of dust and gas, which all affect on each others' formation, evolution and extinction.
% Galaxies are an active and complicated systems, that are constantly changing.
% There are extensive amount of studies about correlations between galaxies' emission and their physical properties, both observationally and theoretically %(Some references here). 
% These studies expands our knowledge of the underlying processes in formation and evolution of galaxies every day, but the details of how these process work are still undetermined.

% Nearby galaxies and their importance 
Nearby galaxies play an important role in our understanding of galaxies' formation and evolution.
These galaxies are close enough that we are able to observe regions inside them in detail.
As a result, many studies have been devoted to finding relations between physical properties of galaxies both in spatially-resolved regions and in galaxies as a whole%(Some more references here)
, and many others use these results in analyzing observations of high-redshift galaxies. %(Some more references here)
%The amount of data that is acquired from nearby galaxies is increasing daily. %PB: not sure this sentence adds much.
Advances in technology allow us to both observe and store enormous amounts of data from the sky.%The sky?! 
Telescopes and surveys make observations of nearby galaxies in various wavelengths and from these data we can measure physical properties such as stellar mass, star formation rate (SFR), dust mass, and gas mass~\citep[e.g.[]{Calzetti07,Dale09,Eskew12}.

% A little bit about M31 and previous studies in M31.
The Andromeda galaxy (M31), at a distance of $\sim 0.78$~Mpc~\citep{McConnachie05}, is the closest spiral galaxy to the Milky Way.
Images of this galaxy provide us with a detailed view of the inside of a spiral galaxy as seen from a distance.
M31 has been observed by many telescopes including the {\it Hubble}, \Spitzer, \Herschel space telescopes and has been the subject of many more studies. % \citep[e.g.][and references therein]{Barmby06, Gordon06, Azimlu11, Sanders12, Dim15, Rahmani16}.  %PB: need a different reference from Dalcanton here -- the Spitzer and eErschel ones are about the telescopes and not a specific program. Or you can drop the telescope references entirely.
% PB joining these 2 paragraphs
\cite{Barmby06} used data from the \Spitzer Infrared Array Camera \citep[IRAC;][]{Fazio04} to show the spatial distribution of Polycyclic Aromatic Hydrocarbons (PAHs) in the interstellar medium (ISM) of M31.
%or to study the stellar and nonstellar mid-infrared (MIR) emission in M31. ?! 
Using data from the Multiband Imaging Photometer for Spitzer (MIPS), \cite{Gordon06} studied the morphology of M31's dust.
\cite{Azimlu11} and \cite{Sanders12} catalogued and studied H {\sc II} regions of M31.
\cite{Draine14, Mattsson14, Viaene14, Smith12} and~\cite{Fritz12} used \Herschel data to study dust in the ISM of the galaxy.
Properties of the current stars in the galaxy were studied by~\cite{Tamm12} and~\cite{Massey07}. %%%And some from PHAT survey
\cite{Rahmani16, Ford13} and \cite{Tabatabaei10} measured the SFR in M31 in order to study star formation laws, and \cite{Dim15} and \cite{Kapala15} used infrared spectroscopy to study PAHs and atomic and molecular line emission in the ISM.

Although all these studies measured some properties of M31, or answered specific scientific questions about this galaxy, we still do not have a complete picture of underlying processes in the galaxy.
The amount of observational data and measured quantities for M31 makes this galaxy a suitable target for a knowledge discovery and data mining study.
Knowledge discovery and data mining methods are designed to extract hidden information from data and have been tested in many astronomical studies.
However, to the best of our knowledge, this study is the first to use a data mining method on observations of nearby galaxies. %%% ehh

% data mining and clustering in general; when we have so many data and we want to map them
\cite{Ball10} gave an extensive review of data mining and machine learning and their usage in astronomy.
A data mining algorithm learns about data from training, which can be supervised or unsupervised.
Supervised training refers to methods that use examples of the desired output to learn about input data; these are valuable tools for classifying data with known target values.
Unsupervised methods train without any prior knowledge of output results: 
they work solely based on the underlying structure of the input data.   
The unsupervised methods are very useful tools in knowledge discovery studies, where we have limited pre-expectations for the data or when we want to make sure that we did not miss any valuable information in  previous studies. %%% ehh to after or part.

%SOM
Some of the most tested methods of data mining in astronomy are artificial neural networks (ANNs)~\citep[e.g.][and references therein]{ Hossein14,Hossein16}.
ANNs are designed to work in the same way that the neurons work in a human brain.
They are networks of interconnected neurons (nodes), in which all of the connections are weighted.
These networks are used to study nonlinear and complex relations between input and output data.
%These relations can be applied to the new sets of data with similar feature
% PB joining these paragraphs
One of the most well-known unsupervised neural networks in astronomy is a Kohonen self-organizing map (also called self-organizing map, or SOM).
SOMs map and visualize complex data~\citep{Kohonen82} and show simple geometrical relationships in non-linear high dimensional data~\citep{Kohonen98}.
The result of a SOM is a 1D or 2D network of neurons, which shows the positions of clusters and their relative distance.
Since the 1990s, many studies utilized SOMs for object classification and clustering (e.g. classifying quasars' spectra, star/galaxy classifications, gamma-ray burst clustering and light curve classification) and photometric redshift estimation~\citep[e.g.][]{Odewahn92, Hernandez94, Murtagh95, Maehoenen95,Scaringi09,Geach12,Fustes13,Meusinger16,Rahmani16b} %%% Why I cannot add submitted in front of the high-z paper %PB: MNRAS style guide says "Private communications or papers in preparation should be listed as such in the text, but omitted from the reference list, e.g. Smith (in preparation) shows that… " -- but I'm not clear on whether this applied to submitted papers or not

 %%add a little bit about PAHs in M31, dim15, drain14 and refs. therein. talk about what questions are still remained unanswered.
The purpose of the present work is to use M31 observations to generate new insights into nearby galaxies, with a focus on relations between PAHs and other properties of the galaxy.
There are very few studies on relations between properties of M31 with its PAH features.
To fulfill this purpose, an unsupervised data mining method is the most suitable choice.
\cite{Cesarsky98} studied PAH spectra in four regions in M31 and found that PAH features in M31 differ from those in other galaxies in having weak or no $6.2 - 8.6\mu$m emission with enhanced 11.2~$\mu$m emission. 
However, \cite{Dim15} by using {\it Spitzer}/Infrared Spectrograph~\citep[IRS,][]{Houck04b} observations, found that the PAH spectra of M31 have the same features as the spectra of other nearby star-forming galaxies.
Using IRAC imaging observations,\cite{Barmby06} compared the observed 8~$\mu$m luminosity with other star formation indicators in the galaxy and found good agreement, and \cite{Draine14} found that the PAH abundance in M31 is almost constant up to a galactocentric radius of $\sim 20$~kpc.
%Therefore, using data mining techniques, we aim to study PAH features in more detail. %PB: not sure this sentence adds much.

%PB: would this paragraph go better if it was before the previous one ("purpose of the present work") ? Or possibly in the method section?
K-means algorithm, SOMs, and hierarchical clustering are the main unsupervised methods that are used in astronomical studies~\citep[e.g.][]{DAbrusco12, Aycha16}. %%add one or two more
For both K-means and SOM algorithms, the user must define the number of clusters, and the algorithms decide how to separate the data into desired number of clusters.
In the hierarchical clustering method, the user must define dissimilarity between the groups; the algorithm combines (or divides) existing groups based on their dissimilarity and creates a hierarchical structure. 
Comparing SOMs, K-means and hierarchical clustering shows that in some cases hierarchical clustering method mis-classifies the data~\citep[][and references therein]{Mangiameli96}.
We chose the SOM method over K-means due to the fact that SOMs not only cluster data, but also show similarities and dissimilarities between the clusters.
Therefore, we can cluster our sample data and study the underlying structure, simultaneously.

In this project we apply the self-organizing map algorithm to M31 data, training 1D and 2D networks.
Using the smaller networks we study the properties of the clusters and investigate relations between PAH features and other quantities in M31.
We create 2D SOMs from subsets of the data as well as all available data, which helps us to understand the effect of each input in the position of the clusters in the SOM. %, which leads to prediction of the unmeasured quantities in a galaxy.
We apply the 2D trained networks to  observations of the Pinwheel Galaxy (M101), another nearby spiral  galaxy, to check whether it has similar properties.
If our hypothesis is correct, we should be able to see that regions in M31 and M101 with the same positions in the SOM have the same properties.

In Section $\S$~\ref{Sec: data_SOMN}, we present the observational data from M31 and M101 that we use in this study. 
We describe the SOM method in Section $\S$~\ref{sec: method}. 
The results of the 1D SOM networks and the studying of PAHs in M31 are presented in Section $\S$~\ref{Sec: 1d_cluster}.
In Section $\S$~\ref{sec: 2d_cluster}, we present the results of 2D SOM networks and their use in extracting information about other galaxies.
In Section $\S$~\ref{sec: summary}, we summarize our results and discuss potential future work in this subject.

### 2016-07-11 sections/data0.01.tex
Applying the minors corrections

--- 2016-07-04 sections/data0.0.tex
@@
 These specific regions were chosen for the availability of mid-infrared PAH spectroscopy.
-Besides PAH line strnegths, for each galaxy, we use spectroscopic and photometric observations as well as their derived properties, such as SFR, stellar mass, dust luminosity (L$_{\rm dust}$) and mass, metallicity, and gas mass.
+Besides PAH line strengths, for each galaxy, we use spectroscopic and photometric observations as well as their derived properties, such as SFR, stellar mass, dust luminosity (L$_{\rm dust}$) and mass, metallicity, and gas mass.
 Table~\ref{tab: data} shows the full list of data and their units for both M31 and M101.
 Observed values were divided by the area of their region (in arcsec$^2$), to remove the distance factor from the data and compare values across galaxies.
-Since the spatial resolution of the observations varies from $<1\arcsec$ to $60\arcsec \times 90 \arcsec$, any attempt to match resolution would have caused a loss of information in some of the input quantities (e.g.
+Since the spatial resolution of the observations varies from $<1$\arcsec to 60\arcsec $\times$ 90 \arcsec, any attempt to match resolution would have caused a loss of information in some of the input quantities (e.g.
 the spectroscopic data).
@@
 
-%M31 data 
-%%%%% Sahar: More detail, right?
     \subsection{M31 observations}
@@
 
-     %The 10 regions in M31 were chosen due to availability of the PAH data for them. 
      \cite{Dim15} using {\it Spitzer}/IRS observations to study PAHs in 10 regions chosen to span a range of mid-infrared flux ratios in M31. 
      Fluxes and equivalent widths of PAH and atomic line features were measured using the~{\sc PAHFIT IDL} tool~\citep{Smith07b}.
-     %For spectroscopy part of our sample, we utilized their measured fluxes for PAH lines. 
      \cite{Dim15} also measured metallicity and radiation hardness index (RHI) for these 10 regions.
@@
     \label{Sec: data_M101_SOMN} 
-     \cite{Gordon08} measured PAH fluxes, metallicity and RHI for M101 in XX regions chosen.. % PB: reason for selecting?
+     \cite{Gordon08} measured PAH fluxes, metallicity and RHI for M101 in 8 regions chosen.. % PB: reason for selecting?
 %     We also added their measurement of metallicity and RHI for these regions to our sample.
@@
 
-      \begin{figure}
+      \begin{figure*}
                 \centering
-                \includegraphics[width=0.5\textwidth]{../images0.01/cor_plots/M31_all_derived_ones_core_plot_for_paper.pdf}
+                \includegraphics[width=\textwidth]{../images0.01/cor_plots/M31_all_derived_ones_core_plot_for_paper.pdf}
             \caption{Pearson correlation coefficients with a confidence level of 95$\%$ for all data in subset 0.
@@
             \label{fig: cor_all}
-        \end{figure}
+        \end{figure*}

### 2016-07-11 sections/intro0.01.tex
Applying the minors corrections

--- 2016-07-11 sections/V0.0/intro0.0.tex
@@
 \section{Introduction} 
-
-%General information about galaxies %(Maybe it is too generic?!!)
-% Inside each galaxy, there are millions of stars and large amount of dust and gas, which all affect on each others' formation, evolution and extinction.
-% Galaxies are an active and complicated systems, that are constantly changing.
-% There are extensive amount of studies about correlations between galaxies' emission and their physical properties, both observationally and theoretically %(Some references here). 
-% These studies expands our knowledge of the underlying processes in formation and evolution of galaxies every day, but the details of how these process work are still undetermined.
-
 % Nearby galaxies and their importance 
@@
 , and many others use these results in analyzing observations of high-redshift galaxies. %(Some more references here)
-%The amount of data that is acquired from nearby galaxies is increasing daily. %PB: not sure this sentence adds much.
-Advances in technology allow us to both observe and store enormous amounts of data from the sky.%The sky?! 
-Telescopes and surveys make observations of nearby galaxies in various wavelengths and from these data we can measure physical properties such as stellar mass, star formation rate (SFR), dust mass, and gas mass~\citep[e.g.[]{Calzetti07,Dale09,Eskew12}.
+Advances in technology allow us to both observe and store enormous amounts of data from the sky.
+Telescopes and surveys make observations of nearby galaxies in various wavelengths and from these data we can measure physical properties such as stellar mass, star formation rate (SFR), dust mass, and gas mass~\citep[e.g.][]{Calzetti07,Dale09,Eskew12}.
 
 % A little bit about M31 and previous studies in M31.
-The Andromeda galaxy (M31), at a distance of $\sim 0.78$~Mpc~\citep{McConnachie05}, is the closest spiral galaxy to the Milky Way.
+The Andromeda galaxy (M31), at a distance of $\sim$~0.78~Mpc \citep{McConnachie05}, is the closest spiral galaxy to the Milky Way.
 Images of this galaxy provide us with a detailed view of the inside of a spiral galaxy as seen from a distance.
 M31 has been observed by many telescopes including the {\it Hubble}, \Spitzer, \Herschel space telescopes and has been the subject of many more studies.
-% \citep[e.g.][and references therein]{Barmby06, Gordon06, Azimlu11, Sanders12, Dim15, Rahmani16}.
-%PB: need a different reference from Dalcanton here -- the Spitzer and eErschel ones are about the telescopes and not a specific program.
-Or you can drop the telescope references entirely.
-% PB joining these 2 paragraphs
 \cite{Barmby06} used data from the \Spitzer Infrared Array Camera \citep[IRAC;][]{Fazio04} to show the spatial distribution of Polycyclic Aromatic Hydrocarbons (PAHs) in the interstellar medium (ISM) of M31.
-%or to study the stellar and nonstellar mid-infrared (MIR) emission in M31. ?! 
 Using data from the Multiband Imaging Photometer for Spitzer (MIPS), \cite{Gordon06} studied the morphology of M31's dust.
@@
 \cite{Draine14, Mattsson14, Viaene14, Smith12} and~\cite{Fritz12} used \Herschel data to study dust in the ISM of the galaxy.
-Properties of the current stars in the galaxy were studied by~\cite{Tamm12} and~\cite{Massey07}. %%%And some from PHAT survey
+Properties of the current stars in the galaxy were studied by many groups~\citep[e.g.][and references therein]{Massey07,Tamm12,Dalcanton12}
 \cite{Rahmani16, Ford13} and \cite{Tabatabaei10} measured the SFR in M31 in order to study star formation laws, and \cite{Dim15} and \cite{Kapala15} used infrared spectroscopy to study PAHs and atomic and molecular line emission in the ISM.
@@
 Knowledge discovery and data mining methods are designed to extract hidden information from data and have been tested in many astronomical studies.
-However, to the best of our knowledge, this study is the first to use a data mining method on observations of nearby galaxies. %%% ehh
+However, to the best of our knowledge, this study is the first to use a data mining method on observations of nearby galaxies.
 
@@
 The unsupervised methods are very useful tools in knowledge discovery studies, where we have limited pre-expectations for the data or when we want to make sure that we did not miss any valuable information in  previous studies.
-%%% ehh to after or part.
 
@@
 These networks are used to study nonlinear and complex relations between input and output data.
-%These relations can be applied to the new sets of data with similar feature
-% PB joining these paragraphs
 One of the most well-known unsupervised neural networks in astronomy is a Kohonen self-organizing map (also called self-organizing map, or SOM).
@@
 
- %%add a little bit about PAHs in M31, dim15, drain14 and refs. therein. talk about what questions are still remained unanswered.
-The purpose of the present work is to use M31 observations to generate new insights into nearby galaxies, with a focus on relations between PAHs and other properties of the galaxy.
-There are very few studies on relations between properties of M31 with its PAH features.
-To fulfill this purpose, an unsupervised data mining method is the most suitable choice.
-\cite{Cesarsky98} studied PAH spectra in four regions in M31 and found that PAH features in M31 differ from those in other galaxies in having weak or no $6.2 - 8.6\mu$m emission with enhanced 11.2~$\mu$m emission.
-However, \cite{Dim15} by using {\it Spitzer}/Infrared Spectrograph~\citep[IRS,][]{Houck04b} observations, found that the PAH spectra of M31 have the same features as the spectra of other nearby star-forming galaxies.
-Using IRAC imaging observations,\cite{Barmby06} compared the observed 8~$\mu$m luminosity with other star formation indicators in the galaxy and found good agreement, and \cite{Draine14} found that the PAH abundance in M31 is almost constant up to a galactocentric radius of $\sim 20$~kpc.
-%Therefore, using data mining techniques, we aim to study PAH features in more detail. %PB: not sure this sentence adds much.
-
-%PB: would this paragraph go better if it was before the previous one ("purpose of the present work") ? Or possibly in the method section?
 K-means algorithm, SOMs, and hierarchical clustering are the main unsupervised methods that are used in astronomical studies~\citep[e.g.][]{DAbrusco12, Aycha16}. %%add one or two more
@@
 
+The purpose of the present work is to use M31 observations to generate new insights into nearby galaxies, with a focus on relations between PAHs and other properties of the galaxy.
+There are very few studies on relations between properties of M31 with its PAH features.
+To fulfill this purpose, an unsupervised data mining method is the most suitable choice.
+\cite{Cesarsky98} studied PAH spectra in four regions in M31 and found that PAH features in M31 differ from those in other galaxies in having weak or no $6.2 - 8.6\mu$m emission with enhanced 11.2~$\mu$m emission.
+However, \cite{Dim15} by using {\it Spitzer}/Infrared Spectrograph~\citep[IRS,][]{Houck04b} observations, found that the PAH spectra of M31 have the same features as the spectra of other nearby star-forming galaxies.
+Using IRAC imaging observations,\cite{Barmby06} compared the observed 8~$\mu$m luminosity with other star formation indicators in the galaxy and found good agreement, and \cite{Draine14} found that the PAH abundance in M31 is almost constant up to a galactocentric radius of $\sim 20$~kpc.
+
+%this project 1 M31 and its extensive data we do not have any SOM in nearby galaxies
 In this project we apply the self-organizing map algorithm to M31 data, training 1D and 2D networks.
@@
 We create 2D SOMs from subsets of the data as well as all available data, which helps us to understand the effect of each input in the position of the clusters in the SOM.
-%, which leads to prediction of the unmeasured quantities in a galaxy.
 We apply the 2D trained networks to  observations of the Pinwheel Galaxy (M101), another nearby spiral  galaxy, to check whether it has similar properties.
@@
 In Section $\S$~\ref{sec: summary}, we summarize our results and discuss potential future work in this subject.
+
+%SOM in Astronomy continued.
+% Large spectroscopic surveys have made available integrated spectra of millions of galaxies.
+% These integrated spectra combine the light of billions of individual stars and nebulae within a galaxy, and
+% finding patterns and common characteristics between galaxies can be a complex task.
+% \citet{In12} introduced a new clustering tool based on the SOM method for analyzing these large datasets.
+% They used $\sim 60000$ spectra from the Sloan Digital Sky Survey \citep[SDSS;][]{Abazajian09} to test their tool, and created very large SOMs to analyze the type of spectra/objects.
+% They also generated SOMs from quasars' spectra in order to find unusual types of spectra. 
+% Later, \citet{Meusinger16} used these SOMs and updated data from SDSS and other surveys to find a new class of quasars.
+% The other application of SOMs is to find outliers or errors in the data.
+% \citet{Fustes13} produced a package based on SOM to classify spectra from the GAIA survey that were previously classified as ``unknown'' by the SDSS pipeline.
+This package can recognize an astronomical object from instrumental errors, and then classify the object based on its spectrum.
+
+%Compare diff methods and say why we chose SOM!
+
+%supervised and unsupervised network

### 2016-07-11 sections/method0.01.tex
Applying the minors corrections

--- 2016-07-05 sections/method0.0.tex
@@
      This phase starts with maximum neighbourhood distance, and an initial high learning factor, usually 0.9, which is provided by the user. 
-     The ordering phase continues for the requested number of iterations or until the learning factor reduces to the tuning phase learning factor and the neighbourhood distance reaches the value set by the user.
-%PB: please check edit to this sentence - is "or until" correct?
-     %PB: combine paragraphs
+     The ordering phase continues for the requested number of iterations.
+     At the end of the iterations, the learning factor reduces to the tuning phase learning factor and the neighbourhood distance reaches the value set by the user. 
      The second phase is the ``tuning phase".
@@
 Each sample had two properties: amount of dust and star formation rate, where the possible values were
-either 0 or 1 for high or low SFR, and 0 or 0.5 for a high or low amount of dust. %PB: check - correct that 0 means high and 1 means low?
+either 0 or 1 for low or high SFR, and 0 or 0.5 for a low or high amount of dust. 
  We generated an SOM from the sample with a size of $10 \times 10$, using the method described in Sec.~\ref{sec: som}.

### 2016-07-13 main text/draft.tex
Applying the minors corrections
after Dave's comments

--- 2016-07-04 main text/draft0.0.tex
@@
 \usepackage{import}
-\usepackage[T1]{fontenc}
 \usepackage{ae,aecompl}
@@
 \usepackage[flushleft]{threeparttable}
-\usepackage{mwe}    % loads »blindtext« and »graphicx«
-\usepackage{subfig}
+%\usepackage{mwe}    % loads »blindtext« and »graphicx«
+\usepackage{slantsc}
+\usepackage[latin1]{inputenc}   
+\usepackage[T1]{fontenc}   
+\usepackage[finnish]{babel}
 
 \newcommand \kpc        {\,{\rm kpc}}
-\newcommand \sigmagas    {$\Sigma_{\rm \bld {gas }} $\ }
-\newcommand \sigmatotalgas {$\Sigma_{\rm \bld {total\, gas }} $\ }
-\newcommand \eqsigmagas    {\Sigma_{\rm \bld {gas }}}
-\newcommand \sigmasfr     {$\Sigma_{\rm \bld {SFR }} $\ }
-\newcommand \eqsigmasfr     {\Sigma_{\rm \bld {SFR }}}
-\newcommand \sigmastar    {$\Sigma_{\rm \bld {star }} $\ }
-\newcommand \eqsigmastar    {\Sigma_{\rm \bld {star }}}
+\newcommand \sigmagas    {$\Sigma_{\mathrm {gas }} $\ }
+\newcommand \sigmatotalgas {$\Sigma_{\mathrm {total\, gas }} $\ }
+\newcommand \eqsigmagas    {\Sigma_{\mathrm {gas }}}
+\newcommand \sigmasfr     {$\Sigma_{\mathrm {SFR }} $\ }
+\newcommand \eqsigmasfr     {\Sigma_{\mathrm {SFR }}}
+\newcommand \sigmastar    {$\Sigma_{\mathrm {star }} $\ }
+\newcommand \eqsigmastar    {\Sigma_{\mathrm {star }}}
 \newcommand \halpha    {H$\alpha $}
-\newcommand \um    {$\mu$m}
-%\newcommand \mice {$\mu$m}
+\newcommand \um    {$\mu$m\ }
+\newcommand \mice {$\mu$m}
 \newcommand \nprime {N$^\prime$}
@@
 \newcommand \Herschel {{\it Herschel }}
-\newcommand \sii {[S~{\textsc II}]} 
-\newcommand \oiii {[O~{\textsc III}]} 
-\newcommand \hi {H~{\textsc I}\ }
+\newcommand \sii {[S~\textsc{ii}]} 
+\newcommand \oiii {[O~\textsc{iii}]} 
+\newcommand \hi {H~\textsc{i}\ }
+\newcommand \hii {H~\textsc{ii}\ }
 
@@
 \begin{keywords} %PB: I think MNRAS only lets you have up to 6 and they are supposed to be from here: http://journals.aas.org/authors/keywords2013.html
-galaxies: individual: M31, galaxies: spiral, galaxies: star formation, galaxies: stellar content, galaxies: ISM, stars: formation, ISM: clouds, methods: observational, methods: statistical, data mining, methods:data analysis, techniques: image processing
+galaxies: individual: M31, M101, galaxies: spiral, galaxies: star formation, galaxies: stellar content, galaxies: ISM, stars: formation, ISM: clouds, methods: observational, methods: statistical, data mining, methods:data analysis, techniques: image processing
 \end{keywords}
@@
 %----------------------------------------------------------------------------------------
-\import{../sections/}{intro0.0.tex}
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%DATA
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-
-\import{../sections/}{data0.0.tex}
+\import{../sections/}{intro0.01.tex}
 
@@
 
-\import{../sections/}{method0.0.tex}
+\import{../sections/}{method0.01.tex}
+
+%----------------------------------------------------------------------------------------
+%----------------------------------------------------------------------------------------
+%----------------------------------------------------------------------------------------
+%DATA
+%----------------------------------------------------------------------------------------
+%----------------------------------------------------------------------------------------
+%----------------------------------------------------------------------------------------
+
+\import{../sections/}{data0.01.tex}
 
@@
 %----------------------------------------------------------------------------------------
-%\import{../sections/}{results0.0.tex}
-\import{../sections/}{R10.0.tex}
-\import{../sections/}{R20.0.tex}
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%Discussion
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-
-%\import{../sections/}{caveat.tex}
+%\import{../sections/}{results0.01.tex}
+\import{../sections/}{R10.01.tex}
+\import{../sections/}{R20.01.tex}
 
@@
 separate all 10 regions; some of the regions in M31 (e.g. regions 4 and 7) have very similar properties.
-% PB joining paragraphs
 Two-dimensional networks provide us with a more complete picture of the data.

### 2016-07-13 sections/app_2d.tex
after Dave's comments

--- 2016-06-18 sections/app_2d.tex
@@
 \section{2D SOMs of subsets}
-        \import{../sections/image_texts/}{col3byall.tex}
-        In Fig.~\ref{fig: subset2}, which is the SOM results from data listed in Table~\ref{tab: subset2}, distance between positions of the region 7, and region 3 is much larger compare to the one in Fig.~\ref{fig: all_derived_ones}.
+\label{sec: app_2d_soms_SOMN}
+
+        We removed IRAC 5.7 $\mu$m; \sii continuum and \oiii continuum; PAH8.3 $\mu$m, PAH12.0 $\mu$m, PAH17.0 $\mu$m, \oiii continuum, stellar mass and metallicity from subset 0, and generated subset samples 2 to 4, respectively (Tables~\ref{tab: subset2} to~\ref{tab: subset4}).
+        In Fig.~\ref{fig: subset2}, which is the SOM results from data listed in Tab.~\ref{tab: subset2}, distance between positions of the region 7, and region 3 is much larger compare to the one in Fig.~\ref{fig: all_derived_ones}.
         IRAC 5.7~$\mu$m flux in the region 7 and the region 3 is similar to each other. 
         Therefore, removing flux from IRAC 5.7 $\mu$m removed the one source of similarity in these two regions and they moved further from each other in the SOM.
+        For subset sample 7 (Tab.~\ref{tab: subset7}) we removed \sii flux, SPIRE 250 and 500~$\mu$m and TIR emission from subset 2 (~\ref{tab: subset5}).
         The positions of the regions 2 and 9 are closer to each other, but the weight distance between them is much higher (the colours between them are became almost black). 
@@
         In Fig.~\ref{fig: subset3}, the positions from the region 9 is much closer to the positions of the regions 4 and 7. 
-        Since region 4 and 5 have a similar [~\oiii] and [~\sii] continuum fluxes, by removing these two values from the input data distance between regions 4 and 5 became much smaller.
+        Since region 4 and 5 have a similar \oiii and \sii continuum fluxes, by removing these two values from the input data distance between regions 4 and 5 became much smaller.
         The positions of the regions 2 and 6 are closer together, but the colours between their neurons are darker.
         The wining neurons for regions 1 and 9 are moved further from each other, but the colours between them are slightly lighter. 
-        moreover, similar to regions 4 and 5, [~\oiii] and [~\sii] continuum fluxes for regions 1 and 9, and regions 8 and 6 are similar to each other, and removing these two values from input data, reduces the similarity between these regions.
+        moreover, similar to regions 4 and 5, \oiii and \sii continuum fluxes for regions 1 and 9, and regions 8 and 6 are similar to each other, and removing these two values from input data, reduces the similarity between these regions.
 Therefore, they moved further from each other.
@@
         Therefore, both of them have similar values in most of the input parameters.
-        However, they have very different fluxes in IRAC 5.7 $\mu$m and [~\sii] continuum, which removing these two fluxes from the input data moved their position on the SOM closer.
+        However, they have very different fluxes in IRAC 5.7 $\mu$m and \sii~continuum, which removing these two fluxes from the input data moved their position on the SOM closer.
         TIR luminosity and IRAC 5.7 $\mu$m flux for regions 3 and 5 are different, and removing them from the input data caused the distance between their position decreases. 

### 2016-07-13 sections/intro0.01.tex
after Dave's comments

@@
 Nearby galaxies play an important role in our understanding of galaxies' formation and evolution.
-These galaxies are close enough that we are able to observe regions inside them in detail.
-As a result, many studies have been devoted to finding relations between physical properties of galaxies both in spatially-resolved regions and in galaxies as a whole%(Some more references here)
-, and many others use these results in analyzing observations of high-redshift galaxies. %(Some more references here)
-Advances in technology allow us to both observe and store enormous amounts of data from the sky.
-Telescopes and surveys make observations of nearby galaxies in various wavelengths and from these data we can measure physical properties such as stellar mass, star formation rate (SFR), dust mass, and gas mass~\citep[e.g.][]{Calzetti07,Dale09,Eskew12}.
+Nearby galaxies are defined as those close enough that we are able to observe their structure and composition in detail.
+As a result, many studies have been devoted to finding relations between physical properties of galaxies, such as morphology, star formation rate (SFR), stellar mass, metallicity, and amount of gas, both for spatially-resolved regions and galaxies as a whole~\citep[e.g.][]{Wong13,Leroy08}, and many others use these results in analyzing observations of high-redshift galaxies~\citep[e.g.][]{Freundlich13,Walch11}.
+Advances in technology allow us to collect data from the sky.
+Surveys such as KINGFISH~\citep{Kennicutt11} and THINGS~\citep{Walter08} have made observations of nearby galaxies in various wavelengths and from these data we can measure physical properties such as stellar mass, star formation rate (SFR), dust mass, and gas mass~\citep[e.g.][]{Eskew12,Dale09,Calzetti07}.
 
 % A little bit about M31 and previous studies in M31.
-The Andromeda galaxy (M31), at a distance of $\sim$~0.78~Mpc \citep{McConnachie05}, is the closest spiral galaxy to the Milky Way.
-Images of this galaxy provide us with a detailed view of the inside of a spiral galaxy as seen from a distance.
-M31 has been observed by many telescopes including the {\it Hubble}, \Spitzer, \Herschel space telescopes and has been the subject of many more studies.
+The Andromeda galaxy (M31), at a distance of $\sim$~0.78~Mpc, is the closest spiral galaxy to the Milky Way~\citep{McConnachie05}.
+Images of this galaxy provide us with a detailed view of the inside of a spiral galaxy as seen from an external perspective.
+M31 has been observed by many telescopes including the {\textit Hubble}, \Spitzer, \Herschel space telescope.
 \cite{Barmby06} used data from the \Spitzer Infrared Array Camera \citep[IRAC;][]{Fazio04} to show the spatial distribution of Polycyclic Aromatic Hydrocarbons (PAHs) in the interstellar medium (ISM) of M31.
-Using data from the Multiband Imaging Photometer for Spitzer (MIPS), \cite{Gordon06} studied the morphology of M31's dust.
-\cite{Azimlu11} and \cite{Sanders12} catalogued and studied H {\sc II} regions of M31.
+Using data from the Multiband Imaging Photometer for Spitzer (MIPS) instrument, \cite{Gordon06} studied the morphology of M31's dust.
+\cite{Azimlu11} and \cite{Sanders12} catalogued and studied \hii~regions of M31.
 \cite{Draine14, Mattsson14, Viaene14, Smith12} and~\cite{Fritz12} used \Herschel data to study dust in the ISM of the galaxy.
-Properties of the current stars in the galaxy were studied by many groups~\citep[e.g.][and references therein]{Massey07,Tamm12,Dalcanton12}
-\cite{Rahmani16, Ford13} and \cite{Tabatabaei10} measured the SFR in M31 in order to study star formation laws, and \cite{Dim15} and \cite{Kapala15} used infrared spectroscopy to study PAHs and atomic and molecular line emission in the ISM.
+Properties of the current stars in the galaxy were studied by many groups~\citep[e.g.][and references therein]{Tamm12,Dalcanton12,Massey07}
+\cite{Rahmani16, Ford13} and \cite{Tabatabaei10} measured the SFR in M31 in order to study star formation laws, and~\cite{Dim15} and \cite{Kapala15} used infrared spectroscopy to study PAHs and atomic and molecular line emission in the ISM.
 
 Although all these studies measured some properties of M31, or answered specific scientific questions about this galaxy, we still do not have a complete picture of underlying processes in the galaxy.
-The amount of observational data and measured quantities for M31 makes this galaxy a suitable target for a knowledge discovery and data mining study.
+What is the correlation between PAHs and SFR, dust mass, and gas mass in M31? 
+Are PAHs features in M31 are similar or they can be divided in various groups? If so, what are properties of each group?
+Does intensity of PAHs emission depends on the underlying structure of their position? 
+How do they compare to properties of galaxies?
+The properties of M31 that derived in various studies and observational data of this galaxy can be used for a knowledge discovery and data mining study.
+%The amount of data for M31 makes this galaxy a suitable target for a knowledge discovery and data mining study.
+the Pinwheel Galaxy (M101), with distance of 6.7 Mpc~\citep{Freedman01}, is another nearby galaxies that has been observed and studied~\citep[e.g][and references therein]{Kennicutt11,Dale09, Leroy08, Gordon08}.
+M101 is a large spiral galaxy with several \hii~regions and high metallicity gradient from centre to outskirt of it~\citep{Kennicutt03}.
+In case of dimensionality data from M101 is a suitable addition to M31 data for a data mining study.
 Knowledge discovery and data mining methods are designed to extract hidden information from data and have been tested in many astronomical studies.
-However, to the best of our knowledge, this study is the first to use a data mining method on observations of nearby galaxies.
+However, this study is the first to use a data mining method on observations of nearby galaxies.
 
@@
 
-%SOM
-Some of the most tested methods of data mining in astronomy are artificial neural networks (ANNs)~\citep[e.g.][and references therein]{ Hossein14,Hossein16}.
-ANNs are designed to work in the same way that the neurons work in a human brain.
-They are networks of interconnected neurons (nodes), in which all of the connections are weighted.
-These networks are used to study nonlinear and complex relations between input and output data.
-One of the most well-known unsupervised neural networks in astronomy is a Kohonen self-organizing map (also called self-organizing map, or SOM).
-SOMs map and visualize complex data~\citep{Kohonen82} and show simple geometrical relationships in non-linear high dimensional data~\citep{Kohonen98}.
-The result of a SOM is a 1D or 2D network of neurons, which shows the positions of clusters and their relative distance.
-Since the 1990s, many studies utilized SOMs for object classification and clustering (e.g.
-classifying quasars' spectra, star/galaxy classifications, gamma-ray burst clustering and light curve classification) and photometric redshift estimation~\citep[e.g.][]{Odewahn92, Hernandez94, Murtagh95, Maehoenen95,Scaringi09,Geach12,Fustes13,Meusinger16,Rahmani16b} %%% Why I cannot add submitted in front of the high-z paper %PB: MNRAS style guide says "Private communications or papers in preparation should be listed as such in the text, but omitted from the reference list, e.g.
-Smith (in preparation) shows that… " -- but I'm not clear on whether this applied to submitted papers or not
-
-K-means algorithm, SOMs, and hierarchical clustering are the main unsupervised methods that are used in astronomical studies~\citep[e.g.][]{DAbrusco12, Aycha16}. %%add one or two more
-For both K-means and SOM algorithms, the user must define the number of clusters, and the algorithms decide how to separate the data into desired number of clusters.
-In the hierarchical clustering method, the user must define dissimilarity between the groups; the algorithm combines (or divides) existing groups based on their dissimilarity and creates a hierarchical structure.
-Comparing SOMs, K-means and hierarchical clustering shows that in some cases hierarchical clustering method mis-classifies the data~\citep[][and references therein]{Mangiameli96}.
-We chose the SOM method over K-means due to the fact that SOMs not only cluster data, but also show similarities and dissimilarities between the clusters.
-Therefore, we can cluster our sample data and study the underlying structure, simultaneously.
-
 The purpose of the present work is to use M31 observations to generate new insights into nearby galaxies, with a focus on relations between PAHs and other properties of the galaxy.
-There are very few studies on relations between properties of M31 with its PAH features.
-To fulfill this purpose, an unsupervised data mining method is the most suitable choice.
+There are very few studies on relations between properties of M31 with its PAH features. %generate?!
 \cite{Cesarsky98} studied PAH spectra in four regions in M31 and found that PAH features in M31 differ from those in other galaxies in having weak or no $6.2 - 8.6\mu$m emission with enhanced 11.2~$\mu$m emission.
-However, \cite{Dim15} by using {\it Spitzer}/Infrared Spectrograph~\citep[IRS,][]{Houck04b} observations, found that the PAH spectra of M31 have the same features as the spectra of other nearby star-forming galaxies.
-Using IRAC imaging observations,\cite{Barmby06} compared the observed 8~$\mu$m luminosity with other star formation indicators in the galaxy and found good agreement, and \cite{Draine14} found that the PAH abundance in M31 is almost constant up to a galactocentric radius of $\sim 20$~kpc.
+However,~\cite{Dim15} using {\it Spitzer}/Infrared Spectrograph~\citealt[IRS,][]{Houck04b} observations, found that the PAH spectra of M31 have the same features as the spectra of other nearby star-forming galaxies.
+Using IRAC imaging observations,~\cite{Barmby06} found good agreement between SFRs derived using observed 8~$\mu$m luminosity with other 
+star formation indicators such as \halpha and far infrared luminosity in M31.
+\cite{Draine14} found that the PAH abundance in M31 is almost constant up to a galactocentric radius of $\sim 20$~kpc.
+With data mining techniques we address that
+compare to other galaxies, are PAHs features in M31 are unique as~\cite{Cesarsky98} mentioned or they are normal as ~\cite{Dim15} and \cite{Draine14} concluded
 
 %this project 1 M31 and its extensive data we do not have any SOM in nearby galaxies
-In this project we apply the self-organizing map algorithm to M31 data, training 1D and 2D networks.
+In this project we apply the self-organizing map algorithm (SOM) to M31 data, training 1D and 2D networks.
 Using the smaller networks we study the properties of the clusters and investigate relations between PAH features and other quantities in M31.
 We create 2D SOMs from subsets of the data as well as all available data, which helps us to understand the effect of each input in the position of the clusters in the SOM.
-We apply the 2D trained networks to  observations of the Pinwheel Galaxy (M101), another nearby spiral  galaxy, to check whether it has similar properties.
+We apply the 2D trained networks to  observations of M101, another nearby spiral  galaxy, to check whether it has similar properties.
 If our hypothesis is correct, we should be able to see that regions in M31 and M101 with the same positions in the SOM have the same properties.
 
+We describe the SOM method in Section $\S$~\ref{sec: method}. 
 In Section $\S$~\ref{Sec: data_SOMN}, we present the observational data from M31 and M101 that we use in this study.
-We describe the SOM method in Section $\S$~\ref{sec: method}. 
 The results of the 1D SOM networks and the studying of PAHs in M31 are presented in Section $\S$~\ref{Sec: 1d_cluster}.
@@
 In Section $\S$~\ref{sec: summary}, we summarize our results and discuss potential future work in this subject.
-
-%SOM in Astronomy continued.
-% Large spectroscopic surveys have made available integrated spectra of millions of galaxies.
-% These integrated spectra combine the light of billions of individual stars and nebulae within a galaxy, and
-% finding patterns and common characteristics between galaxies can be a complex task.
-% \citet{In12} introduced a new clustering tool based on the SOM method for analyzing these large datasets.
-% They used $\sim 60000$ spectra from the Sloan Digital Sky Survey \citep[SDSS;][]{Abazajian09} to test their tool, and created very large SOMs to analyze the type of spectra/objects.
-% They also generated SOMs from quasars' spectra in order to find unusual types of spectra. 
-% Later, \citet{Meusinger16} used these SOMs and updated data from SDSS and other surveys to find a new class of quasars.
-% The other application of SOMs is to find outliers or errors in the data.
-% \citet{Fustes13} produced a package based on SOM to classify spectra from the GAIA survey that were previously classified as ``unknown'' by the SDSS pipeline.
-This package can recognize an astronomical object from instrumental errors, and then classify the object based on its spectrum.
-
-%Compare diff methods and say why we chose SOM!
-
-%supervised and unsupervised network

### 2016-07-13 sections/method0.01.tex
after Dave's comments

@@
 \label{sec: method}
+\subsection{Choosing an Algorithm}
+To fulfill this purpose, an unsupervised data mining method is the most suitable choice.
+
+Some of the most tested methods of data mining in astronomy are artificial neural networks (ANNs)~\citep[e.g.][and references therein]{ Hossein14,Hossein16}.
+ANNs are designed to work in the same way that the neurons work in a human brain.
+These are networks of interconnected neurons (nodes), in which all of the connections are weighted.
+These networks are used to study nonlinear and complex relations between input and output data.
+One of the most well-known unsupervised neural networks in astronomy is a Kohonen self-organizing map (also called self-organizing map, or SOM).
+SOMs visualize complex data~\citep{Kohonen82} and show simple geometrical relationships in non-linear high dimensional data~\citep{Kohonen98}.
+The result of a SOM is a 1D or 2D network of neurons, which shows the positions of clusters and their relative distance.
+Since the 1990s, many studies utilized SOMs for object classification and clustering (e.g.
+classifying quasars' spectra, star/galaxy classifications, gamma-ray burst clustering and light curve classification) and photometric redshift estimation~\citep[e.g.][]{Odewahn92, Hernandez94, Murtagh95, Maehoenen95,Scaringi09,Geach12,Fustes13,Meusinger16,Rahmani16b} %%% Why I cannot add submitted in front of the high-z paper %PB: MNRAS style guide says "Private communications or papers in preparation should be listed as such in the text, but omitted from the reference list, e.g.
+Smith (in preparation) shows that… " -- but I'm not clear on whether this applied to submitted papers or not
+
+K-means algorithm, SOMs, and hierarchical clustering are the main unsupervised methods that are used in astronomical studies~\citep[e.g.][]{DAbrusco12, Aycha16}. %%add one or two more
+For both K-means and SOM algorithms, the user must define the number of clusters, and the algorithms decide how to separate the data into desired number of clusters.
+In the hierarchical clustering method, the user must define dissimilarity between the groups; the algorithm combines (or divides) existing groups based on their dissimilarity and creates a hierarchical structure.
+Comparing SOMs, K-means and hierarchical clustering shows that in some cases hierarchical clustering method mis-classifies the data~\citep[][and references therein]{Mangiameli96}.
+We chose the SOM method over K-means due to the fact that SOMs not only cluster data, but also show similarities and dissimilarities between the clusters.
+Therefore, we can cluster our sample data and study the underlying structure, simultaneously.
+
  \subsection{Self Organizing Maps}
@@
  The process of creating an SOM  happens over a series of $N$ iterations.
- In each iteration, the algorithm calculates the Euclidean distance for each node $j$ as  $D_j^2= \sum_{i=0}^{i=n} (V_i - W_i)^2$, and finds a neuron with $D_{j_, \rm min}}$. 
+ In each iteration, the algorithm calculates the Euclidean distance for each node $j$ as  $D_j^2= \sum_{i=0}^{i=n} (V_i - W_i)^2$, and finds a neuron with $D_{j_,{\mathrm min}}$. 
  This neuron is the winner node and is calling Best Matching Unit (BMU). 
@@
 
-     In order to create self-organizing maps, we used the {\sc MATLAB} neural network toolbox~\citep[NNT,][]{matlabtolbox}.
-     An SOM in {\sc NNT} can be created by the {\sc newsom} library which works in two phases, the ``ordering phase" and ``tuning phase" . 
+     In order to create self-organizing maps, we used the \textsc{ matlab} neural network toolbox~\citep[NNT,][]{matlabtolbox}.
+     An SOM in \textsc{ nnt} can be created by the \textsc{ newsom} library which works in two phases, the ``ordering phase" and ``tuning phase" . 
      Phase one is the ``ordering phase". 
@@
 
-     To present our results, we use {\sc nnt}'s built-in plotting tool.
+     To present our results, we use \textsc{nnt}'s built-in plotting tool.
      Specifically, we combine two of the plots in this tool: a hits map, which shows the number of times each neuron has become the winner (hits), and a distance map, which shows the distance between weight vectors of those neurons.
@@
      Neurons with zero hits are left empty.
-     In Section~\ref{sec: mock_sample} we used {\sc newsom} to create SOMs from a mock sample to illustrate how this method works and how to interpret the results.
+     In Section~\ref{sec: mock_sample} we used \textsc{newsom} to create SOMs from a mock sample to illustrate how this method works and how to interpret the results.
 
@@
      %Based on our data we created our final SOMs with following initial values: number of iteration in ordering phase = 1000; ordering phase learning factor = 0.9; tuning phase learning factor= 0.02; and tuning phase neighbourhood distance to be 1.
-     %All the other parameters are default values in {\sc newsom} library and cannot be changed by the users.
+     %All the other parameters are default values in \textsc{ newsom} library and cannot be changed by the users.
 

### 2016-07-26 sections/R10.01.tex
# Conflicts: #	sections/image_texts/all.tex

@@
 %Why 1D maps are useful
-    The purpose of  exploring the M31 data with 1D maps is to monitor the general behaviour of data. 
+    The purpose of  exploring the M31 data with 1D maps is to monitor the general behaviour of the data. 
     One-dimensional SOMs can have the minimum number of clusters, $1\times2$, up to the highest number of clusters possible.
@@
     On the other hand, larger grid 1D SOMs are a helpful tool to get quick insight into the data.
-%    In the following section, we are going to show how we used 1D SOMs to extract information from available data in M31.
-%Clustering
- %   \subsection{Clustering M31 data}
+
+    \subsection{Clustering M31 data}%I am not sure about it
 
@@
         %%%Talking about four right regions
-        \cite{Dim15} showed that regions 1, 2, 9, and 10 have higher PAH line fluxes compared to other regions (Fig. 5 in \cite{Dim15}). 
+        \cite{Dim15} showed that regions 1, 2, 9, and 10 have higher PAH line fluxes compared to other regions (Fig. 5 in \citealt{Dim15}). 
         %Regions 1, 2, and 9 are in the 10~Kpc ring and region 10 is located in the bulge of M31; however, regions 3 to 8 are located slightly out of the inner ring or the 10~kpc one.
@@
     \begin{figure}
-            \subfloat[$1\times2$~network\label{fig: M31_net_1by2}]{
-             \includegraphics[width=0.5\textwidth]{../images0.01/M31/1D/combine_1D_1by2_all.png}
-             }
+    \begin{subfigure}[b]{0.5\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../images0.01/M31/1D/combine_1D_1by2_all.png}
+        \caption{$1\times2$~network}
+    \label{fig: M31_net_1by2}
+    \end{subfigure}
     \hfill
-            \subfloat[$1\times3$~network\label{fig: M31_net_1by3}]{
-            \includegraphics[width=0.5\textwidth]{../images0.01/M31/1D/combine_1D_1by3_all.png}
-             }
+    \begin{subfigure}[b]{0.5\textwidth}
+        \includegraphics[width=\textwidth]{../images0.01/M31/1D/combine_1D_1by3_all.png}
+         \caption{$1\times3$~network}
+        \label{fig: M31_net_1by3}
+    \end{subfigure}
     \hfill
-            \subfloat[$1\times14$~network\label{fig: M31_net_1by14}]{
-             \includegraphics[width=0.5\textwidth]{../images0.01/M31/1D/combine_1D_1by14_all.png}
-             }%%% What should I do with this one! It doesn't look good visually
+    \begin{subfigure}[b]{0.5\textwidth}
+        \includegraphics[width=\textwidth]{../images0.01/M31/1D/combine_1D_1by14_all.png}
+        \caption{$1\times14$~network}
+        \label{fig: M31_net_1by14}
+    \end{subfigure}
    \caption{SOM of the M31 data from $1\times2$, $1\times3$~and $1\times14$~grids.
@@
     \end{figure}
+
+% \end{figure}
+%         \begin{figure}
+%             \subfloat[$1\times2$~network\label{fig: M31_net_1by2}]{
+%              \includegraphics[width=0.5\textwidth]{../images0.01/M31/1D/combine_1D_1by2_all.png}
+%              }
+%             \hfill
+%             \subfloat[$1\times3$~network\label{fig: M31_net_1by3}]{
+%             \includegraphics[width=0.5\textwidth]{../images0.01/M31/1D/combine_1D_1by3_all.png}
+%              }
+%              \hfill
+%             \subfloat[$1\times14$~network\label{fig: M31_net_1by14}]{
+%              \includegraphics[width=0.5\textwidth]{../images0.01/M31/1D/combine_1D_1by14_all.png}
+%              }
+%              %%% What should I do with this one! It doesn't look good visually
+%             \caption{SOM of the M31 data from $1\times2$, $1\times3$~and $1\times14$~grids.
+The axes show the position of the neurons.
+The purple hexagonal shapes represent the neurons.
+The grey scale colours show the differences between weight of the neurons, with white as the minimum difference and black as the maximum.
+The numbers in the plot show the M31 regions located in each neuron.}
+%             \label{fig: M31_nets_1d}
+%         \end{figure}
 
@@
 
-    \subsection{Inside the 2 neuron network}%%% I will find better title for this subsection
-        %What is going on in this section
+    \subsection{Inside the 2 neuron network}
+
         \label{sec: inside_the_2_neurons}
@@
 
-        \begin{figure}
-        \includegraphics[width=0.5\textwidth]{../images0.01/cor_plots/M31_derived_3_to_8_core_plot_for_paper.pdf}%%% cut the white regions around the figure
+        \begin{figure*}
+        \includegraphics[width=\textwidth]{../images0.01/cor_plots/M31_derived_3_to_8_core_plot_for_paper.pdf}
         \caption{Same as Fig.~\ref{fig: cor_all}, but here we used data from regions grouped in the left sides of Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}. }
           \label{fig: cor_cluster1}
-        \end{figure}
+        \end{figure*}
 
@@
        Regardless of the fact that some of the (anti)-correlations in Fig.~\ref{fig: cor_cluster1} might have physical meaning, we have to mention that we only used 6 regions to calculate these correlation coefficients.
-       The number of data points is not high enough to yield a strong conclusion about PAH properties in M31.%%% it doesn't sound right:((
+       The number of data points is not high enough to yield a strong conclusion about PAH properties in M31.
         However, we can conclude that since the correlation coefficients derived from the clustered data (Fig.~\ref{fig: cor_cluster1}) differ from the correlation coefficients derived from the data from the all regions (Fig.~\ref{fig: cor_all}), the SOM separated a hidden cluster of the data which has different properties.
-%%Again eh!

### 2016-07-26 sections/R20.01.tex
# Conflicts: #	sections/image_texts/all.tex

@@
     As mentioned in previous sections, the size of SOMs are arbitrary and must be decided by users based on their goals for use of the SOM.
+
     In this section we chose $10\times10$ size despite knowing, from the size of our input data, that most of the neurons would be empty.
     Using 2D networks, we are mostly interested in the ability of the SOMs to show the underlying structure of the data rather than its clustering features.
-    \import{../sections/image_texts/}{all.tex}
     Fig.~\ref{fig: all_derived_ones} shows the 2D SOM of the M31 data.
     Similar to Fig.~\ref{fig: M31_net_1by14}, all the 10 regions are completely separated from each other in Fig.~\ref{fig: all_derived_ones}.
+    \import{../sections/image_texts/}{all.tex}
 
@@
             The order in which data were added is the same as the order in Fig.~\ref{fig: cor_all}, i.e.
-the SOM in Fig~\ref{fig: inc_D_col3s}a was created from PAH and H$\alpha$ emission as input data, the SOM in Fig~\ref{fig: inc_D_col3s}b created from PAHs, H$\alpha$ emission and [\sii] continuum, and so on.
+the SOM in Fig~\ref{fig: col3and11_dist} was created from PAH and H$\alpha$ emission as input data, the SOM in Fig~\ref{fig: col3and12_dist} created from PAHs, H$\alpha$ emission and \sii~ continuum, and so on.
             \import{../sections/image_texts/}{col3byall.tex}
@@
             However, the position of each region relative to other regions changes dramatically only when the new sets of input data are given to the algorithm (assuming all the initial values for the run are unchanged).
-            In all SOMs in Fig~\ref{fig: inc_D_col3s}, region 10 is located in the corner of the SOMs, but in  Figs~\ref{fig: inc_D_col3s}a,~\ref{fig: inc_D_col3s}d,~\ref{fig: inc_D_col3s}g,~\ref{fig: inc_D_col3s}k, and ~\ref{fig: inc_D_col3s}l, it is placed in the left side of the SOMs and in the others it is in the right side of the networks.
+            In all SOMs in Fig~\ref{fig: inc_D_col3s}, region 10 is located in the corner of the SOMs, but in  Figs~\ref{fig: col3and11_dist},~\ref{fig: col3and14_dist},~\ref{fig: col3and17_dist},~\ref{fig: col3and21_dist}, and ~\ref{fig: col3and22_dist}, it is placed in the left side of the SOMs and in the others it is in the right side of the networks.
             In our discussion on differences between networks, we do not address the changes in the network due to initialization of the SOM algorithm and only consider the effect of changing the input data.
 
-            Comparing Figs.~\ref{fig: inc_D_col3s}a to ~\ref{fig: inc_D_col3s}o shows that adding \halpha~emission data to PAH features causes regions 9 and 10 become isolated. 
+            Comparing Figs.~\ref{fig: col3and11_dist} to ~\ref{fig: col3and25_dist} shows that adding \halpha~emission data to PAH features causes regions 9 and 10 become isolated. 
             Increasing the dimension of the input data makes region 10 more isolated.

### 2016-07-26 sections/V0.0/R10.0.tex
# Conflicts: #	sections/image_texts/all.tex

--- 2016-07-05 sections/R10.0.tex
@@
 
-    \subsection{Inside the 2 neuron network}%%% I will find better title for this subsection
+    \subsection{Inside the 2 neuron network}
         %What is going on in this section
@@
 
-        \begin{figure}
-        \includegraphics[width=0.5\textwidth]{../images0.01/cor_plots/M31_derived_3_to_8_core_plot_for_paper.pdf}%%% cut the white regions around the figure
+        \begin{figure*}
+        \includegraphics[width=\textwidth]{../images0.01/cor_plots/M31_derived_3_to_8_core_plot_for_paper.pdf}%%% cut the white regions around the figure
         \caption{Same as Fig.~\ref{fig: cor_all}, but here we used data from regions grouped in the left sides of Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}. }
           \label{fig: cor_cluster1}
-        \end{figure}
+        \end{figure*}
 
@@
         Without data from more regions in M31, we cannot confidently say that higher stellar mass decreases PAH fluxes.
-        %% Sahar: Can we have higher PAHs absorbes stellar mass and thats why we see the anti-correlation?!!!
+        %% Sahar: Can we have higher PAHs absorbs stellar mass and that's why we see the anti-correlation?!!!
 

### 2016-07-26 sections/data0.01.tex
# Conflicts: #	sections/image_texts/all.tex

@@
 Our study includes 10 regions in M31 (Fig.~\ref{fig: regions in m31}) and 8 regions in M101 (Fig.~\ref{fig: regions in m101}). 
-These specific regions were chosen for the availability of mid-infrared PAH spectroscopy.
-Besides PAH line strengths, for each galaxy, we use spectroscopic and photometric observations as well as their derived properties, such as SFR, stellar mass, dust luminosity (L$_{\rm dust}$) and mass, metallicity, and gas mass.
-Table~\ref{tab: data} shows the full list of data and their units for both M31 and M101.
+These specific regions were chosen for the availability of \Spitzer/IRS 5 - 15$\mu$m  spectroscopy covering PAHs emission.
+Besides PAH bands strengths, for each galaxy, we use spectroscopic and photometric observations as well as their derived properties, such as SFR, stellar mass, dust luminosity (L$_{\rm dust}$) and mass, metallicity, and gas mass.
+Table~\ref{tab: data} shows the full list of data for both M31 and M101.
 Observed values were divided by the area of their region (in arcsec$^2$), to remove the distance factor from the data and compare values across galaxies.
@@
 
+\begin{figure}
+  \begin{subfigure}[b]{0.5\textwidth}
+        \centering
+    %\centering
+        \includegraphics[width=0.97\textwidth]{../images0.01/M31/M31.png}
+        \caption{MIPS24 image of M31, with position of 10 regions that we studies.}
+        \label{fig: regions in m31}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.5\textwidth}
+        \includegraphics[width=\textwidth]{../images0.01/M101/M101.png}
+        \caption{IRAC1 image of M101, with position of our 8 regions that we studies.}
+    \label{fig: regions in m101}
+    \end{subfigure}
+    \caption{Position of the data in M31 (up) and M101 (down).}
+\end{figure}
+
 %   \begin{figure}
-%   \begin{subfigure}[b]{0.5\textwidth}
-%         \centering
-%     %\centering
-%         \includegraphics[width=0.97\textwidth]{../images0.0/M31/M31.png}
-%         \caption{MIPS24 image of M31, with position of 10 regions that we studies.}
-%         \label{fig: regions in m31}
-%     \end{subfigure}
+%     \subfloat[MIPS 24~$\mu$m image of M31~\citep{Gordon06}, with position of 10 regions from~\cite{Dim15} \label{fig: regions in m31}]{
+%       \includegraphics[width=0.5\textwidth]{../images0.01/M31/M31.png}
+%     }
 %     \hfill
-%     \begin{subfigure}[b]{0.5\textwidth}
-%         \includegraphics[width=\textwidth]{../images0.01/M101/M101.png}
-%         \caption{IRAC1 image of M101, with position of our 8 regions that we studies.}
-%     \label{fig: regions in m101}
-%     \end{subfigure}
-%     \caption{Position of the data in M31 (up) and M101 (down).}
+%     \subfloat[IRAC 3.6~$\mu$m image of M101~\citep{Dale09}, with position of 8 regions.\label{fig: regions in m101}]{
+%       \includegraphics[width=0.5\textwidth]{../images0.01/M101/M101.png}}
+%     \caption{Position of regions that the input data for SOM that obtained from there in M31 (up) and M101 (down).}
+%     \label{fig:dummy}
 %   \end{figure}
-
-  \begin{figure}
-    \subfloat[MIPS 24~$\mu$m image of M31~\citep{Gordon06}, with position of 10 regions from~\cite{Dim15} \label{fig: regions in m31}]{
-      \includegraphics[width=0.5\textwidth]{../images0.01/M31/M31.png}
-    }
-    \hfill
-    \subfloat[IRAC 3.6~$\mu$m image of M101~\citep{Dale09}, with position of 8 regions.\label{fig: regions in m101}]{
-      \includegraphics[width=0.5\textwidth]{../images0.01/M101/M101.png}}
-    \caption{Position of regions that the input data for SOM that obtained from there in M31 (up) and M101 (down).}
-    \label{fig:dummy}
-  \end{figure}
 
@@
 
-     \cite{Dim15} using {\it Spitzer}/IRS observations to study PAHs in 10 regions chosen to span a range of mid-infrared flux ratios in M31. 
-     Fluxes and equivalent widths of PAH and atomic line features were measured using the~{\sc PAHFIT IDL} tool~\citep{Smith07b}.
+     \cite{Dim15} used {\it Spitzer}/IRS observations to study PAHs in 10 regions chosen to span a range of mid-infrared flux ratios in M31. 
+     Fluxes and equivalent widths of PAH and atomic line features were measured using the~\textsc{pahfit idl} tool~\citep{Smith07b}.
      \cite{Dim15} also measured metallicity and radiation hardness index (RHI) for these 10 regions.
@@
 
-    For the photometry part of the sample, we used the \GALEX~\citep{Martin05} far-ultraviolet and near-ultraviolet (FUV and NUV) channel images; \halpha, \sii~and \oiii narrow band images~\citep{Massey07}, IRAC 3.6, 4.5, 5.8 and 8.0$\mu$m images ~\citep{Barmby06}; MIPS24 and 70~$\mu$m~images\citep{Gordon06}; and PACS 100 and 160~$\mu$m and SPIRE 250, 350, and 500~$\mu$m~\citep{Fritz12} images.
+    For the photometry part of the sample, we used the \GALEX \citep{Martin05} far-ultraviolet and near-ultraviolet (FUV and NUV) channel images; \halpha, \sii~and \oiii narrow band images~\citep{Massey07}, IRAC 3.6, 4.5, 5.8 and 8.0$\mu$m images~\citep{Barmby06}; MIPS24 and 70~$\mu$m~images\citep{Gordon06}; and PACS 100 and 160~$\mu$m and SPIRE 250, 350, and 500~$\mu$m~\citep{Fritz12} images.
      The units of all fluxes were converted to W~m$^{-2}$ in order to be the same as the PAH fluxes.
-     $^{12}$CO (J:$1\rightarrow0$) line emission images~\citep{Nieten06} and atomic gas (H\,{\sc I}) 21~cm emission images from~\cite{Chemin09} were added to the input data. 
-     For derived values, we utilized SFR(FUV + 24$\mu$m), stellar mass, molecular gas mass, atomic gas mass, total gas mass, and total infrared (TIR) luminosity (L$_{\rm TIR}$) from \cite{Rahmani16}, and L$_{\rm dust}$ and mass from \cite{Draine14}.
+     $^{12}$CO (J:$1\rightarrow0$) line emission images~\citep{Nieten06} and atomic gas (\hi) 21~cm emission images from~\cite{Chemin09} were added to the input data. 
+     For derived values, we utilized SFR(FUV + 24$\mu$m) measured using combination of FUV and 24$\mu$m emission, stellar mass, molecular gas mass, atomic gas mass, total gas mass, and total infrared (TIR) luminosity (L$_{\mathrm TIR}$) from \cite{Rahmani16}, and L$_{\mathrm dust}$ and mass from \cite{Draine14}.
 
@@
     \label{Sec: data_M101_SOMN}
-     \cite{Gordon08} measured PAH fluxes, metallicity and RHI for M101 in 8 regions chosen.. % PB: reason for selecting?
-%     We also added their measurement of metallicity and RHI for these regions to our sample.
-     We used NED~\footnote{The NASA/IPAC Extragalactic Database (NED) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.} website to gather imaging observations of M101, including
+
+     \cite{Gordon08} measured PAH fluxes and RHI for M101 in 8 star forming \hii~regions.
+     Metallicity of 6 out of 8 regions were measured by~\cite{Kennicutt03} and the other two by~\cite{Gordon08}.
+     We used the NED~\footnote{The NASA/IPAC Extragalactic Database (NED) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.} website to gather imaging observations of M101, including
       \GALEX FUV and NUV~\citep{depaz07}, IRAC $3.6-8.0\mu$m, MIPS~24 and 70~$\mu$m~\citep{Dale09}, and PACS~100 and 160~$\mu$m and SPIRE~250, 350, and 500~$\mu$m emission from~\cite{Kennicutt11}.
-     As for M31, we used $^{12}$CO (J:$1\rightarrow0$) line emission images~\citep{Helfer03} and atomic gas (H\,{\sc I}) 21~cm emission images from \cite{Walter08}.
+     As with M31, we used $^{12}$CO (J:$1\rightarrow0$) line emission images~\citep{Helfer03} and atomic gas (\hi) 21~cm emission images from \cite{Walter08}.
      SFR(FUV + 24$\mu$m), stellar and total gas mass maps were calculated using the same methods as for M31.
 
-     Some of the correlations between single-wavelength emission and galaxy properties are well-known.
+       \subsection{Preparing data for data mining}
+
+     Correlations between some of single-wavelength emission and galaxy properties are well-known.
      Emission in the 3.6$\mu$m band traces the old stellar population very well~\citep[e.g]{Leitherer99,Smith07a} and it can be used to calculate the stellar mass~\citep{Eskew12}.
@@
      Total infrared emission is calculated from a modified version of~\cite{Draine07} calibration using using 8, 24, 70, and 160 $\mu$m emission~\citep{Boquien10}.
-     To make sure that we do not use the observed data as input data in multiple forms, we removed all the observed data that were used to calculate galaxies properties from the input sample.
-     We used this sample of observations as the main input for creating SOMs.
-     Fig.~\ref{fig: cor_all} shows the Pearson correlation coefficients between the observations computed with a confidence level of $95\%$.
+
+    %To guarantee that we do not use the observed data as an input for SOM in multiple forms, we removed all the observed data that were used to calculate galaxies properties from the input sample.
+    We removed all the observed data that were used to calculate galaxies properties from the input sample, to guarantee that they have not been used in multiple forms
+   % We used this new sample of observational and derived data as the main input for creating SOMs.
+    To have a prior knowledge on the data set, %or to have an insight into the data set!
+    we computed the Pearson correlation coefficients between input data.
+    Fig.~\ref{fig: cor_all} shows the Pearson correlation coefficients with a confidence level of 95 per cent. 
+    All the PAHs are correlate with one another very well.
+    They also highly correlate with SPIRE bands and PACS emission, L$_{\mathrm dust}$, L$_{\mathrm TIR}$, SFR and metallicity.
+    Fluxes from PAHs 7.7, 8.3, 12.7 and 17~$\mu$m show weak ant-correlation with RHI.
+    In general, PAHs in our data set highly correlate with most of the other quantities.
 
@@
                 \includegraphics[width=\textwidth]{../images0.01/cor_plots/M31_all_derived_ones_core_plot_for_paper.pdf}
-            \caption{Pearson correlation coefficients with a confidence level of 95$\%$ for all data in subset 0.
-The colours show the Pearson correlation coefficients where 1 means highly correlated and $-1$ means highly anti-correlated quantities.
+            \caption{Pearson correlation coefficients with a confidence level of 95 per cent for all data in subset 0.
+The colours and circles' size show the Pearson correlation coefficients where large blue circles are 1 which means highly correlated and large red circles are$-1$ means highly anti-correlated quantities.
 The non-significant correlations were left empty.}

### 2016-07-26 sections/image_texts/col3byall_org.tex
# Conflicts: #	sections/image_texts/all.tex

--- 2016-07-04 sections/image_texts/col3byall.tex
@@
         \centering
-        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and11.png}
+        \includegraphics[width=54mm, height=38mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and11.png}
+        \caption{Input data: data from Fig.~\ref{fig: only_pahs} and \halpha}
         \label{fig: col3and11_dist}
@@
         \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and12.png}
+        \caption{Input data: data from Fig.~\ref{fig: col3and11_dist} and \oiii}
         \label{fig: col3and12_dist}
@@
         \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and13.png}
+        \caption{Input data: data from Fig.~\ref{fig: col3and12_dist} and \sii}
         \label{fig: col3and13_dist}
@@
         \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and14.png}
+        \caption{Input data: data from Fig.~\ref{fig: col3and13_dist} and IRAC~5.7~$\mu$m emission}
         \label{fig: col3and14_dist}
@@
         \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and15.png}
+        \caption{Input data: data from Fig.~\ref{fig: col3and14_dist} and PACS~100~$\mu$m emission }
         \label{fig: col3and15_dist}
@@
         \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and16.png}
+        \caption{Input data: data from Fig.~\ref{fig: col3and15_dist} and SPIRE~250~$\mu$m emission }
         \label{fig: col3and16_dist}
@@
         \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and17.png}
+        \caption{Input data: data from Fig.~\ref{fig: col3and16_dist} and SPIRE~350~$\mu$m emission }
         \label{fig: col3and17_dist}
@@
         \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and18.png}
+        \caption{Input data: data from Fig.~\ref{fig: col3and17_dist} and SPIRE~500~$\mu$m emission }
         \label{fig: col3and18_dist}
@@
         \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and19.png}
+         \caption{Input data: data from Fig.~\ref{fig: col3and18_dist} and L$_{{\mathrm Dust}}$}
         \label{fig: col3and19_dist}
@@
         \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and20.png}
+          \caption{Input data: data from Fig.~\ref{fig: col3and19_dist} and M$_{{\mathrm Dust}}$}
         \label{fig: col3and20_dist}
@@
         \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and21.png}
+        \caption{Input data: data from Fig.~\ref{fig: col3and20_dist} and SFR}
         \label{fig: col3and21_dist}
@@
         \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and22.png}
+        \caption{Input data: data from Fig.~\ref{fig: col3and21_dist} and M$_{{\mathrm Stars}}$}
         \label{fig: col3and22_dist}
@@
         \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and23.png}
+        \caption{Input data: data from Fig.~\ref{fig: col3and22_dist} and L$_{{\mathrm TIR}}$}
         \label{fig: col3and23_dist}
@@
         \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and24.png}
+        \caption{Input data: data from Fig.~\ref{fig: col3and23_dist} and M$_{{\mathrm Total gas}}$}
         \label{fig: col3and24_dist}
@@
         \centering
-        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and25.png}
+        \includegraphics[width=\textwidth ]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and25.png}
+        \caption{Input data: data from Fig.~\ref{fig: col3and19_dist} and M$_{{\mathrm RHI}}$}
         \label{fig: col3and25_dist}

### 2016-07-26 main text/draft.tex
After thesis

@@
 \usepackage{slantsc}
-\usepackage[latin1]{inputenc}   
 \usepackage[T1]{fontenc}
-\usepackage[finnish]{babel}
 
@@
 %----------------------------------------------------------------------------------------
-\import{../sections/}{intro0.01.tex}
+\import{../sections/}{intro0.02.tex}
 
@@
 
-\import{../sections/}{method0.01.tex}
+\import{../sections/}{method0.02.tex}
 
@@
 
-\import{../sections/}{data0.01.tex}
+\import{../sections/}{data0.02.tex}
 
@@
 %----------------------------------------------------------------------------------------
-%\import{../sections/}{results0.01.tex}
-\import{../sections/}{R10.01.tex}
-\import{../sections/}{R20.01.tex}
+%\import{../sections/}{results0.02.tex}
+\import{../sections/}{R10.02.tex}
+\import{../sections/}{R20.02.tex}
 
@@
 %----------------------------------------------------------------------------------------
-\section{SUMMARY}
+\section{Summary}
 \label{sec: summary}
 
-We present results of studying spatially resolved regions in nearby galaxies using Kohonen self-organizing maps.
+We present the results of studying spatially resolved regions in nearby galaxies using Kohonen self-organizing maps.
 Self-organizing maps both cluster data and show relative distance between the clusters. 
-We utilized the method to find hidden subgroups in the data as well as finding relations between those groups.
+We utilized the method to find hidden subgroups in the data as well as to find relations between those groups.
 
-Using smaller-sized self-organizing maps, we found that the M31 data are clustered into two major groups, which led us to correlations that could not have otherwise been seen without clustering.
+Using smaller-sized self-organizing maps, we clustered M31 data into two major groups, which led us to correlations that could not have otherwise been seen without clustering.
 Six of the regions in M31 create a subgroup with relatively lower mid- and far-infrared emission.
@@
 These anti-correlations are insignificant when the full dataset is considered.
-The most probable reason for PAHs to anti-correlate with optical emission line and RHI is a harder radiation field.
-This makes the size of H {\sc II} regions bigger and the size of photo-dissociation regions smaller, causing more \halpha~emission and less PAH emission, respectively.
+The most probable reason for PAHs to anti-correlate with optical emission lines and RHI is a harder radiation field.
+This makes the size of \hii~regions bigger and the size of photo-dissociation regions smaller, causing more \halpha~emission and less PAH emission, respectively.
 
@@
 This result shows that PAHs in the clustered regions in M31 are not heated by the old stellar populations.
+The reason behind the observed anti-correlation between PAH features and stellar mass needs further investigation, which requires mid-infrared PAH observations for more regions in M31.
 
@@
 We created various subsets of the input data and generated different networks which helped to show relations between regions in M31 more clearly.
-Region 10 always becomes isolated in the networks, except when we  used only PAH data to create a network. %PB: remind the reader where regions 8 and 10 are
-In that network region 10 blends more with other regions and only shows differences with the data from region 8.
+Region 10, which is located in the bulge of M31, always becomes isolated in the networks, except when we  used only PAH data to create a network.
+In that network region 10 blends more with the other regions and is only differentiated from region 8, which is located inside the inner ring of M31.
 These results suggest that the PAHs in all 10 regions have almost the same properties.
 
-% We introduced self-organizing maps as a method that can be used to predict the amount of various quantities based on the relative positions of the regions in the networks.
-% By converting the relative distance between regions to the probability distribution function, we could predict unobserved/unmeasured properties of the galaxies with 10 per cent uncertainty.
+We introduced self-organizing maps as a method that can be used to predict various quantities based on the relative positions of the regions in the networks.
+For regions that lack the observational data for some quantities (e.g. PAH emission), SOMs can be used to extrapolate the unobserved quantities.
 Applying the SOMs from M31 to observations of M101, we found regions with similar properties in both galaxies placed in close regions in the SOMs.
 Using this ability of the SOM, we can predict properties of regions in other nearby galaxies very quickly.
+
 The networks we created used values for 26 quantities from 10 regions in M31, which is not a large sample.
 Increasing the dimension of the data and the number of regions would yield more reliable networks.
-In future we can apply these networks on data from other nearby galaxies (e.g. M33 and M83) and learn about the properties of regions in those galaxies.
+Since there is very little spatially-resolved PAH spectroscopy for other galaxies from the \Spitzer Space Telescope, increasing the size of samples will require data from the James Webb Space Telescope.
+The method described in this work can be used to select target regions for PAH observations with that facility.
 
 \section*{ACKNOWLEDGMENTS}
-The authors thank Dr A.\ Tammour for useful comments. 
+The authors thank Dr.s D.\ Stock and A.\ Tammour for useful comments. 
 S.R., P.B., and E.P.

### 2016-07-26 sections/V0.01/R10.01.tex
After thesis

--- 2016-07-26 sections/R10.01.tex
@@
     The purpose of  exploring the M31 data with 1D maps is to monitor the general behaviour of the data. 
-    One-dimensional SOMs can have the minimum number of clusters, $1\times2$, up to the highest number of clusters possible.
+    One-dimensional SOMs can have the minimum number of clusters, $1\times2$, up to the highest number of clusters possible (infinity).
     In a small sample like ours, smaller grid SOMs are very useful to find correlations that cannot be found without  clustering the data.
@@
 
-      Fig.~\ref{fig: M31_net_1by2} shows that by forcing the regions in the M31 to be divided into two groups, regions 1, 2, 9 and 10 occupy one neuron and the other regions occupy the other one.
+        Fig.~\ref{fig: M31_net_1by2} shows that by forcing the regions in the M31 to be divided into two groups, regions 1, 2, 9 and 10 (shown in Fig.~\ref{fig: regions in m31}) occupy one neuron and the other regions occupy the other one.
         The medium grey colour between two neurons indicates that there are some similarities between two groups, but they are not very similar. 
@@
         %%%Talking about four right regions
-        \cite{Dim15} showed that regions 1, 2, 9, and 10 have higher PAH line fluxes compared to other regions (Fig. 5 in \citealt{Dim15}). 
+        \cite{Dim15} showed that regions 1, 2, 9, and 10 have higher PAH fluxes compared to other regions (Fig. 5 in \citealt{Dim15}). 
         %Regions 1, 2, and 9 are in the 10~Kpc ring and region 10 is located in the bulge of M31; however, regions 3 to 8 are located slightly out of the inner ring or the 10~kpc one.
@@
         The differences in their positions might be the reason for regions 1, 2, 9 and 10 having higher values in some quantities than the others. 
-        Similarities with the other regions in the other input values causes regions 1, 2, and 9 to gradually move towards other regions and away from region 10 in the higher grid SOMs.
+        Similarities with regions 3 to 8 in the other input values (e.g. SFR) causes regions 1, 2, and 9 to gradually move towards other regions and away from region 10 in the higher grid SOMs.
        % Therefore, in 1D networks with 14 neurons or higher, regions 1, 2, and 9 completely are separated from region 10, and show more similarity to other regions than to the region 10.
@@
         Therefore, since at least 14 neurons are needed to separate all 10 regions in M31, we can conclude that some of the regions have very small differences.
-        Regions that are located in similar areas in M31, like region 7 and 4 (see Fig.~\ref{fig: regions in m31}), are most likely to show more similarities to each other.
+        Regions that are located in similar areas in M31, like region 7 and 4 (see Fig.~\ref{fig: regions in m31}), are most likely to have more similarities to each other.
+%%present?
+show?
+represent?
+have?
         In Fig.~\ref{fig: M31_net_1by14}, the right-most neuron is occupied by region 10.
@@
         In Fig.~\ref{fig: cor_all}, which shows the Pearson correlation coefficients from data in all 10 regions, all the PAH features are highly correlated with each other. 
-        Also, there are very strong correlations between all the PAH features and PACS~100~$\mu$m~, SPIRE 250 to 500~$\mu$m~emission, L$_{\rm dust}$, L$_{\rm TIR}$, SFR, and metallicity.
-        However, in Fig.~\ref{fig: cor_cluster1}, the 12.0 and 12.7~$\mu$m~PAH fluxes do not show any significant or strong correlation with PAH fluxes in other wavelengths, or with most of the other quantities.
-        The only exceptions are the strong correlations between PAH flux at 12~$\mu$m and L$_{\rm dust}$, and between the 12 and 12.7~$\mu$m PAH fluxes.
+        Also, there are very strong correlations between all the PAH features and PACS~100~$\mu$m, SPIRE 250 to 500~$\mu$m~emission, L$_{\mathrm dust}$, L$_{\mathrm TIR}$, SFR, and metallicity.
+        However, in Fig.~\ref{fig: cor_cluster1}, the 12.0 and 12.7~$\mu$m~PAH fluxes do not show any significant or strong correlation with PAH fluxes at other wavelengths, or with most of the other quantities.
+        The only exceptions are the strong correlations between PAH flux at 12~$\mu$m and L$_{\mathrm dust}$, and between the 12 and 12.7~$\mu$m PAH fluxes.
         Since there are only 6 regions in this cluster, even one outlier in the data may cause the correlation coefficient to become insignificant.
-        If we ignore the outlier values, the correlations between 12.0 and 12.7~$\mu$m~PAH fluxes and the other quantities show themselves. 
+        If we ignore the outlier values, the correlations between 12.0 and 12.7~$\mu$m~PAH fluxes and the other quantities reappear. 
         For example region 8 breaks correlations between 12.0~$\mu$m and 6.2, 7.7, and 8.3~$\mu$m.
@@
 
-        For the remaining PAH fluxes in Fig.~\ref{fig: cor_cluster1}, there are no significant correlations with PACS~100~$\mu$m, L$_{\rm dust}$, L$_{\rm TIR}$, SFR, or metallicity.
-        These fluxes correlate with SPIRE emission, but to a lesser extent than for data from all regions.
-        Correlations between PAH features and SFR, and L$_{\rm TIR}$ are well-studied~\citep[e.g.][]{Tielens08,Peeters04}. 
+        For the PAH fluxes except 12.0 and 12.7~$\mu$m in Fig.~\ref{fig: cor_cluster1}, there are no significant correlations with PACS~100~$\mu$m, L$_{\mathrm dust}$, L$_{\mathrm TIR}$, SFR, or metallicity.
+        These PAH fluxes correlate with the SPIRE emission, but to a lesser extent than for the data from all regions.
+        Correlations between PAH features and SFR, and L$_{\mathrm TIR}$ are well-studied~\citep[e.g.][]{Tielens08,Peeters04}. 
         Many groups have used PAH features as a tracer of SFR by finding correlations between 
@@
         Further analyses show that the absence of correlations between PAH fluxes and SFR, is because of one outlier: Region 6. 
-        When we disregard this region, high correlations between 6.2 to 11.3~$\mu$m~PAHs and SFR (and L$_{\rm TIR}$) reappear.
-        Strong anti-correlations between 6.2 to 11.3~$\mu$m~PAH features and RHI, stellar mass, \halpha, \sii, \oiii, and IRAC~5.6~$\mu$m~emission in Fig.~\ref{fig: cor_cluster1} were not seen in Fig.~\ref{fig: cor_all}.
+        When we disregard this region, high correlations between 6.2 to 11.3~$\mu$m~PAHs and SFR (and L$_{\mathrm TIR}$) reappear.
 
+        Strong anti-correlations between 6.2 to 11.3~$\mu$m~main PAH features and RHI, stellar mass, \halpha, \sii, \oiii, and IRAC~5.6~$\mu$m~emission in Fig.~\ref{fig: cor_cluster1} were not seen in Fig.~\ref{fig: cor_all}.
         Anti-correlations between PAH features and the \halpha, \sii, and \oiii~emission could be the result of one of the following. 
@@
         The PAH features correlate with the amount of dust while \halpha~emission anti-correlates with amount of dust due to extinction \citep{Calzetti94}.
-        Therefore, higher PAH fluxes imply higher dust abundance and less \halpha~emission, and the same for \sii~and \oiii~emission.
+        Therefore, higher PAH fluxes imply higher dust abundance and less \halpha~emission, and the same holds for \sii~and \oiii~emission.
         Second, is the possible effect of observing apertures.
-        If the observed regions are located near the edge of H {\sc II} regions we would expect to see more PAH and less \halpha~emission. %%% reference? PB: I will try to find one.
+        If the observed regions are located near the edge of \hii~regions we would expect to see more PAH and less \halpha~emission. %%% reference? PB: I will try to find one.
         The anti-correlations between 6.2 to 11.3~$\mu$m~PAH features and RHI have been seen in other studies, as well~\citep[e.g.][]{Dim15, Gordon08, Wu06}.
@@
         On the other hand, \cite{Gordon08} argued that the harder radiation could make the photodissociation regions (PDRs) smaller.
-        The PAH features are mostly coming from the PDRs that are surrounded by H {\sc II} regions, and the PAH features' underlying continuum emission is from the H {\sc II} regions.
+        The PAH features are mostly coming from the PDRs that are surrounded by \hii~regions, and the PAH features' underlying continuum emission is from the \hii~regions.
         Therefore, the lower flux of the PAH features could be the result of the smaller size of PDRs.
@@
 
-        The strong anti-correlation between PAHs and stellar mass suggests that, despite the general assumption that one of the main source of heating PAHs is stellar emission~\citep[e.g][]{Haas02,Bendo08,Calapa14, Lu14,Jones15}, a higher stellar mass decreases PAH emission.
+        The strong anti-correlation between PAHs and stellar mass suggests that, despite the general assumption that one of the main source of heating PAHs is stellar emission~\citep[e.g][]{Jones15,Lu14,Calapa14,Bendo08,Haas02}, a higher stellar mass decreases PAH emission.
         In observations of M33,~\cite{Calapa14} showed that the 8/250~$\mu$m luminosity ratio correlates with 3.6~$\mu$m emission, which translates to stellar mass, and conclude that the PAH emission traces the old stellar population.
@@
         Regions 5, 6, and 8 are located on the stellar disk of the galaxy and have relatively high stellar mass and low PAHs. 
-        According to~\cite{Dim15}, regions 5 and 8 are the only two regions in our sample that do not include an H {\sc II} region, which could be the reason of low PAHs for these regions.
+        According to~\cite{Dim15}, regions 5 and 8 are the only two regions in our sample that do not include an \hii~region, which could be the reason of low PAHs for these regions.
         Regions 4 and 7 have similar quantities for both stellar mass and PAHs and region 3 has high PAHs and low stellar mass.

### 2016-07-26 sections/V0.01/data0.01.tex
After thesis

--- 2016-07-26 sections/data0.01.tex
@@
 
-\section{Study sample}
+\section{Study sample} %%or sample study?!
 \label{Sec: data_SOMN}
@@
 These specific regions were chosen for the availability of \Spitzer/IRS 5 - 15$\mu$m  spectroscopy covering PAHs emission.
-Besides PAH bands strengths, for each galaxy, we use spectroscopic and photometric observations as well as their derived properties, such as SFR, stellar mass, dust luminosity (L$_{\rm dust}$) and mass, metallicity, and gas mass.
+Besides PAH bands strengths, for each galaxy, we use spectroscopic and photometric observations as well as their derived properties, such as SFR, stellar mass, dust luminosity (L$_{\rm dust}$), and mass, metallicity, and gas mass.
 Table~\ref{tab: data} shows the full list of data for both M31 and M101.
-Observed values were divided by the area of their region (in arcsec$^2$), to remove the distance factor from the data and compare values across galaxies.
+All data were divided by the area of their region (in arcsec$^2$), to remove the distance factor from the data and compare values across galaxies.
 Since the spatial resolution of the observations varies from $<1$\arcsec to 60\arcsec $\times$ 90 \arcsec, any attempt to match resolution would have caused a loss of information in some of the input quantities (e.g.
@@
         \includegraphics[width=0.97\textwidth]{../images0.01/M31/M31.png}
-        \caption{MIPS24 image of M31, with position of 10 regions that we studies.}
+        \caption{MIPS~24 image of M31, with position of 10 regions that we studies.}
         \label{fig: regions in m31}
@@
 
-     \cite{Dim15} used {\it Spitzer}/IRS observations to study PAHs in 10 regions chosen to span a range of mid-infrared flux ratios in M31. 
+     \cite{Dim15} used {\it Spitzer}/IRS observations to study PAHs in 10 regions chosen to span a range of mid-infrared flux ratios in M31 (Fig.~\ref{fig: regions in m31}). 
      Fluxes and equivalent widths of PAH and atomic line features were measured using the~\textsc{pahfit idl} tool~\citep{Smith07b}.
@@
 
-    For the photometry part of the sample, we used the \GALEX \citep{Martin05} far-ultraviolet and near-ultraviolet (FUV and NUV) channel images; \halpha, \sii~and \oiii narrow band images~\citep{Massey07}, IRAC 3.6, 4.5, 5.8 and 8.0$\mu$m images~\citep{Barmby06}; MIPS24 and 70~$\mu$m~images\citep{Gordon06}; and PACS 100 and 160~$\mu$m and SPIRE 250, 350, and 500~$\mu$m~\citep{Fritz12} images.
+    For the photometry part of the sample, we used the \GALEX \citep{Martin05} far-ultraviolet and near-ultraviolet (FUV and NUV) channel images; \halpha~(6574.7\AA), \sii~(6730.72\AA) and \oiii~(5024.9\AA) narrow band images~\citep{Massey07}, IRAC 3.6, 4.5, 5.8 and 8.0~$\mu$m images~\citep{Barmby06}; MIPS~24 and 70~$\mu$m~images~\citep{Gordon06}; and PACS 100 and 160~$\mu$m and SPIRE 250, 350, and 500~$\mu$m~\citep{Fritz12} images.
      The units of all fluxes were converted to W~m$^{-2}$ in order to be the same as the PAH fluxes.
      $^{12}$CO (J:$1\rightarrow0$) line emission images~\citep{Nieten06} and atomic gas (\hi) 21~cm emission images from~\cite{Chemin09} were added to the input data. 
-     For derived values, we utilized SFR(FUV + 24$\mu$m) measured using combination of FUV and 24$\mu$m emission, stellar mass, molecular gas mass, atomic gas mass, total gas mass, and total infrared (TIR) luminosity (L$_{\mathrm TIR}$) from \cite{Rahmani16}, and L$_{\mathrm dust}$ and mass from \cite{Draine14}.
+     For derived values, we utilized SFR(FUV + 24$\mu$m) measured using combination of FUV and 24$\mu$m emission, stellar mass, molecular gas mass, atomic gas mass, total gas mass, and total infrared (TIR) luminosity (L$_{\mathrm TIR}$) from~\cite{Rahmani16}, and L$_{\mathrm dust}$ and dust mass from~\cite{Draine14}.
 
@@
 
-     \cite{Gordon08} measured PAH fluxes and RHI for M101 in 8 star forming \hii~regions.
+     \cite{Gordon08} measured PAH fluxes and RHI for M101 in 8 star forming \hii~regions (Fig.~\ref{fig: regions in m101}).
      Metallicity of 6 out of 8 regions were measured by~\cite{Kennicutt03} and the other two by~\cite{Gordon08}.
      We used the NED~\footnote{The NASA/IPAC Extragalactic Database (NED) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.} website to gather imaging observations of M101, including
-      \GALEX FUV and NUV~\citep{depaz07}, IRAC $3.6-8.0\mu$m, MIPS~24 and 70~$\mu$m~\citep{Dale09}, and PACS~100 and 160~$\mu$m and SPIRE~250, 350, and 500~$\mu$m emission from~\cite{Kennicutt11}.
+      \GALEX FUV and NUV~\citep{depaz07}, IRAC 3.6 -- 8.0~$\mu$m, MIPS~24 and 70~$\mu$m~\citep{Dale09}, and PACS~100 and 160~$\mu$m and SPIRE~250, 350, and 500~$\mu$m emission from~\cite{Kennicutt11}.
      As with M31, we used $^{12}$CO (J:$1\rightarrow0$) line emission images~\citep{Helfer03} and atomic gas (\hi) 21~cm emission images from \cite{Walter08}.
-     SFR(FUV + 24$\mu$m), stellar and total gas mass maps were calculated using the same methods as for M31.
+     We calculated SFR(FUV + 24$\mu$m), stellar and total gas mass maps using the same methods as for M31.
 
@@
      Correlations between some of single-wavelength emission and galaxy properties are well-known.
-     Emission in the 3.6$\mu$m band traces the old stellar population very well~\citep[e.g]{Leitherer99,Smith07a} and it can be used to calculate the stellar mass~\citep{Eskew12}.
+     Emission in the 3.6$\mu$m band traces the old stellar population very well~\citep[e.g.][]{Smith07a,Leitherer99} and it can be used to calculate the stellar mass~\citep{Eskew12}.
      FUV, \halpha, and TIR emission are indicators of star forming regions.
-     In this project we used the SFR traced by the FUV emission, corrected for foreground stars using NUV emission and for dust extinction using 24$\mu$m emission.
-     Total infrared emission is calculated from a modified version of~\cite{Draine07} calibration using using 8, 24, 70, and 160 $\mu$m emission~\citep{Boquien10}.
+     In this project, we used the SFR traced by the FUV emission, corrected for foreground stars using NUV emission and for dust extinction using 24~$\mu$m emission.
+     Total infrared emission is calculated from a modified version of~\cite{Draine07} calibrations using using 8, 24, 70, and 160~$\mu$m emission~\citep{Boquien10}.
 
@@
    % We used this new sample of observational and derived data as the main input for creating SOMs.
-    To have a prior knowledge on the data set, %or to have an insight into the data set!
+    To have a prior knowledge on the M31 data set, %or to have an insight into the data set!
     we computed the Pearson correlation coefficients between input data.
@@
                 \includegraphics[width=\textwidth]{../images0.01/cor_plots/M31_all_derived_ones_core_plot_for_paper.pdf}
-            \caption{Pearson correlation coefficients with a confidence level of 95 per cent for all data in subset 0.
+            \caption{Pearson correlation coefficients with a confidence level of 95 per cent for all data from M31.
 The colours and circles' size show the Pearson correlation coefficients where large blue circles are 1 which means highly correlated and large red circles are$-1$ means highly anti-correlated quantities.

### 2016-07-26 sections/app_2d.tex
After thesis

--- 2016-06-29 sections/app_2d.tex
@@
 
-        We removed IRAC 5.7 $\mu$m; [\sii] continuum and [\oiii] continuum; PAH8.3 $\mu$m, PAH12.0 $\mu$m, PAH17.0 $\mu$m, [~\oiii] continuum, stellar mass and metallicity from subset 0, and generated subset samples 2 to 4, respectively (Tables~\ref{tab: subset2} to~\ref{tab: subset4}).
+        We removed IRAC 5.7 $\mu$m; \sii~continuum and \oiii~continuum; PAH8.3 $\mu$m, PAH12.0 $\mu$m, PAH17.0 $\mu$m, \oiii~continuum, stellar mass and metallicity from data from 10 regions in M31 that were described in Section~\ref{Sec: data_SOMN}, and generated subset samples 4 to 6, respectively (Tables~\ref{tab: subset2} to~\ref{tab: subset4}).
         In Fig.~\ref{fig: subset2}, which is the SOM results from data listed in Table~\ref{tab: subset2}, distance between positions of the region 7, and region 3 is much larger compare to the one in Fig.~\ref{fig: all_derived_ones}.
         IRAC 5.7~$\mu$m flux in the region 7 and the region 3 is similar to each other. 
-        Therefore, removing flux from IRAC 5.7 $\mu$m removed the one source of similarity in these two regions and they moved further from each other in the SOM.
-        For subset sample 7 (Table~\ref{tab: subset7}) we removed [\sii] flux, SPIRE 250 and 500~$\mu$m and TIR emission from subset 2 (~\ref{tab: subset5}).
+        Therefore, removing flux from IRAC 5.7~$\mu$m removed the one source of similarity in these two regions and they moved further from each other in the SOM.
+        For subset sample 7 (Table~\ref{tab: subset7}) we removed \sii~flux, SPIRE 250 and 500~$\mu$m and TIR emission from subset 4 (~\ref{tab: subset5}).
         The positions of the regions 2 and 9 are closer to each other, but the weight distance between them is much higher (the colours between them are became almost black). 
-        In general by removing IRAC 5.7 $\mu$m  flux data from the input data, the colours between regions become much more darker.
+        In general by removing IRAC 5.7~$\mu$m flux data from the input data, the colours between regions become much more darker.
+
+        In Fig.~\ref{fig: subset3}, the positions from the region 9 is much closer to the positions of the regions 4 and 7. 
+        Since region 4 and 5 have a similar \oiii~and \sii~continuum fluxes, by removing these two values from the input data distance between regions 4 and 5 became much smaller.
+        The positions of the regions 2 and 6 are closer together, but the colours between their neurons are darker.
+        The wining neurons for regions 1 and 9 are moved further from each other, but the colours between them are slightly lighter. 
+        moreover, similar to regions 4 and 5, \oiii~and \sii~continuum fluxes for regions 1 and 9, and regions 8 and 6 are similar to each other, and removing these two values from input data, reduces the similarity between these regions.
+Therefore, they moved further from each other.
          \import{../sections/tables/}{subset2.tex}
         \import{../sections/image_texts/}{subset2.tex}
-
-        In Fig.~\ref{fig: subset3}, the positions from the region 9 is much closer to the positions of the regions 4 and 7. 
-        Since region 4 and 5 have a similar [~\oiii] and [~\sii] continuum fluxes, by removing these two values from the input data distance between regions 4 and 5 became much smaller.
-        The positions of the regions 2 and 6 are closer together, but the colours between their neurons are darker.
-        The wining neurons for regions 1 and 9 are moved further from each other, but the colours between them are slightly lighter. 
-        moreover, similar to regions 4 and 5, [~\oiii] and [~\sii] continuum fluxes for regions 1 and 9, and regions 8 and 6 are similar to each other, and removing these two values from input data, reduces the similarity between these regions.
-Therefore, they moved further from each other.
         \import{../sections/tables/}{subset3.tex}
@@
 
-        In the results from the subset 4 in Fig.~\ref{fig: subset4}, regions 8 and 6 moved closer to each other. 
+        In the results from the subset 6 in Fig.~\ref{fig: subset4}, regions 8 and 6 moved closer to each other. 
         These two regions have distinct metallicity, removing metallicity from input data caused these two stay in a closer neurons. 
@@
         Therefore, both of them have similar values in most of the input parameters.
-        However, they have very different fluxes in IRAC 5.7 $\mu$m and [~\sii] continuum, which removing these two fluxes from the input data moved their position on the SOM closer.
-        TIR luminosity and IRAC 5.7 $\mu$m flux for regions 3 and 5 are different, and removing them from the input data caused the distance between their position decreases. 
+        However, they have very different fluxes in IRAC 5.7~$\mu$m and \sii~emission, which removing these two fluxes from the input data moved their position on the SOM closer.
+        TIR luminosity and IRAC 5.7~$\mu$m flux for regions 3 and 5 are different, and removing them from the input data caused the distance between their position decreases. 
         In Fig.~\ref{fig: subset7} the relations between all the other regions are mostly unchanged.

### 2016-07-26 sections/data0.02.tex
After thesis

--- 2016-07-26 sections/V0.01/data0.01.tex
@@
 %----------------------------------------------------------------------------------------
-
-\section{Study sample} %%or sample study?!
+\section{Study Sample}
 \label{Sec: data_SOMN}
@@
 Our study includes 10 regions in M31 (Fig.~\ref{fig: regions in m31}) and 8 regions in M101 (Fig.~\ref{fig: regions in m101}). 
-These specific regions were chosen for the availability of \Spitzer/IRS 5 - 15$\mu$m  spectroscopy covering PAHs emission.
-Besides PAH bands strengths, for each galaxy, we use spectroscopic and photometric observations as well as their derived properties, such as SFR, stellar mass, dust luminosity (L$_{\rm dust}$), and mass, metallicity, and gas mass.
+These specific regions were chosen for the availability of \Spitzer/IRS 5--15$\mu$m  spectroscopy covering the PAH emission bands.
+Besides PAH band strengths, for each galaxy, we use spectroscopic and photometric observations as well as their derived properties, such as SFR, stellar mass, dust luminosity (L$_{\rm dust}$), dust mass, metallicity, and gas mass.
 Table~\ref{tab: data} shows the full list of data for both M31 and M101.
 All data were divided by the area of their region (in arcsec$^2$), to remove the distance factor from the data and compare values across galaxies.
-Since the spatial resolution of the observations varies from $<1$\arcsec to 60\arcsec $\times$ 90 \arcsec, any attempt to match resolution would have caused a loss of information in some of the input quantities (e.g.
+Since the spatial resolution of the observations varies from as small as $<1$\arcsec to as high as 60\arcsec $\times$ 90 \arcsec, any attempt to match resolution would have caused a loss of information in some of the input quantities (e.g.
 the spectroscopic data).
 In this project we used flux per unit area, which the convolution methods conserve~\citep{Aniano12}, as the input data.
-Therefore, we did not perform any resolution matching and used data at their original resolution. %PB: Need to discuss these last few sentences; not sure I understand what you're saying.
+Therefore, we did not perform any resolution matching and used data at their original resolution.
 
@@
         \centering
-    %\centering
         \includegraphics[width=0.97\textwidth]{../images0.01/M31/M31.png}
-        \caption{MIPS~24 image of M31, with position of 10 regions that we studies.}
+        \caption{MIPS~24 $\mu$m image of M31, with positions of 10 regions studied.}
         \label{fig: regions in m31}
@@
         \includegraphics[width=\textwidth]{../images0.01/M101/M101.png}
-        \caption{IRAC1 image of M101, with position of our 8 regions that we studies.}
+        \caption{IRAC 3.6 $\mu$m image of M101, with positions of  8 regions studied.}
     \label{fig: regions in m101}
     \end{subfigure}
-    \caption{Position of the data in M31 (up) and M101 (down).}
+    \caption[Position of the data in M31 and M101]{Position of the data in M31 (a) and M101 (b).}
 \end{figure}
 
-%   \begin{figure}
-%     \subfloat[MIPS 24~$\mu$m image of M31~\citep{Gordon06}, with position of 10 regions from~\cite{Dim15} \label{fig: regions in m31}]{
-%       \includegraphics[width=0.5\textwidth]{../images0.01/M31/M31.png}
-%     }
-%     \hfill
-%     \subfloat[IRAC 3.6~$\mu$m image of M101~\citep{Dale09}, with position of 8 regions.\label{fig: regions in m101}]{
-%       \includegraphics[width=0.5\textwidth]{../images0.01/M101/M101.png}}
-%     \caption{Position of regions that the input data for SOM that obtained from there in M31 (up) and M101 (down).}
-%     \label{fig:dummy}
-%   \end{figure}
-
-    \subsection{M31 observations}
+    \subsection{M31 Observations}
      \label{Sec: data_M31_SOMN}
@@
      \cite{Dim15} also measured metallicity and radiation hardness index (RHI) for these 10 regions.
-     We used the measured PAH feature fluxes, metallicity and RHI of each region as an input for SOMs.
+     We used the measured PAH feature fluxes, metallicity and RHI of each region as the input for self-organizing maps.
 
@@
      $^{12}$CO (J:$1\rightarrow0$) line emission images~\citep{Nieten06} and atomic gas (\hi) 21~cm emission images from~\cite{Chemin09} were added to the input data. 
-     For derived values, we utilized SFR(FUV + 24$\mu$m) measured using combination of FUV and 24$\mu$m emission, stellar mass, molecular gas mass, atomic gas mass, total gas mass, and total infrared (TIR) luminosity (L$_{\mathrm TIR}$) from~\cite{Rahmani16}, and L$_{\mathrm dust}$ and dust mass from~\cite{Draine14}.
+     For derived values, we utilized SFR(FUV + 24$\mu$m) measured using combination of FUV and 24$\mu$m emission, stellar mass, molecular gas mass, atomic gas mass, total gas mass, and total infrared (TIR) luminosity (L$_\mathrm{TIR}$) from~\cite{Rahmani16}, and L$_\mathrm{dust}$ and dust mass from~\cite{Draine14}.
 
-    \subsection{M101 observations}
+    \subsection{M101 Observations}
     \label{Sec: data_M101_SOMN}
@@
      \cite{Gordon08} measured PAH fluxes and RHI for M101 in 8 star forming \hii~regions (Fig.~\ref{fig: regions in m101}).
-     Metallicity of 6 out of 8 regions were measured by~\cite{Kennicutt03} and the other two by~\cite{Gordon08}.
+     Metallicities of 6 of the 8 regions were measured by~\cite{Kennicutt03} and the other two by~\cite{Gordon08}.
      We used the NED~\footnote{The NASA/IPAC Extragalactic Database (NED) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.} website to gather imaging observations of M101, including
@@
 
-       \subsection{Preparing data for data mining}
+     \subsection{Preparing Data for Data Mining}
 
@@
 
-    %To guarantee that we do not use the observed data as an input for SOM in multiple forms, we removed all the observed data that were used to calculate galaxies properties from the input sample.
-    We removed all the observed data that were used to calculate galaxies properties from the input sample, to guarantee that they have not been used in multiple forms
-   % We used this new sample of observational and derived data as the main input for creating SOMs.
-    To have a prior knowledge on the M31 data set, %or to have an insight into the data set!
-    we computed the Pearson correlation coefficients between input data.
+    We removed all the observed data that were used to calculate galaxy properties from the input sample, to guarantee that they have not been used in multiple forms.
+    To have prior knowledge of the M31 data set, 
+    we computed the Pearson correlation coefficients between input measurements.
     Fig.~\ref{fig: cor_all} shows the Pearson correlation coefficients with a confidence level of 95 per cent. 
-    All the PAHs are correlate with one another very well.
-    They also highly correlate with SPIRE bands and PACS emission, L$_{\mathrm dust}$, L$_{\mathrm TIR}$, SFR and metallicity.
-    Fluxes from PAHs 7.7, 8.3, 12.7 and 17~$\mu$m show weak ant-correlation with RHI.
-    In general, PAHs in our data set highly correlate with most of the other quantities.
+    If the significant level of correlation becomes smaller than 0.05 (5 per cent), the correlation is marked as insignificant. 
+    All the PAHs correlate with one another very well.
+    They are also highly correlated with the SPIRE and PACS emission, L$_\mathrm{dust}$, L$_\mathrm{TIR}$, SFR and metallicity.
+    The fluxes from PAHs 7.7, 8.3, 12.7 and 17~$\mu$m show a weak anti-correlation with RHI.
+    In general, PAHs in our data set are highly correlated with most of the other quantities.
 
@@
         \includegraphics[width=\textwidth]{../images0.01/cor_plots/M31_all_derived_ones_core_plot_for_paper.pdf}
-            \caption{Pearson correlation coefficients with a confidence level of 95 per cent for all data from M31.
-The colours and circles' size show the Pearson correlation coefficients where large blue circles are 1 which means highly correlated and large red circles are$-1$ means highly anti-correlated quantities.
-The non-significant correlations were left empty.}
+        \caption[Pearson correlation coefficients for data from 10 regions in M31]{Pearson correlation coefficients with a confidence level of 95 per cent for all data from M31.
+The colours and circle sizes show the Pearson correlation coefficients where large blue circles are 1, which means highly correlated, and large red circles are $-1$, which means highly anti-correlated quantities.
+The boxes with non-significant correlations were left empty.}
         \label{fig: cor_all}

### 2016-07-26 sections/image_texts/subset9.tex
After thesis

@@
     \end{subfigure}
-    \caption{Similar to Fig.~\ref{fig: all_derived_ones}, here we show up: the result from subset of data in M31 which is similar to data in M101; Down: the same network of up, but the input data are from M101.}
+    \caption{Similar to Fig.~\ref{fig: all_derived_ones}, here we show a) the result from subset of data in M31 which is similar to data in M101; b) the same network as (a), but the input data of M101.}
     \label{fig: subset9}

### 2016-07-26 sections/R10.02.tex

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Result Part 1: 1D SOMs
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{One-Dimensional Self-Organizing Maps}
    \label{Sec: 1d_cluster}
%Why 1D maps are useful
    The purpose of  exploring the M31 data with 1D maps is to monitor the general behaviour of the data. 
    One-dimensional SOMs can have the minimum number of clusters, $1\times2$, up to the highest number of clusters possible (infinity). %Els asked what is maximum possible #
    In a small sample like ours, smaller grid SOMs are very useful to find correlations that cannot be found without  clustering the data.
    On the other hand, larger grid 1D SOMs are a helpful tool to get quick insight into the data.

    \subsection{Clustering M31 Data}

        In order to monitor how the data behave, we created SOMs with two to fourteen neurons (Fig.~\ref{fig: M31_nets_1d}).
        The $1\times2$ network (Fig.~\ref{fig: M31_net_1by2}) shows how the M31 data can be divided into two broad categories.
        The $1\times14$ network (Fig.~\ref{fig: M31_net_1by14}) is the first network in which all the regions in M31 are completely separated.
        In the higher network sizes, regions have more space to be separated based on their differences. In going from the $1\times2$ to the $1\times14$ network the distance between M31 regions increases, until they are completely separated.

        Fig.~\ref{fig: M31_net_1by2} shows that by forcing the regions in the M31 to be divided into two groups, regions 1, 2, 9 and 10 (shown in Fig.~\ref{fig: regions in m31}) occupy one neuron and the other regions occupy the other one.
        The medium grey colour between two neurons indicates that there are some similarities between two groups, but they are not very similar. 
        By increasing the size of the neurons to three, in Fig.~\ref{fig: M31_net_1by3}, we can see that region 2 separates itself from the other regions and occupies the middle neuron.
        The white colour between the two left neurons suggests that the regions which occupy these neurons are very similar to each other, while the black colour between the two right neurons indicates otherwise.

        %%%Talking about four right regions
        \cite{Dim15} showed that regions 1, 2, 9, and 10 have higher PAH fluxes compared to the other regions (fig.~5 in \citealt{Dim15}). 
        These regions also have relatively high intensities in all the mid-infrared and far-infrared bands and have high dust luminosity and dust mass.
        The higher values for these quantities could be the reason that these four regions become separated from the others in the $1\times2$ network.
        Regions 1 and 9 are in the 10~kpc ring, region 2 is slightly out of the 10~kpc ring and region 10 is in the bulge of M31; however, regions 3 to 8 are located out of the inner ring or the 10~kpc ring (Fig.~\ref{fig: regions in m31}).   
        The differences in their positions account for their difference in input parameters.
        Since region 10 is located in the bulge of M31 and has high surface brightness for most of the input values, regions 1, 2, and 9 to gradually move towards other regions and away from region 10 in the higher grid SOMs.

    \begin{figure}
    \begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../images0.01/M31/1D/combine_1D_1by2_all.png}
        \caption{$1\times2$~network}
    \label{fig: M31_net_1by2}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.5\textwidth}
        \includegraphics[width=\textwidth]{../images0.01/M31/1D/combine_1D_1by3_all.png}
         \caption{$1\times3$~network}
        \label{fig: M31_net_1by3}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.5\textwidth}
        \includegraphics[width=\textwidth]{../images0.01/M31/1D/combine_1D_1by14_all.png}
        \caption{$1\times14$~network}
        \label{fig: M31_net_1by14}
    \end{subfigure}
   \caption[One-dimensional self-organizing map of M31 data]{SOM of the M31 data from $1\times2$, $1\times3$~and $1\times14$~grids. The axes show the position of the neurons. The purple hexagonal shapes represent the neurons. The grey scale colours show the differences between weight of the neurons, with white as the minimum difference and black as the maximum. The numbers in the plot show the M31 regions located in each neuron.}
   \label{fig: M31_nets_1d}
    \end{figure}

        %%Network 1by14
        The network with 14 neurons, in Fig.~\ref{fig: M31_net_1by14}, is the first network that has no neuron occupied by more than one M31 region.
        In a larger-grid SOM, the network pays more attention to smaller details and differences in the input data.
        Therefore, since at least 14 neurons are needed to separate all 10 regions in M31, we can conclude that some of the regions have very small differences.
        Regions that are located in similar areas (e.g. spiral arms, bulge, and 10 kpc ring) in M31, like regions 7 and 4 (see Fig.~\ref{fig: regions in m31}), are most likely to have more similarities with each other.
        In Fig.~\ref{fig: M31_net_1by14}, the right-most neuron is occupied by region 10.
        Two black colours between this region and the others indicate the large differences between this neuron and the other ones.
        Region 10 is located in the bulge of M31, and is physically separated from the other regions, which are mostly located around the inner or outer rings.
        The SOM shows that this region has completely different input values from the others: most of the values for region 10 are much higher than for the other regions, which is the main reason for its isolation.
        Region 8 occupies the right-most neuron in this network, suggesting that this region has the most differences from region 10.

    \subsection{Inside the Two Neuron Network}
        \label{sec: inside_the_2_neurons}
        Using self-organizing maps, we can identify hidden subgroups in our samples. 
        Each of these subgroups separates for a reason.
        This reason can vary from having higher values in some specific properties, as discussed in Section~\ref{Sec: 1d_cluster}, to some unknown correlations between data that cannot be seen in other groups or in the galaxy as a whole.
        To investigate the latter, we show in Fig.~\ref{fig: cor_cluster1} the Pearson correlation coefficients for the inputs from regions 3 to 8, which were clustered together in the $1\times2$ and $1\times3$ networks (see Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}).

        \begin{figure*}
        \includegraphics[width=\textwidth]{../images0.01/cor_plots/M31_derived_3_to_8_core_plot_for_paper.pdf}
        \caption[Pearson correlation coefficients for data from the clustered regions in M31]{Same as Fig.~\ref{fig: cor_all}, but here we used data from regions grouped in the left sides of Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}. }
          \label{fig: cor_cluster1}
        \end{figure*}

        Comparing the correlation coefficient plots for all 10 regions in M31 (Fig.~\ref{fig: cor_all}) and for the clustered data (Fig.~\ref{fig: cor_cluster1}) shows the differences between all 10 regions and clustered data and why regions 3 to 8 become separated from the other regions.
        The main features that differentiate these two plots are the anti-correlations between PAH features and RHI, stellar mass, \halpha, \sii, \oiii, and IRAC~5.8~$\mu$m~emission.
        Additionally, for the PAH fluxes in Fig.~\ref{fig: cor_cluster1}, there are no significant correlations with PACS~100~$\mu$m, L$_\mathrm{dust}$, L$_\mathrm{TIR}$, SFR, or metallicity.
        The PAH fluxes correlate with the SPIRE emission, but to a lesser extent than for the data from all regions.

        \cite{Calzetti10} mentioned that with increasing RHI in regions, metallicity and PAH equivalent widths decrease. 
        \cite{Dim15} investigated the correlation between PAHs features and both metallicity and RHI using the equivalent width of the 8~$\mu$m (combination of 7.7, 8.3, and 8.6~$\mu$m components) and the 7.7 and 11.2~$\mu$m features.
        They did not see any relations between PAHs and metallicity or RHI for 10 regions in M31.
        In Fig.~\ref{fig: cor_all}, we show that all the PAH fluxes correlate with metallicity, and PAH fluxes in the 7.7, 8.3 and 17.0~$\mu$m bands weakly anti-correlate with RHI.
        However, in Fig.~\ref{fig: cor_cluster1}, there is no correlation between the PAH fluxes and metallicity, but all of them strongly anti-correlate with RHI.
        \cite{Dim15} argued that the absence of (anti)-correlation between the PAH features and metallicity and RHI was related to a lack of data in low-metallicity regions.
        Although data from more regions would improve the results, our analysis shows that clustering data would show the missing (anti)-correlations.
        For example, for both clusters in Fig.~\ref{fig: M31_net_1by2},
        we can see anti-correlations between PAHs and RHI, but each of them has a different slope which removes the anti-correlation over all 10 regions.

        Correlations between PAH features and SFR, and L$_\mathrm{TIR}$ are well-studied~\citep[e.g.][]{Peeters04,Tielens08}. 
        Many groups have used PAH features as a tracer of SFR by finding correlations between 
        PAH emission and SFR derived from extinction-corrected \halpha~\citep[e.g.][]{Calzetti07,Khramtsova13,Shipley16}.
        These correlations are seen in Fig.~\ref{fig: cor_all}, when we considered the data from all regions, but not in Fig.~\ref{fig: cor_cluster1} when considering the clustered data.
        Note that, since there are only 6 regions in the clustered data, even one outlier in the data may cause the correlation coefficient to become insignificant.
        Further analyses show that the absence of correlations between PAH fluxes and SFR is because of one outlier: region 6. Region 6 is located in a FUV-bright region, which breaks the correlations. 
        When we disregard this region, high correlations between 6.2 to 17.0~$\mu$m~PAHs and SFR (and L$_\mathrm{TIR}$) reappear.

        Strong anti-correlations between 6.2 to 17.0~$\mu$m~main PAH features and RHI, stellar mass, \halpha, \sii, \oiii, and IRAC~5.6~$\mu$m~emission in Fig.~\ref{fig: cor_cluster1} were not seen in Fig.~\ref{fig: cor_all} (even if we ignore the outlier values).
        Anti-correlations between PAH features and the \halpha, \sii, and \oiii~emission could be the result of one of the following. 
        First, the optical data are not corrected for dust extinction.
        The PAH features correlate with the amount of dust while \halpha~emission anti-correlates with the amount of dust due to extinction as suggested by \cite{Calzetti94}.
        Therefore, higher PAH fluxes imply higher dust abundance and less \halpha~emission, and the same holds for \sii~and \oiii~emission.
        Second is the possible effect of the structure of the observed regions.
        If the observed regions are located near the edge of \hii~regions we would expect to see more PAH and less \halpha~emission. 
        The anti-correlations between 6.2 to 17.0~$\mu$m~PAH features and RHI have been seen in other studies, as well~\citep[e.g.][]{Wu06, Gordon08,Calzetti10,Dim15}. 
        \cite{Wu06} suggested these anti-correlations could be the result of PAH destruction due to a high amount of harder radiation (thus higher RHI).
        On the other hand,~\cite{Gordon08} argued that the harder radiation could make the photodissociation regions (PDRs) smaller.
        The PAH features are mostly coming from the PDRs that are surrounded by \hii~regions, and the PAH features' underlying continuum emission is from the \hii~regions.
        Therefore, the lower flux of the PAH features could be the result of the smaller size of PDRs.%Els: If you have an harder radiation field, you destroy your smaller PAHs. Hence, simply a harder RHI does not argue for a smaller PDRs being more plausible. 
        The latter reason, which could also describe the anti-correlation between PAH features and \halpha~emission, seems to be the more probable one.

        The strong anti-correlation between PAHs and stellar mass suggests that, a higher stellar mass decreases PAH emission. 
        In observations of M33,~\cite{Calapa14} showed that the 8/250~$\mu$m luminosity ratio correlates with 3.6~$\mu$m emission, which translates to stellar mass, %Els: I'm unfamiliar with the details of this translation. But if you look at individual HII regions or starforming complexes, I would think that the 3.6um flux is not dominated by the stellar light as the stars are too hot to have a large fraction of emission at these wavelengths?
        and conclude that the PAH emission traces the old stellar population.
        In Fig.~\ref{fig: cor_cluster1}, we see a weak anti-correlation between SPIRE 250~$\mu$m emission and the stellar mass.
        We see no correlation between 8/250~$\mu$m luminosity and stellar mass, either in the clustered data or in all 10 regions.

        To test that whether the anti-correlation between stellar mass and PAH emission is the result of the destruction of PAHs in high stellar mass regions, or that high stellar mass obscures PAH emission, we compared PAH abundance with stellar mass for the clustered regions.
        The ratio of 8/24~$\mu$m emission, which can be considered as a proxy for PAH abundances~\citep[e.g.][]{Sandstrom10,Khramtsova13}, does not anti-correlate with stellar mass for either the clustered data or all 10 regions.
        Therefore, we conclude that in our sample, stellar mass does not cause the destruction of PAHs.

        The anti-correlation between stellar mass and PAHs could be result of the position of the regions within M31.
        Regions 5, 6, and 8 are located in the stellar disk of the galaxy and have relatively high stellar mass and faint PAH emission. 
        According to~\cite{Dim15}, regions 5 and 8 are the only two regions in thesample that do not include an \hii~region, which could be the reason for the faint PAH emission for these regions.
        Regions 4 and 7 have similar quantities for both stellar mass and PAHs and region 3 has high PAHs and low stellar mass.
        Without data from more regions in M31, we cannot confidently say that higher stellar mass decreases PAH fluxes.

       Regardless of the fact that some of the (anti)-correlations in Fig.~\ref{fig: cor_cluster1} might have physical meaning, we have to mention that we only used 6 regions to calculate these correlation coefficients.
       The number of data points is not high enough to yield a strong conclusion about PAH properties in M31.
       However, we can conclude that since the correlation coefficients derived from the clustered data (Fig.~\ref{fig: cor_cluster1}) differ from the correlation coefficients derived from the data from all 10 regions (Fig.~\ref{fig: cor_all}), the SOM separated a hidden cluster of the data which has different properties.

### 2016-07-26 sections/R20.02.tex

--- 2016-07-26 sections/R20.01.tex
@@
 %----------------------------------------------------------------------------------------
- \section{Two dimensional self-organizing maps}
+\section{Two-Dimensional Self-Organizing Maps}
  \label{sec: 2d_cluster}
     Although 1D networks are helpful to give a general idea about the data, neurons in 1D maps have a maximum of two neighbours, which can limit the usefulness of the results.
-    In 2D networks, each neuron has two to six neighbours, which allows them to to capture a complete picture of the complicated relations in the input data.
+    In 2D networks, each neuron has two to six neighbours, which allows them to capture a complete picture of the complicated relations in the input data.
     Accordingly, we created $10\times10$ 2D networks to study the data in detail.
-    As mentioned in previous sections, the size of SOMs are arbitrary and must be decided by users based on their goals for use of the SOM.
+    As mentioned in previous sections, the sizes of SOMs are arbitrary and must be decided by users based on their goals for use of the SOM.
 
@@
     In Fig.~\ref{fig: regions in m31} it is clear that this region in M31 is physically closer to regions 4 and 7 than to any other region, but it is on the outer side of the star forming ring.
-    Regions 5 and 6 are in the second neighbourhood on the SOM, with a medium gray colour between them.
+    Regions 5 and 6 are in the second neighbourhood (there are two neurons between them) of the SOM, with a medium gray colour between them.
     These two regions are physically located around the inner ring of the galaxy.
@@
 
-    Regions 1 and 9 are close to each other, and in the same side of the star forming ring. 
-    However, region 1 is in an area of the galaxy with less diffuse \halpha~emission than region 9, which might be the reason for their distances in SOM.
-    Region 2 is more distant from other regions in the galaxy and placed in the star forming ring.
+    Regions 1 and 9 are close to each other and in the same side of the star forming ring. 
+    However, region 1 is in an area of the galaxy with less diffuse \halpha~emission than region 9, which might be the reason for their distances in the SOM.
+    Region 2 is more distant from other regions in the galaxy and located in the star forming ring.
     However, similar to regions 1 and 4, region 2 is located in an area of the galaxy with less diffuse \halpha~emission.
@@
     \label{sec: subsets}
-            For analysing subsets, we creating SOMs by using only PAH data, as well as using all data except the PAHs (Fig.~\ref{fig: PAHS_or_not_PAHs}).
+
+            For analysing subsets, we create SOMs by using only PAH data, as well as using all data except the PAHs (Fig.~\ref{fig: PAHS_or_not_PAHs}).
              \import{../sections/image_texts/}{PAHS_or_not_PAHs.tex}
@@
 
-            We increased the dimension of input data in Fig.~\ref{fig: only_pahs} (PAH only data) gradually, by adding other quantities to the input data. 
+            We increased the dimension of input data in Fig.~\ref{fig: only_pahs} (PAH-only data) gradually, by adding other quantities to the input data. 
             The order in which data were added is the same as the order in Fig.~\ref{fig: cor_all}, i.e.
-the SOM in Fig~\ref{fig: col3and11_dist} was created from PAH and H$\alpha$ emission as input data, the SOM in Fig~\ref{fig: col3and12_dist} created from PAHs, H$\alpha$ emission and \sii~ continuum, and so on.
+the SOM in Fig~\ref{fig: col3and11_dist} was created from PAH and \halpha\ emission as input data, the SOM in Fig~\ref{fig: col3and12_dist} created from PAHs, \halpha~emission and \sii~ continuum, and so on.
             \import{../sections/image_texts/}{col3byall.tex}
 
-            The SOM algorithm assigns a random weight to each network that causes the overall position of regions in networks (even with the same input data) to change in each run of the algorithm.
+            At the beginning of each run, the SOM algorithm assigns a random weight to neurons that causes the overall position of regions in networks (even with the same input data) changes in each run of the algorithm.
             However, the position of each region relative to other regions changes dramatically only when the new sets of input data are given to the algorithm (assuming all the initial values for the run are unchanged).
-            In all SOMs in Fig~\ref{fig: inc_D_col3s}, region 10 is located in the corner of the SOMs, but in  Figs~\ref{fig: col3and11_dist},~\ref{fig: col3and14_dist},~\ref{fig: col3and17_dist},~\ref{fig: col3and21_dist}, and ~\ref{fig: col3and22_dist}, it is placed in the left side of the SOMs and in the others it is in the right side of the networks.
+            In all SOMs in Fig.~\ref{fig: inc_D_col3s}, region 10 is located in the corner of the SOMs, but in  Figs.~\ref{fig: col3and11_dist},~\ref{fig: col3and14_dist},~\ref{fig: col3and17_dist},~\ref{fig: col3and21_dist}, and ~\ref{fig: col3and22_dist}, it is placed in the left side of the SOMs and in the others it is in the right side of the networks.
             In our discussion on differences between networks, we do not address the changes in the network due to initialization of the SOM algorithm and only consider the effect of changing the input data.
 
-            Comparing Figs.~\ref{fig: col3and11_dist} to ~\ref{fig: col3and25_dist} shows that adding \halpha~emission data to PAH features causes regions 9 and 10 become isolated. 
+            Comparing Figs.~\ref{fig: col3and11_dist} to~\ref{fig: col3and25_dist} shows that adding \halpha~emission data to PAH features causes regions 9 and 10 become isolated. 
             Increasing the dimension of the input data makes region 10 more isolated.
@@
             Adding SPIRE 350, 500~$\mu$m emission and L$_{\rm dust}$ does not have any obvious effect on the networks.
-            Stellar mass, total gas mass, dust mass and RHI data alternate the distances between neurons effectively, but it seems that adding SFR, L$_{\rm TIR}$ and metallicity data revoke those changes.
+            Stellar mass, total gas mass, dust mass and RHI data alternate the distances between neurons effectively, but it seems that adding SFR, L$_{\rm TIR}$ and metallicity data revokes those changes.
 
-            We generated other subsets of the data based on the results in Figs~\ref{fig: inc_D_col3s} to further study the effects of the input data on SOMs.
-            Subset 1, listed in Tab.~\ref{tab: subset1}, includes all the input data except stellar mass.
-            Tab.~\ref{tab: subset5} lists data used in subset 2, which includes all data except that the PAH fluxes are combined into a total PAH flux. 
-            For subset 3 ( in Tab.~\ref{tab: subset6}), SPIRE 250 and 500~$\mu$m were removed from subset 2.
+            We generated other subsets of the data based on the results in Fig~\ref{fig: inc_D_col3s} to further study the effects of the input data on SOMs.
+            Subset 1, listed in Table~\ref{tab: subset1}, includes all the input data except stellar mass.
+            Table~\ref{tab: subset5} lists data used in subset 2, which includes all data except that the PAH fluxes are combined into a total PAH flux. 
+            For subset 3 (in Table~\ref{tab: subset6}), SPIRE 250 and 500~$\mu$m were removed from subset 2.
             Figs.~\ref{fig: subset1} --~\ref{fig: subset6} show SOMs created by data from subsets 1 to 3, respectively.
-            The remaining subsets are discussed in Appendix.~\ref{sec: app_2d_soms_SOMN}.
+            The remaining subsets are discussed in Appendix~\ref{sec: app_2d_soms_SOMN}.
 
-            The results from Table~\ref{tab: subset1} are shown in Fig.~\ref{fig: subset1}. 
+            The results from Table~\ref{tab: subset1} are used to create the network in Fig.~\ref{fig: subset1}. 
             In this SOM, compared with the SOM from all the data in Fig.~\ref{fig: all_derived_ones}, regions 1 and 9 are closer to region 10. 
             Regions 1 and 9 are the ones with lowest stellar mass values, and region 10 has the highest stellar mass value among those 10 regions. 
-            Since the differences in the amount of stellar mass was one of the most distinct differences between these three regions, removing stellar mass from input data reduced the distance between these regions.
-            Regions 5, 6 and 8 have the same relative distance from each other as in Fig.~\ref{fig: all_derived_ones}, but they all are closer to the position of region 10.
-            Distance between regions 2 and 3 is reduced but in the meantime the colour between them became darker.
+            Since the difference in the amount of stellar mass was one of the most distinct differences between these three regions, removing stellar mass from the input data reduced the distance between these regions.
+            Regions 5, 6 and 8 have the same relative distance from each other as in Fig.~\ref{fig: all_derived_ones}, but they are all closer to the position of region 10.
+            The distance between regions 2 and 3 is reduced but in the meantime the colour between them became darker.
 
@@
 
-            Fig.~\ref{fig: subset6} shows the SOM generated from data listed in Tab.~\ref{tab: subset6}, which includes all the data from Tab.~\ref{tab: subset5} except for  the SPIRE 250 and 500~$\mu$m emission.
-            Although for most of the regions we see the changes in their positions, the colours between neurons changes as well. 
-            %Therefore, we can conclude that these changes caused by the differences in the initial assigned weights.
+            Fig.~\ref{fig: subset6} shows the SOM generated from data listed in Table~\ref{tab: subset6}, which includes all the data from Table~\ref{tab: subset5} except for  the SPIRE 250 and 500~$\mu$m emission.
+            Although for most of the regions we see the changes in their positions, the colours between neurons change as well. 
             The distance between the positions of the regions 4 and 2 is increased as are the
@@
 
-            %Subsets, that some of them  are studied in this section, can be used to learn about the effect of each input on the map as well as they can be used to predict unobserved quantities in the galaxy.
+            Subsets, as studied in this section, can be used to learn about the effect of each input on the SOM and tell us about variation in the input data.
+            Comparing Fig.~\ref{fig: only_pahs} with other networks show us that PAH features are less variable than other input data.
+            These result is consistent with results from~\cite{Draine14}, who showed that the amount of PAHs in M31 for regions within 20~kpc radius is constant.
+            Additional evidence for the PAH features varying significantly less than other parameters is that changing from the PAH single band emission to total PAHs does not affect the networks.
+            In contrary, PACS~100~$\mu$m, stellar mass, total gas mass and RHI
+            are the data with the most variance; adding them to input data increases the dark colours between neurons significantly.
+            Although with changing input parameters for each network the distances between neurons and positions of the regions change, the general positions of the regions relative to one another does not change dramatically.
+            Therefore, the networks created by subsets can be used to predict the properties of unobserved quantities in other regions of the galaxy.
+            For example, photometry data, stellar mass, SFR, L$_\mathrm{dust}$, L$_\mathrm{TIR}$, and dust mass are available for most of M31. 
+            The network from Fig.~\ref{fig: wt_pahs} can be applied to 
+            these data from another region in M31.
+            By comparing the position of the new region with respect to our original 10 regions in the network, one would have an estimate for total PAHs in the new region without having any observational data for it.
 
-            % \subsubsection{Prediction observing data using M31}
+    \subsection{Applying Networks to M101 Observations}
+    Another application of self-organizing maps made with data from a single galaxy is to apply its trained networks on data from other galaxies to make predictions.
+    To demonstrate this, we generated an SOM using only M31 measurements which were also available for M101 (Fig.~\ref{fig: subset9}a). 
+    \cite{Dim15} compared PAHs in M31 with those from \hii~regions in M101, and showed the similarity between PAHs in these two galaxies (for more detail see \cite{Dim15} and \cite{Gordon08}).
+    In order to test whether these similarities are limited to PAH features or can be extended to other features in these two galaxies, we applied the SOM created using M31 data in Fig.~\ref{fig: subset9}a to M101 data (Fig.~\ref{fig: subset9}b).
+    Since the neurons in the SOM network created by M31 data already have their finalized weights, the algorithm finds the minimum differences between parameters for each region in M101 and the weights of neurons and introduces the winner neuron in one iteration.
 
-            %     On SOMs we can see relations between the input data from each region regarding to the other regions.
-            %     These relations are shown by colour in SOMs, when white is 100 per cent similarity and black is 0 per cent similarity.
-            %     Therefore, we have the probability distribution of quantities of each values given data from other regions.
-            %     We can use these probability distribution to estimate missing data for regions.
-
-            %     To demonstrate this conclusion, we assumed the stellar mass value for region 1 is unknown.
-            %     Therefore, we need a SOM that are generated from all the inputs data for all regions except stellar mass (e.g subset 1 in Fig.~\ref{fig: subset1}).
-            %     \import{../sections/image_texts/}{sim_subset1.tex}
-            %     We found the shortest path between region 1 and the other regions and measure their relative similarity ($p_j$).
-            %     Assuming the maximum similarity is 100 per cent between two neurons (white colour), we multiply the similarity values along the shortest path between two regions to find $p_j$ between region 1 and the other regions (Fig.~\ref{fig: sim_subset1}).
-            %     In both Figs.~\ref{fig: subset1} and ~\ref{fig: sim_subset1} are clear that region 1 shows more similarity to regions 2 and 9 than the others and the most dissimilarity to region 8.
-
-            %     We measured probability of stellar mass given other quantities of the region 1 ($P(m_1\mid \forall_1)$) using Equation~\ref{equ: prob1}.
-            %     \begin{equation}
-            %     \label{equ: prob1}
-            %         P(m_1\mid \forall_1) = \sum_{j=2}^{10}p_j*m_j
-            %     \end{equation}
-            %     Where $m_1$ is the stellar mass of region 1 and $m_j$ is the stellar mass of region j (any other region).
-            %     We estimated the stellar mass to be $\sim1377$~M$\odot$ which is 10 per cent less than the observed values.
-            %     This type of the prediction from SOM networks can be used to predict observation values in observational proposals or can be used in pre-phase studies of the big missions such as the James Webb Space Telescope (JWST) and LLST.
-
-    \subsection{Testing networks using M101 observations}
-    Another application of self-organizing maps made with data from a single galaxy is to apply its trained networks on data from other galaxies to make predictions. %%eh
-    To demonstrate this, we generated an SOM using only M31 measurements which were also available for M101 (Fig.~\ref{fig: subset9}a). 
-    \cite{Dim15} compared PAHs in M31 with those from H {\sc II} regions in M101, and showed the similarity between PAHs om these two galaxies (For more detail see \cite{Dim15} and \cite{Gordon08}).
-    In this SOM, as in the others, region 10 is separated from other regions in M31.
+    In the SOM that is created by M31 data in Fig.~\ref{fig: subset9}a, as in the others, region 10 is separated from other regions in M31.
     Regions 7 and 4 are close to each other with very light colours between their neurons, and as in the other SOMs regions 6, 8, and 5 are close to each other, but with medium dark colour between them.
+    Given the fact that we know the relative relation between M31 regions from 2D networks, we can analyze properties of M101 regions from their locations in Fig.~\ref{fig: subset9}b.
+    To do so, we compared positions of regions in M31 and M101 in the networks presented in Fig.s~\ref{fig: subset9}a and~\ref{fig: subset9}b, respectively, and based on colours between regions determine their (dis-)similarities.
     \import{../sections/image_texts/}{subset9.tex}
 
-    We applied the SOM created using M31 data in Fig.~\ref{fig: subset9}a to M101 data (Fig.~\ref{fig: subset9}b).
-    Region 5 in M31 and region 8 in M101 and regions 6 in M31 and region 2 in M101 occupied neurons with a white colour between them in the network in Fig.~\ref{fig: subset9}, which immediately suggests that these regions have similar properties.
-    Region 2 in M101 is a bright H {\sc II} region located at the end of the one of the M101 spiral arms (see Fig.~\ref{fig: regions in m101}) while
+    Region 5 in M31 and region 8 in M101 and regions 6 in M31 and region 2 in M101 occupy neurons with a white colour between them in the network in Fig.~\ref{fig: subset9}, which immediately suggests that these regions have similar properties.
+    Region 2 in M101 is a bright \hii~region located at the end of  one of the M101 spiral arms (see Fig.~\ref{fig: regions in m101}) while
     region 6 in M31 is located near the inner star-forming ring (see Fig.~\ref{fig: regions in m31}).
@@
 
-    Region 5 in M31 is in the inner ring of the galaxy and it is one of two regions in M31 that are not an  H {\sc II} region, while
+    Region 5 in M31 is in the inner ring of the galaxy and it is one of two regions in M31 that is not an  \hii~region, while
     region 8 in M101 is in a spiral arm of the galaxy.
     Relatively low stellar mass, SFR and SPIRE band emission caused these two regions to be nearby in the map.
-    In Sec.~\ref{Sec: 1d_cluster} we showed that regions 3 to 8 in M31 have similar properties; in Fig.~\ref{fig: subset9}b we see that regions 1 to 3 and 5 to 8 in M101 are located near regions 3 to 8 in M101.
+    In Section~\ref{Sec: 1d_cluster} we showed that regions 3 to 8 in M31 have similar properties; in Fig.~\ref{fig: subset9}b we see that regions 1 to 3 and 5 to 8 in M101 are located near regions 3 to 8 in M101.
     These regions all have medium or low PAH emission, dust and SFR compared to the remaining regions.
@@
 
-    Knowing the effects of the different input quantities on the networks from Section~\ref{sec: subsets}, we can have ideas about data entry from other regions/galaxies.
-    In this section we showed that we can use networks that are created by data from nearby galaxies, to study the properties of other galaxies in a fast way.
+    Knowing the effects of the different input quantities on the networks from Section~\ref{sec: subsets}, can yield ideas about data entry from other regions/galaxies.
+    In this section we showed that we can use networks that are created by data from nearby galaxies to study the properties of other galaxies.
+    If an SOM network is available, applying data from other regions to the network is very time efficient to learn about relative properties of galaxies.
     We should note that, since we normalized data before using them in the networks, we only see relative properties of the regions.
-    Therefore, we need data from few regions in the galaxy to use this network cannot use these networks to learn about properties of a single region in other galaxies.
+    Therefore, we need data from at least a few regions in the galaxy to use this application of SOMs and cannot use these networks to learn about properties of a single region in other galaxies.
+    As mentioned before, since we know the properties of regions in M31, from Fig.~\ref{fig: subset9}, we can quickly conclude that region 7 and 4 have relatively higher surface brightness than the other regions in M101.
+    Similarly, we can say that regions 6 and 8 in M101 have very faint surface brightness for most of the parameters, and are very different from regions 7 and 4.

### 2016-07-26 sections/V0.01/R20.01.tex

--- 2016-07-26 sections/R20.01.tex
@@
     Although 1D networks are helpful to give a general idea about the data, neurons in 1D maps have a maximum of two neighbours, which can limit the usefulness of the results.
-    In 2D networks, each neuron has two to six neighbours, which allows them to to capture a complete picture of the complicated relations in the input data.
+    In 2D networks, each neuron has two to six neighbours, which allows them to capture a complete picture of the complicated relations in the input data.
     Accordingly, we created $10\times10$ 2D networks to study the data in detail.

### 2016-07-26 sections/intro0.02.tex

--- 2016-07-13 sections/intro0.01.tex
@@
 As a result, many studies have been devoted to finding relations between physical properties of galaxies, such as morphology, star formation rate (SFR), stellar mass, metallicity, and amount of gas, both for spatially-resolved regions and galaxies as a whole~\citep[e.g.][]{Wong13,Leroy08}, and many others use these results in analyzing observations of high-redshift galaxies~\citep[e.g.][]{Freundlich13,Walch11}.
-Advances in technology allow us to collect data from the sky.
 Surveys such as KINGFISH~\citep{Kennicutt11} and THINGS~\citep{Walter08} have made observations of nearby galaxies in various wavelengths and from these data we can measure physical properties such as stellar mass, star formation rate (SFR), dust mass, and gas mass~\citep[e.g.][]{Eskew12,Dale09,Calzetti07}.
@@
 Images of this galaxy provide us with a detailed view of the inside of a spiral galaxy as seen from an external perspective.
-M31 has been observed by many telescopes including the {\textit Hubble}, \Spitzer, \Herschel space telescope.
+M31 has been observed by many telescopes including the {\textit {Hubble}}, \Spitzer and \Herschel space telescopes. %Els: Use the correct names for telescopes?
 \cite{Barmby06} used data from the \Spitzer Infrared Array Camera \citep[IRAC;][]{Fazio04} to show the spatial distribution of Polycyclic Aromatic Hydrocarbons (PAHs) in the interstellar medium (ISM) of M31.
@@
 \cite{Draine14, Mattsson14, Viaene14, Smith12} and~\cite{Fritz12} used \Herschel data to study dust in the ISM of the galaxy.
-Properties of the current stars in the galaxy were studied by many groups~\citep[e.g.][and references therein]{Tamm12,Dalcanton12,Massey07}
-\cite{Rahmani16, Ford13} and \cite{Tabatabaei10} measured the SFR in M31 in order to study star formation laws, and~\cite{Dim15} and \cite{Kapala15} used infrared spectroscopy to study PAHs and atomic and molecular line emission in the ISM.
+Properties of the current stars in the galaxy were studied by many groups~\citep[e.g.][and references therein]{Tamm12,Dalcanton12,Massey07}.
+\cite{Rahmani16, Ford13} and \cite{Tabatabaei10} measured the spatially-resolved SFR in M31 in order to study star formation laws, and~\cite{Dim15} and \cite{Kapala15} used infrared spectroscopy to study PAHs and atomic and molecular line emission in the ISM.
 
@@
 What is the correlation between PAHs and SFR, dust mass, and gas mass in M31? 
-Are PAHs features in M31 are similar or they can be divided in various groups? If so, what are properties of each group?
-Does intensity of PAHs emission depends on the underlying structure of their position? 
-How do they compare to properties of galaxies?
+Are PAH features in M31 similar or they can be divided into various groups? If so, what are the properties of each group?
+Does the intensity of PAH emission depend on location or global galaxy properties? 
 The properties of M31 that derived in various studies and observational data of this galaxy can be used for a knowledge discovery and data mining study.
-%The amount of data for M31 makes this galaxy a suitable target for a knowledge discovery and data mining study.
-the Pinwheel Galaxy (M101), with distance of 6.7 Mpc~\citep{Freedman01}, is another nearby galaxies that has been observed and studied~\citep[e.g][and references therein]{Kennicutt11,Dale09, Leroy08, Gordon08}.
-M101 is a large spiral galaxy with several \hii~regions and high metallicity gradient from centre to outskirt of it~\citep{Kennicutt03}.
-In case of dimensionality data from M101 is a suitable addition to M31 data for a data mining study.
-Knowledge discovery and data mining methods are designed to extract hidden information from data and have been tested in many astronomical studies.
+The Pinwheel Galaxy (M101), with distance of 6.7~Mpc~\citep{Freedman01}, is another nearby galaxy that has been well-observed and studied~\citep[e.g.
+][and references therein]{Kennicutt11,Dale09, Leroy08, Gordon08}.
+M101 is a large spiral galaxy with several \hii~regions and a large metallicity gradient from centre to outskirts~\citep{Kennicutt03}.
+Since the observational data from M31 and M101 are similar, M101 is a suitable addition to M31 data for a data mining study. 
+Knowledge discovery and data mining methods are designed to extract hidden information from data and have been tested in many astronomical studies~\citep[e.g.][and references therein]{Ball10}.
 However, this study is the first to use a data mining method on observations of nearby galaxies.
@@
 % data mining and clustering in general; when we have so many data and we want to map them
-\cite{Ball10} gave an extensive review of data mining and machine learning and their usage in astronomy.
+\cite{Ball10} gave an extensive review of data mining and machine learning algorithms and their usage in astronomy.
 A data mining algorithm learns about data from training, which can be supervised or unsupervised.
@@
 
-The purpose of the present work is to use M31 observations to generate new insights into nearby galaxies, with a focus on relations between PAHs and other properties of the galaxy.
-There are very few studies on relations between properties of M31 with its PAH features. %generate?!
-\cite{Cesarsky98} studied PAH spectra in four regions in M31 and found that PAH features in M31 differ from those in other galaxies in having weak or no $6.2 - 8.6\mu$m emission with enhanced 11.2~$\mu$m emission.
-However,~\cite{Dim15} using {\it Spitzer}/Infrared Spectrograph~\citealt[IRS,][]{Houck04b} observations, found that the PAH spectra of M31 have the same features as the spectra of other nearby star-forming galaxies.
-Using IRAC imaging observations,~\cite{Barmby06} found good agreement between SFRs derived using observed 8~$\mu$m luminosity with other 
-star formation indicators such as \halpha and far infrared luminosity in M31.
+The purpose of the present work is to use M31 observations to provide new insights into nearby galaxies, with a focus on relations between PAHs and other properties of the galaxy,
+as there are few studies on relations between properties of M31 with its PAH features.
+\cite{Cesarsky98} studied PAH spectra observed by ISOCAM spectro-imaging in four regions in M31 and found that PAH features in M31 differ from those in other galaxies in having weak or no $6.2 - 8.6$~$\mu$m emission with enhanced 11.2~$\mu$m emission.
+However,~\cite{Dim15} using {\it Spitzer}/Infrared Spectrograph~\citep[IRS;][]{Houck04b} observations, found that the PAH spectra of M31 have the same features as the spectra of other nearby star-forming galaxies.
+Those authors re-evaluated the ISOCAM data to compare them to IRS data and found that the earlier results were likely due to incorrect background subtraction.
+Using IRAC imaging observations,~\cite{Barmby06} found good agreement between the M31 SFR derived using observed 8~$\mu$m luminosity with other 
+star formation indicators such as \halpha and far infrared luminosity.
 \cite{Draine14} found that the PAH abundance in M31 is almost constant up to a galactocentric radius of $\sim 20$~kpc.
-With data mining techniques we address that
-compare to other galaxies, are PAHs features in M31 are unique as~\cite{Cesarsky98} mentioned or they are normal as ~\cite{Dim15} and \cite{Draine14} concluded
+With data mining techniques we address the question of whether,
+compared to other galaxies, PAH features in M31 are unique as~\cite{Cesarsky98} claimed, or  are normal as ~\cite{Dim15} and \cite{Draine14} concluded.
 
@@
 In this project we apply the self-organizing map algorithm (SOM) to M31 data, training 1D and 2D networks.
-Using the smaller networks we study the properties of the clusters and investigate relations between PAH features and other quantities in M31.
-We create 2D SOMs from subsets of the data as well as all available data, which helps us to understand the effect of each input in the position of the clusters in the SOM.
-We apply the 2D trained networks to  observations of M101, another nearby spiral  galaxy, to check whether it has similar properties.
+Using networks with fewer neurons, we study the properties of the clusters and investigate relations between PAH features and other quantities in M31.
+We create 2D SOMs from subsets of the data as well as all available data, which helps us to understand the effect on each input on the position of the clusters in the SOM.
+We apply the 2D trained networks to the M101 data to study whether they have similar properties to M31 ones.
 If our hypothesis is correct, we should be able to see that regions in M31 and M101 with the same positions in the SOM have the same properties.
 
-We describe the SOM method in Section $\S$~\ref{sec: method}. 
-In Section $\S$~\ref{Sec: data_SOMN}, we present the observational data from M31 and M101 that we use in this study.
-The results of the 1D SOM networks and the studying of PAHs in M31 are presented in Section $\S$~\ref{Sec: 1d_cluster}.
-In Section $\S$~\ref{sec: 2d_cluster}, we present the results of 2D SOM networks and their use in extracting information about other galaxies.
-In Section $\S$~\ref{sec: summary}, we summarize our results and discuss potential future work in this subject.
+We describe the SOM method in $\S$~\ref{sec: method_SOMN}. 
+In $\S$~\ref{Sec: data_SOMN}, we present the observational data from M31 and M101 that we use in this study.
+The results of the 1D SOM networks and the study of PAHs in M31 are presented in $\S$~\ref{Sec: 1d_cluster}.
+In $\S$~\ref{sec: 2d_cluster}, we present the results of 2D SOM networks and their use in extracting information about other galaxies.
+In $\S$~\ref{sec: summary}, we summarize our results and discuss potential future work in this subject.

### 2016-07-26 sections/V0.01/intro0.01.tex
Updates from ShareLaTeX

--- 2016-07-13 sections/intro0.01.tex
@@
 Images of this galaxy provide us with a detailed view of the inside of a spiral galaxy as seen from an external perspective.
-M31 has been observed by many telescopes including the {\textit Hubble}, \Spitzer, \Herschel space telescope.
+M31 has been observed by many telescopes including the {\textit Hubble}, \Spitzer and \Herschel space telescope.
 \cite{Barmby06} used data from the \Spitzer Infrared Array Camera \citep[IRAC;][]{Fazio04} to show the spatial distribution of Polycyclic Aromatic Hydrocarbons (PAHs) in the interstellar medium (ISM) of M31.
@@
 \cite{Draine14, Mattsson14, Viaene14, Smith12} and~\cite{Fritz12} used \Herschel data to study dust in the ISM of the galaxy.
-Properties of the current stars in the galaxy were studied by many groups~\citep[e.g.][and references therein]{Tamm12,Dalcanton12,Massey07}
+Properties of the current stars in the galaxy were studied by many groups~\citep[e.g.][and references therein]{Tamm12,Dalcanton12,Massey07}.
 \cite{Rahmani16, Ford13} and \cite{Tabatabaei10} measured the SFR in M31 in order to study star formation laws, and~\cite{Dim15} and \cite{Kapala15} used infrared spectroscopy to study PAHs and atomic and molecular line emission in the ISM.
@@
 %The amount of data for M31 makes this galaxy a suitable target for a knowledge discovery and data mining study.
-the Pinwheel Galaxy (M101), with distance of 6.7 Mpc~\citep{Freedman01}, is another nearby galaxies that has been observed and studied~\citep[e.g][and references therein]{Kennicutt11,Dale09, Leroy08, Gordon08}.
+the Pinwheel Galaxy (M101), with distance of 6.7~Mpc~\citep{Freedman01}, is another nearby galaxies that has been observed and studied~\citep[e.g][and references therein]{Kennicutt11,Dale09, Leroy08, Gordon08}.
 M101 is a large spiral galaxy with several \hii~regions and high metallicity gradient from centre to outskirt of it~\citep{Kennicutt03}.
 In case of dimensionality data from M101 is a suitable addition to M31 data for a data mining study.
-Knowledge discovery and data mining methods are designed to extract hidden information from data and have been tested in many astronomical studies.
+Knowledge discovery and data mining methods are designed to extract hidden information from data and have been tested in many astronomical studies~\citep[e.g.][and references therein]{Ball10}.
 However, this study is the first to use a data mining method on observations of nearby galaxies.
@@
 There are very few studies on relations between properties of M31 with its PAH features. %generate?!
-\cite{Cesarsky98} studied PAH spectra in four regions in M31 and found that PAH features in M31 differ from those in other galaxies in having weak or no $6.2 - 8.6\mu$m emission with enhanced 11.2~$\mu$m emission.
-However,~\cite{Dim15} using {\it Spitzer}/Infrared Spectrograph~\citealt[IRS,][]{Houck04b} observations, found that the PAH spectra of M31 have the same features as the spectra of other nearby star-forming galaxies.
+\cite{Cesarsky98} studied PAHs spectra observed by ISOCAM spectro-imaging observation, in four regions in M31 and found that PAH features in M31 differ from those in other galaxies in having weak or no 6.2 - 8.6~$\mu$m emission with enhanced 11.2~$\mu$m emission.
+However,~\cite{Dim15} using {\it Spitzer}/Infrared Spectrograph~\citep[IRS;][]{Houck04b} observations, found that the PAH spectra of M31 have the same features as the spectra of other nearby star-forming galaxies.
+He re-evaluated the ISOCAM data to compare them to IRS data, but its results were inconclusive. %%%%% !!!!!%%%%
 Using IRAC imaging observations,~\cite{Barmby06} found good agreement between SFRs derived using observed 8~$\mu$m luminosity with other 
@@
 In this project we apply the self-organizing map algorithm (SOM) to M31 data, training 1D and 2D networks.
-Using the smaller networks we study the properties of the clusters and investigate relations between PAH features and other quantities in M31.
-We create 2D SOMs from subsets of the data as well as all available data, which helps us to understand the effect of each input in the position of the clusters in the SOM.
-We apply the 2D trained networks to  observations of M101, another nearby spiral  galaxy, to check whether it has similar properties.
+Using networks with fewer neurons, we study the properties of the clusters and investigate relations between PAH features and other quantities in M31.
+We create 2D SOMs from subsets of the data as well as all available data, which helps us to understand the effect of each input on the position of the clusters in the SOM.
+We apply the 2D trained networks to the M101 data to check whether it has similar properties.
 If our hypothesis is correct, we should be able to see that regions in M31 and M101 with the same positions in the SOM have the same properties.
@@
 In Section $\S$~\ref{Sec: data_SOMN}, we present the observational data from M31 and M101 that we use in this study.
-The results of the 1D SOM networks and the studying of PAHs in M31 are presented in Section $\S$~\ref{Sec: 1d_cluster}.
+The results of the 1D SOM networks and the study of PAHs in M31 are presented in Section $\S$~\ref{Sec: 1d_cluster}.
 In Section $\S$~\ref{sec: 2d_cluster}, we present the results of 2D SOM networks and their use in extracting information about other galaxies.

### 2016-07-26 sections/V0.01/method0.01.tex
Updates from ShareLaTeX

--- 2016-07-13 sections/method0.01.tex
@@
 \subsection{Choosing an Algorithm}
-To fulfill this purpose, an unsupervised data mining method is the most suitable choice.
 
-Some of the most tested methods of data mining in astronomy are artificial neural networks (ANNs)~\citep[e.g.][and references therein]{ Hossein14,Hossein16}.
+Some of the most tested methods of data mining in astronomy are artificial neural networks (ANNs)~\citep[e.g.][and references therein]{Hossein14,Hossein16}.
 ANNs are designed to work in the same way that the neurons work in a human brain.
@@
 K-means algorithm, SOMs, and hierarchical clustering are the main unsupervised methods that are used in astronomical studies~\citep[e.g.][]{DAbrusco12, Aycha16}. %%add one or two more
-For both K-means and SOM algorithms, the user must define the number of clusters, and the algorithms decide how to separate the data into desired number of clusters.
+For both K-means and SOM algorithms, the user must define the number of clusters, and the algorithms decide how to separate the data into the desired number of clusters.
 In the hierarchical clustering method, the user must define dissimilarity between the groups; the algorithm combines (or divides) existing groups based on their dissimilarity and creates a hierarchical structure.
-Comparing SOMs, K-means and hierarchical clustering shows that in some cases hierarchical clustering method mis-classifies the data~\citep[][and references therein]{Mangiameli96}.
-We chose the SOM method over K-means due to the fact that SOMs not only cluster data, but also show similarities and dissimilarities between the clusters.
-Therefore, we can cluster our sample data and study the underlying structure, simultaneously.
+Comparing the SOMs, K-means and hierarchical clustering methods shows that in some cases the hierarchical clustering method mis-classifies the data~\citep[][and references therein]{Mangiameli96}.
+We chose the SOM method over K-means method due to the fact that SOMs not only cluster data, but also show similarities and dissimilarities between the clusters.
+Therefore, we can cluster our sample data and study the underlying structure simultaneously.
 
@@
  \label{sec: som}
- The SOM is a clustering method which reduces the dimensionality of data, while preserving topological features ~\citep{Kohonen98}. 
- The results of the SOM are shown with a map of neurons.
- Each neuron has a fixed position in the map, and may contain one or more samples from input data, \boldit{V} $\in \Re^n$.
+ The SOM is a clustering method which reduces the dimensionality of data, while preserving topological features~\citep{Kohonen98}. 
+ The results of the SOM are shown with a map of neurons, which their numbers are set by the user.
+ Each neuron has a fixed position in the map and may contain one or more samples from the input data,~\boldit{V} $\in \Re^n$. % Els said the simbols should be describe?! I think it is pretty obvious!
  A weight vector,~\boldit{W} $\in \Re^n$, with the same dimension as the input data, is associated with each node and will be varied during the training process.
@@
             \label{equ: weight adj}
-            w(t+1)=w(t)+L(t) \times R(t) \times(v(t)-w(t))
+            W(t+1)=W(t)+L(t) \times R(t) \times(V(t)-W(t))
  \end{equation}
@@
 
-     In order to create self-organizing maps, we used the \textsc{ matlab} neural network toolbox~\citep[NNT,][]{matlabtolbox}.
-     An SOM in \textsc{ nnt} can be created by the \textsc{ newsom} library which works in two phases, the ``ordering phase" and ``tuning phase" . 
+     In order to create self-organizing maps, we used the \textsc{matlab} neural network toolbox~\citep[NNT,][]{matlabtolbox}.
+     An SOM in \textsc{nnt} can be created by the \textsc{newsom} library which works in two phases, the ``ordering phase" and ``tuning phase" . 
      Phase one is the ``ordering phase". 
@@
 
-     One feature of the SOM method is that there is no rule or restriction on number of clusters.
-     Users must decide the size of networks based on their data set and their usage of the results.
-     There has been few attempts to find a rule for restricting the number of neurons based on the input sample \citep[e.g.][]{Vesanto05}, but none of them are certain. 
-     We varied the size of SOMs from $1\times2$ to $50\times50$ to choose the most suitable size for our maps, and found that based on the size of our sample, the best size for the 2D SOMs was 10$\times$10.
+     One feature of the SOM method is that there is no rule or restriction on the number of clusters.
+     Users must decide the size of the networks based on their data set and their usage of the results.
+     There has been a few attempts to find a rule for restricting the number of neurons based on the input sample \citep[e.g.][]{Vesanto05}, but none of them are certain. 
+     We varied the size of SOMs from $1\times2$ to $50\times50$ in order to choose the most suitable size for the maps we generated, and found that based on the size of our sample, the best size for the 2D SOMs was 10$\times$10.
      We created our final SOMs with initial values for number of iterations in ordering phase, ordering phase learning factor, tuning phase learning factor, and tuning phase neighbourhood distance of 500, 0.9, 0.02, and 1, respectively.
@@
 To show how self-organizing maps work, we created a mock sample containing only a few regions.
-Each sample had two properties: amount of dust and star formation rate, where the possible values were
+Each sample had two properties: the amount of dust and the star formation rate, where the possible values were
 either 0 or 1 for low or high SFR, and 0 or 0.5 for a low or high amount of dust. 
@@
 
-Using this method, as expected, we are able to divide the mock sample into 4 distinct groups: regions with high SFR and high dust content, regions with low SFR and high dust content, regions with high SFR and low dust content, and regions with low SFR and dust content.
+Using this method, as expected, we are able to divide the mock sample into 4 distinct groups, which their boundaries are shown by grey colours in Fig.~\ref{fig: sample}: regions with high SFR and high dust content, regions with low SFR and high dust content, regions with high SFR and low dust content, and regions with low SFR and dust content.
 The plot in the Fig.~\ref{fig: sample} clearly shows these divisions.
@@
 
-Having two regions with exactly the same values in all their quantities in the real world is almost impossible. 
-Therefore, one can find a network with a high number of neurons, which separates the input data completely, and clusters them into separate groups.
-However, if the input data has high similarity, the number of neurons must be much higher than the number of input samples to be able to separate the groups from each other. 
-Therefore, it is up to the user to decide the similarity or dissimilarity between the input data based on the number of neurons.
-%PB: this praragraph is tricky for me to understand.
-Might need to try rewriting.
+Having two regions with exactly the same values in all their quantities with real data is unprovable. 
+If in an input data, there are two entries with similar (but not identical) values in all dimensions, one can find a network that separate these two entries in two groups.  
+However, in case of multiple similar entries in data, the number of neurons must be much higher than the number of entries for complete separation.
+Therefore, the user learns about similarity/dissimilarity of members of input data based on the ratio of number of entries of input data and number of neurons.

### 2016-07-26 sections/image_texts/all.tex
After-submission

@@
     \caption{Two dimensional SOM of M31 using $10\times10$ grid.
-Similar to Figs.\ref{fig: sample} and \ref{fig: M31_nets_1d}, The hexagonal shapes show the neurons and the grey cycle colours between neurons show the differences between weight of each neuron.}
+Similar to Figs.\ref{fig: sample} and \ref{fig: M31_nets_1d}, the hexagonal shapes show the neurons and the grey cycle colours between neurons show the differences between weight of each neuron.}
     \label{fig: all_derived_ones}

### 2016-07-26 sections/image_texts/col3byall.tex
After-submission

--- 2016-07-04 sections/image_texts/col3byall.tex
@@
         \centering
-        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and11.png}
+        \includegraphics[width=54mm, height=37mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and11.png}
+        \caption{Input data: data from Fig.~\ref{fig: only_pahs} and \halpha}
         \label{fig: col3and11_dist}
@@
         \centering
-        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and12.png}
+        \includegraphics[width=54mm, height=37mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and12.png}
+        \caption{Input data: data from Fig.~\ref{fig: col3and11_dist} and \oiii}
         \label{fig: col3and12_dist}
@@
         \centering
-        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and13.png}
+        \includegraphics[width=54mm, height=37mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and13.png}
+        \caption{Input data: data from Fig.~\ref{fig: col3and12_dist} and \sii}
         \label{fig: col3and13_dist}
@@
         \centering
-        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and14.png}
+        \includegraphics[width=54mm, height=37mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and14.png}
+        \caption{Input data: data from Fig.~\ref{fig: col3and13_dist} and IRAC~5.7~$\mu$m emission}
         \label{fig: col3and14_dist}
@@
         \centering
-        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and15.png}
+        \includegraphics[width=54mm, height=37mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and15.png}
+        \caption{Input data: data from Fig.~\ref{fig: col3and14_dist} and PACS~100~$\mu$m emission }
         \label{fig: col3and15_dist}
@@
         \centering
-        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and16.png}
+        \includegraphics[width=54mm, height=37mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and16.png}
+        \caption{Input data: data from Fig.~\ref{fig: col3and15_dist} and SPIRE~250~$\mu$m emission }
         \label{fig: col3and16_dist}
@@
         \centering
-        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and17.png}
+        \includegraphics[width=54mm, height=37mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and17.png}
+        \caption{Input data: data from Fig.~\ref{fig: col3and16_dist} and SPIRE~350~$\mu$m emission }
         \label{fig: col3and17_dist}
@@
         \centering
-        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and18.png}
+        \includegraphics[width=54mm, height=37mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and18.png}
+        \caption{Input data: data from Fig.~\ref{fig: col3and17_dist} and SPIRE~500~$\mu$m emission }
         \label{fig: col3and18_dist}
@@
         \centering
-        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and19.png}
+        \includegraphics[width=54mm, height=37mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and19.png}
+         \caption{Input data: data from Fig.~\ref{fig: col3and18_dist} and L$_{{\mathrm Dust}}$}
         \label{fig: col3and19_dist}
@@
         \centering
-        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and20.png}
+        \includegraphics[width=54mm, height=37mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and20.png}
+          \caption{Input data: data from Fig.~\ref{fig: col3and19_dist} and M$_{{\mathrm Dust}}$}
         \label{fig: col3and20_dist}
@@
         \centering
-        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and21.png}
+        \includegraphics[width=54mm, height=37mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and21.png}
+        \caption{Input data: data from Fig.~\ref{fig: col3and20_dist} and SFR(FUV\ +\ 24\ $\mu$m)}
         \label{fig: col3and21_dist}
@@
         \centering
-        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and22.png}
+        \includegraphics[width=54mm, height=37mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and22.png}
+        \caption{Input data: data from Fig.~\ref{fig: col3and21_dist} and M$_{{\mathrm Stars}}$}
         \label{fig: col3and22_dist}
@@
         \centering
-        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and23.png}
+        \includegraphics[width=54mm, height=37mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and23.png}
+        \caption{Input data: data from Fig.~\ref{fig: col3and22_dist} and L$_{{\mathrm TIR}}$}
         \label{fig: col3and23_dist}
@@
         \centering
-        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and24.png}
+        \includegraphics[width=54mm, height=37mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and24.png}
+        \caption{Input data: data from Fig.~\ref{fig: col3and23_dist} and M$_{{\mathrm Total\ gas}}$}
         \label{fig: col3and24_dist}
@@
         \centering
-        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and25.png}
+        \includegraphics[width=54mm, height=37mm ]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and25.png}
+        \caption{Input data: data from Fig.~\ref{fig: col3and19_dist} and RHI.}
         \label{fig: col3and25_dist}
@@
     \caption{Similar to Fig.~\ref{fig: all_derived_ones}, here we show the result from increasing dimension of input data from Fig.~\ref{fig: only_pahs} to 25, gradually.
-The order of input data is the same as order of data in Fig.~\ref{fig: cor_cluster1}.}
+The order of input data is the same as the order of data in Fig.~\ref{fig: cor_cluster1}.}
     \label{fig: inc_D_col3s}

### 2016-11-09 sections/R10.03.tex
V0.03; after thesis comments

--- 2016-07-26 sections/R10.02.tex
@@
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%Result Part 1: 1D SOMs
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
 \section{One-Dimensional Self-Organizing Maps}
@@
 
-        Fig.~\ref{fig: M31_net_1by2} shows that by forcing the regions in the M31 to be divided into two groups, regions 1, 2, 9 and 10 (shown in Fig.~\ref{fig: regions in m31}) occupy one neuron and the other regions occupy the other one.
+        Fig.~\ref{fig: M31_net_1by2} shows that by forcing the regions in M31 to be divided into two groups, regions 1, 2, 9 and 10 (shown in Fig.~\ref{fig: regions in m31}) occupy one neuron and the other regions occupy the other one.
         The medium grey colour between two neurons indicates that there are some similarities between two groups, but they are not very similar. 
@@
         The SOM shows that this region has completely different input values from the others: most of the values for region 10 are much higher than for the other regions, which is the main reason for its isolation.
-        Region 8 occupies the right-most neuron in this network, suggesting that this region has the most differences from region 10.
+        Region 8 occupies the left-most neuron in this network, suggesting that this region has the most differences from region 10.
 
@@
         Each of these subgroups separates for a reason.
-        This reason can vary from having higher values in some specific properties, as discussed in Section~\ref{Sec: 1d_cluster}, to some unknown correlations between data that cannot be seen in other groups or in the galaxy as a whole.
+        This reason can vary from having higher values in some specific properties, as discussed in Section~\ref{Sec: 1d_cluster}, to some unknown non-linear or linear correlations between data that cannot be seen in other groups or in the galaxy as a whole.
         To investigate the latter, we show in Fig.~\ref{fig: cor_cluster1} the Pearson correlation coefficients for the inputs from regions 3 to 8, which were clustered together in the $1\times2$ and $1\times3$ networks (see Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}).
@@
         \includegraphics[width=\textwidth]{../images0.01/cor_plots/M31_derived_3_to_8_core_plot_for_paper.pdf}
-        \caption[Pearson correlation coefficients for data from the clustered regions in M31]{Same as Fig.~\ref{fig: cor_all}, but here we used data from regions grouped in the left sides of Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}.
-}
+        \caption[Pearson correlation coefficients for data from the clustered regions in M31]{Same as Fig.~\ref{fig: cor_all}, but here we used data from regions grouped in the left sides of Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}.}
           \label{fig: cor_cluster1}
@@
         Comparing the correlation coefficient plots for all 10 regions in M31 (Fig.~\ref{fig: cor_all}) and for the clustered data (Fig.~\ref{fig: cor_cluster1}) shows the differences between all 10 regions and clustered data and why regions 3 to 8 become separated from the other regions.
-        The main features that differentiate these two plots are the anti-correlations between PAH features and RHI, stellar mass, \halpha, \sii, \oiii, and IRAC~5.8~$\mu$m~emission.
+        The main features that differentiate these two plots are the anti-correlations between PAH features and RHI, stellar mass, \halphadot, \sii, \oiii, and IRAC~5.8~$\mu$m~emission.
         Additionally, for the PAH fluxes in Fig.~\ref{fig: cor_cluster1}, there are no significant correlations with PACS~100~$\mu$m, L$_\mathrm{dust}$, L$_\mathrm{TIR}$, SFR, or metallicity.
@@
         Many groups have used PAH features as a tracer of SFR by finding correlations between 
-        PAH emission and SFR derived from extinction-corrected \halpha~\citep[e.g.][]{Calzetti07,Khramtsova13,Shipley16}.
+        PAH emission and SFR derived from extinction-corrected \halpha \citep[e.g.][]{Calzetti07,Khramtsova13,Shipley16}.
         These correlations are seen in Fig.~\ref{fig: cor_all}, when we considered the data from all regions, but not in Fig.~\ref{fig: cor_cluster1} when considering the clustered data.
@@
 
-        Strong anti-correlations between 6.2 to 17.0~$\mu$m~main PAH features and RHI, stellar mass, \halpha, \sii, \oiii, and IRAC~5.6~$\mu$m~emission in Fig.~\ref{fig: cor_cluster1} were not seen in Fig.~\ref{fig: cor_all} (even if we ignore the outlier values).
-        Anti-correlations between PAH features and the \halpha, \sii, and \oiii~emission could be the result of one of the following. 
+        Strong anti-correlations between 6.2 to 17.0~$\mu$m~main PAH features and RHI, stellar mass, \halphadot, \sii, \oiii, and IRAC~5.6~$\mu$m~emission in Fig.~\ref{fig: cor_cluster1} were not seen in Fig.~\ref{fig: cor_all} (even if we ignore the outlier values).
+        Anti-correlations between PAH features and the \halphadot, \sii, and \oiii~emission could be the result of one of the following. 
         First, the optical data are not corrected for dust extinction.
-        The PAH features correlate with the amount of dust while \halpha~emission anti-correlates with the amount of dust due to extinction as suggested by \cite{Calzetti94}.
-        Therefore, higher PAH fluxes imply higher dust abundance and less \halpha~emission, and the same holds for \sii~and \oiii~emission.
+        The PAH features correlate with the amount of dust while \halpha emission anti-correlates with the amount of dust due to extinction as suggested by \cite{Calzetti94}.
+        Therefore, higher PAH fluxes imply higher dust abundance and less \halpha emission, and the same holds for \sii~and \oiii~emission.
         Second is the possible effect of the structure of the observed regions.
-        If the observed regions are located near the edge of \hii~regions we would expect to see more PAH and less \halpha~emission. 
+        If the observed regions are located near the edge of \hii~regions we would expect to see more PAH and less \halpha emission. 
         The anti-correlations between 6.2 to 17.0~$\mu$m~PAH features and RHI have been seen in other studies, as well~\citep[e.g.][]{Wu06, Gordon08,Calzetti10,Dim15}. 
@@
 Hence, simply a harder RHI does not argue for a smaller PDRs being more plausible.
-        The latter reason, which could also describe the anti-correlation between PAH features and \halpha~emission, seems to be the more probable one.
+        The latter reason, which could also describe the anti-correlation between PAH features and \halpha emission, seems to be the more probable one.
 
@@
         Regions 5, 6, and 8 are located in the stellar disk of the galaxy and have relatively high stellar mass and faint PAH emission. 
-        According to~\cite{Dim15}, regions 5 and 8 are the only two regions in thesample that do not include an \hii~region, which could be the reason for the faint PAH emission for these regions.
+        According to~\cite{Dim15}, regions 5 and 8 are the only two regions in the sample that do not include an \hii~region, which could be the reason for the faint PAH emission for these regions.
         Regions 4 and 7 have similar quantities for both stellar mass and PAHs and region 3 has high PAHs and low stellar mass.

### 2016-11-09 sections/R20.03.tex
V0.03; after thesis comments

--- 2016-07-26 sections/R20.02.tex
@@
- %----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%Result Part 2: 2D SOMs
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
 \section{Two-Dimensional Self-Organizing Maps}
@@
     Similar to Fig.~\ref{fig: M31_net_1by14}, all the 10 regions are completely separated from each other in Fig.~\ref{fig: all_derived_ones}.
+    In Fig.~\ref{fig: all_derived_ones}, all the regions except regions 4 and 7 are surrounded by white colours.
+    This indicates that all the immediate neighbours for neurons occupied with each region have similar properties as the occupied ones, except for regions 4 and 7.
+    These two regions are sitting in very close regions and their smallest dissimilarity causes the changes in distances between their neighbours.
     \import{../sections/image_texts/}{all.tex}
 
-    Regions 4 and 7 are in the top left of Fig.~\ref{fig: all_derived_ones} with a very bright colour between their neurons, indicating that these two regions are very similar.
+    Regions 4 and 7 are in the top left of Fig.~\ref{fig: all_derived_ones} with a very light colour between their neurons, indicating that these two regions are very similar.
     Considering the position of these two regions in M31 (both right on the edge of the star forming rings in the galaxy), similarity of these two regions was predictable.
-    The position of region 3 on the SOM is close to the position of regions 4 and 7, but with a darker colour between the nodes. 
+    The position of region 3 on the SOM is relatively close to the position of regions 4 and 7, but with a darker colour between the nodes. 
     In Fig.~\ref{fig: regions in m31} it is clear that this region in M31 is physically closer to regions 4 and 7 than to any other region, but it is on the outer side of the star forming ring.
@@
     Regions 1 and 9 are close to each other and in the same side of the star forming ring. 
-    However, region 1 is in an area of the galaxy with less diffuse \halpha~emission than region 9, which might be the reason for their distances in the SOM.
+    However, region 1 is in an area of the galaxy with less diffuse \halpha emission than region 9, which might be the reason for their distances in the SOM.
     Region 2 is more distant from other regions in the galaxy and located in the star forming ring.
-    However, similar to regions 1 and 4, region 2 is located in an area of the galaxy with less diffuse \halpha~emission.
+    However, similar to regions 1 and 4, region 2 is located in an area of the galaxy with less diffuse \halpha emission.
     Therefore, the place of region 2 in the SOM tends towards regions 1 and 4. 
@@
              \import{../sections/image_texts/}{PAHS_or_not_PAHs.tex}
-            Comparing the SOM from all data in Fig.~\ref{fig: all_derived_ones} with the SOMs in Fig.~\ref{fig: PAHS_or_not_PAHs} shows that the general position of regions in those networks are the same.
+            Comparing the SOM from all data in Fig.~\ref{fig: all_derived_ones} with the SOMs in Fig.~\ref{fig: PAHS_or_not_PAHs} shows that the general position of almost all regions in those networks are the same.
             Region 10 is in one corner of all three networks.
@@
             In both SOMs in Fig.~\ref{fig: PAHS_or_not_PAHs}, there are dissimilarities between regions in M31 but in Fig.~\ref{fig: wt_pahs}, the colours are much darker than the ones in Fig.~\ref{fig: only_pahs}.
-            This indicates that there is more similarity between the PAH features over all 10 regions than between the other input data.
+            This indicates that there is more similarity between the PAH features over all 10 regions than between the other input quantities.
 
-            We increased the dimension of input data in Fig.~\ref{fig: only_pahs} (PAH-only data) gradually, by adding other quantities to the input data. 
+            We increased the dimension of the input data in Fig.~\ref{fig: only_pahs} (PAH-only data) gradually, by adding other quantities to the input data. 
             The order in which data were added is the same as the order in Fig.~\ref{fig: cor_all}, i.e.
-the SOM in Fig~\ref{fig: col3and11_dist} was created from PAH and \halpha\ emission as input data, the SOM in Fig~\ref{fig: col3and12_dist} created from PAHs, \halpha~emission and \sii~ continuum, and so on.
+the SOM in Fig~\ref{fig: col3and11_dist} was created from PAH and \halpha\ emission as input data, the SOM in Fig~\ref{fig: col3and12_dist} created from PAHs, \halpha emission and \sii~photometry, and so on.
             \import{../sections/image_texts/}{col3byall.tex}
@@
 
-            Comparing Figs.~\ref{fig: col3and11_dist} to~\ref{fig: col3and25_dist} shows that adding \halpha~emission data to PAH features causes regions 9 and 10 become isolated. 
+            Comparing Figs.~\ref{fig: col3and11_dist} to~\ref{fig: col3and25_dist} shows that adding \halpha emission data to PAH features causes regions 9 and 10 become isolated. 
             Increasing the dimension of the input data makes region 10 more isolated.
@@
             Regions 5, 6 and 8 have the same relative distance from each other as in Fig.~\ref{fig: all_derived_ones}, but they are all closer to the position of region 10.
-            The distance between regions 2 and 3 is reduced but in the meantime the colour between them became darker.
+            The distance between regions 2 and 3 is reduced but in the meantime the colour between them becomes darker.
 
@@
             these data from another region in M31.
-            By comparing the position of the new region with respect to our original 10 regions in the network, one would have an estimate for total PAHs in the new region without having any observational data for it.
+            By comparing the position of the new region (with the same spatial size of these 10 regions) with respect to our original 10 regions in the network, one would have an estimate for total PAHs in the new region without having any observational data for it.
 
@@
 
-    Knowing the effects of the different input quantities on the networks from Section~\ref{sec: subsets}, can yield ideas about data entry from other regions/galaxies.
+    Knowing the effects of the different input quantities on the networks from Section~\ref{sec: subsets} can yield ideas about data entry from other regions/galaxies.
     In this section we showed that we can use networks that are created by data from nearby galaxies to study the properties of other galaxies.
@@
     Therefore, we need data from at least a few regions in the galaxy to use this application of SOMs and cannot use these networks to learn about properties of a single region in other galaxies.
-    As mentioned before, since we know the properties of regions in M31, from Fig.~\ref{fig: subset9}, we can quickly conclude that region 7 and 4 have relatively higher surface brightness than the other regions in M101.
-    Similarly, we can say that regions 6 and 8 in M101 have very faint surface brightness for most of the parameters, and are very different from regions 7 and 4.
+    As mentioned before, since we know the properties of regions in M31, from Fig.~\ref{fig: subset9}, we can quickly conclude that regions 7 and 4 have relatively higher surface brightness than the other regions in M101.
+    Similarly, we can say that regions 6 and 8 in M101 have very faint surface brightnesses in most of the parameters, and are very different from regions 7 and 4.

### 2016-11-09 sections/V0.02/method0.02.tex
V0.03; after thesis comments

--- 2016-07-26 sections/V0.01/method0.01.tex
@@
 %----------------------------------------------------------------------------------------
-
-\section{METHOD}
-\label{sec: method}
+\section{Method}
+\label{sec: method_SOMN}
 \subsection{Choosing an Algorithm}
@@
 The result of a SOM is a 1D or 2D network of neurons, which shows the positions of clusters and their relative distance.
-Since the 1990s, many studies utilized SOMs for object classification and clustering (e.g.
-classifying quasars' spectra, star/galaxy classifications, gamma-ray burst clustering and light curve classification) and photometric redshift estimation~\citep[e.g.][]{Odewahn92, Hernandez94, Murtagh95, Maehoenen95,Scaringi09,Geach12,Fustes13,Meusinger16,Rahmani16b} %%% Why I cannot add submitted in front of the high-z paper %PB: MNRAS style guide says "Private communications or papers in preparation should be listed as such in the text, but omitted from the reference list, e.g.
-Smith (in preparation) shows that… " -- but I'm not clear on whether this applied to submitted papers or not
+Since the 1990s, many studies have utilized SOMs for object classification and clustering (e.g.
+classifying quasars' spectra, star/galaxy classifications, gamma-ray burst clustering and light curve classification) and photometric redshift estimation~\citep[e.g.][]{Odewahn92, Hernandez94, Murtagh95, Maehoenen95,Scaringi09,Geach12,Fustes13,Meusinger16,Rahmani16b}.
 
-K-means algorithm, SOMs, and hierarchical clustering are the main unsupervised methods that are used in astronomical studies~\citep[e.g.][]{DAbrusco12, Aycha16}. %%add one or two more
+The K-means algorithm, SOMs, and hierarchical clustering are the main unsupervised methods that are used in astronomical studies~\citep[e.g.][]{DAbrusco12, Aycha16}.
 For both K-means and SOM algorithms, the user must define the number of clusters, and the algorithms decide how to separate the data into the desired number of clusters.
@@
 Comparing the SOMs, K-means and hierarchical clustering methods shows that in some cases the hierarchical clustering method mis-classifies the data~\citep[][and references therein]{Mangiameli96}.
-We chose the SOM method over K-means method due to the fact that SOMs not only cluster data, but also show similarities and dissimilarities between the clusters.
+We chose the SOM method over the K-means method due to the fact that SOMs not only cluster data, but also show similarities and dissimilarities between the clusters.
 Therefore, we can cluster our sample data and study the underlying structure simultaneously.
@@
  The results of the SOM are shown with a map of neurons, which their numbers are set by the user.
- Each neuron has a fixed position in the map and may contain one or more samples from the input data,~\boldit{V} $\in \Re^n$. % Els said the simbols should be describe?! I think it is pretty obvious!
+ Each neuron has a fixed position in the map and may contain one or more samples from the input data in a n-dimensional space,~\boldit{V} $\in \Re^n$.
  A weight vector,~\boldit{W} $\in \Re^n$, with the same dimension as the input data, is associated with each node and will be varied during the training process.
  The process of creating an SOM happens over a series of $N$ iterations.
- In each iteration, the algorithm calculates the Euclidean distance for each node $j$ as $D_j^2= \sum_{i=0}^{i=n} (V_i - W_i)^2$, and finds a neuron with $D_{j_,{\mathrm min}}$. 
+ In each iteration, the algorithm calculates the Euclidean distance for each node $j$ as $D_j^2= \sum_{i=0}^{i=n} (V_i - W_i)^2$, and finds a neuron with $D_{j_,\mathrm{min}}$. 
  This neuron is the winner node and is calling Best Matching Unit (BMU). 
- The weight vectors in the neighbourhood of the BMU will change according to the Kohonen learning rule (equation~\ref{equ: weight adj}). 
+ In each iteration (t),The weight vectors W(t) in the neighbourhood of the BMU ($r^t_{BMU}$) will change according to the Kohonen learning rule (equation~\ref{equ: weight adj}). 
   \begin{equation}
@@
  \end{equation}
-where $L(t) = L_0 e^{(-t/\tau)}$ is the learning factor, which prevents the divergence of the SOM, and $R(t)=\exp(-\frac{D_j^2}{2r^t_{BMU}})$ is the influence rate, which determines how the weight of each node will change.
-Values for the number of neurons, $L(t)$ and $R(t)$ are arbitrary. 
-~\cite{Geach12} and \cite{Rahmani16b} demonstrate the algorithm of the SOM in more detail.
+where $L(t) = L_0 e^{(-t/\tau)}$ is the learning factor with $L_0$ is the initial value of learning, which prevents the divergence of the SOM, and $R(t)=\exp(-\frac{D_j^2}{2r^t_{BMU}})$ is the influence rate, which determines how the weight of each node will change.
+$\tau$ is the number of total iterations.
+Values for the number of neurons is arbitrary, and for various toolboxes values for one or all of $L_0$,$L(t)$, $R(t)$  and $r^t_{BMU}$ are arbitrary.
+\cite{Geach12} and~\cite{Rahmani16b} demonstrate the algorithm of the SOM in more detail.
 
      In order to create self-organizing maps, we used the \textsc{matlab} neural network toolbox~\citep[NNT,][]{matlabtolbox}.
-     An SOM in \textsc{nnt} can be created by the \textsc{newsom} library which works in two phases, the ``ordering phase" and ``tuning phase" . 
+     An SOM in \textsc{nnt} can be created by the \textsc{newsom} library, which works in two phases, the ``ordering phase" and ``tuning phase". 
      Phase one is the ``ordering phase". 
@@
      The second phase is the ``tuning phase".
-     In this phase the neighbourhood distance is at its minimum, but learning factor decreases very slowly.
+     In this phase the neighbourhood distance is at its minimum, but the learning factor decreases very slowly.
      This minimum neighbourhood distance and slowly decreasing learning factor helps to fine tune the topology results and causes a more stable SOM. 
-     The number of iterations in this tuning phase must be much more than the number of iterations in ordering phase, to allow the tuning to happen slowly. 
+     The number of iterations in this tuning phase must be much greater than the number of iterations in ordering phase, to allow the tuning to happen slowly. 
      We chose the number of epochs in the tuning phase to be 3 times more than the number of epochs in the ordering phase.
@@
      One feature of the SOM method is that there is no rule or restriction on the number of clusters.
-     Users must decide the size of the networks based on their data set and their usage of the results.
+     Users must decide the size of the network based on their data set and their usage of the results.
      There has been a few attempts to find a rule for restricting the number of neurons based on the input sample \citep[e.g.][]{Vesanto05}, but none of them are certain. 
-     We varied the size of SOMs from $1\times2$ to $50\times50$ in order to choose the most suitable size for the maps we generated, and found that based on the size of our sample, the best size for the 2D SOMs was 10$\times$10.
+     We varied the size of SOMs from $1\times2$ to $50\times50$ in order to choose the most suitable size for the maps we generated, and found that based on the size of our sample, the best size for the 2D SOMs was $10\times10$.
      We created our final SOMs with initial values for number of iterations in ordering phase, ordering phase learning factor, tuning phase learning factor, and tuning phase neighbourhood distance of 500, 0.9, 0.02, and 1, respectively.
-     %Also for each grid we created different SOM with different, learning factors, neighbourhood distances, and iteration numbers to find the optimize result for our sample.
-     %Based on our data we created our final SOMs with following initial values: number of iteration in ordering phase = 1000; ordering phase learning factor = 0.9; tuning phase learning factor= 0.02; and tuning phase neighbourhood distance to be 1.
-     %All the other parameters are default values in \textsc{ newsom} library and cannot be changed by the users.
 
-\subsection{Mock sample}
+\subsection{Mock Sample}
 \label{sec: mock_sample}
@@
                 \includegraphics[width=0.5\textwidth]{../images0.01/mock_sample.png}
-            \caption{SOM of the mock sample.
+            \caption[Self-organizing map of the mock sample]{SOM of the mock sample.
 The axes show the position of the neurons.
@@
 either 0 or 1 for low or high SFR, and 0 or 0.5 for a low or high amount of dust. 
- We generated an SOM from the sample with a size of $10 \times 10$, using the method described in Sec.~\ref{sec: som}.
- Fig. ~\ref{fig: sample} shows the SOM of the mock sample. 
- The axes show the position of the neurons in a $10 \times 10$ network and the hexagonal shapes are the neurons.
+ We generated an SOM from the sample with a size of $10 \times 10$, using the method described in Section~\ref{sec: som}.
+ Fig.~\ref{fig: sample} shows the SOM of the mock sample. 
+ The axes show the position of the neurons in a $10 \times 10$ network and the hexagonal shapes (depicted by purple hexagons) are the neurons.
 
-Using this method, as expected, we are able to divide the mock sample into 4 distinct groups, which their boundaries are shown by grey colours in Fig.~\ref{fig: sample}: regions with high SFR and high dust content, regions with low SFR and high dust content, regions with high SFR and low dust content, and regions with low SFR and dust content.
-The plot in the Fig.~\ref{fig: sample} clearly shows these divisions.
-In that plot, the upper part belongs to regions with low dust content, while the lower part belongs to regions with high dust content.
+Using this method, as expected, we are able to divide the mock sample into 4 distinct groups.
+Their boundaries are shown by grey colours in Fig.~\ref{fig: sample}: regions with high SFR and high dust content, regions with low SFR and high dust content, regions with high SFR and low dust content, and regions with low SFR and dust content.
+In Fig.~\ref{fig: sample}, the upper part belongs to regions with low dust content, while the lower part belongs to regions with high dust content.
 The left part of the plot is where regions with low SFR belong and the right side is for high SFR regions.
@@
 
-Having two regions with exactly the same values in all their quantities with real data is unprovable. 
-If in an input data, there are two entries with similar (but not identical) values in all dimensions, one can find a network that separate these two entries in two groups.  
-However, in case of multiple similar entries in data, the number of neurons must be much higher than the number of entries for complete separation.
-Therefore, the user learns about similarity/dissimilarity of members of input data based on the ratio of number of entries of input data and number of neurons.
+Having two regions with exactly the same values in all their quantities with real data is extremely unlikely. 
+If, in an input data set, there are two entries with similar (but not identical) values in all dimensions, one can find a network that separates these two entries in two groups.  
+However, in case of multiple similar entries in a dataset, the number of neurons must be much higher than the number of entries for complete separation.
+Therefore, the user learns about similarity or dissimilarity of members of the input dataset based on the ratio of the number of entries in the dataset and  the number of neurons.

### 2016-11-09 sections/data0.03.tex
V0.03; after thesis comments

--- 2016-07-26 sections/data0.02.tex
@@
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%DATA
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
 \section{Study Sample}
@@
 All data were divided by the area of their region (in arcsec$^2$), to remove the distance factor from the data and compare values across galaxies.
-Since the spatial resolution of the observations varies from as small as $<1$\arcsec to as high as 60\arcsec $\times$ 90 \arcsec, any attempt to match resolution would have caused a loss of information in some of the input quantities (e.g.
-the spectroscopic data).
+Since the spatial resolution of the observations varies from as small as $<1$\arcsec to as high as 60\arcsec $\times$ 90 \arcsec, any attempt to match resolution would have caused a loss of information in some of the input quantities (e.g.\ the spectroscopic data).
 In this project we used flux per unit area, which the convolution methods conserve~\citep{Aniano12}, as the input data.
@@
     \begin{subfigure}[b]{0.5\textwidth}
-        \centering
         \includegraphics[width=0.97\textwidth]{../images0.01/M31/M31.png}
@@
      Fluxes and equivalent widths of PAH and atomic line features were measured using the~\textsc{pahfit idl} tool~\citep{Smith07b}.
-     \cite{Dim15} also measured metallicity and radiation hardness index (RHI) for these 10 regions.
+     Metallicity for all regions except regions 5 and 8 was adopted from~\citep{Sanders12}; for regions 5 and 8, \cite{Dim15} estimated metallicity from the radial metallicity profile.
+     \cite{Dim15} also calculated the radiation hardness index (RHI) for these 10 regions using the relation from \cite{Engelbracht08}:
+     \begin{equation}
+        RHI = \left (\log \frac{[Ne~\textsc{iii}]}{[Ne~\textsc{ii}]} + \left [ 0.71 + 1.58\log\frac{[S~\textsc{iv}]}{[S~\textsc{iii}]} \right ] \right )/2.
+     \end{equation} 
      We used the measured PAH feature fluxes, metallicity and RHI of each region as the input for self-organizing maps.
 
-    For the photometry part of the sample, we used the \GALEX \citep{Martin05} far-ultraviolet and near-ultraviolet (FUV and NUV) channel images; \halpha~(6574.7\AA), \sii~(6730.72\AA) and \oiii~(5024.9\AA) narrow band images~\citep{Massey07}, IRAC 3.6, 4.5, 5.8 and 8.0~$\mu$m images~\citep{Barmby06}; MIPS~24 and 70~$\mu$m~images~\citep{Gordon06}; and PACS 100 and 160~$\mu$m and SPIRE 250, 350, and 500~$\mu$m~\citep{Fritz12} images.
+    For the photometry part of the sample, we used the \GALEX \citep{Martin05} far-ultraviolet and near-ultraviolet (FUV and NUV) channel images; \halpha (6574.7\AA), \sii~(6730.72\AA) and \oiii~(5024.9\AA) narrow band images~\citep{Massey07}, IRAC 3.6, 4.5, 5.8 and 8.0~$\mu$m images~\citep{Barmby06}; MIPS~24 and 70~$\mu$m~images~\citep{Gordon06}; and PACS 100 and 160~$\mu$m and SPIRE 250, 350, and 500~$\mu$m~\citep{Fritz12} images.
      The units of all fluxes were converted to W~m$^{-2}$ in order to be the same as the PAH fluxes.
@@
 
-     \cite{Gordon08} measured PAH fluxes and RHI for M101 in 8 star forming \hii~regions (Fig.~\ref{fig: regions in m101}).
+     \cite{Gordon08} measured PAH fluxes and RHI for M101 in eight star forming \hii~regions (Fig.~\ref{fig: regions in m101}).
      Metallicities of 6 of the 8 regions were measured by~\cite{Kennicutt03} and the other two by~\cite{Gordon08}.
@@
      Emission in the 3.6$\mu$m band traces the old stellar population very well~\citep[e.g.][]{Smith07a,Leitherer99} and it can be used to calculate the stellar mass~\citep{Eskew12}.
-     FUV, \halpha, and TIR emission are indicators of star forming regions.
+     FUV, \halphadot, and TIR emission are indicators of star forming regions.
      In this project, we used the SFR traced by the FUV emission, corrected for foreground stars using NUV emission and for dust extinction using 24~$\mu$m emission.
@@
 
-    We removed all the observed data that were used to calculate galaxy properties from the input sample, to guarantee that they have not been used in multiple forms.
+    We removed all the observed data that were used to calculate galaxy properties from the input sample, to guarantee that they were not used in multiple forms.
     To have prior knowledge of the M31 data set, 
@@
         \includegraphics[width=\textwidth]{../images0.01/cor_plots/M31_all_derived_ones_core_plot_for_paper.pdf}
-        \caption[Pearson correlation coefficients for data from 10 regions in M31]{Pearson correlation coefficients with a confidence level of 95 per cent for all data from M31.
+        \caption{Pearson correlation coefficients with a confidence level of 95 per cent for all data from M31.
 The colours and circle sizes show the Pearson correlation coefficients where large blue circles are 1, which means highly correlated, and large red circles are $-1$, which means highly anti-correlated quantities.

### 2016-11-09 sections/intro0.03.tex
V0.03; after thesis comments

--- 2016-07-26 sections/intro0.02.tex
@@
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%Intro
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
 \section{Introduction} 
@@
 The Andromeda galaxy (M31), at a distance of $\sim$~0.78~Mpc, is the closest spiral galaxy to the Milky Way~\citep{McConnachie05}.
+M31 has a similar age, stellar mass, and morphological type to the Milky Way. 
+Both galaxies are located in the ``green valley'' area in the colour versus stellar mass diagram of galaxies, which indicate they both lost most of their cold gas and hence have a low star formation rate.
+In general M31 is considered a typical galaxy that is in a transition state from a starburst galaxy to a quiescent one \citep{Mutch11}.
 Images of this galaxy provide us with a detailed view of the inside of a spiral galaxy as seen from an external perspective.
@@
 % data mining and clustering in general; when we have so many data and we want to map them
-\cite{Ball10} gave an extensive review of data mining and machine learning algorithms and their usage in astronomy.
+\cite{Ball10} gave an extensive review of machine learning/data mining algorithms and their usage in astronomy.
 A data mining algorithm learns about data from training, which can be supervised or unsupervised.
@@
 Unsupervised methods train without any prior knowledge of output results: 
-they work solely based on the underlying structure of the input data.   
+they work solely based on the underlying relation of the input data.   
 The unsupervised methods are very useful tools in knowledge discovery studies, where we have limited pre-expectations for the data or when we want to make sure that we did not miss any valuable information in previous studies.
@@
 We create 2D SOMs from subsets of the data as well as all available data, which helps us to understand the effect on each input on the position of the clusters in the SOM.
-We apply the 2D trained networks to the M101 data to study whether they have similar properties to M31 ones.
+We apply the 2D trained networks to the M101 data to study whether they have similar properties to M31.
 If our hypothesis is correct, we should be able to see that regions in M31 and M101 with the same positions in the SOM have the same properties.
